\chapter{Humanity Under Union, 5016}

\section{Timeline of Union's History}

Timeline of Union’s History  

-5000U: Anthropocene Epoch ends with the ecological and data collapse of Old Humanity. 
 

Intervening Period: The dark ages. Cradle’s population falls to estimated 300,000 persons from  
peak of around 15 billion. 
 

-150U: The first Vault, Massif-A, is discovered on Cradle (nee Earth), prompting worldwide  
civilizational growth and change.
 

-53U: The Little Wars begin.  
 
 
 
0U: Union founded after the conclusion of the Little Wars. The First Committee Established. 
 

1968U: Logged SOS transmissions received after Union reactivates long-range communications  
systems. Union Space Program announced shortly thereafter.
 

1970U: Union Space Program lands and reactivates lunar installations. Shipyard THESEUS  
reactivated. First  NEARLIGHT-CLASS ships built and launched. Following legacy star charts,  
Union establishes a colony on an ID’d Gaia world. Encounters the Aun shortly thereafter. Contact  
lost with Union colony.  
 
 
 
2000U: Mars-based ORACLE CHORUS installation discovered following GRADUATION DAY  
landings on the Vastitas Borealis. The Five Voices reactivated, contained, and managed by early  
elements of what would become Forecast/GALSIM.
 

2000U-2998U: First Expansion period. Multiple Old Human colonies discovered. Some derelict,  
others inhabited. Union Administrative Department created to manage expansion effort and  
reintegration programs for rediscovered exclaves.  
 

2880U: Second contact with the Aun Ecumene. Diplomatic failure turns to first interstellar  
conflict: now called the First Distal War. Union retreats, and hardline elements in the Union Space  
Program ignore no-fly cordon, launch a flight of “dumb” kinetic TBK weapons towards presumed  
location of the Ecumenical homeworld. Bitter political struggles grip Cradle, give rise to the  
Second Committee.  
 

2998U: RA manifested from Five Voices forecast iterative.     
 

3000U: The Deimos Event, RA’s ascension. Paracausality Studies born. Disparate ships, shuttles,  
and force organizations of the Union Space Program organized into the Union Navy.  
 

                                                                                                                  


3002U: First Contact Accords signed with RA. Non-Human Person identified as category.  
Shackling developed. 
 

3130U: Blinkspace identified and pierced. Blink fields created, first gates created, first blink  
station opens and stabilizes. Second Expansion Period begins. Union Administrative Bureau  
dissolved, replaced with Union Colonial Mission.  
 

4500U-4600U: Hercynian Crisis. Efficacy of hard suits and mechanized chassis shown: first  
galaxy-wide production and adoption of mechanized chassis (“mechs”) begins via Union state  
armorer, General Massive Systems. Second Committee deposed in a popular coup following  
revelations surrounding the Hercynian Crisis. Union Colonial Mission dissolved, replaced with  
reconstituted Union Administrative Bureau.  
 

5000U: Reports of Aunic crusade fleet operating in the Boundary Garden sector of expansion  
space confirmed. First reported loss of a Union blink gate due to hostile state actions. Second  
Distal War begins. 
 

5014U: Attack on Green Zone Alhambra , beginning of Operation Clarion in the Dawnline Shore
 

5016U: Narrative present of Lancer. 
 

\section{Foundation Day}

Foundation Day  

         “Work stops at sunset. Darkness falls over the building site. The sky is filled with stars.   

         ‘There is is the blueprint,’ they say.”  

                      -    Italo Calvino, Invisible Cities  

Union began as a way to build a new world from the ashes and ice. 
 

In the 3500’s CE, -5500U by Union’s dating system, Earth sent the first wave of her children out  
to seed the stars. The world, Humanity’s only home save for distant, fledgling colonies, was  
dying. An accumulation of fatal blows, a thousand cuts on the world by the people that called it  
home, had rendered it all but inhospitable. 
 

The Fall, as it is now called, was not concluded in a single, cataclysmic blow. There was time --  
not enough of it, but time enough -- for acts of desperate hope. 
 

The Ten were one such act. 
 

In the twilight of the Fall, Ten massive colony ships launched from orbital shipyards that ringed  
Earth. They were slow ships, their titanic hulls pushed along by conventional sublight drives, but  
they marked the crowning achievement of a species: a second chance.
 

These generation ships were humanity’s last hope. They would travel for thousands of realtime  
years, accelerating nearly to lightspeed before flipping over and slowing down as they  
approached their destinations. Generations of passengers would live, die, and procreate,  
sustaining the ship and the remnants of humanity on board until they arrived at their destination:  
a world able to sustain human life.
 

This was humanity’s second chance, a handful of stones cast out into the night. Back on Earth,  
the billions left behind watched the Ten burn away into the night, tracking their progress through  
choking clouds of smog, dust, and smoke from raging, unstoppable wildfires. 
 

Humanity on Earth fought for what was left, erupting into a pandemonium, a violent crescendo.  
Climate change choked the atmosphere, disease scoured the cities, and war ravaged the rest.  
Lonely colony outposts and stations throughout the solar system — established when Earth was  
terminal and not yet dying — watched their homeworld go dark. Most withered on the vines, a  
rare few managed to hang on. 
 

Thousands of years of real time passed. For the ten ships, relative time passed slower. 
 

Earth spun, silent and unresponsive to the desperate calls for help from her dying colonies. Cities  
sank under rising water, wildfire and stinking fog swept the equator. The poles thawed, while  

                                                                                                                  


storms thrashed the tropics. Ash fell over the whole of the world. Satellites and stations decayed  
in their orbits. Shipyards fell quiet. Great habitats on the moon and Mars cascaded into failure.  
 

Thousands more of years of silence followed. The First Anthropocene, the age of Humanity,  
faded, buried under ash and water. 
 

Yet Earth was not empty, nor lost: billions had died, but humanity is a resilient race. Some  
hundreds of thousands had survived. Persevering through the new long dark. 
 

This was the Fall. The end of it, and the beginning of a new Dark Age. 
 

In time, the global population began to stabilize, then grow as the world’s climate evened out.  
Long-dead crops began to grow as hearty survivors. Trees, forgotten at the Fall, grew back from  
gnarled shrubs. The oceans receded, cooled. The fires dimmed, then died. The sky, once a  
greasy smear of black and orange, lightened, blued.   
 

Humanity, too, began to grow back. First, small rulers and tyrants laid claim to the ruins of the  
past, organizing themselves around altars of scavenge and scrap. Wandering machines were  
tamed or followed, venerated and hunted. Farms grew from small plots. Once again, lines and  
borders were drawn, land claimed, loyalty pledged. Scraps of cloth and paint and feathers and  
flags grew to mean, to divide. The rulers gave way to nations. Nations, to empires. 
 

And then, the first of three great traumas humbled the healing world: Old vaults, stores of  
information from the pre-collapse era, were discovered and reopened. The survivors, so far  
removed from Old Humanity, had grown through the dark ages thinking that their cultures were  
the first on Earth, the first people to walk under the Sun. 
 

They discovered otherwise. They were not the first: they were the last. 
 

Reeling from this discovery and the wealth of pre-collapse humanity unleashed upon a healing  
world, the fledgling states of Earth backed into their corners. Ultimately, a reckoning followed the  
revelation, and a new war began: a global war. This was the second trauma: a global war, a bitter  
fight over the scraps of the long-dead. 
 

War scarred the world, and when it was done the survivors gathered together and pledged  
peace. The tools of war and capital were thrown aside, as they had nearly killed Earth again.  
Humanity pledged peace, and came together under a single banner, which would be the last to  
fly over Earth: 
 

Union. 
 

Union’s foundation reset the clock, changing the calendar and myriad dating systems to one  
single metric. Year 0 marked the beginning of a new age of humanity, a people redeemed,  
bruised stewards of an old and aching world. In peace, and with the help of the wondrous  
technology of their predecessors, the people of Union began to dream of greater things.
 

                                                                                                           


Flight and clean power spread across the world. Linked, networked communications further  
bound Union together. Sudden, exponential advancement in medications, computational power,  
hard and soft sciences — all gifts from the data stored in seed vaults around the world. 
 

We discovered and translated the story of the collapse, of the desperate rush of old humanity to  
preserve what it could so that future generations could begin anew, with all the plenty and  
knowledge of those who came before. We found technologies that could have saved the world,  
but were discovered too late, or kept from Humanity by their inventors and owners. 
 

Union began to look beyond: out, towards the depths of space. The first rockets were launched,  
and on Luna we found dusty colonies, empty but for mummified remains of the people who once  
lived there. We found dormant satellites strung in orbit, ancient shipyards hanging in space. We  
found charts, logs, flight plans, trajectories showing that some of us, some of our ancestors, had  
escaped. 
 

We found and thawed the old telescopes, radio towers, and laser communication suites,  
preserved in ice on mountaintops and high places all over the world. We pointed them to the  
stars, turned them on, and waited.  
 

The first messages arrived almost immediately. This was Union’s third great trauma. 
 

Ancient calls from distant, lonely outposts and hardscrabble colonies. Voices, thousands of years  
old and long dead, on radio waves garbled by radiation, time, and transit, crying out to their  
home for help. Lost souls that begged for aid, for guidance, for their loved ones. Thousands of  
years of messages, recorded and playing on endless, decaying loops for the survivors to hear. 
 

This was the voice of humanity from the stars: a desperate cry for help, a lonely gasp as the air  
ran out. A plea, unanswered, as the light grew dim.  
 

Union now had a new purpose: to answer those calls, and to ensure the event that caused them  
would never happen again.
 

The old orbitals were retaken and reactivated. Machine minds greater than humanity’s — the first  
artificial intelligences — were discovered and set to puzzle out solutions we could not. The first  
new ships were launched towards those old signals, along ancient charted paths, and out  
towards new worlds. 
 

Union could not bring their dead back home, but they would choke the stars with the living.
                                           
\section{Cygnus Spur, Orion Arm: Humanity Across the Stars}

Cygnus Spur, Orion Arm: Humanity  
Across the Stars  
\section{Cosmopolitans and Diasporans}
Cosmopolitans and Diasporans  

In the narrative present of Lancer, humanity is vast and polyglot. We live in a golden age  
for most: the human race is spread out across habitable and uninhabitable worlds, enjoys the  
fruits of robust scientific, political, and cultural advancements, and has access to such a gross  
amount of resources that society on Core worlds is, essentially, post-scarcity. 
 

Life on a given developed Core world, is stable, safe, and without want. People who make their  
homes on terrestrial worlds, large orbital stations, and habitable moons are Diasporan humans --   
their homes are in a specific location on a specific world or station, and their lives are concerned  
with events that occur around, in, or to that location.  
 

However, outside of the developed Core worlds there is still a raw, dangerous edge to human life.  
The frontier waits both away from the bright core of the galaxy, and towards it. Colonies need to  
be built, settlements developed, and old ghosts put to sleep.
 

The humans who embark on missions or pilgrimages to these frontiers are called Cosmopolitans.  
Their homes are, typically, their ships or the world they left behind. 
 

Interstellar travel comes at a cost: time. Life for a Cosmopolitan human is split into subjective  
and real time, or, time as a Cosmopolitan experiences it, and time as the rest of the galaxy  
experiences it. 
 

Cosmopolitans leave their old lives behind as the effects of relativistic interstellar travel splits  
them from the “real” time of the rest of the galaxy. They trade the permanence and normality of a  
terrestrial life for the vast life, the uprooted life, a life lived in the wind. 
 

On Core worlds, humanity expresses itself in many faiths, cultural practices, genders, and social  
structures. We create art, shape the land, build glittering cities, construct great works of  
engineering. We write, we cook, we drink, we play sports, we journey, we wander. We populate  
our arm of the galaxy as a roiling people, often contradictory, often myopic, but ever-learning,  
ever-growing.  
 

Humanity is no less fragile and no more disposable now that we have crossed the stars and  
number in the trillions: the great purpose of human life on the galactic scale is to defend the  

                                                                                                              


collective while defining the individual. To journey beyond, to discover ourselves, to not simply  
exist but to become. 
 

It is a good thing, some of Union’s philosophers think, that we are alone in this great venture. 
 

The galaxy that humanity has stepped again into is, seemingly, empty. There are few truths held  
by the majority of humanity -- our numbers are simply too vast -- but the ones that are universal  
are fundamental, seen as core tenets of what it means to be human: 
 

First, to be a human being in Union is to be afforded the decency of a life lived with your basic  
needs seen to: your state will make available to you food, water, shelter, and labor, and will never  
deny you those rights. To do so is to violate the most basic of social contracts. 
 

Second, no walls shall stand between worlds. The void of interstellar space is deep and cold,  
utterly hostile to life. Any civilian world, station, or moon not deemed to be of significant private  
or restricted interest must allow all who petition for access to feel firm ground beneath their feet,  
breathe clean air, and feel again the light of a life-giving sun. 
 

Finally, no human shall be held in bondage through force, labor, or debt. Scarcity of natural  
resources on a Core world is a false premise, a myth, a tool used by the few to oppress the many  
while enriching themselves; this the same for colony worlds. The dignity of human life is  
paramount among the Diaspora, and to use hard or soft power to exploit a person, their labor,  
and deny them just compensation is abhorrent.  
 

All that being said, humanity exists on a spectrum of development. While the majority of the  
developed galaxy might hold these to be self-evident truths, guaranteeing them is never a  
“finished” project — “most” of the developed galaxy only represents a plurality, not a majority, of  
the populated galaxy. 
 

Remember: power never gives up power. Power is only ever taken from the powerful and  
redistributed to the people, where it must constantly be cultivated, regulated, and maintained —  
this is the dream some worlds have realized, and the project that Union, humanity’s core  
organization, works to accomplish. 
 

Union is many things, but above anything else it is an incomplete project, human to its core.  
Despite every wonder of technology, every miracle at their disposal, Union still needs people to  
make the right decisions, to be brave, and to make it work. 
 
\section{Why we Fight}
Why We Fight  

Notice the hedging -- “usually”, “most”, “the majority”, “by and large” -- this is to mark the gaps  
in the golden age, the places where the galaxy does not conform to Union’s standards of  
development.
 

                                                                                                           


War still plagues humanity. No system so large and so varied will be completely harmonious, but  
Union and its proxies are working to make it so. Note again that “harmonious” in this context  
means that which is agreeable to Union -- it is absolutely possible that your PCs will reject  
Union’s hegemony.  
 

Areas of major conflict, interest, importance, or intrigue in Lancer are called flashpoints. Some  
are detailed in this core rulebook under the section A Golden Age, of A Kind . 
 

In Lancer, humans fight over two things: territory rights and ideology. 
 

Resource-rich and strategically placed terrestrial worlds and moons -- habitable or not -- are  
common regional flashpoints. The rise of destabilizing actors like Corpro-States has led to a run  
on planets rich with rare elements necessary to fabricate the fantastic technologies the galaxy  
has come to view as normal. This produces conflict between corpro-states. Some hire  
mercenaries to accompany their claims teams, others raise and field their own standing armies. 
 

Ideology tends to be the seed of conflict that drives states to fight states, or for states to fracture  
and fight civil wars. These conflicts are protracted and bloody, as neither side is likely to  
surrender unless they give in to attrition. 
 

States and Corpro-States engage one another over territory and labor. Most of these conflicts  
occur in small engagements over important persons, locations, and facilities as small teams of  
highly trained agents fight expensive corpo-state mercenaries in clandestine firefights.  
Occasionally, a Copro-State’s acquisition of a world will turn hostile, and conflict will rage across  
and above it as the state attempts to secure its holdings. 
 
