\section{Union Galactic Organization}
Union Galactic Organization

The galaxy is vast, and humanity contains multitudes. Organizing the galaxy into something
resembling a state is a full-time task that requires a broad, complex bureaucracy: the Union
Administrative Department (UAD).


The UAD has classified humanity into two major categories: Diasporans, or humans who live in
“real” time on terrestrial worlds, moons, and/or space stations; and Cosmopolitans, humans who
spend the majority of their lives in the “subjective” time accrued by interstellar travel.





Larger stations in stable locations or in orbit around uninhabitable worlds generally operate
independently of any terrestrial government, acting as their own states with their own territory of
influence. Generally speaking, stations exist because they were built for a purpose: mining, gas
extraction, a dry dock platform, shipyards, civilian scientific research, and so on. The populations
that live onboard them largely work to support the mission of the station and/or the people who
do that work. Civilian stations usually have permanent populations, the largest of them
numbering in the tens of thousands.


Blink gates are special cases — while they exist outside of the state boundaries of Cradle, they
are integral to Union’s control over the populated galaxy. As such, a blink gate is managed by a
Union Governor, policed by Union security forces, and administered by Union bureaucrats and
personnel. Blink stations serve as gates, points that hold open stable holes into blinkspace.


Military stations are smaller and do not have permanent populations born and raised onboard.
Union claims jurisdiction over all stations, though only maintains a Union-flagged presence on
strategically important stations.


For simple top-down galactic orientation, Union has adopted a concentric ring system of territory
classification centered on the Cradle system. Each ring bears the name of a mountain range
found on Cradle, increasing in length the closer you get to the Cradle system. Blink stations are
named after peaks in the mountain range their ring is named for.


The ring-naming convention is a shorthand system, used in simple civilian and governmental
maps. Think how neighborhoods are named -- there are generally accurate markers, but people
will refer to exact addresses when looking for specific locations.

Rings are concentric: the farther out you get from Cradle, the larger the rings are.

And remember, naming stations after peaks is simply a convention -- there are not yet stations
built for every peak in a given range. If it winds up that there are not enough peak names, Union
will simply make up new ones.


Cradle: ANDES  Line -- Aconcagua Station, Cerro Bonete Station, Galan Station, etc


Ring 1: ROCKY MOUNTAIN Line -- Elbert Station, Lincoln Station, Castle Station, etc


Ring 2: KUNLUN Line -- Kongur Tagh Station, Karakoram Station, Mayakovsky Station, etc


Ring 3: URAL Line -- Manaraga Station, Elbrus Station, Iremel Station, etc


Ring 4: ATLAS  Line -- Toubkal Station, Ouanoukrim Station, M’Goun Station, etc


Ring 5: HIMALAYA Line -- Everest Station, Kanchenjunga Station, Annapurna Station, etc


Ring 6: ALTAI  Line -- Belukha Station, Nairamdal Station, Kharkhiraa Station, etc





Ring 7: CARPATHIAN Line -- Gerlachovsky Station, L’adovy Station, Moldoveanu Station, etc


Ring 8: SIERRA MADRE Line -- Mohinora Station, Peak Station, Bridger Station, etc


Ring 9: VINDHYA Line -- Kalumar Station, Dhupgarh Station, Mahendragiri Station, etc


Ring 10: CASCADE Line -- Rainier Station, Adams Station, Hood Station, etc


Ring 11: ANNAMITE  Line -- Phou Bia Station, Phu Xai Lai Leng Station, Ngoc Linh Station, etc.


The Annamite Line is the current “edge” of Union space. Beyond that line is uncharted territory.

\subsection{Non Human Life}
Non-Human Life
Non-human life is common in Lancer; non-human sentient life (i.e. alien civilization) is unique in
how rare it is.


Contents of the module No Room For A Wallflower dives into this topic more, but generally
speaking, outside of one world there is no non-human alien civilization.


Forecast/GALSIM commonly simulates hostile alien life, though it is widely assumed that such
simulations are low confidence at best.

\subsection{Shelter}
Shelter

Lodging and shelter is important -- in Lancer, specific types of lodging are numberless, as myriad
as the inhabited worlds in the galaxy demand. Here, though, are some possible examples of
shelter:


Temporary Camp - Temporary camps are common in the field. Any settlement, lodging, etc, that
is organized for single night or a few nights is a temporary camp. Usually a collection of pitched
tents and a sketched-out perimeter organized around a fire or heating element. A place to rest
your head for the night while on the march or on the run.


Base of Operations - A more permanent encampment, but not necessarily a permanent
settlement, a base of operations is a longer term encampment typically employed by military or
scientific teams who need a home in the field that can provide necessary shelter and supplies to
complete a long-term mission. Bases like this tend to be supplied at regular intervals by states or
private entities, run by crews working to effect a specific goal. You won’t find many tents at
bases: most structures are sealed buildings, prefabricated and alien to the environment. Bases
tend to have a defined perimeter, a working crew (skeleton or heavily populated), and be located
in remote or hostile environments -- in order to stay at one, you need to be posted, be a prisoner,




or have clearance. Science, mining, signal, and military stations and orbitals fall under this
category of lodging.


Landfall Settlement - Landfall settlements are the first incursions a colony group makes onto a
claimed world. A typical landfall settlement is more of a base or project than a colonial town or
city: like a base of operations, the population of a landfall settlement is task-oriented, small in
number (6-10 engineers), and doesn’t expect visitors. A clonal Companion/Concierge unit
manages the settlement and acts as a personal assistant to the live crew there. There is usually
an environmentally sealed main base -- a low-lying collection of self-contained habitation and
science pods -- and a growing, unoccupied collection of buildings constructed on a planned
layout for a future colonial settlement. The organic population is small, but the Comp/Con unit
controls a large group of subalterns and heavy drones, tasked with gathering raw material for
construction, sowing agrarian land, and doing the bulk of the manual labor. They might have a
spare bunk, but the population at a landfall settlement typically does not expect visitors.


Colonial Settlement - A colonial settlement can range from the first generation to populate a
wave 1 landfall settlement, to a thriving city on the eve of signing its articles of independence
from its Comp/Con administrator. A colonial settlement has beds available, most are utilitarian
and made from native materials, though there might be one or two notable luxury lodgings
available.



Sleeping Tube - Sleeping tubes are common on stations, in commuter interstellar ships, and in
highly developed metropolises. Cheap and functional, sleeping tubes are coffin-sized, warmly lit
and padded micro-rooms meant to provide a place to sleep for a night or a layover. They really
only fit one person; that person’s gear or baggage is stowed in a locker in the lobby of the
establishment that maintains the sleeping tubes.


Rented Room - Room rentals are available anywhere there is a need in a developed city or
station. Rooms can range from a space just larger than a sleeping tube, to opulent suites in
hotel-stations, suspended above pearl worlds.



Apartment  - Apartments are domiciles ranging from small studio apartments to floor-spanning
penthouses. Available to rent or to own on stations and inhabited worlds, apartments are built
into buildings, one unit among many.


Freestanding House - Houses can be found on any world, and are freestanding buildings that are
occupied (typically) by a single family.


Omni Address - In a galaxy connected by a massive internet, an omni address is a viable mental
living space. These spaces are virtual, unique to their owner, and networked. Privacy separators
are a common practice, to the point where keeping your omni address public would likely be
viewed as an odd thing among most people with an address. Omni addresses are unique,
galaxy-and-temporal identification signatures and virtual spaces both; these are commonly
employed by Core world Diasporans and Cosmopolitans, far less so for colonial Diasporans.




\subsection{Gravity}
Gravity

There is no stable artificial gravity in Lancer. Gravity on stations is spin gravity. Gravity on ships is
tied to directional acceleration, magnetized grip pads, or spin gravity.


Artificial gravity can be generated, but in the narrative present it is unstable and is the result of
massive energy expenditure. Unstable artificial gravity can be created in safe containment as a
momentary impulse; as a result, it has been weaponized, and studies into stabilization are
ongoing.


Nonlethal artificial impulse gravity is a necessary component to make nearlight ejections and
bolts survivable for organic life.

\subsection{How to get There}
How To Get There

Not everyone has a ship, knows how to fly, or has the right licenses to get around. Player
characters, typically pilots and their mechs, will need to travel in order to get to where they need
to be.


Generally speaking, if the pilots in your narrative operate under the orders of a state or state-like
entity, they’ll have some kind of transportation afforded to them. Usually this is a temporary
convenience: a transport/tender ship that drops their party off where they need to be, a billet
aboard a passing capital ship, and so on.


So, what are common (and uncommon!) ways of getting around?


Best to arrange modes of transport into the theaters they operate in: global, space, and
interstellar.


Global travel is any travel that takes place on a single world, which includes terrestrial, aquatic,
and atmospheric travel. Terrestrial travel can take the form of trains, caravans, convoys,
landships, long marches, cars, and so on. Aquatic travel can take place above or below the
water, on ships and submarines. Atmospheric travel takes the form of airplanes, airships, low-
orbit vehicles, and the liminal zone of transit on space elevators, sky hooks, etc.


Space travel is common in Lancer, encompassing the zone between a world’s high atmosphere
out to the nearest blink gate. Ships of all size and classification transit in this zone, running
shuttle routes between worlds, making supply runs out to local colonies and settlements, and
engaging in general transit and business.


Some spaceships are rated to operate in a world’s gravity well, and can transit between
atmospheric flight and travel in hard vacuum. These tend to have a low gross weight --  fighters,
bombers, and some smaller corvettes fit into this category of atmosphere-rated ships. Capital
ships are not able to fly for extended periods of time, though should one find itself in
atmosphere, it could burn hard for lateral movement as it plummets to a catastrophic end.





Interstellar travel is common for certain classes of people in Lancer: military personnel,
diplomats, explorers, merchants, Union personnel, colonists, migrants, scientists, and so on.
Many people have many reasons to engage in interstellar travel, but the equipment necessary is
difficult to obtain. Generally speaking, unless you’re military on deployment, an official on Union
business, in the employ of a company, university, or benefactor, or fantastically wealthy, you’ll
need to take a public blinkship. Public blinkships transit between blink stations, which are the
massive, cosmopolitan melting pots of the galaxy, where people mingle, do business, and pass
the time until their scheduled blink ship arrives and they can board.


As a shorthand, the modes of stellar travel can be described as follows:


Blink Travel


Nothing seems out of the ordinary or that much different from normal stellar travel. Your ship is
underway at a comfortable G, you can walk around in plain clothes (if your ship is large enough
and pressurized), eat food, drink, sleep, exercise, etc. Blinkspace is perceived as a blindness, if
you look out through a porthole. Through a screen, blinkspace looks black.


Actual blinkspace travel takes only a moment, and if you were to not look outside of the ship as it
is underway, you would notice nothing out of the ordinary, simply a black void.


Prolonged exposure can lead to complications. NHPs exposed to blinkspace report existential
complications.


Nearlight Bolt

A nearlight bolt (or nearlight ejection, in a combat or emergency scenario) is a sudden, often
traumatic acceleration to .8 or .99 lightspeed. When prepared for the bolt, you are usually
strapped into a pressurized crash couch, medicated for it, secure. If not, there is a very real (to
certain) chance of being pulverized by the sudden movement of the ship.


A nearlight ejection is not a common method of travel: it is an emergency acceleration that
serves to extract/ disengage a ship from a situation that would otherwise be deadly. A nearlight
bolt is an uncomfortable, but often necessary form of travel common among military,
government, and emergency entities.


A nearlight ejection/bolt is dangerous when you’re prepared for it (but normal enough that it is a
combat tactic) and deadly when you are not. Ships equipped for nearlight jumps are equipped
with crash couches that fire corresponding opposing bursts of contained artificial gravity in order
to counteract the G forces that would otherwise pulverize its crew.


Normal Spaceflight




You can walk, talk, eat, and drink, in addition to any other activity you could do on a .1 to 1G
world. This speed is achieved over slow, comfortable acceleration.


Gravity might get a little uncomfortable at peak speed (if that speed is higher than your
native gravity), and always pulls in the opposite direction of travel: “Behind” is always
“down.”

\subsection{Time and its Passage}
Time, And Its Passage

Time, in Lancer, is a rare thing: a commodity that can be exhausted. Whether you’re on a core
world or out in the farthest reach of distal space, time is the one resource that is truly scarce in
that, when your time runs out, you can never find more of it.

That said, there are some methods for extending one’s presence in real time, and the most
common among them is conventional interstellar travel. To venture between worlds without the
blink, one must board a ship that uses some conventional means  -- i.e., non-paracausal system
of movement, like a solar sail, ion drive, rockets, and so on -- to propel itself across space,
generally at a steady pace, to reach its destination. This conventional travel, unlike traversing the
blink with the aid of a blink gate, may best be measured in how much time it will take to reach
their destination, as distance is (to a layperson Cosmopolitan or Diasporan) a more abstract
measurement:

2 Cradle Distance Units (CDU) is so large a number as to be meaningless. The same journey
written as time rather than distance is 10 standard years realtime/ 6 months subjective, a much
more apparent cost.

This stretching of time as a result of travel at great speed is called time dilation. It occurs --
generally speaking -- either because of the difference in velocity between two observers, or
because of a significant difference in their location to a significant gravitational field (like,
say, proximity to a black hole).

For interstellar space travel, velocity causes time dilation. Time, to the person on the ship,
would seem to progress as normal, but to an observer back on the world, the ship carrying
their loved one would appear to slow, to slow, to slow until it stopped. Time on the world, to
the worldbound observer, would of course remain normal.

So what happens to the person on the ship? And what happens to the person on the world?
Both would, from their points of view, experience time as normal. But the fact of the matter
is that time is not equal for the both of them. As the person on the ship accelerates, their
relative velocity to their home world increases; they closer they get to the speed of light,
time back home for them slows, slows, slows, until it all but stops.

But to the people back home, the subjective experience of time progresses as normal. The
family of the interstellar traveller, their friends, their lovers and rivals, could look skyward




and see, distant though it may be, the ship their loved one travels upon. They could walk
out into a field with a telescope, or to an uplift station’s memorial observation decks, and
view their loved one’s ship, frozen, all but preserved in time.

But this frozen state is only due to perception. On the ship, as on the world it left, time
continues as normal. As they rocket ahead, closer and closer to the speed of light, the
difference in time grows, stretches, dilates. It is possible, depending on speed, that for
every year a ship’s passenger experienced, ten would pass back at their home.

States could fail. Disasters could wipe out lands. Wars, famine, disease. And the opposite:
fortunes could change, families grow, businesses prosper. And through it all, frozen in time
to the worldbound observer, the interstellar ship would hang in the sky, a distant light.

If that traveller ever returned home, they would find themselves in their future, having “time
travelled” ahead as a cost of venturing between stars. A journey from their homeworld to a
system-local blink gate, then from the destination blink gate to their target world, and back,
could cost a traveller three years subjective time -- time as they experience it -- and thirty
years real time -- time as people back home experience it.

When your players or NPCs embark on an interstellar journey, they will need to take into account
the amount of time that it will cost them -- to venture between the stars comes at great cost to an
individual; by exposing themselves to time dilation, they will necessarily catapult themselves some
number of years into the future -- a future they may not want to live in without the familiar comforts
of friends, family, and the states, culture, and environment they’re familiar with.

For that matter, matters of politics, economics, or great importance that cast your players between
stellar systems will, necessarily, encounter the complication of time dilation. That urgent distress
call from a neighboring system? The fastest you can respond to it is ten years real, six months
subjective. That promise to fetch a valued item or VIP, and return? Twenty real, two subjective.
And so on.

The blink shortens this steep cost, but the cost is still present: most interstellar travel accrues time
in the transit from a port of origin to a local blink gate, then from the exit blink gate to the intended
destination; without the blink and the gates to pass between, humanity would have to return to
conventional causality, and travel across the vast distances of interstellar space. Instead of
sacrificing ten, twenty, or thirty years real time on a journey, it would be in the range of one, two,
or three thousand, and without any kind of stasis to preserve them, the ship’s crews would die of
old age aboard their ship.

Mechanically, what does the reality of interstellar space travel mean for your players? Either a
narrative defining mechanic, or nothing important, depending on their backstories, characters’
attachments, and the overarching narrative. If your players travel in a mercenary company, camp
followers in tow, then it is of no great concern that time passes differently for them -- their friends
and families travel with them. However, if your players travel alone, their families left behind, then
after even one trip there is a chance that their homes will be vastly different when they return than
when they left.




We recommend a mix of hard cost and narrative liberty. While time dilation certainly is a factor
even in systemic travel (travel between worlds and stellar bodies of the same solar system), it
likely won’t be a tool of massive dramatic import. We recommend slipping a few days here and
there, no more than a month at most of difference between when they left and when they
returned.

For larger distances -- say, moving between solar systems connected via blink gates, then the
cost of interstellar travel would come into play. We recommend a simple formula, more narrative
than hard math: for a distant frontier system, travel to and from blink gate would take at least a
     3
year  subjective, five real. For a developed, heavily populated Core system, travel to a blink gate
would take three months subjective, nine months real. Crossing blinkspace is, essentially,
instantaneous.

You may, if you want, choose to adopt a far more hard science fiction approach to interstellar
travel; if so, we recommend utilizing online tools to keep fidelity to your constraints.




\subsection{Common societies}
Common Societies

The inhabited galaxy in Lancer is complex and, seemingly, contradictory: it is both a polyglot mix
of many different cultures, states, religions, and economies, and a single entity managed by a
centralized power with near-total control over galactic travel, communication, and economy.


The galaxy as administered by Union is a single entity: Union is the hegemonic power, and all
human societies are constituents of Union. Without those states, there is no Union; without
Union, there is no unified human race. States adjacent to Union’s home system, Cradle, proudly
fly both Union’s flag and their own, but few other states display such dual loyalties.


Most states in the populated galaxy (“states” in this context refers to any organized social
structure, from colonial settlement to interstellar nation) assent to Union’s control in order to
effectively manage their territory. Without the blink network, manna, or omninet, the vast
distances of space would make communication, travel, trade, migration, etc, essentially
impossible. Humanity would be isolated without Union.


That being said, Union is by and large a background entity at best for the vast majority of people
in the galaxy. While heads of state, church, tribe, commune, etc, might meet with Union
representatives (usually an Administrator and their subaltern), your average Diasporan human will
never see a Union flag in person.


3 To keep sane, we recommend using measurements of time equal to or simple orders of magnitude more
or less than standard Earth measurements. I.e one year in Lancer’s narrative present is the same as one
year on Earth at the time of publication.




Player characters and non-player characters (NPCs) who call a common society home are
members of the Diaspora or the Cosmopolita. They are the galactic “normal”, though individual
expressions of normal may vary


Examples of a common society in Lancer are listed below.

 Democratic Republic                                   A consensus government, usually
                                                       constitutional, of representatives elected by
                                                       their constituents.

 Ruling Council - Labor                                A council of labor leaders, typically union
                                                       bosses, that plan for the greater good.

 Ruling Council - Meritorious                          A council of elected representatives, the
                                                       “best of the best”, that plan for the greater
                                                       good.

 Ruling Council - Dynastic                             A council of nobles who inherit their position
                                                       by birth, marriage, or death, that plan for the
                                                       perpetuation of their dynasty and state.

 Technocracy - Liberal                                 A centrally administered state that weighs,
                                                       assigns value to, and tracks metrics of its
                                                       constituents.

 Technocracy - Machine Rule                            A state run by an NHP, cycled regularly, to
                                                       enforce an impartial government that
                                                       prioritizes efficiency.

 Socialist Collective                                  A true socialist state, run by a central
                                                       committee. Its relationship to manna may be
                                                       unknown by its general population.

 Corpro-State                                          A new form of government, but one growing
                                                       in popularity thanks to the aggressive political
                                                       maneuverings of Union Economic Bureau
                                                       agents. A private entity organized with a
                                                       single goal: maximize profit.

 Commune - Small Band Coalition                        Smaller population of environmentally-
                                                       conscious bands, typically organized around
                                                       small commune-villages.

 Commune - Single State                                A global government of stewards, run in
                                                       accordance and harmony with the ecology of
                                                       the world on which they live.

 Commune - Filial Constellation                        As the previous two entries, but with strong
                                                       family ties between the communes.

 Caste-Ordered State - Gene Stock                      A state ordered along genetic markers -- SSC
                                                       is an example of a blended COS/GS and CS.




 Caste-Ordered State - Labor Structured                Caste-ordered labor states are divided along
                                                       lines of work: you are born into your caste
                                                       and can only associate with others in your
                                                       caste (note: this also includes military caste
                                                       states)

 Tyrant State - Patronizing                            A single, tyrannical ruler, who casts
                                                       themselves as a benevolent leader while
                                                       holding total power over the government and
                                                       its people. Can be hereditary or dynastic.

 Tyrant State - Fascist Central Power                  A centrally controlled state, often run by a
                                                       demagogue, with strong nationalist rhetoric
                                                       and and emphasis on the supremacy of its
                                                       people over others.

 Monarchy - Divine Right                               A classical kingdom, with a hereditary ruler
                                                       deemed to be a representative of god made
                                                       flesh. Tends to have a wide nobility.

 Monarchy - Constitutional                             A kingdom ruled by a monarch, but
                                                       administered by an elected parliament.

 Monarchy - Dynastic                                   A kingdom ruled by a single family, with a
                                                       developed nobility and a church in support
                                                       (though helmed by a powerful papal figure)

 Religious - Holy See                                  A state ruled by a church, with a single figure
                                                       deemed to be the sole voice of god at the
                                                       head. May be hereditary, may be chosen by
                                                       council, the people, or signs.

 Religious - High Priest Council                       A state ruled by a church, which is lead by a
                                                       council of religious leaders.

\subsection{Uncommon Societies}
Uncommon Societies

Uncommon societies in Lancer are states, groups, and territories organized in ways that are rare
in the galaxy. States that do not participate in galactic politics, states that have little interaction
with the Cosmopolita, states that have been lost or otherwise hidden, and states that do not
have a permanent home are examples of some uncommon societies.


Players who hail from uncommon societies often have views on Union and galactic politics that
skew far from common political leanings, complicating their relationships with other players and
NPCs that they encounter during your campaign.


Fledgling societies have populations in the hundreds to the thousands. Developing societies
from the thousands to the hundreds of thousands. Developed societies in the hundreds of
thousands to billions.





More examples are listed below:


             Hermit State                         A purposefully isolated, developed state that rejects
                                                  diplomatic advances (or only extends diplomatic
                                                  offers rarely).

             Lost Colony - Young                  A colony world recently lost in the administrative
                                                  shuffle, as a result of an omninet blackout, or other
                                                  catastrophe.

             Lost Colony - Established            A colony world lost long ago, developed in isolation
                                                  from (and usually without the knowledge of) other
                                                  civilizations.

             Nomadic State - Terrestrial          Terrestrial nomadic states tend to be small, as they
                                                  travel across the world they inhabit, usually moving
                                                  from habitable zone to habitable zone.

             Nomadic State - Stellar              Stellar nomadic states are similar to terrestrial
                                                  nomadic states, only they travel through space
                                                  instead of a single world.

             Failed State/ Anarchic World         A failed state is a temporary state; it exists only in the
                                                  fall.

             Monastic World                       Monastic worlds are peaceful worlds, places of
                                                  contemplation with relatively small populations. They
                                                  may be devoted to study of a text, of a fighting style,
                                                  or the stars.

             Band - Pirate                        Similar to nomadic states, but focused on raiding
                                                  interstellar shipping lanes.

             Band  - Slaver                       As a pirate state, but with the aim of stealing people.

             Reservation -  Pre-Industrial        A reservation world is a quiet world, set aside to
                                                  emulate a “simpler” time. Knowledge of Union is
                                                  limited -- if people know about Union at all--  and
                                                  people live in a manner like old humanity before the
                                                  information age.

             Reservation - Arcadian               Similar to a pre-industrial reservation world, but taken
                                                  even farther back. Union tends to observe these
                                                  worlds, but not interfere. Arcadian reservations worlds
                                                  are the pre-pastoral, hunter-gatherer idyll, and tend to
                                                  be excluded from Union’s tithes.


\subsection{Unique Locations}
Unique Locations

\subsubsection{Cradle}
Cradle




Cradle refers to both the home system and home world of Union, what we call the Solar System
and Earth, respectively.


Cradle -- the system and the world -- is highly developed, heavily populated, and dedicated to
the daily and long term maintenance, planning, and running of Union. Humanity's homeworld is
the beating heart of the galactic hegemony, Union, part memorial, part privileged residence, part
central hub of bureaucracy.


The terrestrial worlds of Cradle -- Mercury, Venus, Cradle, and Mars, are developed and
populated. These worlds, like their gaseous sisters, are proving grounds as well for technologies
developed by GMS and Union.


Mercury is, largely, a world given over to generate and manage the incredible amounts of solar
power emitted by the Sun and transmit it to Venus, Cradle, and Mars. Mercury is the anchor
point for solar nets hundreds of thousands of kilometers long that expand, weblike, from the
world to absorb solar power. It was Humanity’s first Dyson Panel, and Union continues to work to
perfect and grow the massive, ancient engineering.


Venus is an archive world. Populated stations scatter the surface, but are meant more for
rotational work than long-term occupation. The world has not been terraformed, and is hostile to
humans outside of the vast subterranean archives. Here the the bulk of Union’s prime non-
human persons are kept in reserve, shuttled and entombed in the world for study since the
Deimos Event of 3000U.


Cradle is the administrative and cultural heart of Union. It is humanity’s birthplace -- once called
“Earth” -- and the capital of the populated galaxy. Cradle has a fixed population of two billion,
mostly administrative and support staff for CentComm, the Second Committee,  and the various
archives on-world. Cradle herself is home to a massive transient population of Cosmopolitans
and Diasporans engaged in trade, diplomatic, scientific, religious, and other missions to and from
the galaxy.


Cradle is a world healing from the terrible effects of the Anthropocene. Pre-Fall, humanity
crippled the world in its development: even as they cracked the wonders of the universe, they
grew in the heart of the world a cancer that, in the end, scoured life nearly entirely from its
surface. As such, Union’s Cradle bears the markings of that global, epochal trauma. The waters
have lowered, the fires have quieted, and the seasons have becalmed, and in the wake of their
recession Humanity has slowly, carefully repopulated the world. They have explored the ruins of
their ancient cities, reopened old vaults of wonders, and built a new society, one that is strict in
its stewardship.


To that end, Cradle is off-limits for most. Despite being the ancestral home of Humanity and the
administrative heart of the power that controls the galaxy, the world itself is calm. It is rare that
one hears the roar of a jet high overhead. Off the clock, life, generally speaking, is slow. The
people there are peaceful. Great parks preserve some old wonders and remains of the pre-Fall
world, reminders to those that live now of the dangers of hubris, of consumption, of rapidity.





There are still wonders, tucked away in the lost corners of our ancient homeworld, and some
terrors locked even deeper. Union may have lived through turbulent times as central committees
are dissolved and cobbled together, but its bureaucracy has a long memory; none more
important than which depths one should take care in exploring.


Mars is linked by terrestrial blink to Cradle and is a satellite campus to the larger world’s
administrative heart. Mars is the location of Forecast/GALSIM and the Union Navy’s FLEETCOM
center. It has been partially terraformed, an artifact from pre-collapse humanity left to its own
devices. Life flourishes in Mars’s deep canyons, where air, flora, and fauna is vibrant and hardy;
the world, like Cradle before her, is healing from the ancient loss of its atmosphere. Outside of
these oasis, Mars is still a windswept desert, with barely a gasp of air to be had, on vast, terribly
cold planes of ice and sand.


Beyond the terrestrial worlds, humanity has hardpoint bases on a number of moons orbiting
Saturn, Jupiter, Uranus, and Neptune. These are science stations, R\&D stations, quarantine
holds, drydocks, mining stations, pilot houses, and so on. The Jovian moons, in particular, play
host to a large naval population; Callisto and Ganymede are home to important ready-posture
fleets and terrestrial training facilities, Io and Europa feature important bases and facilities as
well.


More information on Cradle can be found scattered throughout this rulebook, namely under the
sections Foundation; Union: The Tyrant, The Watcher, The Guiding Hand; and elsewhere.

\subsubsection{Deimos}
Deimos

Deimos, a moon of Mars, is missing. The circumstances of its disappearance gives name to the
Deimos Event that lead to the discovery of paracausality, blinkspace, and non-human persons.


Deimos -- wherever it may be -- is assumed to be home to the physical architecture of RA, if
such physical architecture is necessary for the MONIST entity’s function. At the time of the
Event, Deimos was home to humanity’s most advanced artificial intelligence research and
development campus, built following RA’s manifestation at ORACLE CHORUS.


To date, there is no accurate or reliable way to track the location of Deimos, as it appears to be
able to slip into blinkspace without the use of a stable gate; furthermore, RA is able to manifest a
suite of anomalous phenomena inconsistent with (or ignorant of) current understandings of
causality.


Distal and proximal worlds have omni’d in panicked reports of the moon appearing both in orbit
and, most distressingly, in their atmosphere. When this phenomenon occurs above population
centers, there is no corresponding damage that, by all logic, should occur.


Missing persons reports do spike after such an appearance, as do anomalous paracausal
events.




\subsubsection{Hercynia}
Hercynia

Hercynia is, to date, the location of the only known sentient, sapient, and conscious alien
civilization. Further information detailed in No Room For A Wallflower.

\subsubsection{Bastion (Aun’Ist)}
Bastion (Aun’Ist)

Bastion is the translated name of the homeworld of the Aun Ecumene, an advanced, powerful
religious order at the distal edge of Union space. The descendants of Old Humanity settled
Bastion well after Earth had plunged into is Dark Age, having discovered the world seeded by a
Union nearlight ship and ready for them. They developed in isolation for thousands of years
before Union made first contact, after a second nearlight arrived with another wave of contracted
Unionite colonists.


Bastion is a holy world, and the Aunic people make pilgrimage to it, mirroring (in a way) the
migrations that humans make to Cradle in Union. The Aun were peaceful, initially, but following
diplomatic friction as a result of Union’s strict hegemonic impositions, a war (to the Aun, a
crusade) began.


Questions abound in Union FLEETCOM as to why the Aun, a single people, were in need of as
competent and numerous military ships and ground forces as they possess.

\subsubsection{Cornucopia}
Cornucopia

Cornucopia is the capital world of the Autumn People’s Republic, a state created following the
successful revolution and overthrow of its previous monarchist masters. Being the most proximal
Union territory to the Aun Ecumene, and the home of the system-local blink gate it has borne the
brunt of the Aun’s crusade against Union.


Isolated following the Aun’s surprise attack on the system, the APR and a single Union MEF in-
system fight a desperate stand against the Aun crusade, holding out as long as they can for
Union reinforcements.

\subsubsection{Karrakis}
Karrakis

A palace world, Karrakis is the capital of the Karrakin Trade Baronies, an oligarchic interstellar
state in close proximity to Cradle.

Karrakis is home to Throne Karraka, the original palace-city of the Baronies, a sprawling estate-
city now grown to encompass roughly 8 million square kilometers. The original palace, the first
colony of Karrakis, was seeded pre-fall -- it is now a living royal museum, an enclave set inside
the crown district of Throne Karraka.




Karrakis is a temperate world, a Gaia planet seeded pre-Fall and left isolated during the dark age.
It has developed divergent from Union for thousands of years and under the assumption that it
alone had survived the fall: re-contact with Karrakis and the Baronies occurred first via comm-data
packet transmissions sent from Union to ID’d pre-Fall colony sites. Karrakis, having flourished for
nearly 7 millenia, responded rapidly. It would be another two hundred years before physical
contact was established, then in the form of conventional nearlight drone ships sent from Union to
Karrakis.

But for the Deimos Event and Union’s meteoric technological ascendancy, Karrakis would have
been the seat of humanity’s power. Unencumbered by the events of the Fall, the colony on
Karrakis was well-rooted on the world, and for thousands of years its people developed at
conventional rates. By the time of first contact with Union, the Baronies had made landfall on
nearby worlds; by the time of the Deimos Event, the Baronies had developed mass industries and
megastructural engineering. However, by the time Union’s first ships arrived in-system, the
Baronies were far outstripped in offensive and defensive capabilities. Recontact occured in the
3200s under the Second Committee: fearing significant resistance -- which, indeed, they faced --
the Second Committee sent a fleet before their diplomats. The war, such that it was one, between
the Baronies and Union was short. The Union Navy smashed aside the Baronic fleet and secured
the Baronies’ surrender without making landfall on Karrakis.

Their fleet eliminated and faced by Union’s singular control over paracausal entities and
technology, burdened with a baroque monarchy crippled by conventional interstellar
communications and transportation, the Baronies took the unprecedented step -- by their history
and internal mythology -- of ceding galactic sovereignty to Union.

In return, Karrakis became the raw heart of Union’s industrial base, providing the hegemon with
the vast boon of resources and extraction techniques that ensure Cradle and her colonies -- by
extension, the rest of the Core worlds in the galaxy -- never want for any material good. The
Barons, suddenly united by the Blink and the Omninet, chose not to demand rule over the galaxy,
but to fund the people who did. In time, their economic sway has become inextricable from
Union’s galactic dominion.

It is a grim truth of Union -- and an uncomfortable tension among the Terrans that sit the Central
Committee -- that whoever holds Karrakis has at least one hand on the levers of Union’s power.
The Karrakin embassy on Cradle is constantly trafficked by Union diplomats and officials, as is the
Union campus on Karrakis inundated by nobles and magnates.

Karrakis is the heart of the Baronies and now home to the galaxy’s premier naval and finishing
college, the Royal Karrakin Admiralty. Pro-Union Houses view attendance at the Admiralty as a
necessary path for their children, and service as an honorable achievement. They are happy to
send their children to the college, often at great temporal cost to their families, as local blink is far
less developed in the Baronies than in Cradle -- this, some barons grumble, by design.

Following the introduction of mechanized chassis as a warfighting machine, the Karrakin Cavalry
College adapted the new technology, and is now known for the quality of officer and machine its
cohorts produce. While attendance and service in the Admiralty is still viewed as the most




prestigious track for a Barony youth, attendance and service in the Cavalry is a parallel honor --
one more martial than mental.

\subsubsection{Ras Shamra}
Ras Shamra

Ras Shamra is a world of hard contrast. It has a severe beauty, one that Ras Shamrans take a
fierce pride in and seek to emulate in their architecture, style, and culture in general.

Tidally locked, Ras Shamra is divided between a “hot” side, ever-exposed to its sun, and a “cold”
side, ever turned away from the light. The only temperate zone is a comparatively small strip of
land and thawed sea where the two sides meet: the terminator line, bordered on one side by
boiling desert, and on the other by frozen tundra.

This terminator line is a global oasis, a band of life-sustaining tropical jungles, warm river-oceans,
and balmy valleys. It is in this stormy, humid equatorial region that the first colonists of what would
become Harrison Armory’s homeworld made their landfall. Now, the terminator line is a globe-
circling arcology home to roughly 300 million permanent residents.

The arcology -- the eponymous Harrison Armory -- is the habitable stripe of Ras Shamra; from the
world’s surface to many thousand meters below, the arcology combines natural landscape with
cultivated landscape, inorganic with organic, blending world and building together into one
homeostatic, cultivated biome. Its surface levels are lush, varied climates that seamlessly
integrate Armory habitats into the natural environment. If a building is exposed, it is meant to be
exposed, to serve a mechanical, technical, aesthetic, or other official purpose. The surface level is
widely regarded as home to the finest domiciles, offices, and campuses; the Armory’s capital is
located on the surface level, at the heart of a pan-galactic botanical park that sprawls for
hundreds of square kilometers.

The lower levels of the arcology is where the bulk of the “clean” technical, mechanical, mercantile,
political, and administrative work that sustains the Armory is done. The arcology underground is
defined by hundred-meter tall airlight wells that funnel light from the surface down, wide
concourses packed with shops and office fronts, and vast strips of cultivated biomes meant to
emulate the surface. Circumnav hyperloops ring the world, forming the backbone of Ras
Shamra’s global transport network. Here, in the arcology underground, one can find the finest of
the Armory’s Distant-Classical architectural signature, marked by titanogeometric features,
achromatic-primary/primary-secondary color schemes, and play with the contrast between airy
open space and brutalist inclination towards the subterranean massive.

Outside the safety of the Armory itself, Ras Shamra’s day and night sides are home to the
Armory’s “dirty” work: research, development, and implementation of the Armory’s catalog. RDI
Campuses are metropolises in their own right, oases in unrelenting desert or deep, perpetual-
winter night, where Armory personnel live and work in project-rotation. Thousands of technicians,
engineers, scientists, and support personnel live and work in RDI campuses for the duration of
their project and, when it is done, they are rotated out.




The day and night sides of Ras Shamra and the RDI campuses that populate them serve as
proving grounds for the Armory’s massive field equipment catalog -- civilian and military. The day
and night sides of the world also serve as proving grounds for the Armory’s colonial officers,
where both infantry and mechanized cavalry are trained and tested in extreme terrestrial
environments.

Currently the Armory is engaged in a massive project of installing a new subterranean hyperloop
ring to serve the scattered RDI campuses, one that would ring perpendicular to the arcology loop.
The circadian loop is still a century at minimum away from completion; in the meantime, regular
shuttle flights serve the RDI campuses.

Ras Shamra is also home to the Armory’s Special-Exception Persistent-Cultivation Legionspace
Environment -- colloquially known as the Think Tank. Its location is classified, though suspected to
be buried somewhere on the night side of the world.

In local Ras Shamran space, the Armory maintains a number of lunar bases where on-duty
legions prepare and specialize for distant colonial missions. Massive orbitals process the wealth
of empire that flows daily into Ras Shamran space -- tithes and tributes, colonial tax from the
Armory’s holding -- via its local blink gate, Capitol Peak Station.

\subsubsection{Carina}
Carina

Carina, an ocean world in the Argo Navis system, is the jewel of IPS-N and home to its largest
corporate campus, Northstar, where IPS-N’s master shipbuilders live and work alongside the top
corporate brass and Cosmopolitan scholars.

With only 10% of the world’s surface not covered by ocean water, Carina’s terrestrial population is
far outnumbered by its orbital population, where IPS-N’s vast shipyards produce the galaxy’s most
ubiquitous freight, civilian, and military hulls. Local space around Carina is a mesh network of
slingshot gravitational shipping lanes, proving grounds, and ejecta-orbit racing courses, where the
wealthy IPS-N board and officers enjoy easy access to the stars and the newest vessels that
cross them.

Settled soon after the opening of the Blink, Carina was selected by IPS-N’s planners as the
primary site for the newly merged corpro state; an ocean world ringed by rich terrestrial moons,
Carina would be the jewel of the old Cradle corporation.

The great project of relocating IPS-N’s physical infrastructure from Cradle and environs to Carina
and the Argo Navis system was a centuries-long project. Planners laid out a design for the world’s
land masses and began converting the raw earth to arcologies akin to Harrison Armory’s
equatorial installation. Meanwhile, back in Cradle, pilots and engineers set about the massive
work of making IPS-N’s shipyards ready for flight, breaking up the great manufactories by section
and setting them on course to Argo Navis: their passage through the blink would set the initial
calibrations that would become Union-standard for ships across the galaxy.




Carina is a campus-world, unscarred by war or a deep history of human occupation. The bulk of
the time, Carina is a temperate, mediterranean world, with warm oceans and shallow, high-salinity
seas -- typically no deeper than two to three meters.

A notable feature of Carina’s endless oceans are a series of polar “wells”, underwater pits where
the ocean floor drops to titanic depths of tens of thousands of meters. These wells render the
poles of Carina uninhabitable; they pierce nearly to the core of the world and act as geyser-spout
generators, boiling the sea in off-years as trapped gasses build underwater. Typically a decade
between interruptions, these trapped gasses release in a colossal gout of steam, venting high into
the atmosphere and plunging the world into a steamy, months-long wet season of hazy
circumglobal rain and elevated temperatures.

Save for this once-a-decade phenomenon, Carina is often described as a beautiful, if boring,
world. Though to the mariner, or the Cosmopolitan, boring isn’t necessarily a thing to be avoided.

Carina’s local blink gate is Galan Station.
