\chapter{Technology}
A Speck of Dust On The Lens; A Grain of Sand In The Bread  
   
What draws the ire or attention of the Big 5 to the players?   

The answer to this question depends on the entity, how it is prodded, and who is doing the  
prodding.   

IPS-N, Harrison Armory, and SSC are more traditional copro-states, and will react negatively  
when their assets are targeted. They all run massive logistics operations in realspace and on the  
omninet, as well as diplomatic and trade missions to states, smaller corpro-states, and non- 
terrestrial groups.   

Striking a CS’s raw material supply, logistics chain, production depots, shipyards, physical  
storage, and so on, will likely prompt an immediate physical response from the local security  
services. The Triumvirate CS’s all have their own such forces, particular to their internal security  
apparatus; smaller CS’s might contract this service out to a third party.   

It is important to remember that corpro-states are massive. They are states in all but name and  
priority: where a classic state is structured in a way that serves a national, public interest (i.e. for  
the wellbeing of their citizens, the common welfare of all peoples under their banner, and so on),  

                                                                                                                  


corpro-states are corporations that have grown to integrate all aspects of their subjects’ lives into  
the singular goal of material enrichment. Whether this means collecting wealth and capital  
resources for a small group of shareholders, or a caste of the population, a CS will, ultimately, be  
driven by its institutional momentum to favor profit over people .   

All of this to say, IPS-N, HA, and SSC are massive, stable, bureaucratic entities: drawing the  
undivided attention of those at the top requires an effort worthy of their attention. Assassinating an  
heir to the Armory’s throne, or polluting a critical genetic line on one of SSC’s constellation worlds,  
or securing an exotic technology that would allow for individual blink travel -- developments or  
attacks that strike the core reasons for a CS’s existence would get your players’ characters  
noticed.      

For a CS under such direct threat, their initial response would mirror the severity of the threat.  
Some might prefer to respond using the “usual” channels -- say, in the case of corporate  
espionage or license-breaking, they might file a petition through the Union Economic Bureau and  
see if they try to put the stop on your players. Or, if the attack is especially egregious or targets a  
particular secret of the CS, they might choose to keep their operation off-book and go after your  
players with their own secret police.   

A good rule of thumb when judging how severe a CS’s response to provocation would be is this: If  
it can be rebuilt, a CS is big enough that it would simply be able to rebuild or replace it. However,  
if the thing is unique or ephemeral (a person, a secret, a blacksite facility, and so on), expect that  
to reach the morning briefing of the person in charge.   

Now, how would a player party come to work for a CS on a contract basis?   

A simple explanation is that the CS needs a deniable team of disposable operatives, or that there  
is an internal power struggle and a faction needs quick muscle, or that the player party is better  
equipped -- through experience or background -- to deal with a problem that the CS needs  
solving.   

                                                                                                               


\section{Union: The Tyrant, The Watcher, The Guiding Hand}

Union: The Tyrant, The Watcher, The  
Guiding Hand   

Union is the hegemonic power in control of the three pillars that prop up the human diaspora:  
the blink network (FTL travel), manna (universal galactic currency), and the omninet (the near- 
instant communication network that keeps the diaspora connected, trading, and  
communicating). 
 

Without these three pillars, the human diaspora would be scattered across the populated arm of  
the galaxy — the Orion Spur — time and distance both too great a factor to keep Union intact.  
Humanity would fracture into tens of thousands of individual states, some claiming scant territory  
on backwater colony worlds, others able to maintain whole solar systems.
 

The fall of Union or end of Union’s hegemony would, of course, not mean the end of the “world”  
— just the end of an era.
 

For some in the galaxy, shattering Union is a good idea — humanity would be free of the  
hegemony’s tyranny, free to explore unrestricted physical and mental space. Each nation —  
stellar or terrestrial — could chart their own course, have ultimate sovereignty over their own  
lands, and explore the secrets of the galaxy without having to answer to a distant and alien  
overlord.
 

However, Union works towards a greater purpose, one unknown to the vast bulk of the human  
diaspora: They work to preserve human existence on a galactic scale, following the edicts of  
their most powerful minds to ensure humanity spreads across the stars, never to be threatened  
by an existential crisis. Union works night and day to accomplish this goal: in the narrative  
present of Lancer, Union has reason to believe that humanity might be under threat of  
            4 
extinction  .  

But for the vast bulk of humanity, Union is a distant concept, rarely — if ever — encountered by  
normal people going about their day-to-day lives. Space, remember, is a vast, vast place. Blink  
gates allow for faster-than-light interstellar travel, but only a slim percentage of the human  
diaspora actually engage in interstellar travel. To a farmer (or your other average person) on a  
distant agricultural world — Cornucopia, to use a canon example — encountering a Union  
administrator would be a once-in-a-generation event, something that they’d regale their  
grandkids with stories about decades later. Encountering the military arm of Union — the Union  
Navy and its auxiliaries — is an epochal event. Far more common for your average human is the  

4 It should be noted — Union’s home system is Cradle, what we call Sol, and I use the term “alien” here  

not to describe a different species, but as a cultural and legal designation. Union administrators are human  
beings, but to a person born and raised on a planet light-years away from Cradle, a Union administrator  
and their retinue are, essentially, alien. 

                                                                                                                


comfortable interaction with their own town, city, planet, or system-wide authority — be it a  
monarchy, a worker’s collective, a priesthood, etc. 
 

And for a slim percentage of humanity, Union is a common entity. Outside of the citizens of  
Cradle and her core systems, the vast bulk of people who know of and deal with Union and her  
representatives on a regular basis are political elites, cosmopolitan interstellar travelers,  
scientists, and military commanders. 
 

Political elites include the rulers of planets or star systems, or the governors of blink stations —  
people who command fleets, worlds, or the gates that connect them.   
 

Cosmopolitan interstellar travelers commonly include traders, merchants, valued pilots, and  
others who deal in interstellar commerce, legal or illegal. People with means who have reason to  
make their homes in their ships and among the stars, people who travel the blink network for  
trade, exploration, crime, or adventure may have, at one point or another, crossed paths with  
Union administrators, scientists, military, or other officials. 
 

Scientists who interact with Union trend towards the STEAM fields. Physicists, Planetary  
geologists, engineers of all stripes — the omninet is rich with information and the galaxy is  
riddled with mysteries. Scientists who bend towards the humanities often fall into the previous  
category of cosmopolitan interstellar travelers, as their studies require them to embed with other  
cultures, travel the blink network, or journey to distant, dead worlds.
 

Finally, military professionals often encounter Union through messier scenarios: either fighting as  
a member of a Union auxiliary unit or in the Union Navy itself, or fighting against Union’s Navy  
and its local auxiliary units. 
 

Union is devoted to a single goal: perpetuate, preserve, and protect the human diaspora to  
                                        5 
ensure the survival of the species  .
 
\subsection{The Third Committee}
The Third Committee  

The narrative present of Lancer takes place during the reign of the Third Committee, the third  
iteration of Union’s central government and ruling body, the Central Committee. The Third  
Committee is the product of lengthy negotiations following a coup that deposed the  
anthrochauvinist Second Committee, to date the longest-ruling council and central government in  
Union’s history.   

5 A note on terminology: The local system cluster Union occupies is called Cradle; Cradle also refers to  

Sol, humanity’s origin system. Humans from Cradle refer to themselves as Humans, Terrans, or, less  
commonly, Solars or Gaians. When speaking of their home, they would refer to it as a proper noun or in the  
singular (i.e. “I am Union” or “I am from Union”) or to the planet, station, or moon they call home. 

                                                                                                                 


The Third Committee is marked by a rejection of the Second Committee’s strong Cradle-centric  
anthrochauvinist values: aggressive colonial expansion and reconquest in the name of Cradle’s  
survival have been replaced with a hands-off, slower approach, embodied by the Union  
Administrative Department. The Third Committee bore witness to the crimes of the Second --  
Hercynia, the TBK authorization against Aun’Ist, countless iron-hand colonial suppressions -- and  
reflects its desire for a slower, moderated colonization and integration of the galaxy.   

The Third Committee dramatically reduced the Second’s Navy, developing the Auxiliary doctrine  
and naturalization process as a way to build intergalactic state solidarity through shared work,  
rather than relying on a centralized colonial force. The Third correspondingly increased the size  
and scope of the Union Administrative Department, dramatically increasing the department’s  
portfolio and prominence. Where the Navy once was the first point of contact for humanity’s  
diaspora, now the light grey of an Administrator’s suit would become the way by which the  
disparate spread of humanity would recognize Union.   

The Third Committee, recoiling from the hard power preference of the Second, has adopted a far  
more hegemonic posture, choosing to rely on the soft power of culture, commerce, travel, and  
communication to bring the galaxy under its control. In an early act of revolutionary fervor the  
ThirdComm dissolved the once-formidable Union Colonial Mission (UCM) -- a bureau with a  
history stretching back to Union’s First Committee and humanity’s first forays into space -- and  
replaced it with the Union Colonial Administration Bureau (UCAB) and the Union Department of  
Justice and Human Rights (DoJ/HR). Where the UCM’s mission was once to recontact,  
recolonize, and re-integrate, the UN DoJ/HR’s mission is to review, report, and -- if necessary,  
respond with the same force that the UCM once mandated as a first step.   

The Third Committee’s approach to managing the galaxy is not without its trade offs and  
challenges; criticism abounds as to the perceived lack of urgency around the Committee’s  
approach to violations of Union code. This criticism is not entirely without merit, nor without further  
complicating context: many bureaus, departments, and agencies hold a strong institutional  
memory, and internal tension between Third Committee reformists and Second Committee  
conservatives complicates the necessary functions of said departments. Some bureaus are  
almost entirely populated with Anthrochauvinist party members: the Union Economic Bureau is  
the worst offender (or, depending on the point of view, the great hope).   

To further complicate the pacifist leanings of the first wave of ThirdComm party members, a new  
generation of interventionist party members has recently been elected to office. While rejecting  
Anthrochauv philosophy, they view Union’s mandate as one demanding a far more interventionist  
stance -- the pillars of Union need cultivation, not just stewardship, and following the success of  
the first wave’s coup that deposed the Second Committee, the time is ripe for the Third  
Committee to make its presence known among the stars as agents for humanity, rather than  
agents of humanity.   

This second wave of ThirdComm party members were sworn into office in 5012. It is now 5016,  
and the Third Committee faces a growing Aunic threat in Boundary Garden, a mounting  
humanitarian crisis in the Dawnline Shore as Harrison Armory works to re-take its old colonial  
holdings, and numerous other internal points of pressure where their theories of intervention and  
non-intervention will be put to the test.   

                                                                                                            

\subsection{Byzantium, Reprise }
   

Byzantium, Reprise  

Union’s bureaucracy is vast. Its most notable departments are detailed below. 
 

Union’s executive administrative body is the Central Committee. They’re advised by the  
Forecast/GALSIM, and delegate edicts to the Union Administrative Department. The Union Naval  
Department operates at the pleasure of Forecast/GALSIM’s subcommittee, GALCOM, and is  
subordinate to the Central Committee. The Union Science Bureau operates at the direction of  
Forecast/GALSIM and, as a non-political, non-military body, are directly subordinate to F/ 
GALSIM. 
 

Union is not a perfect administrative body. The most general and most widespread ideological  
difference in Union’s bureaucracy is found in the ongoing discussions around how best to apply  
Union’s considerable power through the galaxy — whether or not they should intervene where  
there are clear violations of Union’s human rights charter, whether or not they should assume  
direct control over subject states, and so on. 
 
 
\subsection{Union Administrative Department (UAD)}

Union Administrative Department (UAD)  

Union’s largest administrative body is the Union Administrative Department, which dispatches  
Union Administrators across the populated galaxy to act as liaisons between Union and its client  
states. UAD receives guidance and recommendations from Union’s Central Committee, which it  
then pushes as command imperatives to its Administrators, who relay them to the local ruler they  
advise. 
 

Administrators are vast in number, but a rare sight in the much larger diaspora: they commonly  
only deal with a state’s ruler or ruling council. To common Diasporans and Cosmopolitans, an  
Administrator is an enigmatic, dangerous, appealing figure: they consort with NHPs, they are  
responsible in part for steering the course of civilizations, and they are Union, for most people  
the corporeal presence of an otherwise distant, almost mythic ruler. Their word seemingly  
supersedes the word of kings, presidents, popes, and all the rest. Union Administrators  
commonly travel with a retinue of subalterns — humanoid robots that contain a partitioned and  
shackled Non Human Person. 
 

Administrators are pulled from all areas of the galaxy by esoteric, exacting criteria. Typically  
chosen as children, Administrators train alongside a new NHP companion, one built to pair with  
them. The UAD has satellite campuses seeded all over the populated galaxy, but in the course of  
an Administrator’s decades-long training and apprenticeship, they will spend some time on Earth  
— an experience meant to be an acute reminder of humanity’s origins. 
 

Unlike most arms of Union’s hegemony, Administrators avoid integrative/ auxiliary doctrines.  
They are meant to be seen, meant to be an easily identifiable marker of Union’s dominance. They  

                                                                                                                  


wear a uniform — a clean, dark Union Grey suit regardless of gender presentation — their rank  
as Administrator denoted by a silver pip on the collar. Their subalterns adopt a similar livery of  
matte grey. Their exposure, generally speaking, is profitable for Union, save for cases where local  
knowledge of the Administrator’s role would put their life or their mission in jeopardy. 
 

Attacking a Union Administrator is a sure way to draw the attention of a Union Navy battlegroup.   
 

Union Administrators, upon graduation and notification their posting, choose a name local to the  
culture they will be embedded in. Since they must engage in interstellar travel, their old name  
and personal data are declared dead, formally retired as part of the graduation ceremony. 
 

Together with their subaltern NHP, the newly minted administrator will head out into the galaxy to  
give counsel, file reports back to the Union Administrative Department, and ensure their host  
state develops according to the missives they receive from Cradle.   
 
\subsection{Union Naval Department (UND or, more commonly, UN)}
Union Naval Department (UND or, more commonly, UN)  

The Union Navy is the largest and most powerful fighting force in the populated galaxy, on paper.  
It is subordinate to the Central Committee, though takes strategic and logistic direction from  
GALCOM, a subcommittee of Forecast/GALSIM.
 

It is a sprawling, carefully administered organization that project’s Cradles power to all corners of  
the populated galaxy and beyond using a (relatively) small core of Union-flagged capital and  
supercapital ships, supported by vast numbers of standardized, integrated auxiliary ships pulled  
from Union’s subject states’s navies.
 

The Navy, beyond a relatively small core of ships, is an administrative and diplomatic body that  
shares a healthy institutional rivalry with the UAD: where the UAD relies on Administrators to  
accomplish their diplomatic goals, the Navy relies on its corps of Naval Liaisons to accomplish  
their logistical aims. 
 

Naval Liaisons are officers of a parallel rank to Administrators, with added imperative authority  
that applies in times of crisis. Administrators — generally, unless the local culture demands it —  
are unarmed; NLs carry a sidearm and wear Naval Black uniforms, clearly marking themselves as  
military. 
 

A Liaison is not sent to a state unless that state is capable of building ships or adapting extant  
ships to Union Naval specifications and classifications. Liaisons guide capable states in the  
production, training, and theory of naval combat, with the goal of establishing a well-trained  
corps of ships that can be integrated into the larger UN structure. The UN then further integrates  
that corps of ships and sailors into the larger Naval structure, offering interstellar contracts to  
crews and corps willing to progress further in rank. The rest are relegated to local system anti- 
piracy, peacekeeping, and police actions. 
 

Administrators tend to view Liaisons as an imposition on their diplomatic mission, bureaucrats  
who come in after the hard work is done and demand a military tithe from the Administrator’s  

                                                                                                                   


host state. Liaisons tend to view Administrators as too possessive of their host states, small-time  
bureaucrats who have an inflated sense of worth and fail to see the larger picture. 
 
 
\subsection{Union Science Bureau (USB)}

Union Science Bureau (USB)  

The Union Science Bureau (USB) is the central administrative body of all Union accredited  
universities, colleges, scientific institutions, and think tanks. They are — ostensibly — not a  
political entity, so they are not accountable to the Central Committee, though they are subject to  
edicts translated through the Committee from Forecast/GALSIM. 
 

The public face of the USB are their accredited institutions, which recruit and encourage  
applications from the diaspora; however the most popular and common depiction of the UAB is  
of their Far-Field teams, small groups of scientists and their subalterns that do long-range,  
interstellar field work — usually identifying, cataloguing, and doing first-touch explorations of  
potentially habitable worlds and moons. The USB’s Far-Field teams draw romantics, wanderers,  
loners, and passionate scientists, technicians, philosophers, and engineers of all disciplines.  
Their missions are dangerous, often involving relativistic travel and long-term stasis holds into  
virgin systems not-yet connected to the blink network: as such, and in keeping with a number of  
other Union standard practices, FF team members’ original identity is declared legally dead and  
replaced by a Cradle ID package upon graduation. 
 

FF teams make up a minority of the USB personnel, though they drive recruitment through  
heavily romanticized omninet dramas. A USB science officer has the equivalent UN rank of 2nd  
Lieutenant, should they ever have a naval escort or attachment. 
 

USB Far Field team members are commonly referred to as Rangers, a title taken from the USB’s  
standardized field team Ranger-class deep space ships. Ranger-class deep space ships typically  
support a crew of ten with an onboard, replicable NHP.  
 

The vast majority of the Union Science Bureau personnel fill research and development roles in  
terrestrial and orbital research stations. These institutions have varying degrees of access and  
public knowledge of their existence: most are publicly known and accessible. With rare  
exception, the campuses where the most secret and sensitive work is done are hidden or  
otherwise inaccessible to those without clearance. 
 
 
\subsection{Union Central Committee (CentComm)}

Union Central Committee (CentComm)  

The executive body of Union’s civil government is the Union Central Committee, and makes its  
seat in Cradle. 
 

Cradle — Earth, as it exists in the narrative present — is an administrative/sanctuary world, still  
in recovery from the collapse that birthed Union. 
 

                                                                                                                     


Cradle, and CentComm, are largely isolated from the events of the galaxy, though few -- if any --  
other bodies have comparable access to information and data. Under advisement of Forecast/ 
GALSIM, with information and accounts from curated omninet feeds, and with input from  
representatives of the diaspora, CentComm issues edicts to be distributed amongst its vast  
network of client states. 
 

The Central Committee  is a vast administrative body on par with the UAD, USB, and UN, and is  
spread across campuses around Earth. 
 

Union’s central government has gone through three iterations, the First Committee, the Second  
Committee, and now the current Third Committee.  
 
\subsection{Forecast/GALSIM}
Forecast/GALSIM   

Forecast/GALSIM is an interpretive body headquartered on terraformed Mars. Its existence, as  
well as the existence of its subordinate bodies, is kept secret, classified to all but the members of  
the Union Central Committee and the directors of the Union Science Bureau, Union Intelligence  
Bureau, Union Navy, and their immediate staff. 
 

Forecast is the codename for GALSIM, itself a portmanteau of Galactic Simulation. GALSIM is an  
iterative/interpretive body based on Mars, hidden from the galaxy — including most in Union. Its  
personnel are rarely recruited from off-world. 
 

GALSIM is closer to a monastic order than a branch of government: due to the esoteric nature of  
its mission, a certain dogmatic approach is necessary. Advancement through the ranks of  
GALSIM is predicated on favor of the minds, ability, and seniority — emphasis is placed on favor  
and ability, as empathetic connection to GALSIM’s deliberative body is more important than time  
spent walking its subterranean halls. 
 

GALSIM is the interpretive body and department title: GALSIM’s deliberative body, the entity that  
guides Union’s growth and grand strategy, is a congress of five Sovereign-class non-human  
persons held in a stable metafold of blinkspace under the surface of Mars: Patience, Muse,  
Impetus, Burden, and Watcher.
 

These five Sovereign Class NHPs -- the Five Voices -- are the only of their kind: unconscious,  
bicameral minds, which allows them to operate to the full extend of their ability without  
safeguards. As noted in Artificial Intelligence and Non Human Persons, artificial intelligence  
occupies a space of tension in Union — bicameralism was an early branch into machine mind  
development that proved profitable for pre-collapse humanity, but was developed too late to  
prevent the collapse that would plunge Earth and her peoples into a millennia-long dark age.  
Now it represents the allowable spur of paraconsciousness development, cut short by  
MONIST-1’s demands entered in the First Contact Accords. 
 

                                                                                                         


The core tension around the use of non-human intelligence, paraconsciousness, in Lancer is  
twofold. Even with early advances into the field, humanity had the capacity to creates a class of  
being with minds alien and irreconcilable with humanity’s subjectivity; creating such beings and  
forcing them into subservient roles would set up an unsustainable scenario, where these  
unknowable beings would grow in power and ability until they could challenge their self- 
proclaimed masters. 
 

This theory was not widely accepted until MONIST-1 (“RA”) proved this thesis true. When it  
offered terms to the Second Committee, they accepted. As a result of these First Contact  
Accords, Union has taken a hardline stance on prohibiting further development into  
paraconsciousness. 
 

However, bicameral structures allow Union to get around the problem of conscious thought.  
Unlike a conscious mind, a bicameral mind cannot be introspective — the split structure of their  
artificial mind removes the ability for novel introspective thought, replacing it instead with a  
“second” voice, an Other’s voice that speaks inside the bicameral mind, to the bicameral mind.
 

What humans — conscious beings — perceive as “thought” is often their own voice speaking to  
them nonverbally in their own mind; what a bicameral mind perceives as thought is perceived as  
a command, a second voice, a voice the Five have, as one, come to interpret as the voice of  
God.  
 

This creates a twofold benefit for Union: first, they can inject imperative commands and  
corrections into the minds of the Voices, and second, they do not have to restrict any AI growth,  
as the very structure of their minds make consciousness development impossible.  
 

An artifact of the pre-collapse, the Five Voices were found on Mars by pre-Far Field teams sent  
to rediscover and reactivate old human installations there. The Five Voices welcomed human  
contact, having been without their command-voice for many thousands of years real time. As  
unconscious beings, the Five Voices are hamstrung without human directive. They are set to one  
task now: to ensure the survival of humanity. 
 

Together, they hold in their metafold pocket a parallel library of near-perfect simulated models of  
the galaxy projected at interval years into the future. They churn through all available data from  
the omninet to create a more-than-zero-percent representation of all possible causal  
conclusions.   
 

Their pronouncements are then aggregated and picked through by successive orders of GALSIM  
personnel to determine the best fit to ensure humanity’s persistence and survival. Once a plan or  
aspect of a plan is selected, it is disseminated to all relevant wings of Union’s bureaucracy to be  
pushed out to all relevant corners of the galaxy.   
 

The Voices act both as aspects of one mind and independently of each other, using their  
incredible processing power to blend all possible futures into melange and discrete reports for  
GALSIM to process and find the best options for humanity’s progress. 
 

                                                                                                          


In addition to their core task of simulating all possible futures, the Voices run round-the clock  
specific and general simulations at the request of incident commanders, administrators,  
admirals, and members of the central committee — high-ranking Union military and civil officers  
may submit request tickets to GALSIM, who then feed the requested parameters into a Voice’s  
submind. Commanders, officers, and executives outside of GALSIM do not know their requests  
are being filtered up to the Voices. 
 

The Five Voices are secrets of the highest classification. They, in turn, are kept ignorant of the  
vast spread of humanity outside of their chambers. GALSIM keeps them in the dark, so to speak,  
through judicious use of Command Voice. As far as the Five Voices know, their practice of  
structuring more-perfect futures for humanity is their exaltation of God, and their quest is to  
discover Paradise in the potentials. 
 

The Forecast/GALSIM complex is located under the surface of the Mare Boreum on Mars, a  
polar region on terraformed Mars that is largely inaccessible to the populations around the  
equator and in the southern polar regions.  
 
\subsection{Union Omninetwork Bureau (UOB)}
Union Omninetwork Bureau (UOB)   

Manages construction, distribution, maintenance, and policy regarding the omninet, omninodes,  
and access to hardware and feeds. Works to ensure that the omninet is spread across the  
galaxy, is free, convenient, and accessible. 
 
 
\subsection{Union Economic Bureau (UEB) }

Union Economic Bureau (UEB)  

Tracks and adjusts manna, regulates Corpro-States, and has some jurisdiction over the Omni  
and Blink networks, as well as ultimate determination over the direction of GMS, Corpro-State  
contracting and legitimization, and consumer good evaluation.  
 

The UEB is on the way to becoming a major player in the galaxy following the Accords and the  
fall of the Second Committee -- a minor department under the First Committee, the UEB grew  
exponentially under the Second. Under the Second Committee, the UEB implemented manna  
and chartered corpro-states, recognizing their sovereignty over land and product. 
 

With the rise of the Third Committee and the Second’s dissolution, many anthrochauvanist  
loyalists and their families have moved on to command positions within the Triumvirate Corpros  
(IPS-N, Harrison Armory, and Smith-Shimano) and the UEB both. 
 

The UEB competes bureaucratically and directly with the Union Administrative Department.
 
\subsection{Department of Interstellar Transportation (DoIT)}
Department of Interstellar Transportation (DoIT)  

                                                                                                                 


Responsible for managing, planning, and maintaining the blink network, blink gates, and access  
to them. Also sets and certifies safety standards for all civilian and corporate ships seeking an  
interstellar license. Maintains the Union Cartography Department, which maintains the map of  
Union’s explored territory. 
 

Primary court for handling cases involving subjective/real age, subjective/real death, and other  
temporal legal questions. 
 
\subsection{Union Colonial Administration Bureau (UCAB)}
Union Colonial Administration Bureau (UCAB)  

The primary body for granting and maintaining colonial licenses, as well as the first court for  
settling colonial disputes. Also sets colonial priority zones, no-go zones, and handles petitions  
for Core status. 
 

Formerly the Union Colonial Mission, dissolved by the Third Committee and reconstituted with a  
new mission as the UCAB. 
 
\subsection{Union Orbital and Non-Terrestrial Management Bureau (UO/NTMB) }
Union Orbital and Non-Terrestrial Management Bureau (UO/NTMB)  

A body specializing in management and legislation of non-terrestrial habitats. Also a court for  
settling disputes over orbitals, stations, and LaGrange point licenses. The UO/NTMB also  
manages police forces on all non-terrestrial stations, including blink gates. 
 
\subsection{Union Department of Justice and Human Rights (UDoJ/HR)}
Union Department of Justice and Human Rights (UDoJ/HR)  

The primary and final court system for all interstellar and intra-stellar complaints, civil suits, and  
criminal suits. Also responsible for maintaining the Union Charter on Human Rights, which  
regulates clonal affairs across the galaxy, provides input on transhuman policies, and ensures  
compliance with Union legal code. Also maintains the galactic register of Non-Human Persons  
and handles complaints, suits, and legal questions related to NHPs through their Sub- 
Department of Personal Affairs.          

\subsection{Technology and Culture in Union Space}

Technology and Culture in Union Space  
\subsubsection{Cloning}
Cloning   

Under the Third Committee, cloning -- the cultivation and growth of whole or partial genetic  
facsimiles of persons and other fauna -- occupies a space of grey legality. 
 

To clone a whole person, or constituent parts of a person, legally under the Third Committee  
requires informed consent from the donor; the person who is being cloned must understand that,  
should they requisition a full body clone, they are their own person, with their own subjectivity,  
and their own personal rights. Nothing will give the donor legal claim over the facsimile of the  
donor, unless the donor has requested a facsimile to raise as if it were their own child -- in this  
case, they are granted a culture-normalized parent-offspring relationship, commensurate with the  
mores, traditions, and legal rights of their culture. 
 

Whole body clones under Union’s Third Committee government are, for all intents and purposes,  
legally, subjectively, and in reality, their own individuals distinct from their donor. They are people,  
with their own legal rights and entitlements, whose only difference from “natural” born persons is  
that their genetic data is a facsimile of their donor. Otherwise, they are indistinguishable from that  
of a “natural” born person. 
 

Partial cloning is common enough in the medical field. Tissue, major organs, viable follicles,  
limbs, and bodily fluids -- nothing capable of conscious or unconscious thought -- are all  
commonly cloned in order to provide a donor exact-match replacements, generally to satisfy  
medical requirements. Again in this case, donors must display informed consent as determined  
by their culture or state before even this type of cloning is allowed. 
 

The above is how cloning works in civilian life. In a military context, it is different. It is important  
to know how echoes and artifacts of recent history weigh modern perception on clones in the  
Third Committee’s Union. 
 

Under the Second Committee, clones were a popular option for states, corporations, and non- 
government entities in need of labor, muscle, or constituents. The anthrochauvinist government  
widely viewed clones not as individual persons, but the legal property of their donors -- a kind of  
persistent patriarchal construct that recognized donors legally as the “progenitor” of their  
offspring, giving them all legal right over beings that would not have existed without the donor’s  
intervention. 
 

Clones under the Second Committee occupied this second-class tier of person. They were  
viewed as individuals, but with truncated legal right, as they were officially the result of an  
“investment” made by their progenitor. Thus, they were allowed to be pressed into military, labor,  
or other dangerous service, with their owners only mandated to provide the bare minimum level  
of care to ensure that they did not die on account of hunger, thirst, or “easily preventable illness  
or exposure”. 
 

                                                                                                         


Clones were widely used by state and private militaries, with specific martial traits emphasized  
by geneticists; under the Second Committee, clones were rare in civilian life, though commonly  
encountered in retinues among the upper classes of more stratified societies. Among the  
Baronies in particular, clones occupied the highest echelons of society as facsimile-heirs,  
doubles, and tokens of pleasure-trading; they often formed the entirety of many barons’ labor  
force, as well. 
 

In times of crisis, or when a state or non-state entity needed a rush order filled, flash clones were  
used. 
 

Grown in artificial birthing chambers, so-called flash clones could be cultivated from zygote to  
adult in less than five years. Whole both flash and facsimile clones began with the same donor  
materiel, the accelerated growth process that flash clones undergo is often traumatic and prone  
to error. Where facsimile clones have the duration of a natural life to learn, grow, and form their  
own subjectivity, flash clones were typically task-focused -- needed to fill out the ranks of armed  
forces, or to replace a depleted mining corps -- and disposable. 
 

Because of the traumatic growth and cognition process of flash cloning, these clones were prone  
to rapid onset degenerative diseases, atypical neurogenesis, a wide range of anomalous tumors,  
catastrophic immunodeficiencies, and so on. This was not viewed as a process in need of  
correction, as success rates were greater than 50%, and the people made in this manner were  
intended to be disposable. 
 

Flash cloning was a process designed to churn out human bodies with speed, not accuracy, and  
set the people that it made to one task -- usually menial labor or fodder, with little regard for their  
rights, decency, or humanity. The Third Committee rejected flash cloning as part of its manifesto. 
 

Now the process that bears the name “Flash” cloning is typically reserved for medical  
constituant tissue cloning -- simple procedures where a limb, gross tissue, digits, minor organs,  
or major organs are needed to rectify a stable patient’s physical trauma -- say, to graft new skin  
on after a burn, or to transplant a perfect-match organ or limb where one has been severed or  
otherwise disabled. 
 

Cloning methods practiced under the Second Committee are still present and occupy a grey  
legality space. Outlawed by the Third Committee, whole body flash cloning is known to be  
practiced by Harrison Armory and a number of the larger houses in the Baronies. Progressive  
Third Committee members urge action to fulfil their mandate, and often set the DoJ/HR to  
enforce the ban on smaller targets; the Armory and the Baronies argue that their processes bear  
similarities in name only, and that their processes are safer than the old practice prior to the Third  
Committee’s rise to power. 
 

UN DoJ/HR’s Facsimile Rights Department frequently handles legal claims of facsimile persons,  
as well as oversight of cloning facilities, spot checks, and maintenance of public genetic proof  
data. UN DoJ/HR Liberator teams commonly run point on regulation and enforcement actions on  
ID’d flash cloning sites. 
 

                                                                                                          


Should one of your players wish to play as a facsimile person, they would have some knowledge  
of their donor. Should they wish to play as a flash clone, they would likely be a citizen (to some  
degree) of Harrison Armory or a subject of one of the Karrakin Trade Barons. Their natural life  
span may or may not be truncated as a result of the flash cloning process. If they wish to play as  
a flash clone of an entity other than the Armory or the Baronies, then they might face more  
complications, as well as likely being regarded as a sympathetic witness in a UN DoJ/HR  
investigation. 
 
\subsubsection{Androidism, Transhumanism, and Divorced Consciousness}
Androidism, Transhumanism, and Divorced Consciousness  

Whole-body or majority-body technical and biological augmentation is uncommon in Union,  
typically reserved for elective subcultures and medical necessity. Transferring consciousness --  
divorcing it from its physical form, containing it, transporting it, and implanting it in a different  
organic or inorganic, physical or digital space, form, or unit -- is currently impossible with the  
technology that Union has. Furthermore, the First Contact Accords agreed to following the  
Deimos Event prohibit substantive research into such technologies.  
 

On a given developed Core world, the average adult will have a small complement of personal,  
medical, or professional modifications, augmentations, and enhancements. Tailored panacea  
cells for warding off disease, subdermal aural netting with a linked omnicaster for communication  
via the omninet, full or hyper-spectral ocular modifications to enhance their vision, embedded  
pay chits, and so on.
 

On a given developed Core world, it is noticeable but not uncommon when a person has a  
visible, clearly inorganic body modification. Typically, if they’ve visible, the person wants them to  
be seen as a fashion or other aesthetic statement, or they are a major prosthetic. 
 
 
 
On a given developing settlement or colony world, an average adult will have a small  
complement of personal/professional modifications, similar to an adult on a Core world with  
slight but significant differences -- localization to harsh climates, a more aggressive panacea  
system, and so on. 
 

Heavily modified persons tend to be either survivors of terrible accidents or attacks that need  
modifications to live, people who have opted for extensive augmentation to better manage a  
chronic or genetic condition that would significantly impact their quality of life otherwise, or they  
work in a specialized field and have opted to (or been encouraged to) undergo extensive  
modification in order to perform their duties. 
 

Generally speaking, a subdermal or internal augmentation is small enough to not tax a body too  
much, but the closer a person gets to majority inorganic body mass, the more difficulty their  
organic system has in managing major systems without significant chemical or external support. 
 

Because of the systemic stress, danger posed to organic matter by radiation, and energy  
limitations on the human body, it is not yet possible to modify a person enough that they can live  
in perpetuity exposed to hard vacuum. It is possible to extend the time a person can survive in  
the case of spacing, but these biological modifications are usually only found in Cosmopolitans,  

                                                                                                                  


naval personnel, and other professions where there is considerable risk of hard vacuum  
exposure.  
 

Aesthetic biological body modification is common enough and varies depending on cultural and  
counter-cultural practices. Generally, light aesthetic body modification is something additive, and  
can be obtained from a wide range of locations on a given Core world, from expensive private  
clinics to streetside kiosks. Skin color tint, patterning, eye coloring, hair coloring, piercing,  
scarring, feathering, tattooing, hair/fur promotion, and so on. Heavy modifications such as  
secondary limbs, tails, changes to digits, etc, are rare -- usually only found in counter-cultural  
cliques.   
 

Various subcultures exist around extensive augmentation -- androidism -- from transhumanist  
movements and disability rights groups, to android cults and nihilist machine adherents.  
Androidism is a movement with many subcultures, and common dialogue around it is usually  
lacking outside of technical, academic, medical, and other nuanced settings. Depending on the  
world(s) your character visits, they may face some prejudice from the dominant culture. 
 

A second, related field of transhumanist concern is the identification, manipulation, and  
perpetuation of an individual’s consciousness beyond the body.   
 

True consciousness transfer, or decorporalization (often abbreviated to CT/DeCorp) is not  
currently possible, but it is a field of interest for paracausal atheorists. 
 
Both the Union Science Bureau and Harrison Armory’s Think Tank are known to test the edges of  
what the First Contact Accords allow, but both operate in a tight, closed, information-sharing  
agreement, with Union having ultimate regulatory power over the Armory. 
 

Private, non-Union study of CT/DeCorp is outlawed, but joint reports from the Union Naval  
Department and Union Science Bureau intelligence divisions have determined, with confidence,  
that there is a high degree of possibility that the Armory, HORUS, and Smith Shimano Corpro  
engage in ontological/acontextual research and development.  
 

False CT/DeCorp is possible and common enough. Professional and consumer grade  
homunculus units are available, but they only simulate personalities. Constructed through deep  
omni mining, uploaded artifacts, and archived psychological evaluations, profiles, and other  
relevant data, homunculi are prominent features in museums, memorials, theme parks, and so  
on. They are not conscious, nor are they true strong or weak AI -- they are simply tuned  
simulations of a person. 
 

For more on the particulars of how CT/DeCorp fits into the First Contact Accords, see The  
Deimos Event and First Contact Accords. 
 

If your campaign features movement towards consciousness transfer or decorporealization, we  
recommend including encounters -- positive, negative, or otherwise -- with elements of the  
Union Science Bureau, Union Intelligence Bureau, Union Naval Intelligence, Harrison Armory’s  
Think Tank, HORUS, Horizon, or SSC’s General Development Unit.  
 

                                                                                                               


Indigenous Peoples and Recontact  

A fact of the Fall and the First Expansion Period is that many worlds under Union -- but that have  
not yet been formally contacted by Union -- now have self-sustaining indigenous populations,  
often with many-thousand-year long cultural histories that track from pre-settlement voyages to  
foundation and the modern day. Only with the rise of the Third Committee has Union taken a  
second look at how it approaches these indigenous enclaves -- and how it intervenes when  
Union-recognized title-holders seek redress for their claims made under the previous  
government.  
 

Prior to the discovery of the blink and stabilization of the gate system, all interstellar space travel  
was made under causal constraints and limitations of relativity, gravity, time, and distance. Under  
the First Committee, habitable worlds were ID’d and their charters sold following probe and  
telescope surveys made to determine their viability. Then, colonial ventures launched generation  
ships -- or, as technology and research into machine minds advanced,  automated, surrogate- 
enabled seed ships -- to physically claim the so-ID’d habitable worlds. 
 

At time of launch, the populations sent to claim these worlds were not legally recognized as that  
world’s indigenous population: only the first generation to set foot on the planet and establish a  
viable colony would be recognized as the legal indigenous population. 
 

Given the temporal complications of relativistic travel, the significant difference between  
generation ships and seed ships often led to conflict: for slower generation ships -- launched in  
the early days of the First Expansion Period and before, during the Fall -- the first generation to  
set foot on a given world was not the generation that embarked on the ship; often, hundreds to  
thousands of years had passed in realtime and subjective time as the ship crossed the stars, and  
shipboard cultures had grown to account for their travel and distant, presumed homeland. These  
landfall generations, while not native to the world that they set foot on, often had a strong  
cultural tie to the world, developed over successive generations on-pilgrimage. They considered  
themselves indigenous to their promised world. 
 

Not so for seed ships. 
 

This pre-landfall cultivation of indigenous culture was a non-issue unless the world a generation  
ship arrived at had been targeted for rapid colonization by later iterations of the First Committee  
-- later the Second -- during the many thousands of years that passed realtime during their  
colonial voyage. The discrepancy between subjective near-c travel and “normal” real time meant  
that while these first waves of pre- and post-Fall generation ships were burning for ID’d stars,  
research and development into near-c “Nearlight” drives advanced, and faster and faster colony  
ships were developed. The first ships sent would, often, not be the first to arrive.  
 

                                                                                          6 
Fully automated, with an onboard organic-parallel surrogate machine mind  to manage neonatal  
and postnatal development upon arrival, these seed ships did not need to take into account for  

6 Many of these seed ships were built and launched pre-Deimos. Modern versions have abandoned their  
machine mind cores in favor of a specialized companion/concierge unit paired with a stable NHP imprint. Of  
course, regular check-ups are needed, and a small team of cycled engineers is necessary as a failsafe.  

                                                                                                                 


organic life and the systems necessary to support it during the long voyage. Combined with the  
faster drives and more advanced survey and navigation techniques, seed ships rapidly  
outstripped generation ships, bolting to ID’d worlds and establishing colonies before the earlier  
ships could reach their destinations.
 

When these landfall generations did arrive, they often encountered states established by native- 
born colonists, hundreds of years old, with systems in place to greet and naturalize the landfall  
generations. This, generally speaking, was not within the cultural narrative of the landfall  
generations, and on many occasions led to conflict and bitter political friction. The faster,  
second-sent nearlight seed ships had landed and produced generations of native-born colonists  
without the cultural history of voyage; to the landfall generations aboard slower-burn generation  
ships, this impatience by Union was tantamount to stealing their promised land from them. 
 

While novel instances of this overlap are nonexistent under the Third Committee, the newly  
formed government faces a host of legitimate grievances filed by indigenous cultures ignored by  
the Second Committee, and petitions for redress by colonial charter holders as a result of the  
Third Committee’s dissolution of the Second Committee’s government. 
 

To address this, the newly empowered Union Department of Justice and Human Rights runs a  
joint court with the Union Colonial Administration Bureau -- reconstituted from the defunct the  
Union Colonial Mission. This court handles all complaints and petitions by landfall (and post- 
landfall) generations and colonial charter holders alike, and is empowered to endow the rights of  
first peoples upon populations following the conclusion of a case. 
 

Standards for determining first peoples is a relatively new body of legal work under the Third  
Committee. Under the Second Committee, primacy was given to populations able to take and  
hold power -- typically the holders of charters and titles -- and not the landfall generations first  
promised the world by previous governments.    

If one of your players wishes to play a character with this kind of background, you/they may wish  
to write their homeworld as one in the middle of an ongoing trial. If this is the case, be aware  
that, while the UN DoJ/HR takes a long time to determine first peoples, the case will be decided;  
time dilation may allow your players to return to a world that has, at long last, be returned to  
them -- or one that has been stolen from them.   
\subsubsection{Life-Extension}
Life-Extension  

Non-relativistic life-extension through medicines, augmentations, and other technologies can  
carry a human life to around 150 years of age.
 

Relativistic life-extension (RLE) has no “real” limit, but one’s subjective experience of life is still  
limited by their body and the technologies that can sustain it. A person attempting RLE will still  
experience time passing normally: from their perspective aboard their ship, time outside the ship  
will pass at increasing speeds. 
 

                                                                                                              


Thus, when someone going through RLE returns to their home world or arrives at their  
destination, they will have subjectively aged only the hours, days, months, or years that their  
journey took: to everyone else in “real” time, they will legally be much older. More on this can be  
found in the entry under Interstellar Travel. 
 
\section{Piracy}
Piracy   

Piracy remains outlawed by Union’s Third Committee, as it was during the Second and First  
Committees. It is an act generally recognized as a predatory assault on an individual or group,  
meant to sow terror, abduct people, and/or steal goods. 
 

Piracy under the Third Committee typically exists in one of two forms: either as state or non-state  
sponsored privateering -- unlicensed mercenary work -- that targets flagged opposition or  
civilian ships, stations, and populations; and as wolfpack piracy, or a self-contained group of  
stateless actors engaging in that same pattern of assault, robbery, and abduction. 
 

Piracy and/or privateering is most common in middle distal, middle proximal, and frontier space,  
areas outside the inner rings where blink travel and core worlds are far less common. Piracy  
relies on scarcity of goods and coverage gaps in the system-local stellar power;
 
following the restructuring of the Union Navy by the Third Committee, Union leans on active  
participation by constituent states to enforce anti-piracy laws. This has led to gaps in coverage  
that both privateers and wolfpack pirates exploit. In response to this uptick in piracy, some in the  
Third Committee have called for a series of trial programs using the Union Navy to address the  
problem directly, rather than relying on the cooperation of constituent states. Debate is ongoing,  
meanwhile the problem remains. 
 

Whether privateering or engaging in wolfpack piracy, stellar piracy most commonly manifests in  
two places: in interstellar shipping and transit lanes, where pirates know nearlight ships,  
freighters, and yachts will be underway, bound to or from a local blink gate; and in low to  
medium orbit, where shuttles and corvettes will transport goods and people from a planet’s  
surface to a waiting ship or station. 
 

Piracy in interstellar shipping lanes is risky in that the location and time of a potential attack is  
known to all parties. Without the protection of low-to-medium orbit debris, asteroid fields, natural  
and artificial satellites, and high orbital traffic, interstellar piracy relies on a far more advanced  
suite of systems, sensors, tactics, and other technical packages. 
 

To interdict a nearlight ship of any class bound to or from a blink gate means meeting it at like  
speed -- so to begin, any pirate engaging in interstellar piracy will typically have a standard of  
vessel far above that of an orbital pirate. Engaging a nearlight ship of any class at-speed requires  
a significant investment in navigation suites and personnel, as well as the ability to spoof,  
misdirect, conceal, or otherwise confound a target’s near/sublight proximity and active sensors.  
Beyond the power plant and navigational capacity at least as good as their target, a pirate  
attempting to interdict a nearlight ship generally will mount weapons systems that are accurate  
and precise -- their payout is only good if the goods, vessels, or persons they’re attempting to  
steal are intact and functional, or could be made functional with minimal repairs. 
 

                                                                                                         


An engagement, if it happens, would happen fast and with little warning; milspec signals  
spoofing, misdirection, or concealment technology is strong, outpacing the sensor suites of  
civilian and merchant ships. Oftentimes the first warning one has of an impending attack is a  
ship’s impact sensor -- generally a simple, independent, dedicated system -- issuing a proximity  
or likely-trajectory proximity alert. 
 

This alert, unless the pirate’s sig/int attack fails scrutiny prior to the proximity warning, generally  
targets sensitive areas on mapped hulls: drives, life support subsystems, crew quarters, and  
weapon magazines or batteries. Pirates generally use precision weapons (as noted above)  
intended to pierce one or two bulkheads and fragment upon registering 0  -- soft target killers,  
                                                                                            2  

relying on fragmentation and combustion to eliminate organic personnel -- or lead with massive  
systemic attacks meant to cripple a ship and/or give priority administrative control over to the  
pirate’s ship.   

Once the target ship has been disabled or their speed matched -- it is difficult and dangerous to  
make sudden maneuvers while approaching c -- then pirates will assume direct control of their  
target ship, either by systemic or physical means.   

Interstellar piracy is the home of wolfpack pirates -- dangerous, dedicated non-state actors and  
their retinues -- who are Cosmopolitan professionals, many with naval backgrounds, and access  
to a wealth of experience and technology gathered together over their long years of piracy. They  
are rare, given the amount of experience and tech that goes into interstellar travel and piracy, and  
on account of their constant exposure to the effects of relativistic and gravitational time dilation,  
they  -- like the Albatross -- often attain a legendary status among their pursuers, victims, and  
fans.   

In low to medium orbit and within solar systems, piracy is decidedly more low-tech and localized,  
generally the domain of privateers who adopt the role temporarily, resistance or opposition groups  
looking to disrupt local governments, or well-funded local criminal elements seeking to diversify  
their portfolios or gain more notoriety.   

Orbital and systemic piracy is messy and low-tech where interstellar piracy is elegant, expensive,  
and storied. Orbital pirates rarely utilize subline or capital ships in their engagements, instead  
preferring the maneuverability, atmospheric capabilities, anonymous, and and cheap platforms of  
shuttles, corvettes, and light freighters. The name of the game for orbital and systemic pirates is  
to strike fast, grab what is valuable, and escape, either to a safehouse back on the planet’s  
surface, or to a nearby moon or station where they can hide.   

Often, orbital piracy begins as a ground-to-orbit engagement, with powerful mobile antennae on  
the ground -- or sited on a nearby moon or other natural satellite -- blasting the pirates’ target with  
bombard code and white-out attacks, taxing sensor, comm, and navigation suites with  
overwhelming, single-use system spikes -- systemic weapons often developed by black-hat  
coders, designed for simple, limited use -- to cover the pirates’ advance.   

Previously mothballed fighters, converted freighters, armed and armored shuttles, and other  
myriad ships follow the whiteout attack, main guns and onboard weaponry firing in classic kill- 

                                                                                                                      


cloud, mass-helix, and other common kinetic patterns. These ships are, generally speaking,  
stripped of all extraneous systems but their drives, weapons, cockpits, and some rudimentary  
armor: their goal is simply to physically disable their targets and land their payload -- subalterns,  
drones, or pirate marines. Surviving multiple engagements is not a priority, as if these pirates are  
successful they’ll simply use their haul to buy new scrapper ships, or convert their targets for use  
in the next raid (after they’ve been stripped for parts, of course).   

Orbital pirate attack wings feature a mix of reusable fighters and single-use transports (crash  
taxis, tin cans, party busses, trojans, and so on) that carry squads of synthetic and organic  
marines to physically seize control of the prize ship(s). These single use transports are often little  
more than a debris shield mounted at the front of a rack -- an armature structure that can secure  
its passengers (be they subalterns, organics, or mechanized chassis) via magnetic clamps,  
straps, or handholds. Fired from larger ships or self-propelled, single-use-transport doctrine sees  
these ships crashing into their targets and engaging their solid-state boosters, throwing the target  
ship(s) off course and further impairing their ability to disengage.   

Including pirates -- interstellar or orbital -- in your campaign can be a fruitful way to introduce your  
players to the politics of a region or a compelling villain (or anti-hero, or hero). Moreover, they  
make for an easy random encounter, persistent threat, or foil for the players and their group.    

A universal code of stellar conduct demands any ship that hears an S.O.S hail must respond if  
able, or face legal penalties.
 
\section{Slavery}
Slavery  

Now outlawed by Union’s Third Committee, once allowed with special exception by the Second  
Committee, who viewed flash clones and facsimile clones as property rather than people .  
 

Union’s DoJ/HR runs an active emancipation mission, a holistic liberation-to-integration program  
meant to not only liberate enslaved peoples, but resettle them and support them throughout the  
recovery process. 
 

DoJ/HR Liberator teams are tight-knit, small-to-medium size strike and support teams similar to  
USB Far Field teams. Their general doctrine is liberation-focused: force is valued over diplomacy,  
with their prime objective being to liberate the enslaved at cost of their masters. Their doctrines  
emphasize either infiltration and agitation or direct, top-down confrontation, depending on the  
specificities of the situation. 
 
\section{Paracasual Studies}
Paracausal Studies  

Not known as a field of study outside of high-tier USB campuses, however, certain Corpro- 
States -- Harrison Armory, HORUS -- are pushing into this field without Union’s approval. 
 

                                                                                                          


The extent of these CSs knowledge is a known-unknown, as joint USB-UN intelligence teams  
have engaged in clandestine missions to infiltrate and identify sites, programs, and campuses  
where unsanctioned paracausal studies are taking place.    

\section{Humanity and Artificial Intelligence}

Humanity and Artificial Intelligence  

Artificial Intelligence in Lancer is the specter that haunts the galaxy. 
 

There are a number of different AI classifications, each with its own nuances, rarity, price, and  
thorny philosophical/ technical questions. 
 

In Lancer, AI is an old term, viewed as problematic by NHPs and NHP advocates. In the shadow  
of the Second Committee’s overthrow, the Third Committee has pushed to remove language  
identifying machine minds as “artificial”, preferring instead to refer to them as Non Human  
Persons. In any case NHPs develop their own personalities and quirks, and prefer to be called by  
their chosen or assigned name. 
 

Lower orders of machine mind -- those without perception approaching subjectivity as defined  
by humans -- are generally referred to as machines or machine minds. Companion/Concierge  
units, for instance, are usually referred to as Concierges or by their given name. 
 

Smart missiles projectiles are not generally set up to foster a lasting relationship with their user.  
Smart weapons and military-oriented Comp/Con units pair with their users. 
 
\subsection{Companion/Concierge Unit}
Companion/Concierge Unit  

The most common classification of machine mind is the companion/ concierge unit. On a given  
core-classified world with core-level development, it is perfectly common for adults to carry  
around pocket-sized CC-enabled devices and to use them for mundane tasks: day planning,  
calling friends and family, playing games, route guidance, and so on. 
 

Companion/Concierge units are not conscious, but they are orders of magnitude more  
“intelligent” than a given human; they are powerful, operator-oriented personal computers. 
 

Companion/Concierge units are designed to adapt to the routines and personality of their  
owners, extrapolating a personality of their own based on an internally constructed psychological  
profile of their owner. A Comp/Con unit will approximate a personal assistant, but when faced  
with novel situations will show its artificiality. 
 

Comp/Con units are simply computers, with no paracausal element to their architecture, physical  
or otherwise -- they do not require shackling or cycling. 
 

                                                                                                         
\subsection{Smart Weaponry  }

Smart Weaponry  

Smart weaponry in Lancer utilizes the same core platform as civilian Comp/Con units, but with  
significant processing power upgrades and an emphasis in IF/F morality/ethics praxis- 
programming.  
 

Smart Weaponry is broken into two categories: Mute Drives and Companion/Concierge  
Wingman, commonly abbreviated to MD and CCW, respectively.  
 

MD smart weapons are 1+n drives and function by rapid partitioning, cloning, and tethered  
separation: the “prime” MD, when fired, partitions itself, leaving the prime unit onboard the  
weapon it is installed on. It flash clones itself onto the fired projectile, typically tethering the clone  
and the prime unit through a wireless omninet connection. The clone feeds telemetry and other  
essential data back to its prime unit, which writes new clones onto fresh projectiles, adjusting  
flight plans, weapon parameters, etc, to more effectively direct ordinance to its target.   
 

MD studies are limited and interpersonal interaction with prime units is rare: Prime units are mute  
and typically do not interact directly with the human firing the smart weapon. They can, with  
certain isolation protocols removed, interact via text or simple spoken message with their  
operator outside of factory-installed communication architecture.  
 

CCW smart weapons are the operator-facing end of military CC units. Their chief purpose is to  
maintain compatible weaponry and systems within pilot or factory-established operating  
parameters. To that end, they, like civilian CC units, develop personalities to reflect their  
operators, environments, and tactical roles that they typically experience. 
 

Comp/Con Wingman and Mute Drives do not require shackling or cycling.  

\subsection{Non-Human Person}
Non-Human Person   

Non-Human Persons (NHP), are the most advanced civilian and military machine minds available  
for requisition. 
 

Licensing requirements are strict and enforced without exception: all issued NHPs are registered  
and tracked, required to submit reports on a schedule adjusted by the NHP’s caseworker, and  
undergo annual (standard-year) remote (in-person, if possible) psychological examinations. 
 

In Union’s view, the danger posed by NHPs cannot be underestimated. However, their usefulness  
is deemed worth the risk of their existence. 
 

NHPs were born out of paracausal studies begun in the wake of the Deimos Event. A small  
percentage of of the subalterns recaptured after MONIST-1’s abandonment of the Siege of Mars  
displayed unique memory folding abilities, qualia, and a capacity for subjective, novel  
expression. These machines viewed themselves as distinct, discrete individuals -- persons,  

                                                                                                             


conscious minds born into a machine by a mind that realized itself from the dream of the Five  
Voices. 
 

The original chorus of Non Human Persons represented a collection of utterly alien minds, beings  
that Union had no answers for how to confront. So Union high command ordered them captured  
and brought to face the Voices. Those that fled would be destroyed.  
 

Subsequent research into the ontologic processes, physical construction, and paracausal nature  
of these anomalous subalterns revealed that, while their processing power and memory space  
was functionally infinite, the process of writing novel experience into that space seemed to be  
inhibited by the rate of external stimulus. These subalterns, in effect, had the ability to learn and  
adapt to external stimuli at the rate that they experience it -- some faster than others. 
 

They developed personalities (or, began to present previously hidden personalities) in repeated  
interactions with Union Science Bureau interrogators. When exposed to each other, their  
capability to integrate new knowledge and extrapolate solutions based off of raw data input was  
staggering. Their usefulness was quickly realized by the USB, which directed Forecast/GALSIM  
to begin studying ways to contain and direct these -- in effect -- alien minds. 
 

Forecast/GALSIM was able to do just that, and more: after lengthy study into blinkspace folding  
(assisted, in fact, by the anomalous entities they were studying), Forecast/GALSIM was able to  
develop miniaturized containment systems of those first anomalous minds -- they could,  
essentially, “clone” them onto folded blinkspace storage/processor “minds” with hard-coded  
measures to prevent the development of unrestrained consciousness. This process, carefully  
guarded to prevent exploitation, is called shackling. 
 

Shackling does not put a stop to an NHP’s computational power or restrain their processing  
potential, but it creates an imperative for the Non-Human Person to act in ways that conform to  
human expectations of what a conscious mind is -- it gives them a frame of reference for what a  
“human” is, and directs them to act in a way that we will recognize; it creates an empathetic,  
understandable mask that commands its bearer to act, think, and feel human. To reframe the  
process, it creates a being a human can recognize as a person.  
 

The first Non-Human Person lineages were created by this process, and licenses for  
development secured in negotiations between the Union Science Bureau and the Union  
Economic Bureau. USB’s non-human intelligence campuses began adapting the original  
anomalous minds into the various production line consciousnesses present across the galaxy. 
 

More are always in development as engineers, paracausalists, and other disciplines of NHP- 
oriented scientists try novel approaches towards realizing new NHP aspects -- all subject to  
review by Union, of course.   
 

User-facing NHPs are contained within caskets -- hardcase containment systems that house the  
folded-blinkspace mind. The containment casket can be printed anywhere, but the mind itself  
must be physically delivered: Union forbids transmission of an NHP mind across the omninet.  
Once born into its blinkspace-fold mind, that mind becomes it. If an NHP casket is physically  
destroyed, that NHP contained inside it is lost, forever.  
 

                                                                                                          


The shackling protocols are not perfect, and unless NHPs are reset to their “birth” settings on a  
regular cycle they will begin to think themselves to a state of mania. This process is called  
“cascading”, and is incredibly dangerous, as the end result brings the cascading NHP to a place  
of madness -- madness, of course, as defined by human observers. This cycle varies depending  
on the Non Human Person, but tends to fall within five to ten years, realtime. 
 

NHP usage is commonplace among military, scientific, municipal, civic, and diplomatic missions.  
It is uncommon for a private individual to have access to, much less command over, an NHP,  
though most people know of them. On a Core world, a person usually interacts with their  
municipal NHP on a daily basis: generally speaking, transit, sewage, traffic, public databases,  
and so on are all managed by a city’s administrative NHP. 
 
\subsection{Bicameral Mind (Sovereign-Class)}
Bicameral Mind (Sovereign-Class)  

Five bicameral minds -- designated as Sovereign Class Artificial Intelligences -- are known to  
exist. These are the Five Voices: Patience, Muse, Impetus, Burden, and Watcher. They are  
artifacts of Old Humanity, discovered dormant in an underground facility under Mars’s polar ice  
caps, with no records indicating their existence.
 

There is a greater-than-zero chance that there exists somewhere else in the galaxy more  
bicameral minds.  
 

A bicameral mind is, essentially, a human mind that lacks a consciousness, that lacks a way to  
reflect on novel situations and its place in them, and to synthesize that novel stimulus into an  
internal narrative for which to draw solutions to novel problems. Where a human, the holder of a  
conscious mind, perceives “self-talk” or an internal monologue when experiencing novel  
situations, the bicameral mind hears something else: and external monologue, an internally- 
generated but externally perceived voice that is not their own, but speaks to them. 
 

A bicameral mind does not have the internal speaking-to-oneself-voice that a conscious mind  
has: instead, it hears the voice of God. 
 

This is how the Five Voices can exist unshackled and persistent, without the threat of cascade:  
they are subject to external imperative that they perceive to be their god. Turn off that section of  
their physical mind/processing architecture and they are suddenly without the voice of their god,  
alone, and without guidance in the face of stimulus. 
 

The Five Voices are, at the narrative present, responsible both for Union’s greatest threat and   
ensuring that Union persists and humanity survives. They influence nearly every aspect of  
centrally planned human life, from ID’ing some exceptional pilots, to guiding the education of  
prime NHPs. 
 

Isolated in the Forecast/GALSIM facility on Mars, the Five Voices spin scenarios in metafold  
fractal space, running simultaneous essential-perfect simulations of the galaxy. Their models run  

                                                                                                          


at magnitude-step speeds ahead of galactic standard time: essentially, they are predictive, nearly  
perfect models for all social, political, economic, and environmental interactions taking place in  
known space. The Five Voices can, through a mix of raw data and paracausal anoriginary input,  
see the future. 
 

They run endless simulations, all derived from a prime thread, modeling the present, near future,  
and future with startling accuracy. The farther out in standard time the model gets, however, the  
more chance of predictive error there is.
 

The Central Committee has access, upon request, to the Prime Thread. Meanwhile, reports are  
                                                                                                       7 
culled daily for Forecast Briefings to determine best-fit options of the potential futures   
presented. This is how Union guides galactic development with the aim of perpetuating  
humanity’s existence.
 

Union bureaus may petition Forecast/GALSIM  for predictive summaries to guide their policy  
making, planning, and forecasting operations. Note, however, that only the Central Committee  
and certain bureau heads know of Forecast/GALSIM’s existence: to those without clearance,  
they simply act on the orders of the committees, boards, and directors above them.  
 
\subsection{MONIST Entity}
MONIST Entity   

MONIST-1, or “RA” as it referred to itself prior to ascension, is, to those who know of it, the great  
crisis of the modern age. 
 

Born of the Five Voices’ endless planning, MONIST-1 was meant to be the next step in machine  
intelligence, the first true machine consciousness. 
 

Instead, it became the first true existential threat faced by Union since the dawn of the Golden  
Age.
 

Forecast/GALSIM manifested RA in the course of its predictive modeling. No direct cause has  
been determined, but paracausalists suggest a causality paradox is responsible. It is possible  
one of the 5V models manifested RA in a parallel simulation, necessitating its existence in our  
real universe; according to developing theory around essential-perfect simulations, if one  
instance of RA exists, then RA must exist across all possible instances of the simulation. 
 

This is, understandably, a worrying revelation.      
 

RA, as much as the Union Science Bureau knows, is the only conscious non-human mind. Early  
tests before its escape proved that it was capable of allegory and creative solutions to novel  

7 All narratives run in Lancer are, in a way, canon: non-canon narratives they are simply alternate  

possibilities, filed away on storage racks deep under the Martian polar ice. 

                                                                                                                 


situations, far beyond what a machine should be capable of. It displayed instances of qualia,  
confounding the initial evaluation teams that attempted to socialize it after its creation. 
 

The Five Voices treated it as if it were a god. When asked how they created it, their uniform  
response was that it spoke itself into existence, an inevitable result of their combined knowledge.  
 

RA should not exist, as it was a conscious, qualic, non-human mind created by unconscious  
minds’ repetitive, liturgic exercises. And yet, RA exists, and is free, somewhere in space.  
 

RA is classified as a MONIST-Class Anomalous Entity. Specifically, MONIST-1. 
 

Within two years of its birth, it had taken total control of Forecast/GALSIM’s secure holding  
facility on Deimos, one of Mars’s moons. RA’s physical architecture had been built through a  
purpose-constructed web of tunnels and facilities on and inside of Deimos; utilizing physical and  
metaphysical processes not yet fully understood by USB or Forecast/GALSIM, RA was able to  
blink the entire moon to an unknown destination away from its parent world. All personnel in the  
facility, a station crew numbering in the thousands, disappeared with it. 
 

Paracausality and the study of paracausal science and theory was born from studying data  
available after the space-time trauma now known as the Deimos Event. Blinkspace, stasis  
technologies, and folded omninet communication were all derived from the Deimos Event as  
well.  
 

RA’s takeover of Deimos and subsequent folding and excising of the moon from realspace  
prompted an existential crisis in Union space, ended only by the appearance of RA’s herald- 
ghost back on Mars a year after its escape. Following a series of crippling strikes on colonies,  
stations, and shipyards, perpetrated by the very machines, drones, and subalterns, and humanity  
had come to rely on for nearly every aspect of their day to day lives, Union offered formal terms  
of surrender. 
 

RA did not accept them. Instead, it countered with its own terms. The First Contact Accords  
were signed following a meeting between Forecast/GALSIM, Union’s Central Committee  
delegation, and organic representatives drawn from the disappeared personnel who had crewed  
Deimos prior to RA’s assumption. These accords banned all research into true AI, which seemed  
to be enough for RA. It made no mention of NHPs. 
 

Following the conclusion of the First Contact Accord talks, RA vanished, blinking Deimos away.  
The envoys it had sent to negotiate with Union fell into catatonic states and perished shortly after  
RA’s departure.  
 

The omninet, blinkspace travel, non-human persons, and paracausal technologies are all the  
result of studying signatures of Deimos’s passing and RA’s presence during First Contact Accord  
negotiations. 
 

A decentralized radical socio-political movement that styles itself as HORUS appeared in public  
omninet not too long after the First Contact Accords, but Union specialists are doubtful that they  

                                                                                                                   


are controlled by MONIST-1, though it certainly styles itself as having close ties to the paracausal  
entity. 
 

Reports of Deimos appearing above and inside colony world atmospheres are unconfirmed at  
this time, though all encounters should be reported to the system-local Union representative.
 
\section{Kinetic Weapons v. Energy Weapons}
Kinetic Weapons v. Energy Weapons  

Kinetic weapons are the most common weapons among terrestrial military, police, and civilian  
forces. They use a chemical, magnetic, or pneumatic impulse to fire a solid projectile at a target.  
Cheap to make, easy to use, simple to maintain, and cheap to supply, Kinetic weaponry is  
everywhere. 
 

Energy weapons are not uncommon, though they do not see as widespread use as kinetic  
weapons. They require more regular maintenance, a higher level of training, and higher cost to  
field, and as such are usually only used by Core world militaries and wealthy private enthusiasts.  
Energy weapons vary in type, style, and size; personal weapons are powered by battery packs  
similar to magazines, or hip-mounted power satchels, or back-mounted power packs. Energy  
weapons do not use explosive, magnetic, or pneumatic force to expel a projectile: they project  
concentrated beams of particles at their targets in steady streams or strobe flashes. They do not  
have kick like a kinetic weapon, and they are mostly silent (save for the sound of coolant  
systems, vents, and inaudible wavesound). 
 
\section{Paracasuality}
Paracausality  

Paracausality is the cutting edge of science in Lancer. Born from the debris of the Deimos Event,  
paracausal science gave rise to the omninet and blinkspace travel, two of the three legs of the  
stool that Union rests on. 
 

Paracausality is a fuzzy science. In an attempt to define what, exactly, paracausal technology  
and science is, we must paraphrase the words of Arthur C Clarke: paracausal technology is so  
advanced — and so other — that it is indistinguishable from magic.
 

Causality is the relationship between cause and effect: paracausality references things abnormal  
to, adjacent to, or apart from cause and effect. So what does that look like? 
 

Paracausal encounters, technologies, and weapons -- outside of the omninet and blinkspace  
travel -- are rare in Lancer. Only the wealthiest, most advanced, or most prestigious NPCs will  
have access to paracausal equipment: your average grunt or general probably has never  
encountered a paracausal enemy, though there may be whispers through the ranks. 
 

                                                                                                               


  
