\subsection{IPS-N Core Bonuses}


                                        IPS-N CORE BONUSES  

When you choose a core bonus every 3 license levels, you can pick a bonus from this list as long  
as you have at least 3 license levels in IPS-N licenses for each IPS-N bonus you have. For  
example, if you have 6 points in IPS-N licenses, you could take up to 2 bonuses. IPS-N bonuses  
are focused on increasing durability, survivability, and melee combat.
 

These bonuses apply to any mech you create each time you create it, and each can be chosen  
only once.
 

BRIAREOS frame reinforcement  
The BRIAREOS is the newest development in IPS-N’s line of near-fail frame upgrades, templates designed  

to maximize what pilots can get out of frames before the need for a reprint or catastrophic failure.  
BRIAREOS fabricates a frame that is superlight, woven throughout with Goliath Weave meshing, to  

increase the resilience of all inorganic components.   

Your mech has resistance to all damage when it has 1 or less points of structure remaining.
 

FOMORIAN frame reinforcement  

The FOMORIAN is an up-scaled version of the stock IPS-N template, following guidelines suggested by  
long-haul Cosmopolitans in need of robust micro/macro-impact protection, as well as additional brachial/ 
manipulator needs.  

Your mech goes up in size to the next increment (1/2 > 1 > 2 > 3), up to size 3 maximum. It gains  
+1 threat with melee weapons, and cannot be knocked prone, pulled, or knocked back by  
targets smaller than itself (as part of a grapple, for example).
 

GYGES frame reinforcement  

Gyges is a frame upgrade built for combat, with finely tuned stabilizers and a robust suite of targeting  
software and hardware included at-fabrication.   

Your mech gains +1 accuracy on all hull checks
 

Reinforced Frame  

The addition of redundant shock-absorption systems increases the survivability of a pilot in combat, flight,  
and kinetic situations.   

Your mech gains +6 HP
 

Sloped Plating  

A simple, common enough option among pilots with the necessary licensing, IPS-N’s armor integration  
fabrication reduces the plating coverage gaps in stock systems by a significant percentage.   

Your mech gains +1 armor, up to the maximum (+4).
 

                                                                                                                 


Titanomachy Mesh   
A doubled overlay of Goliath Weave, fabricated in identified stress points, as well as beefed-up  

specifications, dramatically improve the baseline functionality of this mech.   

1/round when you successfully ram or grapple a mech, you can make an additional ram or  
grapple action as a free action. When you knock targets back with a melee attack, you knock  
them back 1 additional space.
 

                                                                                                                     


                                                                                                                         
