\subsection{IPS-N Lancaster}

                                         IPS-N LANCASTER  

The IPS-N LANCASTER is a mil-spec variant of an older IPS-N design, modernized and streamlined for  
military/operator use. The LANCASTER features multiple redundant systems and object/environment- 

interact projectors to facilitate pinpoint accuracy when engaging with delicate systems, damaged or intact.  
Commonly piloted by sapper and engineer-designate pilots in frontline support/specialist roles. 
 

                                                   License:
 
I. Restock Drone, Cable Winch System
 
II. LANCASTER FRAME, MULE harness, Sealant Spray
 
III. Plasma Cutter, Aceso Swarm
 

                                                LANCASTER 

  HP: 6          Evasion: 8                            Speed: 6           Heat Cap: 7        Sensors: 10 

  Armor: 1       E-Defense: 8                          Size: 2            Repair Cap: 10     Tech Attack:  
                                                                                             +0 

                                                   TRAITS: 

  Redundant Systems: Other friendly mechs of the Lancaster’s choice that are adjacent to it can spend  
  the Lancaster’s repairs as if they were their own
 
  Combat Repair: The Lancaster can spend a full action and 4 repairs in combat to repair a destroyed  
  mech, returning it to 1 structure and 1 HP 

                                             SYSTEM POINTS: 8 

                                                   MOUNTS: 

  Main/Aux Mount 

                                                CORE system 

                                                                                                            


                                                      Latch Drone  

  Known colloquially as a ‘Wingman’ drone, latch drones are companion drones carried upon and  
  deployed from a chassis. Pilots are advised against developing attachments to these drones, given their  
  high casualty rate.
 

   Integrated Mount:
 
  Latch Drone  
  Auxiliary Launcher
 
   Range 8
 
   Make a grit roll vs evasion 8 and target any friendly mech in range (still take cover and line of sight into  
   account). On hit, your target can spend up to 1 repair to heal.
 

  Active (requires 1 Core Power):
 
   Supercharger
 
   Quick action
 
  You fire your drone at a friendly mech in range, where it clamps onto the target. For the rest of this  
   scene, you take 1 heat at the start of your turn, but the targeted mech gains +1 Accuracy on all attacks  
   and checks, and is immune to the impaired, jammed, Slowed, and immobilized conditions. This effect  
   ends if you or the targeted mech is stunned or shut down. While this system is active, you cannot fire  
  your drone as a weapon (using the passive of this system). 

Restock Drone   

A simple, reliable, and sturdy drone mounting a printer, a restock drone allows for limited logistic capability  
through autosalvage: the bulk of the drone is RawMat, a generalized mix of silicates and metallic materials  
meant to be processed for high-yield printing. Pilots often call restock drones a “mech snack”.    

2 SP, Limited (2)  

Drone  
As a quick action, you can set this drone down in any adjacent space. After your turn ends, the  
drone primes. Any allied mech that moves adjacent to the drone can activate it as an interaction.  
That mech can then cool 1d6 heat, reload all weapons with the loading tag, and end one  
condition affecting it. The drone is then consumed, deactivating and disintegrating.
 

Cable Winch System   

A winch system consists of a spool of nanocarbon-weave cable mounted externally, and recovery  
subroutine software uploaded onto the recovery mech’s datamind.   

1 SP  

Quick action  
As a quick action, you can attach the cables to an adjacent mech. If the mech is shut down,  
stunned, or a willing target, this action is automatically successful, otherwise it can make a hull  
check to resist this effect. Once attached, your mech and the attached mech cannot move more  
than 5 range away from each other. One mech can tow the other, but is Slowed while doing so,  
and must successfully pass a hull check to do so. Any mech can make a successful melee or  
improvised attack to remove the cables (removed on a hit, the cables have evasion 10). The  

                                                                                                                      


cables can also be attached to the environment or any object. They are 10 length when used this  
way and can take a combined size of 6 in strain if using them to climb, etc, before they break.
 

MULE harness  
The Multiple User, Light Entanglement harness is a mass-produced version of a common battlefield  
modification that allows friendly soldiers to ride along on friendly chassis. Some systems are large and  
sturdy enough to allow for smaller chassis to accompany larger chassis; these are typically employed in  
High Altitude, Low Orbit insertions to reduce radar signatures.  

2 SP, Unique  
Your mech has mounts, straps, and hard points built to carry a total number of actors whose   
total size is less than your own (so size 1 = 1 size 1 actor, two size 1/2 actors). Actors of your  
choice that are adjacent to you can spend a quick action to mount your mech. While mounting  
your mech, they occupy your mechs’s space, move when you move and benefit from light cover.  
Any area of effect attacks that target your space will also target your rider. If your mech is  
knocked prone or is destroyed, they fall off into an adjacent space. They can dismount by  
moving normally off your mech any time.  

Sealant Spray  

2 SP  
Quick Action  

This system can be used on any actor or free space within range 5 and line of sight. It has  
different effects depending on what it is used on
 
         	Hostile actor: Make a ranged attack vs the target. On hit, the target is Slowed until the  
         start of your next turn but immediately ends any Burn affecting them.
 
         	Empty space: This creates a blast 2 area around the targeted space. The area becomes  
         difficult terrain for the rest of this scene and this puts out any fires in the area.
 
         Allied actor: 	  Your target is Slowed until the start of your next turn but can immediately  
         end any Burn effecting them.
 

Plasma Cutter
 

Plasma cutters were tools first, simple blades built to toggle and sustain a plasma sheath to make cutting  
metal easier for its user. Repeated ad-hoc use of cutters as a personal defense weapon to repel pirate  

boarding actions convinced IPS-N of the need for a mil-spec variant of the civilian tool. They developed the  
Cutter, now in its second generation. The Cutter MkII is hard-lined into the mech’s power core, with a port  
to attach power packs in case of cord severance. The cutting edge can be shortened to a knife variant, but  

is most popular in its “cutlass” option, a middling length variant that allows for a balance of reach and  

maneuverability in close quarters.    
 

Auxiliary Melee
 
1 heat (self)
 
Threat 1
 
1 energy damage +1 heat + Burn 1
 
Against objects and the environment, the cutter deals 10 AP energy damage
 

                                                                                                                     


Aceso Swarm  

The IPS-N Aceso Swarm system is a useful triage measure to address scoring and minor mechanical  
damage that results from combat engagements or negative environmental interaction. Due its low  

processor demand, an Aceso Swarm can be controlled by even a comp/con unit; this allows the pilot to  
concentrate on more complex repairs or immediate threat neutralization.    

3 SP, Unique  
Drone, Quick action  
Once per round, as a quick action at any point during your turn, your mech takes 1d6 heat and  
one other mech of your choice in your sensor range can spend 1 repair to heal.   
