\subsection{IPS-N Nelson}

                                              IPS-N NELSON  

The IPS-N NELSON brings the close-quarters doctrine espoused by ISP-N to its most pure form. The  
NELSON is built to brawl in environments too volatile for firearms or when ordnance has been exhausted.  

With its functional size, the NELSON can attack fast while remaining a difficult target to track. Layers of  
fractal-fold BULWARK plating allows for ceramic-analogous carbon flaking, effectively nulling the impact of  
incoming solid-state fire by dispersing kinetic energy across a rounded hull. This null-k plating protects the  

pilot from impact trauma, allowing for sustained combat efficacy in high-trade scenarios.   

The NELSON is an iconic IPS-N chassis, known across the galaxy as the FRAME of choice for the  

Albatross, the Cosmopolitan interstellar anti-piracy agency. Their distinctive white, gold, and red livery and  
mastery of the war pike -- as well as seeming agelessness due to time dilation -- has won both the  
Albatross and the NELSON a venerated place in Diasporan lore -- and secured the Albatross an  

endorsement contract with IPS-N in perpetuity.   

                                                     License:
 
I. War Pike, Bulwark Mods
 
II. NELSON FRAME, Thermal Charge, Armor Lock System
 
III. Power knuckles, RAMJET
 

                                                    NELSON 

  HP: 8           Evasion: 10                            Speed: 5            Heat Cap: 6        Sensors: 10 

  Armor: 0        E-Defense: 8                           Size: 1             Repair Cap: 5      Tech Attack:  
                                                                                                +0 

                                                     TRAITS: 

  Momentum: After making the boost action, the next melee attack from the Nelson deals +1d6 bonus  
  damage on hit
 
  Skirmisher: After making any attack, the Nelson can move 1 in any direction. This movement doesn’t  
  provoke reactions, ignores engagement, and doesn’t count against its movement for the turn. It can’t  
  make this move if immobilized or slowed. 

                                               SYSTEM POINTS: 6 

                                                    MOUNTS: 

  Flex Mount                          Main/Aux Mount 

                                                  CORE system 

                                                                                                                


                                             Perpetual Momentum Drive 

  IPS-N’s PMD exploits fighter-tier nearlight spooling to conserve and sustain a passive .000001LS 
  charge, able to be dumped into extant boost systems at the pilot’s command. The chassis fielding this 
  system must be heavily adapted through strengthening joints, limbs, and installing a k-comp crash 
  couch to protect the pilot from sudden g force and shear. 

  Active (requires 1 Core Power): Spool up PMD 
   Protocol 
   Once activated, this system remains active until the rest of the current scene. While its active, the free 
   movement from the Nelson’s Skirmisher trait increases to 4. 

War Pike  

A War Pike is a simple weapon. A long haft, topped with a dense, slim point, meant to puncture armor.  
Derivative of a mining pylon, the modern war pike is a sturdy, balanced, and reliable weapon, perfect for a  
charge.    

Main Melee
 
Thrown 5, Threat 3, Knockback 1
 
1d6 kinetic damage
 

Bulwark Mods  

A mark of pride for IPS-N, all proprietary mech cores feature IPS-N’s QuickMod system, a modular, legacy- 
compatible system of joints, hardpoints, and internal slots that make installing upgrades simple.   

1 SP  
Your mech has extended or armored arms or legs, redundant motor systems, or is otherwise  
reinforced for harsh terrain. Your mech ignores difficult terrain.
 

Armor Lock System  

IPS-N’s Armor Lock System is a total-body modification for a mech core that provides additional chassis  
stability when pilots are faced with a situation that puts their core under greater-than-anticipated stress.   

1 SP, Unique  

2 heat (self)  
When you take the Brace reaction, you can activate this system. Until the end of your following  
turn, enemy attacks targeting you are made with 1 additional Difficulty, you can’t fail agility or hull  
checks, be knocked back, grappled, knocked prone, or moved by any external force smaller  
than size 5. You end any grapples currently affecting you.
 

Thermal Charge  

Pilots have long made this popular modification to their pikes. Now, IPS-N is offering these pilots’  
modifications as a licensed and quality-tested suite for pan-galactic printing. A pike modified with a charge  

-- often colloquially called a “Fire Pike”-- is a simple plasma projector integrated into war pike, tuned to  
project a plasma sheath over the pike’s head.  

                                                                                                                      


2 SP  
Mod  

Limited (3)  
This mod can only be applied to a melee weapon. As a free action when you hit with any melee  
attack, you may spend a charge of this system to activate the shaped charge on your weapon  
and deal +1d6 bonus explosive damage.
 

Power Knuckles  

A simple weapon system, IPS-N’s power knuckles are a popular modification for pilots of CQB mech cores.  
Whether as shaped studs, hyperdense knuckles, or a series of magnetically-accelerated micro-rams, power  

knuckles amplify the already incredible hitting power of a mech core.   

Auxiliary Melee
 
Threat 1
 
1d3+1 explosive damage
 
On a Critical Hit, your target must pass a hull check or be knocked prone
 

RAMJET  
Air. Air and momentum. There’s a threshold that veteran Nelson pilots know well, the Point of Endless  
Momentum. When you get moving fast enough, in the right atmosphere, the air itself feeds into auxiliary  
ports on the chassis, compressing, howling out like a demon’s angry scream. The Point of Endless  
Momentum is a giant’s hand on your chest and a god’s chariot under your feet and you feel like you can  
outrun light itself and there’s nothing else like it.  

3 SP, Unique
 
Protocol
 
2 heat (self)
 
Until the start of your next turn, your mech gains +2 speed when boosting and its melee attacks  
(including rams, grapples, etc) gain knock back +2. However, your mech must move its  
maximum speed each time it moves and can only move in straight lines (it can stop if it would  
collide with an obstacle or enemy, and it can change direction between movements).
 
