\subsection{IPS-N Raleigh}
                                                             
                                              IPS-N RALEIGH  

The IPS-N RALEIGH, more so than any other mech in IPS-N’s core line, is meant to meet any enemy, any  

where, in any combat scenario. The RALEIGH is an all-rounder build that trends towards the midrange. It is  
commonly outfitted with an auxiliary hand cannon for ranged capability, a massive hammer to deal with  
anything that gets close, and the iconic, chest-mounted MJOLNIR cannon.  

                                                      License:
 
I. Hand Cannon, Breaching Charges
 
II. RALEIGH FRAME, ROLAND Chamber, Bolt Thrower
 
III. UNCLE class NHP, Kinetic Hammer
 

                                                                                                                  


                                                    RALEIGH 

  HP: 10          Evasion: 8                              Speed: 4            Heat Cap: 5         Sensors: 10 

  Armor: 1        E-Defense: 8                            Size: 1             Repair Cap: 5       Tech Attack:  
                                                                                                  +0 

                                                      TRAITS: 

  Full Metal Jacket: If the Raleigh makes no attack rolls during its turn, it can re-load all weapons with  
  the loading tag at the end of its turn as a free action.
 
  Shielded Magazines: The Raleigh can still make ranged attacks if it is Jammed. 

                                               SYSTEM POINTS: 5 

                                                     MOUNTS: 

  Aux/Aux                             Flex Mount                              Heavy Mount 

                                                  FRAME system 

                                           IPS-N M35 ‘Mjolnir’ cannon  

  IPS-N’s M35 MJOLNIR cannon is a carryover from Northstar’s WATCHMAN line of defensive weapons,  
  reworked for frontline combat. The MJOLNIR is a hard-mount, multi-barrel auxiliary cannon that uses  
  magnetic acceleration to fire stacks of airburst projectiles at its target. It is an impulse weapon, a system  
  tied to a pilot’s second-tier neural processes as dictated and coached by their partner Comp/Con or  
  NHP; even in death, a pilot’s MJOLNIR will continue to identify and attack hostile targets until total  
  systemic failure. For this reason, the MJOLNIR is often referred to as a deadgun, one of many such  
  weapons common among CQB-oriented pilots.        

  Integrated Mount:
 
  M35
 
  Main CQB
 
  Range 5, Threat 3
 
  4 kinetic damage
 

  Active (Requires 1 Core Power):
 
  Thunder God
 
  Protocol
 
  Until the end of the current challenge, if you didn’t fire your M35 on your turn, it gains 2 more rounds in  
  the chamber at the end your turn (you can use a d6 to track this). It starts with 0 rounds in the chamber.  
  When you next fire the weapon, it fires all chambers, for 4 damage per chamber. The M35 has six  
  chambers, for a maximum of 24 damage. If 4 or more chambers are fired at once, this weapon gains  
  the AP tag and any target struck must pass a hull check or be knocked prone. 

Hand Cannon  

                                                                                                                 


The IPS-N HAND CANNON is a licensed version of GMS’s Pattern I Pistol, chambered for a heavier caliber  
of round. This modification requires a change from the belt-fed system of the P1P to a magazine-based  
system, limiting the number of rounds that a mech can load at a time.   

Auxiliary CQB
 
Loading, Reliable 1
 
Range 5, Threat 3
 
1d6 damage
 

Breaching Charge  
A breach/blast charge is simply a shaped, milspec pattern of IPS-N’s generalist/civilian blasting charge,  

meant to crack asteroids. The IPS-N BB features a far more pure blend of high explosives designed to  
cause massive traumatic damage to mechs and other hardened structures.   

2 SP, Limited (2)  
Grenade, Mine  
If thrown as a quick action, the charge explodes on impact. If planted as a mine, it can be  
detonated as another quick action by whoever planted it (or detonates normally when a target  
moves adjacent). The charge deals 2d6 Energy damage to targets in a burst 1 area around the  
charge. Targets can pass an agility check to reduce this damage by half. Against objects, this  
charge does 10 AP kinetic damage.  

ROLAND Chamber  
Packed into sealed, self-contained cylinders, IPS-N’s ROLAND rounds are heavy shells purpose-built for  
any kinetic weapon that can accept cylindrical magazines. Packed with a non-O2 dependent accelerant,  
ROLAND Chambers can be used to reliably send air-or-impact burst shells downrange.   

For use in outdoor or Certain-Kill environments; use extreme caution when firing in pressurized spaces.  

2 SP, Unique  
When you reload, your very next attack deals +1d6 bonus damage as explosive damage and  
targets affected by this bonus damage must pass a hull check with 1 difficulty or be knocked  
prone.
 

Bolt Thrower  
IPS-N’s bolt thrower is a milspec variant of a civilian mining tool. A bolt thrower fires self-propelled  

explosive bolts that can be triggered manually, on a timer, on impact, on designated-depth penetration, on  
proximity, on on some combination of any allowable parameter.   

Heavy Rifle
 
Loading, Range 8
 
Reliable 2
 
2d6 kinetic + 1d6 explosive damage
 

UNCLE-class NHP  

                                                                                                                  


IPS-N’s UNCLE NHP is the result of the DARKSTAR Program, an NHP think tank funded by IPS-N’s  
Administrator Partnership. UNCLE is a pocket-AI, meant to be bound to a weapon system and assist its  
owner in peak-efficiency operation. UNCLE AI’s are currently available only as a beta system and, as such,  

owners are expected to accept all pushed updates; IPS-N waives culpability for any sub-optimal  
performance of UNCLE systems not kept current via Omninet updater.   
UNCLE NHPs are (perhaps unfairly) regarded as lesser compared to their compatriots and their inferiority  

complexes tend to display themselves as unstable personalities.  

3 SP, Unique  
Mod  
Choose 1 weapon - The weapon and its associate systems gain an NHP that has control over  
that specific weapon. This is not a full AI and can’t control your mech or become unshackled  
(and doesn’t have the AI tag).
 

It can attack by itself once on your turn as a free action, using the mech’s attack bonuses but  
with +2 Difficulty. It can’t fire a weapon that has already been fired this turn, and if you fire a  
weapon with UNCLE you cannot use it until the start of your next turn.
 

Kinetic Hammer  
A Kinetic Hammer is, in the trend of IPS-N weapons, a simple tool. A supermassive, shaped head fused to  

a long haft, the Hammer impacts with enough force to create massively traumatic pressure waves upon  
landing a successful blow.   

Heavy Melee
 
Reliable 3
 
Threat 1
 
2d6+2 kinetic damage  

                         