\subsection{SSC Core Bonuses}

                                         SSC CORE BONUSES  
When you choose a core bonus every 3 license levels, you can pick a bonus from this list as long  
as you have at least 3 license levels in SSC licenses for each SSC bonus you have. For example,  
if you have 6 points in SSC licenses, you could take up to 2 bonuses. SSC bonuses are focused  
on increasing speed, evasion, and ranged combat.
 

FULL SUBJECTIVITY SYNC  

By creating a strong, stable, and secure biased two-way ontologic bridge, SSC has removed the need for a  
pilot to rely primarily on physical controls to crew their mech. With a full subjectivity sync installed, pilots in  

their chassis perceive the mech to be their own body, and can control it with no input lag. Dissociation  
remains a concern, however, and SSC engineers do not recommend extended periods of sync without  

proper desync and cooldown.   

Your mech gains +2 evasion. You control the mech with no separation between your subjectivity  
and your input; a second set of physical controls are built in to a retractable panel. 
 

GHOSTWEAVE  

A scaling up of the same systems found in SSC’s Mythimna panoply, Ghostweave is the name of a  
proprietary applique that licensed pilots use to better camouflage their mechs to any environment.   

Your mech is invisible during your turn (from the start until the end of your turn). If you do nothing  
on your turn except move, hide, or boost (no other actions), keep this invisibility until the start of  
your next turn. It breaks if you take a reaction.
 

INTEGRATED NERVEWEAVE  

Like the pilot-tier system, integrated nerveweave relies on dual technologies to grant a pilot total battlefield  
alacrity. Mech-tier integrated nerveweave assures a pilot will never be left behind.   

Your mech gains +2 speed when boosting.
 

KAI BIOPLATING  
Adapted from SSC home system-local fauna, Kai Bioplating adds a lamellar layer of insulated, anchored,  

chitinous plating over key brush-points on a mech. Essentially a cheaper, feasible version of living metal,  
bioplating guards sensitive systems from minor impacts that would otherwise lead to maintenance during  

downtime.   

You gain +1 accuracy on all agility checks
 

NEURO-LINKED TARGETING  

To further shrink the information gap between pilots and the machines the crew, SSC developed a stable,  
non-invasive, limited-transfer ontologic bridging system that all pilots of sufficient license could use. Neuro- 
linked targeting is a common “ability” employed by pilots who use this system, a simple protocol that  

brings them closer to feeling rather than thinking -- a more natural expression of pilot ability.     

                                                                                                                  


All ranged weapons your mech mounts gain +3 range.
 

SSC ALL-THEATER MOVEMENT SUITE  

A popular SSC modification, the AT-MS adds a stock system of short-cycle impulse drives that dramatically  
improve a chassis’ mobility.   

Your mech can fly when it moves or boosts. Generate 1 heat at the end of any turn it flies.
 
