\subsection{SSC Swallowtail}

                                                           
                                          SSC SWALLOWTAIL  

The SWALLOWTAIL platform is Smith-Shimano’s primary long range/long term scouting platform,  
built for rapid and sustained ranging across hostile, volatile environments.   

                                                     License:
 

                                                                                                                


I. Markerlight, Scout Drone Nexus
 
II. SWALLOWTAIL FRAME,  Oracle light machine gun, Low Profile
 
III. ATHENA-class NHP, Cloaking Field
 

                                                SWALLOWTAIL 

  HP: 6           Evasion: 10                            Speed: 6            Heat Cap: 6         Sensors: 20 

  Armor: 0        E-Defense: 10                          Size: 1             Repair Cap: 3       Tech Attack:  
                                                                                                 +1 

                                                      TRAITS: 

  Integrated Cloak: If the Swallowtail doesn’t move during its turn, it becomes invisible at the end of its  
  turn. This invisibility immediately breaks if it moves, attacks, takes a reaction, or starts its next turn.
 
  Prophetic Scanners: Targets suffering from Lock On from the swallowtail are also Shredded 

                                               SYSTEM POINTS: 6 

                                                     MOUNTS: 

  Aux/Aux                                                 Flex Mount 

                                                   CORE system 

                                          Cloudscout TACSIM Swarms  

  Cloudscout TACSIM Swarms are packets of networked microsensors, launched in nonlethal mortar  
  canisters that detonate high above the battlefield. Once seeded in such a way, the TACSIM program the  
  cloudscouts create begin to run brevity cycles: tight, contained simulations of tactical possibility.  
  Probability results are then fed to the pilot’s NHP, who in turn feeds it to the pilot and their networked  
  squad members, ensuring high-probability successful outcomes.       

  Active (Requires 1 core power): Prophetic Interjection  
  Until the end of the current challenge, once per round, as a reaction when an allied target you can see  
  is damaged by another target you can see, you can make a systems check. On success, the attack  
  hitting was actually a simulation that your mech predicted. Your ally gains resistance to all the damage  
  from that attack, and your ally can move 3 in any direction to where they ‘actually’ were. This  
  movement does not provoke reactions and ignores engagement. 

Scout Drone Nexus  
The scout drone is a small, active-camouflaged mini-drone launched from a mounted LOTUS projector.  

The LOTUS projector fires scout drones at subsonic speeds in bursts of ten, blanketing a wide area with  
the single-use drones in order to relay information about terrain and targets within.    

2 SP
 
Drone, Quick Action
 

                                                                                                                 


Sensor Range
 
When you use this system, you can deploy your drone to an area in sensor range and line of  
sight. The drone then emits a burst 2 area around it that grants the following benefits:
 
  - Gain perfect vision of that area
 
  - Hostile targets that end their turn in the area immediately lose invisibility or hiding.
 
  - Reveal current HP, Evasion, E-defense, and heat levels of targets in that area
 
The drone can be attacked and targeted as normal, but it is also permanently invisible. It can be  
recalled or redeployed by taking this action again.
 

Markerlight  
Main Rifle
 
1 SP
 
Range 20
 

This weapon deals no damage and cannot deal damage (from talents or otherwise) or take  
weapon mods, but on hit, it inflicts Lock On on your target at the end of your turn.
 

ORACLE Light machine gun  
Auxiliary Rifle
 
1 SP, Arcing, Accurate
 
Range 15
 
1d3 kinetic damage
 

Low Profile  

A hallmark of a well thought out mech platform is the ability for pilots to work with their technicians to  

adapt their stock model to the specifications of the environments they operate in. Lowering a mech’s profile  
removes extraneous protrusions, tunes any broadcast software, and masks heat signatures — all an effort  
to reduce optical and scanner signatures.   

1 SP, Unique  
Protocol  
Your mech can retract its major systems to reduce its profile. You can activate this protocol at  
the start of your turn. While active:
 
     -   Rolls to find your mech while hidden are made at +1 Difficulty
 
     -   All ranged and tech attacks against you are made at +1 Difficulty
 
     -   Your mech is Slowed and cannot make ranged, melee, or tech attacks
 

ATHENA-class NHP  

Smith-Shimano’s ATHENA is the pinnacle of total hyperspectral environmental facsimile. Through a  

combination of unfettered Omninet access, hyperspectral relays fired out from a Cloudscout TACSIM  
projector, sub-networked squadmates, and active/hostile intrusion protocols, ATHENA bootstraps a near- 
flawless reconstruction of the immediate environment around its host core. ATHENA is unparalleled in its  

processing power, and with this reconstructed environment it can provide trustworthy, accurate advising to  
pilots in need of strategic counsel.   
ATHENA clones tend to be patient, cautious, and measured in their relations with their pilots.  

                                                                                                               


   
3 SP, Unique
 
AI  

Your mech gains the AI property and gains the ATHENA protocol:
 

         ATHENA protocol  
          Quick Action
 
          Choose a blast 3 area within 1 mile of you. Your AI constructs a perfect, real-time, 3d  
          model of this are that you can rotate and interact with, including actors that move in and  
          out of that area, and extreme detail. You can re-target or move this area by taking this  
          quick action again. It lasts until the end of the current scene (or about 10 minutes in  
          narrative time).
 

         Your mech gains perfect vision of this area and can relay this to allies, letting any attacks  
         from yourself or allies in the area ignore cover. Hostile targets that end their turn in this  
          area lose invisibility or hiding, and you can see the current heat and HP levels of all  
         targets in the area.
 

Cloaking Field  

SSC’s milspec cloaking field is the result of extensive experimentation in cooling and light-reflecting  
technology. Born from a need to bounce harmful radiation away from ships and EVA modules in deep  

space, the SSC-MILSPEC LIGHTBEND/OVERCLOAK is a system often equipped by ranger and long-patrol  
scout pilots to ensure not only radiation protection, but optical concealment as well. The light and  
radiation-bending properties of the LB/OC conceals anything inside of its projected bubble from sensor  

suites and optical spotting.   

4 SP  

2 heat (self)  
Quick Action
 
You can activate or deactivate the light bending properties of this module as a quick action. It  
lasts until the end your next turn. When you activate this module, your mech and all allied targets  
within a burst 3 area centered on you become invisible while they remain in the area. This area  
moves when you move, and remains centered on you. If you become stunned, shut down, or  
take damage, this module immediately becomes inactive.
 