\subsection{IPS-N Blackbeard}

                                         IPS-N BLACKBEARD 
 

The IPS-N BLACKBEARD is IPS-N’s solution for an aggressive, front-facing, preemptive anti-piracy  
platform. The BLACKBEARD license range is built for environments where combustible kinetic weaponry is  

either useless, too dangerous, or would prompt unnecessary collateral damage. Its distinctive, slim frame is  
a evocative of its speed and reduces its radar profile, making it hard to track and harder still to hit. The  
BLACKBEARD platform has been split into two model lines, the IPS-N/BB-L, which is the standard  

production line model, and the IPS-N/BB-Sk, a prototype limited print run of BB models purpose-built to  
contain IPS-N’s SEKHMET NHP platform. 
 
                                                     License:
 
I. Synthetic Muscle Netting, Chain Axe
 
II. BLACKBEARD FRAME, Flechette Launcher, Nanocarbon Sword
 
III. Reinforced Grapples, SEKHMET class NHP
 

                                                BLACKBEARD 

  HP: 12          Evasion: 8                             Speed: 5            Heat Cap: 4        Sensors: 5 

  Armor: 1        E-Defense: 6                           Size: 1             Repair Cap: 4      Tech Attack: -2 

                                                     TRAITS: 

  Cable Grapple: The Blackbeard can initiate grapples up to range 5 away. If it successfully grapples its  
  target, the Blackbeard is immediately pulled adjacent to its target by the straightest path possible (if it  
  can’t move adjacent to its target, the grapple breaks).
 
  Lock/Kill Subsystem: The Blackbeard can boost and take reactions while grappling.
 
  Exposed reactor: The Blackbeard gets +1 Difficulty on engineering checks 

                                               SYSTEM POINTS: 5 

                                                     MOUNTS: 

  Flex mount                          Main Mount                             Heavy Mount 

                                                  FRAME system 

                                                                                                                


                                                   Assault Grapples  
   The IPS-N branded assault grappling system is a proven, class-leading system rated to handle hauling,  
  supporting, and securing chassis up to Galactic Standard Size 4. Grapple heads are interchangeable  
  and can be swapped for hard or soft targets, electrified, or loaded with codespike systems to  
  incapacitate targets at a distance. 
 

  Active (Requires 1 Core Power): Omni-harpoon  
   Quick Action
 
  This one-shot system fires harpoon-like grapples at any number of targets within line of sight and within  
   range 5. Those targets must pass a hull check with 1 difficulty or be knocked prone and pulled adjacent  
  to your mech, or as far as possible towards your mech without being obstructed. All targets are then  
   immobilized until the end of your next turn 

Synthetic Muscle Netting  

IPS-N’s proprietary Synthetic Muscle Netting is a field-proven augmentation compatible with existing IPS-N  

FRAMEs. A spray-on catalytic/structural enhancement, the SMN system boosts manipulator and  
propulsion subsystems by roughly 25% without impacting the operational life of augmented components.  
The spray-on catalytic also acts as a mild impact-absorption and thermal insulation layer; IPS-N  

recommends pilots only apply the SMN system to interior components and practice frequent cleaning to  
prevent septic-analogous decay.    

2 SP, Unique  
When grappling or ramming, you always count as the same size as your opponent if your  
opponent is larger than you, and larger than your opponent if they are the same size or smaller.  
Your lifting and dragging capacity doubles.
 

Chain Axe  

A simple tactical scale-up of a felling axe, IPS-N’s chain axe is a serrated, powered chainblade hardlinked  
to a chassis’ power core. The teeth of the IPS-N chain axe are tungsten-tipped, hardened to chew through  

hard and soft targets both. It is an effective weapon and utility tool, and is often used by boarding parties to  
make initial breaches in ship and station bulkheads.   

Main Melee
 
Threat 1
 
Reliable 2
 
1d6 damage
 
On a critical hit, your target is Shredded until the end of your current turn
 

Nanocarbon Sword  

IPS-N’s nanocarbon sword is a new spin on an old essential. Embedded nanosensors along the length of  

the blade capture a full spectrum of data while in use, recording to cloud-based Omninet storage banks for  
after-action review. Live feedback is relayed to the user, interpreted by their equipped sensor suite, and  
real-time adjustments are made to the molecular composition of the blade edge.  

Heavy Melee
 

                                                                                                                      


Reliable 3
 
Threat 2
 
1d6+4 kinetic damage
 

Flechette Launcher  
The IPS-N Flechette Launcher utilizes a hive-analogous construction to project a total soft target kill zone in  

a dome around the user, denying personnel the opportunity to engage in aggressive infantry-tier actions.   

Auxiliary CQB
 
Burst 1
 
1 Kinetic Damage
 
This weapon deals 3 damage instead of 1 against grappled targets or targets with the biological  
tag.
 

Reinforced Grapples  
2 SP  
Grapple movement: Once a turn, your mech can use this grapple when it makes a regular move,  
allowing it to Fly as long as it moves in a straight line and there is a clear path. It must end its  
move on an object or surface or fall, but can grab on to that surface (even vertical or overhanging)  
as long as it remains immobile. If it’s knocked prone or knocked back while grabbing onto a  
surface this way, it falls.  
Drag Down: These grapples can also be used to target another actor within range 5 as a quick  
action. Make a contested hull check with your target. The loser is knocked prone.
 

SEKHMET-class NHP  

The IPS-N SEKHMET Co-pilot is ready to be your First Mate! SEKHMET comes standard with remote,  
Omninet, IR tag, and voice control systems and is fully versed in all current and legacy IPS-N mech cores.  

Your own SEKHMET system will learn with you, and should the worst happen, will continue as you would,  
running an emulated neural net doppelgänger to control your IPS-N chassis until forced or voluntary  

shutdown.   

SEKHMET-class systems tend to have aggressive attitudes and dark sense of humor; pilots often like to call  

them a berserker system, a dangerous NHP that values combat efficacy over its pilot’s well being.  

3 SP, Unique  
AI  
Your mech gains the AI property. In addition, gain the SEKHMET protocol:
 

SEKHMET protocol  
Protocol
 
        • All melee Critical Hits do an additional +1d6 bonus damage  
        •  You can make a skirmish action using only melee weapons as a Free Action at any point  
          during your turn.
 

                                                                                                                  


While active, you lose direct control of your mech. Your mech uses all available actions and  
movement to first attempt to get into melee range of the closest target (friend or foe!) and then  
attack them using all weapons. If your mech isn’t in melee range of a target, it attempts to use all  
actions to get into melee range, even if it could still fire a ranged weapon using those actions.  
You can decide to overcharge your mech or not, but if you do, it uses the overcharge action for  
the same purposes.
 

To end this protocol, you must pass a successful engineering check at the start of your turn.  
Otherwise, this protocol will continue until your mech is destroyed. Death or incapacitation of the  
pilot will not stop it.
 