\subsection{IPS-N Pilot Gear}

                                                IPS-N Pilot Gear  

  Name                     Tags                                      Range            Damage                   Rarity 

  “Peacekeeper” R35        Limited (4), Sidearm                      3                2 explosive              1 

 Hackiron                  Reliable 1, Inaccurate                   Threat 1          3 kinetic                2 

 Ripjack                   -                                        Threat 1,         2 kinetic                3 
                                                                    Thrown 4 

 Siege Hammer              Loading, AP, *                           Threat 1          4 kinetic                3 

 Prism Gun                 Inaccurate                                Cone 3           2 energy                 4 

                                                     Pilot Weapons  

*See Entry
 

Hackiron  
This blade uses an ultra-dense carbon polymer to magnify the brute strength from hard suits to crude but  

brutal effect. Made popular by security forces and pirates both, the hackiron-type saw sword was put into  
heavy use in early micro/null gravity melee combat where mass is not always a necessary consideration,  
gravity can fluctuate, and it is likely that any combat will be powered combat.  

A pilot must be wearing armor with the armor tag to even wield this weapon  

“Peacekeeper” R35  
IPS-N’s Peacekeeper model R35 is a popular option from their ARGONAUT line of luxury/collector goods.  

Handcrafted by IPS-N gunsmith artisans, the Peacekeeper model R35 is fashioned after ancient pre- 
collapse frontier weaponry: functional, reliable, and simple in its action, the P-R35 hides its expertly crafted  
interior elements under its simple matte finish. It is a statement weapon, functional, that can be chambered  

for heavy slugs, self-propelled microrockets, or single-core hotshots.  

Prism Gun  

A common secondary weapon found among stellar security forces and pirates, a prism gun is a shotgun  
analog, a blend between the kinetic and the exotic that projects a superheated blast of synthetic-crystalline  
nanoflechettes when fired. Ineffective against hardened targets, it is nevertheless a popular choice as a  

finishing option should a hardened targets external armor be breached; when fired into compartments,  
between armor joints, or into confined spaces with soft targets, the prism gun is a terribly deadly weapon.   

Ripjack  
Another standardized utility weapon born from early micro/null-grav combat, ripjacks are employed both as  
a last-result method of locomotion and a distance-closing utility weapon. Offered both as a handheld  

launcher and an integrated hardsuit system, the ripjacks are fired using gaussian acceleration to create as  
light a Newtonian feedback as possible when used in null-grav.     

                                                                                                                       


The ripjack can be used as a Thrown 4 weapon against a human sized, non-mech target in range,  
immobilizing them on hit instead of dealing damage until the end of next round. It can also be used as a  

regular grappling hook.
 

Siege Hammer  

When faced with sealed bulkheads in O   rich environments, boarding teams needed a way to tear down  
                                             2  

doors without potentially catastrophic explosions -- enter the siege hammer, or Nutcracker, as it became  
known to forces that employed it. Requiring two hands to wield effectively, and held like a battering ram, it  

cocks and primes a superheated cylinder of ultra-hard alloy that fires on activation to punch through even  
the thickest armor.  

While wielding this weapon, your pilot cannot take the boost action.
 

                                                 Clothing and Armor  

 Name                                  Tags          Bonuses                        Armor     Evasion/      Sp     Rarit 
                                                                                              E-            d      y 
                                                                                              defense 

 Combat Webbing                        Upgrade       Bonus weapon                    -        -             -      1 

  WAYLAND Mobile Cuirass               Armor         +3 HP, Increased Mobility      0         10/10         4      2 

 DURENDAL Mobile Cuirass               Armor         +3 HP, Unarmed attack          1         8/8           4      2 

 CALADBOLG Mobile Cuirass              Armor         +5 HP                          2         7/7           3      4 

 Goliath Weave                         Upgrade       Bonus HP, increased            -         -             -      3 
                                                    strength 

*See Entry
 

CALADBOLG Mobile Cuirass  

The CALADBOLG-MC is a heavy tactical hardsuit, with plated armor coverings, an integrated powered  
exoskeleton, and hardpoints for systems, integrated weapons, external power sources, and high-fidelity  
chassis links; it is fully sealed, modular, and hardened from radiation and other HAZMAT threats. The  

CALADBOLG-MC boasts one of the highest survival rates of all hardsuits in the field and is known for its  
reliability and durability. No fancy tricks with this one, the CALADBOLG is heavy, simple, and does its job.     

Combat Webbing  
A series of straps and combat gear that allows the wearer to bring an extra weapon into battle past the 1-2  

normally allowed. If you like pouches, this one’s for you. 
 

DURENDAL Mobile Cuirass  

IPS-N’s DURENDAL-MC hardsuit is a popular choice for frontline marines, security forces, and mercenaries  
who expect to see high-fragmentation, high-kinetic combat. Built on top of a base, sealed suit of mixed  
anti-ballistic weave and insulated cordage, the DURENDAL features sloped core and dorsal plating, leg and  

                                                                                                                       


groin plating, brachial plating with mounts for integrated systems and weapons, compatibility with any IPS- 
N helm, and total powered-system integration. the DURENDAL is IPS-N’s signature frontline hardsuit, and  
through its modularity it is well-suited to space and terrestrial movement.        

Even while unarmed, a pilot wearing a Durendal counts as having a sidearm (1 kinetic damage, sidearm,  
range 3) and a light melee weapon (1 kinetic damage, sidearm, threat 1). They don’t count against  

weapons a pilot can take with them on a mission.
 

Goliath weave  

Goliath Weave is an innovative new approach to the standard IPS-N exoskeleton. A product of IPS-N’s R\&D  
campus on Vela, Goliath Weave is a woven, miniaturized, fiber-adjacent mesh augmentation that can be  
layered over extant structures in order to boost physical durability and strength.  

A pilot must be wearing armor to benefit from this enhancement. While wearing this armor, a pilot gains +3  
HP. They can lift, drag, or push items other than mechs up to size 1.
 

WAYLAND Mobile Cuirass  
The WAYLAND-MC builds off of IPS-N’s DURENDAL platform, stripping some of the integrated weapons  

and systems and replacing them with a system of integrated grapples and an impulse pack, which allows  
for limited periods of thrust-assisted mobility.   

The WAYLAND-MC has an integrated grapple system and short-burst jetpack, allowing a pilot to fly their  
speed when they take the boost action (the pilot must land by the end of their turn or fall). The grapple has  
a range of 4 and can also be used to cling to walls, snag on to items, etc.
 

                                                      Miscellaneous 

  Name                          Tags         Description                                                            Rarity 

  K-Cal Wafer                   Upgrade      Provides a full day’s worth of sustenance in compact form.             1 
                                             Nobody can vouch for the taste. 

  Null-Rad Caps                 Upgrade     Anti-radiation medication for extended interstellar trips. If           1 
                                            taken in concentrated form, a pilot can pass through areas  
                                             of high or even deadly radiation for around an hour, with  
                                             relative safety. 

  Lifesaver                     Upgrade     A personal transponder and vacuum movement device, in                   1 
                                             case you get spaced. The lifesaver compacts to a tiny  
                                             pack that can be strapped on the body, provides good  
                                             EVA movement, and once deployed has power for several  
                                             days. 

  Vascular Stabilizers          Gear        A custom drug cocktail that helps the human body deal                   2 
                                            with combat-rated gee forces; ensures blood movement to  
                                             brain, mixed with a suite of anti-nausea and anti-fatigue  
                                             drugs. When you take them, until the end of the current  
                                             challenge, you can re-roll any Down and Out check you  
                                             make, though you must choose the second result. 

                                                                                                                          


*See Entry
 
