\subsection{IPS-N Vlad}
                                                                 
                                                     IPS-N VLAD  

The IPS-N VLAD is a variant of the IPS-N NELSON, built to handle hardened targets that would present  

strategic difficulty for the NELSON platform. The VLAD features a suite of myth-inspired weaponry and  
heavy armor and is meant to take a frontline role, absorbing fire from dangerous targets in order to protect  
its allies while lining up the perfect shot.   

                                                                                                                          


                                                      License:
 
I. Snare Trap, Impact Lance
 
II. VLAD FRAME, Nail Gun, Caltrop Launcher
 
III. Combat Drill, Charged Stake
 

                                                       VLAD 

  HP: 10          Evasion: 8                              Speed: 4            Heat Cap: 4         Sensors: 5 

  Armor: 2        E-Defense: 8                            Size: 1             Repair Cap: 4       Tech Attack:  
                                                                                                  +0 

                                                      TRAITS: 

  Dismemberment: When the Vlad successfully immobilizes a target, that target is also Shredded for the  
  same duration
 
  Shrike Armor: When the Vlad is attacked by any actor within range 3, the attacker takes 1 AP kinetic  
  damage before they attack 

                                                SYSTEM POINTS: 5 

                                                      MOUNTS: 

  Flex Mount                          Main Mount                               Heavy Mount 

                                                   CORE system 

                                                    Shrike Armor 
  A nod to the pre-Fall namesake of the VLAD, Shrike armor plating bristles with shaped spikes, hardened 
  with chromium/tungsten alloy tips. Strategic studding places Shrike tips in high-likelihood kinetic 
  encounter areas: gauntlet covers, manipulator joint covers, shoulder plating, and so on. Primarily a 
  defensive modification, Shrike armor is uncommon among Coreside pilots, and seen as a mark of 
  underdeveloped -- if terrifying - tactics. 

  Active (requires 1 Core Power): 
  Tormentor spines 
  Protocol 
  Until the end of the current challenge, you gain resistance to all damage from within range 3, and your 
  damage from this mech’s Shrike Armor trait increases to 3 AP kinetic damage. 

Snare Trap  
The IPS-N WEBJAW Explosively-Accelerated Filament system is a deployable all-theater perimeter  
defense system designed to arrest hostile movement in pre-determined kill-corridors. Deployable by hand  
or launch tube, the WEBJAW EAF system consists of a cluster of filament anchors scattered across an  
area. When triggered remotely or by a series of programmable physical, electronic, or chemical triggers, the  
anchors target and fire at the triggering foe, embedding hard-tip barbs deep inside both hard and soft  
targets. The barbs, anchored to their bases by arachnosilk-analog filament, immobilize and entangle the  
target.  

                                                                                                                  


1 SP  
Mine, Limited 1  

This trap triggers when any actor passes directly over it. The target must pass a hull check or  
take 2d6 AP kinetic damage and become immobilized. Once triggered, the trap becomes an  
object with 10 HP and 5 evasion, and immobilizes its target as long as it is not destroyed.
 

Impact Lance  
The Impact Lance is a milspec variant of a common mining tool: the single-use, proximal-distance chemical  
survey laser. IPS-N’s military variant mounts a series of Impact Lances on a brachial or thoracic carriages,  
leaving a chassis’ manipulators free to field other weapons and systems; the Lance can be wired directly  
into a chassis’ core, or charged with single-use chemical batteries.   

The lances fire for a microsecond, burning through their stored charge in a milisolar burst of light that stabs  
out in a tight, pulsed beam capable of searing through multiple meters of hardened bulkhead.  

Main Melee
 
Threat 2
 
1d6 energy damage
 
This weapon attacks in a line drawn between its target and your mech, attacking all other actors  
in between, but deals +1 heat to your mech for each target hit past the first
 

IPS-N “Impaler” Nailgun  

The milspec Nailgun utilizes non-combustible, sabot-jacketed two-stage macroflechettes to pierce even  

the most substantial of armor. First catapulted from its launcher, the macroflechette’s sabot disengages on  
approach to its target, triggering a second stage where internal propulsion drives the macroflechette  
forward with incredible velocity. Against soft targets, over-penetration is certain: IPS-N advises pilots  

employ this weapon platform only when the area behind the target is clear of allies and/or noncombatants.   

Main CQB
 
1 heat (self)
 
Range 8, Threat 3
 
1d6 kinetic damage
 
On a Critical Hit, the target of this attack must pass a hull check or be immobilized until the end  
of its next turn
 

Caltrop Launcher  
A wicked anti-organic, anti-vehicle, proximity denial system, chassis-mounted caltrops are fired in great  
clouds of shimmering metal (or deployed in long swathes) to blanket an area.   

IPS-N’s HX-CAL caltrop system adds small, shaped explosives to the mix of hardened pyramids.  

1 SP, Unique
 
Quick Action
 
When this system is activated, your mech targets a free space within range 5 and blankets a  
blast 1 area centered on that space with explosive caltrops. That area becomes difficult terrain,  

                                                                                                                     


and mechs moving across the space (voluntarily or otherwise) take 1 AP explosive damage for  
each space they move.
 

Combat Drill  

The IPS-N combat drill is a brutal close combat weapon, powered by a massive catalyst pack mounted  
externally on a mech core. The drill is tipped with micro-plasmatic projectors designed to pre-treat the  

target to ensure bit purchase and facilitate drill penetration.   

Superheavy Melee
 
Overcharged, AP
 
Threat 1
 
3d6 kinetic + 1d6 energy
 

Charged Stake
 

Built from gear meant originally for blast mining, this enormous, improvised system is loaded and cocked  
prior to embark into a specially primed chamber. It is designed to penetrate and immobilize hardened  

targets, then send powerful, vaporizing charges into its vulnerable internal systems.  

2 SP
 

Full Action  
This brutal system can be used against any adjacent target. That target must pass a hull check  
with 1 difficulty or take 2d6 energy damage damage and become immobilized and impaled. At  
the end of each of its turns, the target can repeat this check to end the effect on itself, otherwise  
it takes 3 AP energy damage and remains immobilized until it makes the check successfully. Only  
one target can be immobilized by this system at once, but it can be picked up as a quick action.
 

                                                                                                                    
