\subsection{GMS General Market Deployables}
                               GMS General Market Deployables   

GMS Pattern-A “Apple” High Explosive Grenades  

The GMS Pattern-A HEX Grenade is a pilot’s best friend in a tight spot. Inert until activation by its neuro- 

coded welder, the “Apple” is guaranteed to neutralize any hard or soft target within its effective radius.  
 

1 SP, Limited (1)  

Grenade  
Range 5, Blast 1  
Attacks all targets caught in the blast radius for 1d6 explosive damage on hit.
 

GMS Pattern-A “Jericho”  Deployable Cover  

2 SP  
Deployable, Quick Action  
Using this system creates a Line 2 section of size 1 Heavy Cover adjacent to the user (in any  
orientation, as long as there is free space). Requires a full action to pick up. Reusable. The cover  
has 5 Evasion, 40 HP, and can be targeted and destroyed. A mech can spend 1 repair during a  
rest to repair it to full HP.
 

GMS “Pancake” Anti-Vehicular Mines  

                                                                                                                  


Used primarily for area denial, the GMS AV Mine system has begun to see more offensive employment by  
GMS pilots in combat theaters.   

1 SP, Limited (2)
 
Mine
 
This mine detonates when any target moves adjacent to it for a burst 1 attack, 1d6+3 explosive  
damage. A target can pass an agility check to halve this damage.
 

GMS Pattern-A “Filter” Smoke Grenade  

The Pattern-A/SL is a cheap, reliable, and low-system-cost method of deploying effective cover in a high- 
velocity kinetic scenario. Mixed with a proprietary blend of chaff, particulates, accelerants, and defilade- 

enhancers, Pattern-A/SL smoke is effective at obscuring most all sensor suites.   

1 SP, Limited (1)  
Grenade  
Range 5, Blast 3  
The blast area grants light cover to all within, friend or foe. Lasts until the end of the user’s next  
turn, then disperses.