\subsection{GMS General Market Systems List}
                                GMS General Market Systems List  

Companion/Concierge-Class Dummy Plug  

The Companion/Concierge Class Dummy Plug conforms to galaxy wide standards for comp/con units. A  
Com/Con DP will pass even the most rigid Turing-Null classifications and is cleared for operations even  

when the pilot is not present.   

2 SP, Unique  
AI  
Your mech has a basic companion/concierge unit installed in it, gaining the AI tag. It can speak  
to you and has a personality but is not truly capable of independent thought, as a true AI would  
be. It is obedient to you alone. When you hand over the controls, it can take actions and move  
on its own prerogative when not piloted, using its stats, but has no independent initiative (it must  
take and follow commands from you, or else takes no action other than to defend itself).
 

Dummy Plugs are not true AIs and thus cannot be unshackled.
 

GMS Shield Type-I  

The GMS Shield Type-I utilizes a projected, aggressive, anti-ballistic super-positional shield to trap and  

deny incoming solid and wave-based projectiles.   
   

2 SP, Unique
 
Shield, Protocol, 1 heat (self), Unique
 

                                                                                                                       


You can choose to activate this shield protocol at the start of your turn. Nominate an enemy you  
can see. All that enemy’s ranged or melee attacks against you are made at +2 difficulty until the  
start of your next turn, but your ranged or melee attacks against them also suffer the same  
penalty.