% \subsection{SSC Monarch}

\begin{mech}{SSC}{Monarch}

\fluff{The SSC MONARCH platform is Smith-Shimano's solution for a fast, self-propelled missile/barrage battery. Able to mount ground-to-ground, ground-to-air, ground-to-space, and all-theater missile tubes and their guidance systems, the MONARCH can be adjusted to deliver any payload at any distance to any target. The MONARCH is commonly deployed in a fire-support role, though field tests of a MICROMONARCH mid/close range system is underway.}

\begin{license}
\item Sharanga missiles, Companion Gun
\item MONARCH FRAME, Stabilizer weapon mod, Gandiva Missiles
\item Pinaka Missiles, TLALOC class NHP
\end{license}

\frameBox
[hp = 8,
evasion = 8,
speed = 5,
heat cap = 6,
sensors = 15,
armor = 1,
e-defense = 8,
size = 2,
repair cap = 3,
tech attack = +0,
traits = {\textbf{Avenger Silos:} Once a round, when you score a Critical Hit with a weapon, a target different to your first target in range 10 and line of sight takes 3 explosive damage (no roll required).

\textbf{Seeking payload:} The monarch's launcher attacks against targets suffering from Lock On gain the seeking tag},
sp = 5,
mount one = flex mount,
mount two = main mount,
mount three = heavy mount,
core system name = Avenger silos,
core system text = {The SSC 30 High-pen missile system is a FRAME mounted micro missile system capable of tremendous output in combat. The MONARCH is fitted to hold upwards of 60 of these deadly miniaturized warheads at once.},
core active name = Divine Punishment,
core active text = {Active (requires 1 Core Power): Divine Punishment
Full Action
You unload your Avenger Silos. All targets of your choice on the battlefield (or a burst 50 area from your mech) must pass an agility check with 1 difficulty or take 1d6+3 explosive damage, and half on a suc- cessful save. You do not need line of sight to any targets, and the self-guiding missiles can perfectly seek any target as long as they can trace a path. Once used, you cannot benefit from the Avenger Silos trait until you take a full repair.}]

\gearBox
[name = {Sharanga Missiles},
fluff = {},
template = {\Main \Launcher\newline
\Range{15},\newline
\Arcing\newline
3 \explosive damage},
rules = {When you fire this weapon, you can choose one or two targets in range and line of sight, making attack rolls for each.}]

\gearBox
[name = {Companion Gun},
fluff = {},
template = {2 SP, \Unique},
rules={Once a round, whenever you score a Critical Hit against a target, this shoulder-mounted gun can calibrate and rapidly fires a projectile that also deals 3 explosive damage to a different target within range 10 and line of sight, no attack required.}]

\gearBox
[name = {Stabilizer weapon mod},
fluff = {A stabilizer modification is a series of modifications to physical mounts and targeting software that ensures weapons will remain level, steady, and angled at max-optimum in order to ensure positive target engagement at range.},
template={2 SP\newline
\Mod},
rules = {Choose 1 launcher or cannon weapon. Increase its base range by 5, but it gains the ordnance tag.}]

\gearBox
[name={Gandiva Missiles},
fluff = {Gandiva missiles are a reliable mainstay from Smith-Shimano's EWAR line. Like the Pinaka, the Gandiva platform is equipped with jet-assisted mid-flight repositioning systems, allowing the Gandiva to respond to changing battlefield environments with a high degree of expected successful navigation to its target. Each Gandiva missile platform comes pre-loaded with a hivemind companion/concierge class drone AI, making an equipped system capable of learning from each right-of-launch experience.},
template = {\Heavy \Launcher
\Smart, \Seeking, \Accurate
1 SP
\Range{15}
1d6+3 \energy damage}]

\gearBox
[name = {Pinaka Missiles},
fluff = {Pinaka missiles are massive, two-stage missiles mounted along the spine of a mech core or carried disassembled, to be affixed and launched from a brachial mount.  Pinaka missiles are adapted from ship-to- ship missiles, their second stage intended to be able to re-orient in flight through jet-assisted repositioning.},
template = {\Superheavy \Launcher\newline
\Arcing, \HeatSelf{2}\newline
\Range{30}, one or two \Blast{1} areas*
2d6+1 \explosive damage},
rules = {When this weapon is fired, it chooses one or two Blast 1 areas within range to attack. The areas cannot overlap.}]

\gearBox
[name = {TLALOC class NHP},
fluff = {TLALOC-Class NHP systems provide advanced multi-system targeting and co-pilot functions, taking over subroutine control to ensure persistent lock-on and engagement. With TLALOC installed and operational, a pilot can trust that their back is always covered and every possible advantage will be exploited. TLALOC clones are often stereotyped as a hasty, impetuous NHP. They are well known for having a superiority complex.},
template = {3 SP, \Unique\newline
\AI},
rules = {Your mech gains the AI property and the TLALOC protocol\newline
TLALOC protocol\newline
\Protocol
2 heat (self)

Your mech is capable of rapidly firing and re-targeting your weapons, far faster than you can think. When you activate this protocol, your mech is immobilized until the start of your next turn, but for the same duration, if you miss any weapon attack, you can immediately re-roll the attack as long as you target a different target in range or area of effect (if the attack was blast, line, or cone). You can take this re-roll only once for each attack (if the second attack misses you don't get to keep making it), and a target already hit by this attack (from a re-roll or otherwise) cannot be targeted again.}]

\end{mech}
