\subsection{SSC Death's Head}

                                         SSC DEATH’S HEAD  

The DEATH’S HEAD is Smith-Shimano’s answer to all other long range, low splash artillery mechs. By  
sacrificing hull strength for stability and alacrity, the DEATH’S HEAD manages to avoid incoming fire while  

holding a near-perfect lock through advanced maneuvers.   

                                                    License:
 
I. Hi Stress Mag Clamps, Tracking Drone
 
II. DEATH’S HEAD FRAME, Core Siphon, Vulture DMR
 
III. Kinetic Compensator, Railgun
 

                                               DEATH’S HEAD 

  HP: 8           Evasion: 10                           Speed: 5            Heat Cap: 6        Sensors: 10 

  Armor: 0        E-Defense: 8                          Size: 1             Repair Cap: 2      Tech Attack:  
                                                                                               +0 

                                                     TRAITS: 

  Neuro-linked: The Death’s Head can re-roll the very first ranged attack it makes per round. It must keep 
  the second result. 
  Perfected Targeting: The Death’s Head gets a bonus +1 to all ranged attacks (a flat +1 to the attack 
  roll) 

                                              SYSTEM POINTS: 6 

                                                    MOUNTS: 

  Main/Aux Mount                     Heavy Mount 

                                                  CORE system 

                                                                                                               


                                                 Precognitive Targeting  
  Precognition is the next step in human/AI interaction. By allowing AI data-dump and REM learning via a  
  neural bridge, a pilot can learn to read situations before they begin to develop. The nature of  
  precognition is as-yet unknown, so SSC recommends limited, monitored use of this protocol.   

  Active (requires 1 core power): Activate Neural Shunt  
   For the rest of this scene, you can take the following action:  

  Mark for Death 
  Full Action 
   Choose a target in range 30 but further away from range 5 of the Death’s Head. You concentrate on that 
  target. While concentrating, your mech cannot move or take reactions. You can stop concentrating at 
  the end of any of your turns as a free action, and can only concentrate on one target at once. 
  While concentrating on a target, as long as that target is not in cover from you or within range 5 of you, 
  your ranged attacks against the target deal +4d6 bonus damage on Critical Hit. 

Hi-stress Mag Clamps  
A simple, reliable system. When installed, it seeds toggleable electromagnets into the locomotive systems  
of a chassis. When turned on, the mag clamps allow a chassis to cling to ferrous surfaces. Of especial use  
in micro and null gravity environments.  

1 SP, Unique  
Your mech treats all vertical and overhanging surfaces as flat ground for the purposes of  
movement. You no longer count as climbing on these surfaces and can move, stand, and run at  
full speed, though if you are knocked prone you fall.
 

Tracking Drone  

A modified version of a tracer round, a tracking drone must hit its target in order to activate. Once a  
successful hit is registered, a tracking drone will feed live, surreptitious data back to its shooter across  

multiple theaters.   

1 SP
 
Quick Tech
 
Gain the following quick tech action:
 
	        Tracking Drone: Make a tech attack against a target in your sensor range. On a hit, you  
know the target’s exact location, HP, Structure, Heat, and speed, and it cannot hide or benefit  
from invisibility from you until the drone is removed from them. It takes a quick action and a  
successful engineering check from the targeted mech to remove a tracking drone.
 

Core Siphon  

By shunting some core waste-heat from dispersal systems to weapon systems, the Death’s Head can  
overclock its weapons’ targeting, catalytic, and processing systems. This comes with a trade-off, however,  

as reliance on overclocking without sufficient cooling can damage systems not built to handle the influx of  
power.   

                                                                                                                        


2 SP  
Unique  
At the beginning of your turn, you can choose to give the first attack roll of your turn +1  
Accuracy. If you do, however, any additional attack rolls until the end of your turn gain +1  
difficulty
 

Vulture DMR  

The SSC VULTURE-BR is Smith-Shimano’s core line battle rifle, chambered for 12.7x108mm HTI rounds.  

Field performance reports of the VULTURE report low TTK rates and satisfactory all-theater capability,  
though some pilots have reported fouled-fire incidents as a result of the high burst rate.   

Main Rifle
 
2 heat (self)
 
Overcharged, Accurate
 
Range 15, 1d6+1 damage
 

Kinetic Compensator
 
Another common modification, a system of electronically modulated gyroscopes and hydraulic  
compensators work in concert to absorb and disperse recoil caused by firing heavy weaponry.   

2 SP, Unique
 
When you miss with any ranged weapon attack roll, your very next ranged attack roll gains +1  
Accuracy.
 

Railgun  
A railgun is a simple, elegant weapon. With no moving parts and a magnetically-accelerated  
projectile, a railgun can be used at peak efficacy in any combat theater and is entirely self- 
contained in a disposable unit. However, power draw is massive, and it is necessary for mechs  
mounting a railgun to be fitted with a core-charged auxiliary power pack.   
   
Heavy Rifle
 
AP, Ordnance
 
Line 20
 
1d6+4 kinetic damage
 