\subsection{SSC Dusk Wing}

                                           SSC DUSK WING  

The SSC DUSK WING is built from a legacy-inspired modification package to hazardous/hardened EVA  
suits; in the early days of deep space exploration, there was a need for mechanized exoskeletons that  

provided not only amplified capacity, but plated kinetic defense. The DUSK WING is the spiritual heir of  
those early deep space suits. Fast and small, the DUSK WING mounts a complement of all-theater  

maneuverability jets that allow for perfect (or near-perfect) flight.    

                                                    License:
 
I. Veil Rifle, SSC neurospike Mk1
 
II. DUSK WING FRAME, Burst Launcher, Flicker Field
 
III. StunCrown, OASIS
 

                                                 DUSK WING 

  HP: 6           Evasion: 12                           Speed: 7            Heat Cap: 5        Sensors: 10 

  Armor: 0        E-Defense: 8                          Size: 1/2           Repair Cap: 2      Tech Attack:  
                                                                                               +1 

                                                     TRAITS: 

  Integrated Hover Flight: The Dusk Wing can hover when it moves or boosts (it can fly, doesn’t need to  
  move, it can move without going in a straight line, and doesn’t need to land). While flying, it generates 1  
  heat at the end of its turn.
 
  Harlequin Cloak: The Dusk wing is invisible during its turn. It re-appears at the end of its turn.
 
  Fragile: This mech has +1 Difficulty on Hull Checks 

                                              SYSTEM POINTS: 6 

                                                    MOUNTS: 

  Aux/Aux Mount                      Flex Mount 

                                                  CORE system 

                                                                                                               


                                                  Hall of Mirrors 
  Active (requires 1 core power): For the rest of the scene, gain the following quick action: 
  Hall of Mirrors 
  Each time your mech takes the boost action or its regular move on its turn, it leaves a holographic 
  imprint of itself behind in the space where it started. This hologram is an illusory projected object the 
  same size as your mech (it can be moved through and doesn’t actually take up any space). The 
  holograms detonate if any non-allied actor moves through or adjacent to their space, dealing 1d6 
  energy damage (an actor can pass an agility check to halve this damage). In addition, any time as a 
  quick action, you can instantly teleport to one of the hologram’s locations. Doing so detonates all 
  holograms for a burst 1 attack centered on their areas for the same effect and prevents you from 
  generating new holograms until the start of your next turn. 

Veil Rifle  
Main Rifle  
Line 10
 
1d3 energy damage
 
Allies caught in the area of this rifle do not take damage but are instead are covered in  
coruscating energy that throws off targeting systems and count as in light cover until the start of  
your next turn.
 

SSC Neurospike Mk1  
Building off SSC’s strain of dormant DHIYED viral code, the Neurospike Mk1 was the first all-theater, single- 
use spike system developed by the Exotic Materials group. N-Mk1 comes pre-packaged with a basic, but  
effective, activated DHIYED virus: when fired or otherwise implanted in a synthetic target, it pumps a  
cocktail of DHIYED virus into the codebase, altering crew outputs and onboard systems’ battlefield  
perception.    

2 SP, Unique
 
Quick Tech
 
Gain the following options for invasion:
 
         Shrike Code: Until the end of your next turn, each time your target makes an attack roll,  
         it first takes 2 heat.
 
         Mirage: Choose yourself or a friendly mech you can see. Your target’s systems relay  
         blurred, illusory images of that mech over its real image that confuse your target’s  
         systems. That friendly mech (or your mech) counts as invisible to your target until the end  
         of your next turn.
 

Burst Launcher  

Typically dorsally mounted, Burst Launchers fire rapid streams of explosive cores. These thermal spheres  

are tuned for an airburst detonation, overwhelming the target zone with rippling chain explosions that  
damage and suppress units in the area.   

Main Launcher
 
Arcing
 
Range 10
 

                                                                                                                


1d3 explosive damage
 
On a Critical Hit, a target struck by this weapon is impaired until the start of your next turn.
 

StunCrown
 

The SSC StunCrown is a simple system, a ring of WHITEOUT flash lamps in hardened mounts that can be  
triggered to fire an overwhelming burst of light. The StunCrown is usually mounted on a short post or in a  

ring around a mech’s cranial suite; due to the intense energies running through the flash bulbs, this system  
only has a limited number of uses before the lights burn out.   

2 SP, Limited (2)  
Quick action  

All hostile targets in a burst 5 area centered on your mech that can see your mech must pass an  
agility check or become Jammed, and a systems check or become Impaired. Both effects last  
until the end of your next turn. Mechs in cover from you when this system is activated are not  
affected. 
 

Flicker Field  

Flicker Fields are generated by holochaff, a blend of photoreactive slivers, mirrorchips, LEDs, and strips of  
flare-out. Fired from launchers at a pilot’s command, holochaff looks at first like a cloud of smoke: within  

moments it adapts to its surroundings and begins to project out a shattered, shifting image of the terrain  
around it, creating a distorted field that confounds both visual and systemic targeting.     

1 SP, Unique
 
When you move or boost, you project a holographic pattern around your mech that leaves  
dazzling afterimages, making it hard to discern your mech’s location. After moving or boosting  
you count as having invisibility against the very next attack roll against you. The field disperses  
after this attack, hit or miss. You can only gain the effect of this field once (you can’t ‘stack’ up  
several instances of it).
 

OASIS  

2 SP, Unique
 
Protocol
 
2 heat (self)
 
Until the start of your next turn when you move or boost you can move only in straight lines, but  
create a holographic trail behind your mech as you move. The trail lingers until the start of your  
next turn, creating a light construct 1 space high and the same length as your movement. It can  
be used for light cover by adjacent allies, and any allies that benefit from this cover also have  
resistance to energy damage.
 
