\subsection{SSC Pilot Gear}

                                                SSC Pilot Gear  

  Name                  Tags                                       Range            Damage                     Rarity 

 Implanted Gun          Sidearm, Upgrade                           2                1 kinetic                  1 

 Arc Blade              Reliable 1                                 Threat 1         2 energy                   2 

 Coldcore Sabot         Accurate, Loading, Ordnance                15               3 energy                   3 
 AA Rifle 

 Micropack              Loading                                    5, Blast 1       2 explosive                3 
 Launcher 

  Variable Sword        AP, Limited 3                              Threat 2         3 kinetic                  4 

                                                    Pilot Weapons  

*See Entry
 

Arc Blade  

This master-forged sword is threaded with fine filaments and powered either by a slim battery in its handle,  
or a long cable with a universal power adaptor that can be attached to any standardized power pack. A  
sturdy, light weapon, the charged filaments can be triggered by the sword’s user or by proximity to lash  

their enemies with an electric arc even if they do not connect.
 

Coldcore Sabot AA Rifle  

This heavy anti-armor rifle is recognisable by its long, minimalist construction and classic Smith-Shimano  
matte-black colorway. A COLDCORE sabot anti-armor rifle is a consumable-sabot energy weapon that  

uses depleted demi-coldcore units to create a superheated, precise, directed blast of plasma on its user’s  
target. After firing, it must be reloaded; COLDCORE Sabot-AA rifles can be breech-fed, box-fed, or belt- 
fed, depending on their receiver.   

Implanted Gun  
This bespoke biological weapon, integrated with its user’s circulatory, respiratory, and nerve systems, can  

be fired by a triggering thought, association, movement, or memory. Commonly installed in the arm or  
hand, it is a quiet, small weapon, a gun in name only -- it launches a spasm-propelled, fin-stabilized needle  
from a keloidal canal grown to be inserted in the bearer’s arm. With a short effective range and untraceable  

profile, it is a popular choice for assassins.  

Whenever you fire a weapon, you can fire this gun at the same or a different target. As an upgrade, this  

gun doesn’t count against weapon limits.
 

Micropack Launcher  

This heavy rifle is a drum-fed micro-rocket launcher capable of single or automatic fire. A popular choice in  
total-combat environments, the Micropack is a squad-tier support weapon usually carried by a single  
trooper or mounted on a hardsuit’s tertiary arm. SSC developed the Micropack as an all-theater weapon,  

capable of being used in vacuum, submerged, or in any atmosphere -- the Micropack uses an electronic  

                                                                                                                      


trigger to catapult its self-propelled ordinance to a minimum safe distance before the projectile ignites,  
allowing for its use in close-quarters; some skilled handlers learn to use this brief ignition period to skip the  
miniature rockets around corners in boarding actions and station combat.   

Variable Sword  
This pilot-scale variant of the popular SSC weapon is a field-sheathed length of mono-molecular wire  

completely invisible to the naked eye. Only the handle and the tip guide are visible. Coiled while not in use,  
the wire itself can be extended up to 20 feet from the handle, creating an incredibly light and extremely  
deadly weapon that cuts through nearly anything. Due to immense power usage, this weapon can only be  

unsheathed for a short period.  

                                                  Clothing and Armor  

 Name                    Tags           Bonuses                                  Armor        Evasion/     Spd     Rarity 
                                                                                              E- 
                                                                                              defense 

  “FallingWater”          Clothing      Smart, omni-net linked coat              -            -            -       1 
 Overcoat 

 Sylph                    Upgrade       Semi-biological undersuit                -            -            -       1 

 Acherontia              Armor          +3 HP, Extremely fast                    0            10/10        6      2 
 Panoply 

 Eloria Panoply          Armor          +3 HP, Flight                            0            10/10        5      3 

 Mythimna Panoply        Armor          Invisibility                             1            10/10        4      4 

 Nerveweave               Upgrade       Gain bonus speed and evasion             -            -            -      4 

*See Entry
 

Acherontia Panoply  
Named for the fine colors of the spring swift migration on Triaara I, a plains-paradise world in the SSC  

Constellation, the Acherontia Panoply is a lightweight hardsuit with minimal paneling over a tailored half- 
brigandine. Visible armored paneling is kept to a minimum, and without its helm, it is hard to tell that a pilot  
is even armored.   

Eloria Panoply  

The Eloria is the heavier cousin of the Acherontia, a plate-forward brigandine with reinforced panels and  
contrast-color ablative cuirass built for rapid aerodynamic/null gravity movement. The Eloria system  
employs a move/arrest system of impulse thrusters to ensure a pilot using the Eloria’s rapid-reposition  

capabilities always lands in the way they want. 
 

A pilot can use the integrated flight systems in this hardsuit to fly when they move or boost.
 

“FallingWater” Overcoat  
The FallingWater is a signature SSC sartorial anti-ballistic personal protective garment. Created with a  

                                                                                                                        


charged magnetorheological hydrofiber and coached by an attendant comp/con, the FallingWater pre- 
adapts to incoming threats moments before they transfer their kinetic/thermal impulse upon its wearer.   

This couture overcoat fits over any armor or clothing and is interwoven with infowebbing. It has full  
ominnet access, can display image, color, or video on its internal or external paneling, and has an  
integrated companion/concierge unit. 
 

Mythimna Panoply  
The Mythimna panoply is another light, minimalist design by SSC, built to support an anti-optic/photon  

platform that blends its user into any background environment.   

This light hardsuit has a reactive weave that allows a wearer to turn invisible. A pilot can become invisible  

as an action. The invisibility breaks if a pilot takes damage or makes an attack roll. Used outside of  
combat, it lasts about 10 minutes before it must be recharged for another 10.
 

Nerveweave  
Nerveweave blends fibers of HORUS-derived, SSC-modified greywash nanites with fibrous Sylph silk into a  
smart fabric capable of augmenting its wearer’s movement. The predictive/kinetic capabilities of the  

greywash and semi-autonomous/symbiotic nature of the Sylph create an expensive, powerful system  
dedicated to reflexively protecting its pilot (within established parameters)  
 

This enhancement can only be taken as a part of armor. While wearing this armor, a pilot gains +2 speed  
and +2 evasion.
 

Sylph  
Discovered on Acrimea IV, an SSC biome cultivar world, the Sylph is an organic lifeform that appears to  

find homeostasis in nearly any and all environments. Working with breeding-analogous methods familiar to  
SSC bioengineering doctrines, SSC developed Sylph Undersuits -- sterile, living sylphs grown as an  
envelope, fitted to its owner. Once fitted, the Sylph bonds, creating a symbiotic relationship -- it sustains  

itself off the waste products of its host, while protecting its host from a number of hostile environmental  
factors. It can be removed and stored when not in use, where it conforms to whatever container it is placed  
in.  

This semi-biological, skin-tight undersuit can be worn for extended periods. In its natural form, it is  
translucent and semi-liquid, and can be stored easily. It cleans the body, aids its natural healing processes,  

and eliminates waste. Parts of it can be made opaque or translucent or change color or texture. It can cowl  
over the head, providing sealant from vacuum, high protection against radiation, and filtering of air or  
liquid, providing the ability to breathe water for a limited time.
 

                                                       Miscellaneous  

  Name           Tags            Description                                                              Rarity 

                                                                                                                           


Infoskin        Upgrade        This reactive, synthetic polymer bonds easily to real skin               1 
                                and hair. It responds to electronic signals and can rapidly  
                                change color, texture, or even contort or distort, allowing a  
                               wearer to make minor changes in their appearance such as  
                               facial features, hair color, or makeup patterns with a linked  
                                program. 

Panacea         Gear           This fast healing injectable derived from the Sylph protects             3 
                                its host from disease and promotes rapid healing. This  
                                gives 1 use. When injected as a full action, heals a pilot to  
                               full HP, but the shock means a pilot is stunned until the end  
                                of their next turn 
