
\subsection{SSC Metalmark}
                                                                                                                          
                                             SSC METALMARK  

The METALMARK is SCC’s backbone-class line mech, fully equipped with SSC’s proprietary design and  
engineering hallmarks to ensure that it is just as survivable as it is agile. The METALMARK base model  
reflects SSC’s deep-space and long patrol heritage in its aquiline design, sturdy construction, and multiple  

redundant systems. All METALMARK models come standard with a SMITH CUSTOM LEATHER gimbaled  
pilot seat to ensure comfort on long distance ranging expeditions.   

                                                                                                                     


                                                     License:  
 I. Flash Grenade, Reactive Weave
 
 II. METALMARK FRAME, Shock Wreath, Rail Rifle
 
 III. Active Camo, Shock Knife
 

                                                METALMARK 

  HP: 8          Evasion: 9                             Speed: 5            Heat Cap: 5         Sensors: 10 

 Armor: 1        E-Defense: 8                           Size: 1             Repair Cap: 4       Tech Attack:  
                                                                                                +0 

                                                     TRAITS: 

  Flash Cloak: The metalmark is invisible while moving (regular move, boosting, moves from talents, etc),  
  but reappears after it finishes its movement.
 
  Carapace Adaptation: When the METALMARK would benefit from light cover, it instead benefits from  
  heavy cover 

                                              SYSTEM POINTS: 5 

                                                    MOUNTS: 

 Aux/Aux                             Main                                   Heavy Mount 

                                                 CORE system 

                                                 Tactical Cloak  

 A tight-knit, tight-bind weave of reactive fabric, tactical cloaks are high-license tech, restricted to pilots  
  of METALMARK classification II or higher. The weave covers roughly 80% of a chassis, giving it an  
  overall dull quality when viewed through optics or with the naked eye. It is difficult to target, and when  
 activated it bends light in such a way that makes it nearly impossible to see.   

 Active (Requires 1 core power):  
  Cloaking Protocol
 
  Protocol
 
  Until the end of the current challenge, or when you deactivate this module at the start of your turn, you  
  become invisible. If you take damage, you lose the benefit of this module until the start of your next  
  turn. No other action will deactivate it. 

Reactive Weave  

A woven CSAJ (Critical Systems And Joints) cover, Reactive Weave not only protects sensitive systems and  
joints from fouling and poor weather, but provides a surface for SSC engineers to apply their unique  
loomware technology. This weave is powered, capable of free-flexing to augment a mech’s mobility and  

reduce the stress placed on a chassis’ joints.   

                                                                                                                


1 SP, Unique  
When you brace, your mech can immediately move its speed as a reaction and it also gains  
invisibility until the end of its next turn.
 

Flash Grenade  
2 SP, Limited (2)
 
Grenade
 

This grenade can be thrown to a space in range 5. When this grenade explodes, it creates a  
burst 2 zone that lasts until the end of your next turn. Actors other than you (allied or enemy)  
caught inside can’t trace line of sight out of the zone (they can attack other targets inside  
normally), and actors inside the zone benefit from light cover.
 

Shock Wreath  

An after-fabrication modification popular among melee-oriented pilots, the Shock Wreath applies an  

integrated bundle of conductive filaments to the blade, point, tip, or surface of a close combat weapon.  
Paired with a power source (typically in the hilt or half of a weapon, but sometimes external), the Shock  
Wreath adds a thermal element to the kinetic, and a distinct visual marker: their weapons are picked out in  

fine lines of white-hot light, shrouded in heat shimmer.     
2 SP  
Mod  
Choose 1 melee weapon. It gains Burn depending on its size (Aux: Burn 1, Main: Burn 2, Heavy  
or larger: Burn 3). If it already has Burn, this increases the burn it deals by the same amount.
 

Rail Rifle  

A rail rifle is a popular weapon for pilots in any theater, but the only choice for those operating in  
atmospheres made up of highly combustible gasses. Using a line of cascading electromagnets, a rail rifle  

accelerates a small projectile up to tremendous speeds, launching it without combustion or heat reactions.  
A rail weapon is kinetic and comparatively quiet when fired next to combustion weapons, though its energy  
signature is difficult to mask given the massive power requirements demanded by the weapon system.   

Main Rifle
 
1 heat (self), Line 12
 
1d6 kinetic damage
 

Active Camo  

Active camouflage represents the pinnacle of counter-optic defense systems. By interpreting incoming  
visible-light spectrum data, an active camouflage system can project a light-bending field around its user,  

effectively hiding them in plain sight.    

3 SP, Unique  

2 heat (self), Protocol
 

                                                                                                                   


You can activate or deactivate the light bending properties of this module at the start of your  
turn. It lasts until the end of your next turn. While this module is active you are invisible. If you  
take damage, this module immediately deactivates.
 

Shock Knife
 
The shock knife is a mech-sized blade made to accept and integrate the post-fabrication Shock Wreathe  

system. The knives are custom-fabricated by SSC’s Terashima artisan enclave, each one bearing its stamp.  

Auxiliary Melee
 
1 heat (self)
 
Thrown 5, Threat 1
 
1 energy damage + Burn 2
 
