\subsection{SSC Monarch}

                                             SSC MONARCH   

The SSC MONARCH platform is Smith-Shimano’s solution for a fast, self-propelled missile/barrage battery.  
Able to mount ground-to-ground, ground-to-air, ground-to-space, and all-theater missile tubes and their  

guidance systems, the MONARCH can be adjusted to deliver any payload at any distance to any target.  
The MONARCH is commonly deployed in a fire-support role, though field tests of a MICROMONARCH  
mid/close range system is underway. 
 
                                                     License:
 
I. Sharanga missiles, Companion Gun
 
II. MONARCH FRAME, Stabilizer weapon mod, Gandiva Missiles
 
III. Pinaka Missiles, TLALOC class NHP
 

                                                    MONARCH 

  HP: 8           Evasion: 8                             Speed: 5            Heat Cap: 6         Sensors: 15 

  Armor: 1        E-Defense: 8                           Size: 2             Repair Cap: 3       Tech Attack:  
                                                                                                 +0 

                                                      TRAITS: 

  Avenger Silos: Once a round, when you score a Critical Hit with a weapon, a target different to your  
  first target in range 10 and line of sight takes 3 explosive damage (no roll required).
 
  Seeking payload: The monarch’s launcher attacks against targets suffering from Lock On gain the  
  seeking tag 

                                               SYSTEM POINTS: 5 

                                                     MOUNTS: 

   Flex Mount                         Main mount                             Heavy Mount 

                                                   CORE system 

                                                   Avenger silos 

  The SSC 30 High-pen missile system is a FRAME mounted micro missile system capable of tremendous 
  output in combat. The MONARCH is fitted to hold upwards of 60 of these deadly miniaturized warheads 
  at once. 

  Active (requires 1 Core Power): Divine Punishment 
   Full Action 
  You unload your Avenger Silos. All targets of your choice on the battlefield (or a burst 50 area from your 
  mech) must pass an agility check with 1 difficulty or take 1d6+3 explosive damage, and half on a suc- 
  cessful save. You do not need line of sight to any targets, and the self-guiding missiles can perfectly 
  seek any target as long as they can trace a path. Once used, you cannot benefit from the Avenger Silos  
  trait until you take a full repair. 

                                                                                                                 


Sharanga Missiles  
Main Launcher
 
Range 15
 
Arcing
 
3 explosive damage
 
When you fire this weapon, you can choose one or two targets in range and line of sight, making  
attack rolls for each.
 

Companion Gun  
2 SP, Unique
 
Once a round, whenever you score a Critical Hit against a target, this shoulder-mounted gun can  
calibrate and rapidly fires a projectile that also deals 3 explosive damage to a different target  
within range 10 and line of sight, no attack required.
 

Stabilizer weapon mod  
A stabilizer modification is a series of modifications to physical mounts and targeting software that ensures  

weapons will remain level, steady, and angled at max-optimum in order to ensure positive target  
engagement at range.   

2 SP  
Mod  
Choose 1 launcher or cannon weapon. Increase its base range by 5, but it gains the ordnance  
tag.
 

Gandiva Missiles  

Gandiva missiles are a reliable mainstay from Smith-Shimano’s EWAR line. Like the Pinaka, the Gandiva  

platform is equipped with jet-assisted mid-flight repositioning systems, allowing the Gandiva to respond to  
changing battlefield environments with a high degree of expected successful navigation to its target. Each  
Gandiva missile platform comes pre-loaded with a hivemind companion/concierge class drone AI, making  

an equipped system capable of learning from each right-of-launch experience.     

Heavy Launcher
 
Smart, Seeking, Accurate
 
1 SP
 
Range 15
 
1d6+3 energy damage
 

Pinaka Missiles  
Pinaka missiles are massive, two-stage missiles mounted along the spine of a mech core or carried  

disassembled, to be affixed and launched from a brachial mount.  Pinaka missiles are adapted from ship-to- 
ship missiles, their second stage intended to be able to re-orient in flight through jet-assisted repositioning.   

Superheavy Launcher
 
Arcing, 2 heat (self)
 

                                                                                                               


Range 30, one or two Blast 1 areas* 
 
2d6+1 explosive damage
 
When this weapon is fired, it chooses one or two Blast 1 areas within range to attack. The areas  
cannot overlap.
 

TLALOC class NHP  

TLALOC-Class NHP systems provide advanced multi-system targeting and co-pilot functions, taking over  
subroutine control to ensure persistent lock-on and engagement. With TLALOC installed and operational, a  

pilot can trust that their back is always covered and every possible advantage will be exploited.   

TLALOC clones are often stereotyped as a hasty, impetuous NHP. They are well known for having a  

superiority complex.  

3 SP, Unique
 

AI
 
Your mech gains the AI property and the TLALOC protocol
 

TLALOC protocol  
Protocol  
2 heat (self)
 
Your mech is capable of rapidly firing and re-targeting your weapons, far faster than you can  
think. When you activate this protocol, your mech is immobilized until the start of your next turn,  
but for the same duration, if you miss any weapon attack, you can immediately re-roll the attack  
as long as you target a different target in range or area of effect (if the attack was blast, line, or  
cone). You can take this re-roll only once for each attack (if the second attack misses you don’t  
get to keep making it), and a target already hit by this attack (from a re-roll or otherwise) cannot  
be targeted again.
 

                                                                                                                     
