\subsection{Armsman}


                                                  Armsman  

 Think of a firefight. What’s your average pilot or trooper gonna sling? Jacketed lead of course. A mag or  
three of depleted uranium if their target’s a big one. Boring. No, worse than boring -- dull. Predictable.  
Basic.   

Dull isn’t fun. Predictable gets you killed. Basic leaves a boring body. Put down the depleted uranium and  
pick up a magazine of anoriginary stutter-blink slugs, or at least a pack of tachyon flechettes. Lay waste in  
style, and live forever.  

Armament (Rank I): You have an custom supply of ammunition that can be used with all your  
main ranged weapons. The ammo case is a limited (6) system that doesn’t take any SP but can  
be destroyed by system damage, etc. You can load special ammo when you fire a main weapon,  
expending a use of this system and choosing one of the following options (you can only load one  
type at once). The ammo lasts for one shot.
 
         	- Ripper - The attack gains the AP tag and deals kinetic damage
 
         	- Thumper - The attack gains knockback 2 and deals explosive damage
 
         	- Shock - The attack deals energy damage. Any actors adjacent to the primary target  
         take 3 energy damage (no attack required). The primary target doesn’t take this damage.
 
Underslung (Rank II): Gain the following ammo types. They cost 2 charges instead of 1.
 
         	- Hellfire - The attack becomes kinetic damage and deals +2 burn
 
         - Jager - The attack becomes explosive damage, gains knock back 3, and a target struck  
         must pass a hull check or be knocked prone
 
         	- Mag - The attack deals energy damage and gains the Arcing tag
 
Efficiency (Rank III): If you score a Critical Hit with special ammo, you don’t expend it’s use.
 