\subsection{Centimane}

                                                   Centimane  

In the aftermath of the terrorist attack on Tartarus Bay, an unnamed source named Barony Intelligence as  
the culprit. BI announced their official denial, which was never countered with hard evidence. Rumors of raw  
data from the attack were unsubstantiated. Public reaction -- anger, terror -- to the station’s destruction  
quieted.   

 Tartarus Bay’s corpse was shunted away from its stable orbit, directed towards Karrakis’ star.   

A month later, Karrakis’ omninet was flooded with previously suppressed footage from the attack on the  
station. Barony agents released the swarm into Tartarus Bay; further data dumps by Ungrateful agents  
indicated the existence of a secret program - Centimane. The Hundred Hands.  

                                                                                                                     


Expose Weakness (Rank II): 1/round, when you Critical Hit a target with a nexus weapon, that  
target must pass a systems check or become shredded until the end of its next turn.
 
Hivemaster (Rank I): When you consume Lock On as part of an attack from a drone system or  
nexus weapon, on hit, your target is also impaired and Slowed until the end of the next round
 
Obliteration (Rank III): 1/round when you hit a target with a nexus weapon, you can force the  
target to pass a systems check or suffer one of the following effects until the end of their next  
turn:
 
	        - Blinding Swarm - Your target only has line of sight to adjacent squares
 
	        - Virulent Swarm - Your target is Shredded. Any adjacent actors of your choice within  
must repeat this check or also become Shredded.
 
	        - Restricting Swarm - Your target takes 2 Burn each time they take an action or reaction.
 