\subsection{Crack Shot}

                                                   Crack Shot  

Everyone can hit anything these days with the help of modern technology. Targeting-assist. Smart  

Weapons. An AI whispering in your ear, moving your hand for you, squeezing the trigger for you, doing  
everything but taking credit for the kill. But you, pilot, are different. Hitting your target is as easy as looking  
at it, inside of your mech and out. No targeting assist for you, no AI necessary. All you need is a zeroed  

sight, a fresh magazine, and a target downrange.   

Stable, Steady (Rank I): At the start of your turn, you can choose to steady your aim as a Free  
Action. If you do, you are immobilized until the start of your next turn, but gain +1 Accuracy on all  
your rifle attack rolls.  
Accurate and Precise (Rank II): You can now attack targets with your rifles even when they are  
outside of their maximum range, up to twice your rifle’s maximum range, but your attacks gain  
+1 difficulty if attacking this way.
 
Watch This (Rank III): While wielding a rifle and steading your aim, if you score a Critical Hit, you   
deal +1d6 bonus damage and can force your target to pass a hull or agility check (defender’s  
choice) or additionally suffer one of the following effects. If you have accuracy on the attack roll,  
before you make the attack you can sacrifice any number of accuracy dice to give the target an  
equivalent amount of difficulty on the check.
 
     -   Headshot: Your target has line of sight only to adjacent spaces until the end of its next  
         turn
 
     -   Legshot: Your target is immobilized until the end of its next turn
 
     -   Bodyshot: Your target is knocked prone.
 