\subsection{Drone Commander}


                                           Drone Commander  

For a pilot fresh out of boot, keeping a drone swarm in line is like trying to carry water with a net. They  
seem to have a mind of their own, well, because they do, and it’s not that smart. Your initial frustration was  

enough to get you practicing, and practice pays off. Now, your swarm obeys almost before you order — an  
unnerving trend, but a useful one. The swarm is yours.   

(Rank I): Your deployed systems with the drone tag gain +10 HP. In addition, at the start of your  
turn, you can move one of your deployed drones up to 5 spaces as a free action.  
Energized Swam (Rank II): Once a round, when you consume Lock On with any attack, your  
mech and your deployed drones immediately emit vicious pulses of energy, attacking a burst 1  
area centered on your mech and each deployed drone system. Targets caught in the area must  
pass an engineering skill check or take 2d6 energy damage, and half on a successful check. A  
target can only be affected by this attack once (even if the areas overlap).
 
Invigorate (Rank III): As a quick action, you can send a pulse of energy out, to an ally or  
deployed drone of your choice within range 3. You can repeat this energy pulse from your  
target’s location to another drone within range 3 of that target, and so on, as long as you don’t  
choose the same target twice. This effect creates a continuous line drawn between characters hit  
by its effect. Allied mechs and drones hit by this line can heal 1d6 HP, and enemies caught in the  
line of effect are damage from the same amount as energy damage (no roll required).