\subsection{Infiltrator}

                                                    Infiltrator  

Whether by spoofing signatures on enemy scanners, skillful movement through cover, or personally  
modified optical camouflage, you are adept at never being seen unless you want to. Whatever the size of  

the mech, whatever the terrain, whatever the enemy, you can get in and get out without raising alarm.   

                                                                                                                  


Defilade Navigator (Rank I): When you start your turn hidden, your first attack (melee, ranged,  
or tech) you make from hidden gains +2 Accuracy.
 
Dummy Switch (Rank II): Your mech has a special reserve power mode. When it would be shut  
down (voluntarily or otherwise), it can instead go into reserve power (you can still shut down your  
mech normally otherwise). It’s not detectable by conventional electronic systems and can only be  
seen with the naked eye.
 
While in reserve power mode, your evasion is 5, your mech is Slowed, and you cannot use any  
systems that cause you to gain heat. Your mech is totally immune to all tech actions and attacks,  
but cannot take or benefit from tech actions. Weapons with the Smart, Drone, or Nexus tags  
cannot target it. In addition, any system attacks or conditions caused by tech actions currently  
affecting you end immediately. You can enter this mode by taking the shutdown action, remain in  
this mode indefinitely, and can exit it as a Free Action.
 
Steel Assassin (Rank III): When you end your turn hidden, your next melee or ranged attack  
from hiding does +1d6 bonus damage for each enemy turn that passes before you attack, up to  
a maximum of +3d6.