\subsection{Leader}

                                                    Leader  

On the battlefield, you are The Old Man, regardless of age. The light to your friends and allies, as a leader  
you are the steadfast eye of a howling storm. Your steady voice, tall stance, and cool command sets allies  
at ease, as your commands lead to victory every time. With you at the helm, victory is attainable, and  

heroes seem a little bit more real.   

                                                                                                                


Field Commander (Rank I): Gain 3 leadership dice (this is a d6, set it aside from your other die).  
Once on your turn, you can give a command as a free action to give the die to an ally other than  
yourself that can communicate with you, describing a course of action. Your target can use the  
die as +1 Accuracy on any action that directly follows that command. Alternately, an ally can  
ignore your command as a free action, returning your die to you. 
 
An ally can hold on to one leadership die at a time, and must use it before the end of the current  
challenge, otherwise they lose it. You get all leadership dice back when you rest or full repair. You  
can’t gain leadership dice from any source if you have any leadership dice remaining in your pool  
(if you run out, other pilots with this talent can give you commands as normal).
 
Open Channels (Rank II): Gain 2 more leadership dice, and you can now make a command as a  
reaction at the start of another player’s turn. You can only issue one per other player’s turn, but  
any number per round.
 
Inspiring Presence (Rank III): Gain 1 more leadership die. Allies that gain a leadership die from  
you can spend it to reduce damage taken by 1d6 when they take damage or gain 1d6 bonus  
damage on any attack when they roll damage. After spending it this way, the die is consumed.
 