\subsection{Spotter}

                                                      Spotter  
To be all-seeing. To divide each subject of your vision from its unit or cohesion, to pull them apart  
like individual fibers in a vast sheet. To count them as individuals, to make human and fragile the  
force you face is to know how to beat them.   

Break apart the monolith. See the grains that make the stone. Crush them all into yet smaller  
dust.  
 
 
Panopticon (Rank I): If you didn’t move during your turn, at the end of your turn you may make  
a Lock On attack as a free action. In addition, when you Lock On to a target successfully, you  
may learn the target’s current HP, armor, speed, HASE skills, Evasion, and E-defense. This  
information lasts as long as lock on is maintained and can be freely shared with your party.
 
Particularize (Rank II): When you or any adjacent ally consumes Lock On to make an attack, in  
addition to the Accuracy bonus, you or they can roll twice for the attack, choosing either result.
 
Bentham/Foucault Elimination (Rank III): When you successfully Lock On to a target, you can  
use a quick action to nominate an ally you can see. That ally can immediately consume Lock On  

                                                                                                                    


to make any quick action as a reaction. They benefit from any bonuses from consuming Lock On  
as normal, including bonuses to any attack rolls they make, but can make other actions, even  
those that aren’t attack rolls.