\subsection{Ace}
\begin{npc}{Ace}

\fluff{A pilot more comfortable the closer they get to their roots, the Ace enemy-type employs high-speed
strafing runs, agile maneuvers, and a reckless approach to piloting their mech. Cocky and self-assured,
\textnormal{Ace}-type enemies relish a good duel.}

\npcBox
[hull = -1,
agility = +3,
systems = +1,
engineering = +0,
hp = 16,
evasion = 11,
e-defense = 9,
heat cap = 8,
armor = 0,
speed = 6,
sensors = 10,
size = 1/2 or 1]

\textbf{Base systems:}

\npcGearBox[name = {SS Corpro flight system},
template = {System},
rules = {Whenever this mech moves or boost, it can fly.}]

\npcGearBox[name = {Missile Launcher},
template = {\Main \Launcher\\
  +1 vs evasion/tier\\
  \Seeking\\
  Range 10, \Blast{1}\\
  4/6/8 \explosive damage}]

\textbf{Optional systems:}

\npcGearBox[name = {Bombing Bay},
template = {System, \Limited{6}\\
  1/turn},
rules = {When the mech flies while it moves or boosts, it can drop a bomb on one target below as a free
action it that it passes over or adjacent to. Bombs create a blast 1 area with at least 1 square on
their target. All affected targets must pass an agility check or take 6/9/12 \explosive damage and
be knocked prone.}]

\npcGearBox[name = {Strafing Module},
template = {System, \QuickAction\\
1/round},
rules = {The mech flies its speed in any direction in a strafing run, dealing 3/5/7 \kinetic damage to any
  enemy it passes over or adjacent to (no roll required).}]

\npcGearBox[name = {Burst/Dash module},
template = {System\\
  Recharge (5+)},
rules = {The mech may activate this module instead of moving normally, engaging powerful thrusters. It
  flies its speed in a straight line in any direction. This movement doesn’t provoke reactions,
  ignores, engagement, and any mechs engaged with the target when it activates this module
  must pass an agility check or be knocked prone.}]

\npcGearBox[name = {Chaff Launchers},
template = {System, \Reaction\\
Recharge (6+)},
rules = {In response to any hostile tech action or attack, the mech launches chaff and engages digital
  scramblers, causing the attack to miss, and granting it immunity to tech attacks and ranged or
  melee attacks with the smart keyword until the end of its next turn.}]

\npcGearBox[name = {Attitude Thrusters},
template = {System, \Reaction\\
  1/round, Recharge (5+)},
rules = {In response to being hit by any ranged attack, the mech does a barrel roll, flying 3 in any
  direction and gaining resistance to all the damage of that attack.}]

\textbf{Tier II:}

\tierBox
[hp = 18,
evasion = 14,
e-defense = 10,
heat cap = 8,
hull = -2,
agility = +4,
systems = +2,
engineering = +1,
armor = 0,
speed = 7,
sensors = 10]

All agility checks made as a response to the Ace’s attacks are made at +1 Difficulty.

\textbf{Tier III:}

\tierBox
[hp = 20,
evasion = 18,
e-defense = 11,
heat cap = 8,
hull = -2,
agility = +6,
systems = +3,
engineering = +1,
armor = 0,
speed = 8,
sensors = 10]

\end{npc}