\subsection{Aegis}
\begin{npc}{Aegis}

\fluff{Aegis-style mechs are squat, defend-and-suppress chassis built to hold ground, support their allies, and
suppress enemies. Higher-tier Aegis mech pilots have access to hardlight and blackwall defensive
measures - technology that makes bulwarks out of even the smallest barricade.}

 \npcBox
 [hull = +0,
 agility = -2,
 systems = +2,
 engineering = +2,
 hp = 14,
 evasion = 7,
 e-defense = 10,
 heat cap = 10,
 armor = 2,
 speed = 3,
 sensors = 8,
 size = 2]

 \textbf{Base systems:}

\npcGearBox[name = {Light Laser},
template = {\Main \Cannon\\
+2 vs evasion/tier\\
\Seeking\\
Range 8\\
2 \energy damage + 3 \Burn/tier}]

\npcGearBox[name = {Defense Net},
template = {System, Shield, Quick Action},
rules = {This system spreads a powerful shimmering repulsion shield over a large area. While this system
is active, this mech is immobilized, but all attacks against any target within a burst 3 zone around
the mech originating outside of that zone take +1 Difficulty/tier. Attacks out of the zone or
between targets that are both inside of the zone are unaffected. It can be deactivated as an
action.}]

\textbf{Optional systems:}

\npcGearBox[name = {Adaptive Shielding},
template = {System, Reaction\\
1/round},
rules = {The first time an allied target inside the defense net is damaged, all targets inside gain resistance
to the damage type of the triggering attack until the end of the Aegis's next turn.}]

\npcGearBox[name = {Ring of Fire},
template = {System},
rules = {All targets hostile to the Aegis that start their turn inside the Defense Net or enter it for the first
time on their turns take 3 heat and become Shredded while inside the net (they can end this
condition by leaving the net).}]

\npcGearBox[name = {Hardlight cover system},
template = {System, shield, deployable, quick action\\
Recharge (5+)},
rules = {This system spreads a powerful shimmering repulsion shield over a large area. While this system
is active, this mech is immobilized, but all attacks against any target within a burst 3 zone around
the mech originating outside of that zone take +1 Difficulty/tier. Attacks out of the zone or
between targets that are both inside of the zone are unaffected. It can be deactivated as an
action.}]

\npcGearBox[name = {EM Shielding},
template = {System},
rules = {The Aegis creates a line 3 section of hardlight, which grants light cover (1 difficulty) against
incoming fire. Mechs adjacent to this cover have resistance to damage from line, blast, and cone
attacks. The cover is immune to damage.

At tier II onwards, this cover grants heavy cover.
The Aegis' defense net also grants its difficulty to tech attacks made from outside the shield.}]

\npcGearBox[name = {HA Blackwall system},
template = {System, Full Action\\
Limited (1)},
rules = {The Aegis creates a pitch black wall of blinkspace that takes up a free line 10 zone 5 spaces high
that must have at least one point within 5 spaces of the Aegis. The wall breaks line of sight
between its two sides and no effect or attack can be drawn across it. Any mech that starts its
turn on the wall or crosses it for the first time on its turn has a 50\% chance to be lost in
blinkspace momentarily. If this occurs, remove the mech from play. It returns at the end of its
next turn, in any free space within range 10 of either side of the wall. If there is no space
available, it returns when there is. The wall disappears when the Aegis is destroyed or it uses an
action to deactivate it, also returning any stranded mechs.


}]

\textbf{Tier II:}
\tierBox
[hp = 18,
evasion = 8,
e-defense = 12,
heat cap = 10,
hull = -1,
agility = +3,
systems = +3,
engineering = +2,
armor = 2,
speed = 3,
sensors = 10]

\textbf{Tier III:}
\tierBox
[evasion = 8,
e-defense = 14,
heat cap = 10,
hull = 0,
agility = -1,
systems = +4,
engineering = +5,
armor = 3,
speed = 3,
sensors = 10]

\end{npc}