\subsection{Assassin}
\begin{npc}{Assassin}

\fluff{Assassin style mechs trend towards agility, damage, and speed. Their pilots sacrifice comfort for a chassis

efficiency — unnecessary life-support systems, pilot care systems, communications systems, and others
are stripped out and replaced with systems that increase processing power, run-silent ability, and increase
chassis range.

Assassin pilots work alone or in small groups, piloting their small, sleek mechs into territory thought
impenetrable by their targets. One of the few doctrines to employ bladed weapons, assassin-style pilots

train both in the cockpit and out of it to be able to fight with any weapon, in any theater, as efficiently as
possible.}

 \npcBox
 [hull = +1,
 agility = +2,
 systems = +0,
 engineering = -1,
 hp = 15,
 evasion = 12,
 e-defense = 8,
 heat cap = 7,
 armor = 0,
 speed = 8,
 sensors = 12,
 size = 1]

\textbf{Base systems:}

\npcGearBox[name = {Light Laser},
template = {\Main \Cannon\\
+2 vs evasion/tier\\
\Seeking\\
Range 8\\
2 \energy damage + 3 \Burn/tier}]

\npcGearBox[name = {Kai Bioplating},
template = {Trait},
rules = {This mech gains +1 Accuracy on all agility checks. It can climb with no penalty, takes no penalty
for difficult terrain, and doesn't make dangerous terrain tests.}]

\npcGearBox[name = {Variable Knife},
template = {\Auxiliary \Melee\\
+1 vs evasion/tier with 1 Accuracy/tier\\
\AP\\
Threat 2\\
4/6/8 \kinetic damage}]

\npcGearBox[name = {Pulse Rifle},
template = {\Heavy \Rifle\\
+1 vs evasion/tier with 3 Accuracy\\
\Seeking\\
Range 12\\
7/9/11 \energy damage}]

\textbf{Optional systems:}

\npcGearBox[name = {Boltok Rifle},
template = {\Heavy \CQB\\
+1 vs evasion/tier\\
\Loading, \Knockback 1\\
Range 3, Threat 3\\
10/15/20 \kinetic damage\\
This heavy, archaic weapon replaces the Pulse Rifle.}]

\npcGearBox[name = {Spinning Kick},
template = {Trait, Quick Action},
rules = {A target adjacent to the Assassin must pass a hull or agility check with 1 difficulty/tier or be
knocked back 4 spaces away from the assassin and knocked prone.}]

\npcGearBox[name = {Shroud module},
template = {System, Quick Action},
rules = {The Assassin creates a burst 3 zone of light cover within range 8. The zone disperses at the end
of its next turn, or when the Assassin creates a new one. Mechs other than Assassins that enter
the zone for the first time on their turns or start their turn there must pass a systems check with 1
difficulty/tier or become Jammed until the end of their next turn.}]

\npcGearBox[name = {Explosive Knives},
template = {Quick Action\\ Limited (3)},
rules = {A knife can be thrown at any surface or mech as a quick action. Make a ranged attack roll for +2
vs evasion/tier, attaching on hit. At the start of the assassin's next turn, the knife explodes,
dealing 6/8/10 \explosive damage in a burst 2 area centered on the knife or mech. A mech can
remove and disarm the knife by passing a successful systems check as a quick action if they are
adjacent to it.}]

\npcGearBox[name = {Tracker Missiles},
template = {Quick Tech\\ +2 vs e-defense/tier},
rules = {The Assassin makes a tech attack vs e-defense against a target in sensor range. On hit, the
target has the missiles latch on to them. While attached, the target cannot hide or benefit from
invisibility, and the Assassin always knows its location up to a 10 mile distance. The missiles can
be removed during a rest or by taking a quick action and successfully repeating this check.}]

\textbf{Tier II:}
\tierBox
[evasion = 15,
e-defense = 8,
heat cap = 7,
hull = +2,
agility = +3,
systems = +1,
engineering = -1,
armor = 1,
speed = 8,
sensors = 12]

\textbf{Tier III:}
\tierBox
[evasion = 17,
e-defense = 8,
heat cap = 7,
hull = +3,
agility = +4,
systems = +2,
engineering = -1,
armor = 2,
speed = 8,
sensors = 12]

\end{npc}