\subsection{Barricade}
\begin{npc}{Barricade}

\npcBox
[hull = +0,
agility = -2,
systems = +1,
engineering = +3,
hp = 16,
evasion = 6,
e-defense = 9,
heat cap = 10,
armor = 1,
speed = 4,
sensors = 10,
size = 1]

\textbf{Base Systems}:

\npcGearBox[name = {Cycle Lance},
template = {\Main \Cannon\\
Range 10\\
+0 vs evasion with 1 Accuracy/tier\\
6 \energy damage\\
This weapon can attack twice at tier III with the attack action}]

\npcGearBox[name = {Mobile Printer},
template = {Recharge (6+)},
rules = {As a free action at the start of its turn, the barricade may print a line 3 section of size 3 cover (3
spaces high) in any adjacent and free space. The cover provides heavy cover and has evasion 5
and 30 HP.}]

\npcGearBox[name = {Shock Plating},
template = {System},
rules = {The Barricade is resistant to \kinetic damage}]

\textbf{Optional Modules}:

\npcGearBox[name = {Drag Drone},
template = {Quick Tech\\
+2 vs e-defense/tier},
rules = {A target struck by this drone takes 2 AP \energy damage for each 1 space that it voluntarily or
involuntarily moves until the start of the Barricade's next turn. The target is aware of this effect.}]

\npcGearBox[name = {Seismic Repulsor},
template = {Quick Action, recharge (5+)},
rules = {All non-flying targets within a burst 3 area centered on the Barricade must pass a hull skill check
with 1 difficulty/tier or be knocked back 3 space directly away from the barricade and knocked
prone. The area in the blast then becomes difficult terrain permanently.}]

\npcGearBox[name = {Rapid Extruder},
template = {System},
rules = {The Barricade can print twice as fast (can print two sections of cover at once)}]

\npcGearBox[name = {Mag Mines},
template = {Quick Action, Recharge 6+},
rules = {The Barricade rapidly prints and deploys a field of tiny mines that seek out targets and clamp on
to them in droves, slowing them down and inhibiting movement. The mines take up a 5x5x5
cube. The area is both difficult and dangerous terrain, and any target other than the Barricade
that enters the area or starts its turn there must pass a systems check with 1 difficulty/tier or
become Slowed the end of its next turn.}]

\npcGearBox[name = {Snare Drone},
template = {Quick Action, Drone\\
Limited (1)},
rules = {The Barricade rapidly prints and deploys a snare drone in an adjacent space. This drone is size
1, has 10 evasion and 10 HP. When any hostile mech moves within range 3 of the drone or starts
its turn in range of the drone, it emits a pulse, immediately immobilizing that mech until the drone
is destroyed (no check allowed).}]

\textbf{Tier II:}
\tierBox
[hp = 19,
evasion = 7,
e-defense = 11,
heat cap = 11,
hull = +1,
agility = -2,
systems = +1,
engineering = +5,
armor = 1,
speed = 4,
sensors = 10]

\textbf{Tier III:}
\tierBox
[hp = 22,
evasion = 8,
e-defense = 13,
heat cap = 12,
hull = +2,
agility = -2,
systems = +2,
engineering = +6,
armor = 1,
speed = 4,
sensors = 10]
\end{npc}