\subsection{Bastion}
\begin{npc}{Bastion}

\fluff{Bastion doctrine chassis trade the pure defensive edge of an Aegis doctrine chassis for one that
allows more mobility. Blending area-denial offensive capability with hardened defense systems
and advanced communication suites, Bastion doctrine chassis make for strong squadron
commanders.}

\npcBox
[hull = +2,
agility = -3,
systems = +0,
engineering = +2,
hp = 16,
evasion = 6,
e-defense = 8,
heat cap = 8,
armor = 3,
speed = 4,
sensors = 8,
size = 1]

\textbf{Base systems}:

\npcGearBox[name = {Cycle Lance},
template = {\Main \Cannon\\
Range 10\\
+0 vs evasion with 1 Accuracy/tier\\
6 \energy damage\\
This weapon can attack twice at tier III with the attack action}]

Rotary Grenade Launcher
Main Launcher
Arcing, Loading
+1 vs evasion/tier
Range 8, Blast 1
8/11/14 explosive damage

\npcGearBox[name = {Cycle Lance},
template = {\Main \Cannon\\
Range 10\\
+0 vs evasion with 1 Accuracy/tier\\
6 \energy damage\\
This weapon can attack twice at tier III with the attack action}]

Heavy Assault Shield
Heavy Melee
Threat 1
+1 vs evasion/tier
3 kinetic damage/tier

As a quick action, the Bastion can deploy or retract its shield as a line 2, size 2 piece of heavy
cover, disarming it of this weapon. The Bastion can leave the shield deployed and move away
from it if it so wishes (it can pick it up again as a quick action). Any mech that gains the benefit of
this cover against an attack also has resistance to all damage from that attack. The cover has
evasion 5 and 20 HP and can be attacked and destroyed as normal.

\textbf{Optional systems}:

\npcGearBox[name = {Shard Launcher},
template = {System, Reaction},
rules = {The first time a Bastion takes damage in a round, all mechs in a cone (3) area in front of it must
pass an agility check or take 5/7/9 \explosive damage, and half on a successful save.}]

\npcGearBox[name = {Shieldwall},
template = {Trait},
rules = {As long as it's holding its shield, the Bastion and one adjacent mech of its choice has resistance
to all damage from a target of its choosing that it can see. It can only change this target at the
start of its turn.}]

\npcGearBox[name = {Immortality},
template = {System, Full Action\\
Recharge (5+)},
rules = {The Bastion and one adjacent mech of its choice are immune to all damage and effects until the
start of the Bastion's next turn, guarded by a flickering pane of Blackshield tech. The mech
adjacent to the Bastion loses this benefit if it breaks adjacency. On the start of the Bastion's next
turn, it is stunned until the start of its following turn and cannot gain or benefit from resistance or
immunity of any kind for the same duration.}]

\npcGearBox[name = {Defender},
template = {Trait, Reaction},
rules = {Once a round, when an allied mech is damaged, if the mech is in movement range of the Bastion
and the bastion is not immobilized, it can immediately move adjacent to that mech and take that
damage instead of the targeted mech. This movement doesn't provoke reactions and ignores
engagement.}]

\npcGearBox[name = {Hypo-reinforcement servos},
template = {System, Shield, Protocol\\
Recharge (4+)},
rules = {The bastion activates this system at the start of its turn as a free action if it has it available. While
active, it reduces all damage from the very next melee or ranged attack it takes to 0. This effect
can only stack once.}]

\textbf{Tier II:}
\tierBox
[hp = 18,
evasion = 7,
e-defense = 8,
heat cap = 9,
hull = +4,
agility = -3,
systems = +0,
engineering = +3,
armor = 3,
speed = 4,
sensors = 8]

\textbf{Tier III:}
\tierBox
[evasion = 7,
e-defense = 8,
heat cap = 10,
hull = +6,
agility = -2,
systems = +0,
engineering = +4,
armor = 4,
speed = 4,
sensors = 8]

\end{npc}