\subsection{Berserker}
\begin{npc}{Berserker}

\fluff{Berserker doctrine mechs build to take advantage of advanced heat cycling systems to shunt
system heat tax into an offensive force, increasing their weapon output by orders of magnitude.}

\npcBox
[hull = +3,
agility = +2,
systems = -2,
engineering = -1,
hp = 15,
evasion = 10,
e-defense = 6,
heat cap = 6,
armor = 1,
speed = 4,
sensors = 5,
size = 1]

\textbf{Base systems}:

\npcGearBox[name = {Chain Axe},
template = {\Heavy \Melee\\
+2 vs evasion/tier with\\
Threat 1\\
7/10/14 \kinetic damage\\
This weapon deals an extra +1d6 damage/tier on Critical Hits}]

\npcGearBox[name = {Volcanic Re-route},
template = {System, Protocol},
rules = {The Berserker can choose to activate or de-activate this system at the start of its turns. While
this system is active, the Berserker can make two attacks with its chain axe when it takes the
attack action, but it takes 4 heat at the end of its turn.}]

\textbf{Optional systems}:

\npcGearBox[name = {Molten Shield},
template = {System, Shield, Reaction},
rules = {Once per round, the Berserker can activate this dispersal shield when it takes damage from any
melee attack. The damage is reduced by half, and the attacker must pass an engineering check
with 1 Difficulty/tier or take Burn 2/tier}]

\npcGearBox[name = {Harpoon},
template = {\Main \CQB\\
+1 vs evasion/tier\\
Range 5, Threat 3\\
2/4/6 \kinetic damage\\
Targets struck by this weapon the same size or smaller than the Berserker are pulled in a straight
line adjacent to the Berserker or as far as possible. If the target is pulled adjacent to the
Berserker, the Berserker grapples them automatically.}]

\npcGearBox[name = {Calamity module},
template = {System, Full Action},
rules = {The Berserker can only activate this system against a target it is grappling. Auxiliary strength
servos engage and the Berserker hurls its target with incredible violence. The target must make a
hull check with 1 Difficulty/tier. On a failed check, it takes 8/12/16 \kinetic damage, is knocked
back 4 spaces away from the berserker, and is stunned until the end of its next turn. On a
successful check it takes the damage and knockback, but is not stunned. The Berserker ends its
grab after making this move, success or failure.}]

\npcGearBox[name = {Nail Gun},
template = {\Main \CQB\\
+1 vs evasion/tier\\
Range 5, Threat 3\\
5/7/9 \kinetic damage\\
Targets struck by this weapon must pass an engineering check with 1 difficulty/tier or become
immobilized until the end of their next turn.}]

\npcGearBox[name = {Hunter jets},
template = {System, Reaction},
rules = {Once per round, as a reaction to any enemy movement, the Berserker can make the boost action.}]

\textbf{Tier II:}
\tierBox
[hp = 20,
evasion = 11,
e-defense = 6,
heat cap = 6,
hull = +4,
agility = +4,
systems = -2,
engineering = -1,
armor = 1,
speed = 4,
sensors = 5]

\textbf{Tier III:}
\tierBox
[hp = 25,
evasion = 12,
e-defense = 6,
heat cap = 6,
hull = +6,
agility = +4,
systems = -2,
engineering = +0,
armor = 1,
speed = 5,
sensors = 5]
\end{npc}