\subsection{Bombard}

                                             BOMBARD  

The Bombard doctrine calls for unending salvos of punishing artillery bombardments. Chassis  
tuned to this style of combat are found miles behind the line in fortified positions, or otherwise  
removed from combat: one common strategy for prolonged area-denial bombardment is to place  
a battery of bombard chassis on a world’s local moon(s). From that movable satellite, the battery  
can rain FRAMEs down upon the world below, well removed from the dangers of combat. 
 

       BOMBARD 

       Mech 

       Hull      Agility     Systems       Engineering 

       +0        -1          +1            +2 

       HP        Evasion     E-defense     Heat Cap. 

       20        7            12           8 

      Armor      Speed       Sensors       Size 

       0         2            11           2 

Base systems:  
Bombard cannon  
Superheavy cannon  
Ordnance, Arcing, Loading
 
+2 vs evasion/tier with 1 difficulty
 
Range 20, Blast 2
 
10/14/18 kinetic damage
 

Stabilizers  
System, Full Action
 
As a full action, this mech can engage or disengage its stabilizers. While they are active, the  
mech cannot move or be knocked prone, but it gains +1 accuracy and +10 range on its attacks  
and cannot fire any weapons at a target within range 5 of itself. If this system is destroyed, the  
mech is immobilized.
 

Molded Armor  
System
 
The Bombard has resistance to explosive damage
 

Optional systems:  
H.A. Siege Shield  

                                                                                                       


System, Shield, Passive
 
The mech has resistance to all damage that it takes from attacks further away than range 5.
 

High-Impact shells  
Trait
 
The Bombard cannon gains knock back 3
 

LMG
 
Main Cannon
 
One or two targets
 
Range 10
 
+1 vs evasion/tier
 
4/6/8 kinetic damage
 

Cluster-seeker Bombs  
System
 
After the artillery fires its bombard cannon, 3 additional targets within range 10 of the primary  
target take 2 explosive damage/tier (no check or roll required).
 

Devastator Protocol  
Trait, Full Action, recharge (6+)
 
Choose 1d3 points within range of the mech, and mark them (so they are clearly visible to all  
players). The bombard must be activated last next round. At the start of its next turn, the mech  
fires at each of those points with its bombard cannon, as a free action, attacking all targets and  
structures within. It cannot choose these points so that the blast area from these attacks overlap  
in any way.
 

Tier II:
 
HP: +5
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          8        14     8        +1   -1    +2    +3      0            3        11 

Tier III:  
HP: +5
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          8        16     8        +1   -1    +3    +5      0            3        11 
