\subsection{Engineer}
                                              ENGINEER  

Engineer doctrine chassis are common throughout the galaxy, their patterns unique to the world  
or theater in which they operate, but their charge the same: defend, maintain, secure. Engineers  
operate best in the mid to rear of the line, coordinating the defense of important positions and  
ensuring total operational deployment of all mission assets. Remember: if your chassis can’t  
make it to the line, you lose.
 

 Engineer 

 Mech 

 Hull       Agility      Systems       Engineering 

 -1         -1           +1            +3 

 HP         Evasion      E-defense     Heat Cap. 

 20         7            11            12 

 Armor      Speed        Sensors       Size 

 0          3            15            1 

Base systems:
 
Flak Cannon  
Heavy Cannon
 
Smart
 
+1 vs e-defense/tier
 
Range 15
 
5/7/9 kinetic damage
 
This weapon gains +1 Accuracy against flying targets. Flying targets damaged by this weapon  
must pass an agility check or fall.
 

Deployable turret  
System, Drone, Quick Action, Recharge (4+)
 
The engineer deploys a self-building turret in an adjacent, open space. The turret is an immobile  
size 1 drone with simple AI that attacks the nearest hostile target. It has evasion 10, 10 HP, and 1  
armor. It attacks on the Engineer’s turn for +1/tier vs evasion, range 10, 2/3/4 kinetic damage,  
but can take no other actions.
 

Ablative Shielding
 
System
 
The Engineer has resistance to energy damage
 

                                                                                                          


Optional systems:  
Power deployer  
System
 
The Engineer can deploy two turrets when it uses its deployable turret system
 

Arsenal  
The Engineer can deploy stronger turrets, and three different types of turrets, and can choose  
which to deploy when it uses its system. Each have the same statistics as a base turret, with the  
following changes:
 
         Inferno: The turret’s weapon becomes +1/tier vs evasion, cone 5, Burn 3/4/5
 
         Hellstorm: The turret’s weapon becomes +1/tier vs evasion, range 15, blast 1, 2/3/4  
         explosive damage
 
         Hunter: The turret’s weapon gains the smart tag
 
         Primed: When the turret or the engineer is destroyed, it explodes in a burst 1 area around  
         it. Targets caught inside must pass an agility check or take 7/9/11 explosive damage
 

Skyshield protocol  
System
 
The Engineer’s deployable turrets gain +1 accuracy against flying targets.
 

Point Defense Drone  
System, Drone, Quick Action, Recharge (5+)
 
The engineer deploys a drone in an adjacent space which creates a burst 1 zone around it. The  
engineer can only deploy one drone at a time. While inside this zone, targets allied to the  
engineer are immune to weapons with the Seeking and Smart tags. The drone can be attacked  
and destroyed, though it benefits from its own zone.
 

Tracking Computer  
System, Reaction
 
Once per round, the Engineer’s Flak Cannon can be fired once as a reaction to any boost action  
or movement outside of regular movement by a hostile mech it can see.
 

Tier II:
 
HP: +2
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

          9        12     12      -1   +0    +2   +4       0           3        15 

Tier III:  
HP: +2
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

          11       12     12      -1   +0    +3   +6       1           4        15 
