\subsection{Exotic}
                                                      EXOTIC   

Exotic-type enemies are, even for a galaxy of wonders, strange and dangerous enemies. Some  
feature unique technologies not yet available to the wider galaxy, others wield primitive weapon  
styles updated to the modern day, and others carry equipment or adopt tactics that are alien to  
Union doctrine.  
 
 
Making an Exotic NPC:
 
All Exotic NPCs get the following features added to their base NPC type:
 
     -   Xenotech: Scans reveal no information about exotic modules  
     -   Hardened Target: Hostile tech actions take +1 difficulty against exotic targets  
     -   Exotic systems: Any NPC with the exotic tag can choose one or two of the optional  
         exotic modules below  

Exotic modules
 
Bio-integrated  
Trait
 
You may only choose this trait for a mech. The mech gains the biological tag (it loses heat  
capacity and cannot take or be the target of tech actions except Lock On and scans).
 

                                                                                                                     


Blinkspace Carver  
System
 
When the NPC moves, it teleports.
 

Extrusion  
Trait
 
The NPC is only a partial extrusion of a higher-concept entity and only partially present in  
physical space. It gains resistance to all damage but all its weapons also deal half damage and it  
can be passed through as if it wasn’t there (it doesn’t provide obstruction).
 

Living Weaponry  
Trait
 
The NPC becomes immune to the Jammed condition. Its weapons have biotechnical and semi- 
organic components that spontaneously generate ammunition.
 

Paracausal Weapon  
Trait
 
Choose one of the NPC’s weapons. Damage from that weapon cannot be reduced in any way  
(by armor, resistance, or otherwise)
 

Ouroboros Brand  
System
 
1/round the NPC can force a re-roll by themselves or any allied or hostile target (but must choose  
the second result) by causing localized distortions in the flow of time.
 

Regenerator  
Trait
 
The NPC heals 2/3/4 HP at the end of its turn. This trait does not function if the NPC took energy  
damage at any point during the round.