\subsection{Grunt}
                                                 GRUNT   

Grunt-type enemies in Lancer are the most common enemies faced en-mass by players. Grunts  
are a step above cannon fodder: cheap and trained to be disciplined fighters before deadly ones,  
grunts follow orders under threat of death, imprisonment, or some other kind of censure. Alone, a  
grunt-type enemy may not be a threat, but in a group, they can present an overwhelming mass of  
bodies and fire that threatens even the most powerful individual.   

Making a Grunt
 
All grunts get the following features added to their base NPC type:
 
    -   Weak: The Grunt’s maximum HP becomes 1, with 1 structure. It loses any heat capacity it  
         has (so it takes energy damage instead of heat). It cannot gain structure or heat capacity  
         in any way.  
    -   Surprisingly Hardy: Grunts don’t take damage from systems, talents, or weapons that  
        automatically deal damage (such as the reliable tag). When they would take half damage  
        on a successful save from a source of damage, they instead take 0.
 
    -   Still a mech: Grunts can only be killed by pilot weapons that have a total attack roll of  
        20+  
    -    Bonus activations: When a Grunt is activated, up to 2 other grunts can also be activated  
        at the same time and take their turns at once
 
    -    Max systems: The Grunt can’t have any more than 1 optional system  
    -    Exclusive templates: The Grunt can’t take the Veteran, Squad, Elite, or Ultra templates  
    -    Max attacks: The Grunt can’t attack with more than 1 weapon a turn.  
    -    Max damage: None of the grunt’s attacks can deal more than 4 damage, heat, or burn  
        total per attack at tier 1, or half if the attack is AOE or has more than one target. This  
         increases to 6 at tier II and 8 at tier III. Adjust as needed.  
