\subsection{Infantry}
                                               INFANTRY   

Infantry-type enemies represent a squad-level group of human or subaltern infantry: not a single  
chassis like the Grunt-type, but (generally) a group of five to ten armed and armored individual  
soldiers. Like the Grunt, an Infantry-type enemy alone might not present a threat to a chassis, but  
operating as a squad with the right gear and training, infantry groups are a formidable threat.    

       INFANTRY 

       Squad, Biological 

       GRIT +2/tier 

       HP         Evasion      E-defense     Heat Cap. 

       10         8            8             - 

       Armor      Speed       Sensors        Size 

       0          4            10            4 (individual:  
                                             1/2 ) 

HP per member: 1
 
Number of members: 10
 

Primary squad weapon
 
Main Rifle
 
+2 vs evasion/tier
 
Range 10
 
3/4/5 kinetic, energy, or explosive damage (choose on creation)
 
This weapon can be fired three times when the squad attacks. If the squad is under 1/2 HP, it can  
only be fired once.
 

Anti-mech squad weapon
 
Heavy cannon
 
AP
 
+2 vs evasion/tier
 
Range 20
 
4/tier kinetic, energy, or explosive damage (choose on creation)
 

Tier II:
 
HP: +5 (+5 members)
 

       Evade    E-D    Heat    Armor       Spd      Sense 

                                                                                                           


        8         10     -        0            4         10 

Tier III:  
HP: +5 (+5 members)
 

        Evade     E-D    Heat    Armor         Spd      Sense 

        8         10     -        1            5         10 

Optional modules for squads (both types): 
 
Armored  
Trait
 
The squad gains +1 armor
 

Ambushers  
Trait
 
The squad gains +2 Accuracy on all attacks and rolls on the first round of combat only, and gains  
+2 Accuracy to avoid being discovered while hiding
 

Go to ground  
Trait, reaction
 
Once per round as a reaction, the squad gains resistance to all the damage from an incoming  
attack, but cannot move or boost on their following turn. They must decide before the damage is  
rolled.
 

Rapid Insertion  
Trait
 
The squad can fly when it moves or boosts.
 

Technicals  
Trait
 
The squad can take the Invasion action (as per player rules). Disable this action if the squad is  
under 1/2 HP.
 

                                      