\subsection{Operator}

                                              OPERATOR  

Operator doctrine chassis are a known-unknown. Operators typically field smaller chassis not  
commonly encountered on the front lines; do not mistake this for fragility. Pilots who are recruited  
and trained into this doctrine, regardless of culture, are dangerous, deadly, the best of their  
state’s armed forces or martial tradition. They operate alone or in small teams under the auspices  
of black-site state agencies, engaging in the most sensitive and dangerous AMNESIAC-tier  
missions. Their chassis — and their bodies — are loaded with some of the most advanced tech  
available; if they die in combat, it is not uncommon for their bodies and their chassis to self- 
immolate, rendering what technology and data they had into waste and ash. 
 

 OPERATOR 

 Mech 

 Hull       Agility      Systems       Engineering 

 +2         +2           +2            +2 

 HP         Evasion      E-defense     Heat Cap. 

 14         10           10            9 

 Armor      Speed        Sensors       Size 

 0          4            10            1 

Base systems:
 
‘Raptor’ plasma rifle  
Heavy Rifle
 
+2 vs evasion/tier
 
Range 15
 
8 energy damage
 
This weapon can attack twice at tier III with the attack action
 

‘Nightcloak’ type omnishield  
System, Shield
 
While this system is active, the operative has resistance to one of the following types of damage:  
kinetic, explosive, energy, heat. The operative must decide which when it starts combat (setting it  
is a Free Action) and cannot change it during combat.
 

Self-erasing  
Trait
 
When this mech is destroyed, it immediately self-immolates into superheated plasma. All targets  
adjacent to it when it is destroyed must pass an agility check or take 4/6/8 energy damage or  

                                                                                                           


half on a successful check. This mech is then removed from the battlefield - it is utterly  
annihilated.
 

Optional systems:  
Fade generator  
System
 
While this system is intact, at the end of its turn, the Operative becomes invisible until the start of  
its next turn. This effect is immediately disabled if the Operative takes damage until the start of  
the Operator’s next turn.
 

Refractive shield  
System, Shield
 
This system is permanently disabled if the operative overheats. While it is active, the operative  
gains the Hardened Target trait (scans, lock on attempts, and invasions against it are made at +1  
difficulty).
 

Skirmisher implant  
System
 
Once at any point on its turn, the operative can make a boost action as a free action.
 

Nova missile  
Auxiliary Launcher
 
Smart, Seeking
 
+1 vs e-defense with 1 Accuracy/tier
 
Range 30, blast 1
 
4/6/8 energy damage
 

Trace Drive  
System
 
Once on its turn, when the Operative moves or boosts, it instead teleports up to 8 spaces away,  
as long as its target destination is a free space. This movement does not provoke reactions and  
ignores engagement, such as overwatch.
 

Tier II:	
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          12       12     9       +3    +3    +3    +3      1            4        10 

Tier III:
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          14       14     9       +4    +4    +4    +4      2            5        10 
