\subsection{Spacer}
                                                 SPACER  

Spacer-type enemies are born and bred in the hard vacuum of deep space. They are adept at  
maneuvering in and around the difficult, kinetic, low-gravity environments found only in space:  
blink stations, space stations, among asteroid fields, in low orbit over worlds, and between ships  
in military and commercial fleets.     

Making a Spacer:
 
All Veterans get the following features added to their base NPC type:
 
    -    Maneuverable: The Spacer does not suffer the impaired condition for operating in space,  
         underwater, or in zero-g environments and always counts as having an EVA module in  
        those environments.  
    -   Optional modules: The Spacer can choose from optional Spacer modules when  
        deciding additional modules  

Spacer modules
 
Concussion gun
 

                                                                                                           


Main Rifle
 
Cone 3
 
+1 vs evasion/tier with 1 Accuracy/tier
 
Mechs hit by this weapon are 3 spaces away from the direction of the zone.
 

Gravity Rifle
 
Main Rifle
 
Range 10
 
+1 vs evasion/tier with +1 Accuracy/tier
 
The target of this attack must pass a hull check with 1 difficulty/tier or be pulled in a straight line  
towards the wielder of this weapon up to 10 spaces, or as far as it can move. If this causes it to  
collide with an obstacle or another mech, it is additionally knocked prone.
 

Sealant Trap
 
Mine, Limited (1)
 
This self deploying trap can be placed in a vacant space. It counts as a mine and can be  
scanned to be detected and disabled with a successful systems check. Once any target walks  
over or adjacent to the trap, it explodes, creating a burst 2 area centered on it. All targets caught  
inside must pass an agility check or be covered in thick, fast-drying hull sealant and immobilized.  
The only way to break out of the sealant is to do enough damage to break it (evasion 5, 15 hp).
 

Thumper grenades
 
Grenade, Limited (1)
 
Thrown 5
 
Once thrown to an impact point as a quick action, these grenades explode outwards with a  
concussive pulse in a blast 1 area around the space where they are targeted. Targets caught in  
the area must pass an agility check or be knocked back 3 spaces directly away from the impact  
point. If this causes them to collide with an obstacle or another mech, they are additionally  
knocked prone.
 