\subsection{Veteran}
                                                   VETERAN  

Veteran-type enemies are hardened, experienced fighters that have survived direct engagement  
with their foes. Their encounter with your players is not their first rodeo: their ability to withstand  
morale shocks is far higher than an untested greenhorn.
 

Making a Veteran:
 
All Veterans get the following features added to their base NPC type:
 
     -   Bonus structure: The veteran gains +1 structure.
 
     -   Bonus stress: The Veteran gains +1 reactor stress  
     -   Veterancy: The Veteran gains +1 accuracy on all checks of one statistic: Hull, Agility,  
         Systems, Engineering (choose on creation)  

Then choose up to 1 Veteran trait per tier:  
AI co-pilot  
Trait  
The veteran’s mech or vehicle gains the AI tag. The veteran’s mech or vehicle is autonomous and  
can function even if the veteran is not piloting it (per the player rules). The AI can be unshackled,  
with the same effects as player AI.
 

Acrobat  
Trait  
When the veteran moves or boosts, it can fly 3 after the move or boost completes. This flight  
does not provoke reactions and ignores engagement.
 

Deadly  
Trait  
This mech can Critical Hit, dealing +2 bonus damage/tier to its attacks on crit.
 

EM-shielding  
Trait  
The veteran is resistant to heat
 

Engineer  
Trait, Quick Action  
The Veteran can take the repair quick action:
 
         Repair (limited 1): This mech heals 4 hit points per tier and ends one condition currently  
         affecting it (impaired, Slowed, immobilized, shut down, jammed)
 

Feign Death  
Trait  

                                                                                                                  


The first time in a challenge this enemy would be destroyed, though it appears destroyed, it is  
instead shut down, remaining at 1 hp. A successful scan or pilot notice check will reveal it is still  
active.
 

Hacker  
Trait  
The veteran’s invasion attacks deal +3 heat
 

Headshot  
Trait  
1/round when the veteran scores a Critical Hit, the target of its attack must pass an engineering  
check or be jammed until the start of the veteran’s next turn.
 

Hardened Target  
Trait  
Invasion, scan, and lock on attempts on this target are made with +1 difficulty
 

Legendary  
Trait  
The veteran can enter the CRITICAL state (like the player) instead of being destroyed when  
ticking off its last structure point.
 

Lesser Sight  
Trait
 
Within range 3 of the Veteran, targets cannot hide from it, and cannot benefit from invisibility  
against it while inside that area.
 

Limitless  
Trait
 
The veteran can use Overcharge
 

Lightning Reflexes  
Trait  
Reaction
 
The first time in a round the veteran is targeted by any weapon system of size heavy or larger, roll  
a d6. On a 5+, the weapon automatically misses this mech.
 

Parting Gift  
Trait  
The veteran can use the Self Destruct action.
 

Rodeo master  
Trait  

                                                                                                                     


The veteran can jockey (in a hard suit) and gains +1 Accuracy on jockeying attempts
 

Shock Armor  
Trait
 
The veteran has resistance to damage from main size weapons
 

Skirmisher  
Trait
 
1/round the veteran can move or boost as a reaction to any enemy movement or action that it  
can see.
 

Slippery
 
Trait
 
The veteran does not provoke reactions and ignores engagement with its move (its boost still  
provoke reactions) 
 

Steel Jaw  
Trait  
The most damage an auxiliary weapon can do to the veteran is 1.
 

Viper’s Speed  
Trait  
The veteran always takes its turn first, even over player characters. If there is a question of who  
acts first (in the story, or combat), it is always the veteran.
 