\subsection{Harrison Armory Pilot Gear}

                                  HARRISON ARMORY Pilot Gear  

                                                    Pilot Weapons  

  Name                    Tags                                      Range            Damage                  Rarity 

 KOTTOS AA/               Ordnance                                  8                1d3 kinetic             1 
 Largearm Rifle 

 MicroCore Laser          Loading                                  5                 1 energy + Burn 1       2 
 Rifle 

 Atlatl                   Seeking                                  Threat 1
         1 explosive             3 
                                                                   Thrown 5 

 Hardlight Weapon         -                                        Threat 1          1 energy + Burn 1       4 

Atlatl  

Developed following the suppression of anti-Armory elements in the initial wave of recolonization in the  
Dawline Shore, the Atlatl is a neo-primitivist weapon indigenous to New Madrassa, a voluntary Arcadian  
world set in a blended Neo-Bronze/Information Age idyll.   

Though deceptively simple in appearance, this javelin-like weapon contains a hardened suite of intelligent  
hardware and a miniaturized pressure wave generator in the tip. It can be thrown very accurately up to  

range 5, recalled to hand as an action, and guides itself around cover and other obstacles.
 

Hardlight Weapon  

One of a limited supply scavenged from Boundary Garden, this hardlight blade has been patched by  
independent Ecumenical contractors to a serviceable, minimum-milspec functionality. These are exotic  

weapons, and their wielders must be coached in their use by trained handlers.    

These rare and powerful weapons project a sheathed energy field that ignites targets on impact.
 

KOTTOS AA/Largearm  
Harrison Armory’s KOTTOS distance-denial anti-armor system was ordered following repeated instances of  

HAAT legionnaires encountering hostile local chassis armed with sufficient anti-kinetic/ablative armor;  
KOTTOS, developed in conjunction with GMS’s Distant Venture campus, the KOTTOS represents the  
pinnacle of infantry-portable kinetic anti-armor kinetics.    

This heavy anti-armor rifle fired superheated bullets used to punch through infantry-scale hardsuits and  
light mechs. It requires mounting on a tripod before use, though some models come with a built-in stand.  

The enormous kick from this weapon is infamous for dislocating rookie pilots’ shoulders.
 

MicroCore Laser Rifle  

                                                                                                                     


A Think-Tank product, the MicroCore is a miniaturized, infantry-portable version of the popular SolidCore  
laser cannon mounted atop HA’s Sherman Chassis. The MicroCore has been tuned to not require windup  
on firing, but as a result must be “reloaded” after each shot with a new power core.   

An infantry-scale model of the larger, mech mounted lasers, this weapon requires heavy cooling after each  
use. Standard squad-support weapon for Armory legionnaires.
 

                                                 Clothing and Armor  

  Name                  Tags        Bonuses                                    Armor      Evasion/       Spd    Rarity 
                                                                                          E-defense 

 Buckler                Clothing    Provides protection in plain clothes       -          -              -      1 

 STAMBHA               Armor        Offers a short ranged protective            0          10/10          4      2 
  Overarmor                         shield. 

 DJED Overarmor    Armor            Provides stasis instead of Down            1          8/8            4      3 
                                    and Out 1/full repair 

 ASHOKA                Armor        +3 HP, Reduces heavy damage                1          8/8            3      4 
  Overarmor 

 ICEPACK                Upgrade     Gain the ability to overcharge             -          -              -      4 

Buckler  
This personal energy shield fits snugly under clothing and is standard issue to protect the Armory’s colonial  

bureaucrats and collaborators while venturing outside of green zones.   

While wearing plain clothes (not armor or a hardsuit), as a reaction to taking damage from a single source,  

you can activate this shield to reduce that damage to 0. This shield must recharge and can be used once  
every full repair.
 

ASHOKA Overarmor  
The Ashoka Overarmor Hardsuit is favored by frontline HAAT legionnaires in hostile colonies. Large and  
heavily armored, the ASHOKA is built to appear imposing: when it is needed, soft power has failed, and the  

Armory does not discount the memetic power of an intimidating appearance.   

This heavy armor disperses shock and heat from overwhelming damage, reducing it to manageable levels.  

While wearing this armor, if you would take more than 1/2 your maximum HP in damage, reduce the  
damage instead to 1/2 your maximum HP.
 

DJED Overarmor  
The DJED Overarmor is a medium weight, combat-posture hardsuit designed to preserve its user in case of  
sudden traumatic/catastrophic injury. Favored by legionnaires on patrol-and-liaise missions, the DJED is an  

Armory favorite and the most commonly requisitioned hardsuit among HAAT personnel.   

                                                                                                                      


When you go Down and Out, instead of rolling a check, you can activate this armor’s stasis system. Until  
the end of the current challenge, you are put into a stasis state where you cannot take damage, but also  
cannot move or take any actions (or be revived from this state). Once the challenge ends, roll for Down and  

Out as normal.
 

ICEPACK  

A stabilized sliver of coldcore, the ICEPACK is a near-perpetual power system that allows for momentary  
overclocking of powered hardsuit components.   

This miniaturized reactor is integrated into armor and cannot be used without it. While wearing armor with  
this enhancement, as a limited (3) system you can spend a charge as a pilot to take an extra quick action  
on your turn.
 

STAMBHA Overarmor  
Another combat-posture hardsuit, the STAMBHA employs a beefed-up buckler/flickershield system that  

protects its wearer from hostile fire. Resting somewhere between the Armory’s DJED and ASHOKA lines,  
the STAMBHA is a favorite of the officer class who are willing to trade mobility for protection.   

If you didn’t move on your turn, at the end of your turn, until the start of your next turn, gain a protective  
shield that grants all ranged weapon attacks against you +1 difficulty.
 

                                                   Miscellaneous  

  Name                Tags         Description                                                               Rarity 

 Dataplating          Upgrade      Linked jewelry/faceplates that allow sub-vocal communication               1 
                                   and augmented reality. Dataplates can quickly translate many  
                                   languages, and anyone with a dataplate can talk to any other  
                                   person with a dataplate without vocalizing, creating something  
                                   eerily similar to telepathy. 

 Flexsuit             Upgrade      A strong, under-clothing suit that recycles water, generates               1 
                                   nutrients, and adapts very rapidly to hostile environs, keeping its  
                                   wearer in a state of stability and extending their survivability. Very  
                                   good for colonists adapting to a new environs. 

 Sleep suit           Upgrade      Once activated, the suit can put an individual into a state of             1 
                                   human hibernation for as little as 3 hours and up to 6 months,  
                                   lowering their vital signs to almost nothing, relieving them of the  
                                   need for food, air, or sleep, and halting the process of any  
                                   diseases. During the first 10 minutes, the suit extrudes a  
                                   hardened polymer around the sleeper, protecting them from  
                                   impact and making them resistant to all damage. 

                                                                                                                   


 Hold/Lock          Gear        This mine can be planted in a free adjacent space as an action,      1 
 Nonlethal                      and detonated remotely as an action. It can also be set to  
                                detonate once any target moves adjacent to it. Once detonated,  
                                any target caught in a burst 1 zone around the mine is stunned  
                                and immune to all damage until the end of their next turn. Mechs  
                                cannot be affected. 

 Dispersal          Gear        This shield can be deployed as an action in a free adjacent          2 
 Dropshield                     space. Once deployed, it creates a burst 2 zone around it.  
                                Ranged attacks against all non-mech targets size 1/2 or smaller in  
                                the zone suffer from +1 difficulty. The shield deactivates after the  
                                current challenge and must recharge on a full repair. 

*See Entry  
