\subsection{Horus Pilot Gear}

                                          HORUS Pilot Gear  

 Name                   Tags                                   Range           Damage                Rarity 

 Smart Knife            Accurate, Sidearm                     Threat 1         1 kinetic              2 

 PGR\_GOURD              Smart, Seeking                         5               1 kinetic              2 

 Sidekick               Reliable 1, Sidearm                    3               1 kinetic              2 

 Null Spike             *                                     Threat 1        *                       3 

 Nanobot Whip           *                                     Threat 2         1 kinetic              3 

 EYESTACK\_WINK          Limited 1, AP, Upgrade                 2              3 kinetic               4 

                                                Pilot Weapons  

*See Entry
 

EYESTACK\_WINK  

Also known as a ‘Skullgun’, this miniaturized, superposed charge weapon is implanted in the head,  
generally in the orbital void left by a removed or missing eye. It is completely undetectable by almost any  
electronic system or security and can be fired with sub-vocal commands.   

As an upgrade, this weapon doesn’t count against your maximum weapons wielded.
 

Nanobot Whip  
The first instance of a technology akin to what is now called a nanobot whip was encountered during a raid  

on an Ungrateful cell by Barony lawmen. With word secreted to them by informants seeded in the  
movement, lawmen descended on a cell hidden in the wildcat stations lashed around the House of Dust.  
Blasting open the doors, they encountered Ungratefuls wreathed in clouds of charcoal smoke; the  

Ungratefuls used these clouds, shaping them into thin whips that cut through armor and flesh like it was  
nothing. After the cell was wiped out and the control nodules cut from their bodies, Barony codemasters  
were able to crack and replicate -- safely -- the HORUS code.   

This whip is made up of linked microbots that flow in ring-like arcs around the body when not in use,  
defending against drone and nanorobotic threats. If you don’t attack with this weapon, until the end of  

your next turn, weapons or systems with the Smart, Nexus, or Drone tags cannot target you.
 

Null Spike  

A HORUS-developed ecstatic/exult device, the generic null spike is an effective, single-fire, non-lethal  
weapon that simulates a cascade-analogue in organics through specific neuron excitement. Upon skin  
contact, they deliver a bio-electric shock to a victim’s brain that causes them to feel overwhelming  

pleasure, completely disabling them. Null Spikes, it is said, are used by HORUS adherents in realspace to  
bring themselves closer to RA’s subjectivity. 
 

                                                                                                             


Has no effect against non-organic targets, but on a successful hit, any human target is stunned until the  
start of your next turn. A target develops a short term resistance to this weapon and can only be affected  
by it once per challenge.
 

PGR\_GOURD  
The PGR\_GOURD pattern portable hive killed the first people who printed it. Fabricated in secret by a  

desperate cell of Ungrateful in the undercity of Dune Redoubt, a team of Barony Authority officers first  
encountered the aftermath of a PGR\_GOURD burnout; an organic smear, ringed around the printer that  
crafted the gourd. Subsequent encounters of the PGR\_GOURD system saw it used as a remote-detonated  

device until the BA was able to find and edit the plan into a more controllable, less deadly format. Since  
then, the House of Sand controls the distribution of any PGR\_GOURD system; however, there are  
unconfirmed reports of the unedited version of the GOURD available on the omninet.   

This shoulder mounted drone hive is usually integrated into armor and releases a neurally linked, short  
ranged hunter-killer drone swarm. Designed to expire within moments of release, the aerosolized greywash  

swarm sweeps over the target, devouring organic and inorganic material with equal rapidity. 
 

Sidekick  

Typically affixed to a back-mounted, over-the-shoulder armature, the SIDEKICK is an eyelinked  
subcompact/caseless machine gun developed by a collective of unknown, potentially HORUS-aligned  
scripters. Paired with a C/C Wingman unit, the SIDEKICK will always watch your back; its placement,  

commonly perched over its operator’s shoulder, has earned it the common nickname of “Parrotgun”.  

This HORUS-marked SMG has a companion/concierge unit built into it which provides aim assist in real  

time. It also has helpful and frequent tips for improving your combat skills and organizes your calendar,  
sometimes without you asking it.
 

Smart Knife  
A “Smart” knife is the combination of a HORUS-tuned external-mount processor and any mundane  

charged blade. Piggybacking off the current coursing through the charged blade, the HORUS mount can  
be loaded with null or fry-code, making this blade a threat not only to organic targets, but to synthetic ones  
as well. Particular models have an adjustable subliminal suggestion corrective, which guides its user’s hand  

to identified weaknesses in their target’s hardsuit, armor, or other plating.   

The tip of the knife is semi-solid and re-moldable and can be inserted into most electronic ports and used  

as a point of insertion for hacking rigs.
 

  Name                     Tags        Bonuses                                 Armo     Evasion/     Spd    Rarit 
                                                                                r       E-                 y 
                                                                                        defense 

  WILD\_AND\_CRAZY           Upgrade     Count adjacent spaces as your            -       -            -      2 
                                       mech’s sensor range 

 UNCLEAR\_END/NTT          Armor        Limited action during                    1       8/8          4      2 
                                       unconsciousness/death 

                                                                                                                


 UNAVOIDABLE\_VOI           Armor       +3 HP, Completely undetectable by        0        10/*         4     3 
 D                                     electronic systems 

 MINE/ALL/MINE             Armor       +3 HP, Able to hack mechs while          0        10/10        4     4 
                                       jockeying 

 Metafold processor        Upgrade     Bonus e-defense and ability to           -        -/+2         -     4 
                                       make invasion actions 

                                               Clothing and Armor
 

UNCLEAR\_END/NTT  
A relic-code predating HORUS’s official foundation date, UNCLEAR\_END/NOT THIS TIME seems to be a  
dead branch of transhumanist exploration: thanatologic praxis. Utilizing a now-classically HORUS greywash  

nanite swarm, this system triggers on one of a number of user-defined parameters to “reanimate” the user’s  
body using a backup homunculus subjectivity. The readme urges users of this system to regularly purge  
and reset the failsafe homunculus.   

While wearing this suit, if you go unconscious due to Down and Out or if you die, the suit injects you with a  

thanatologic necroanimate cocktail that temporarily replaces you by a digital homunculus of yourself that  
animates your corpse or unconscious form
 

You’re still unconscious (or dead), you can only take quick action on your turn, and you cannot benefit  
from talents while in this state. You regain 5 HP and can otherwise act as normal. If you go to 0 again, you  
are returned to a normal Down and Out state or death. This effect also wears off after the current challenge  

or about 10 min, and can’t be activated again until you take a full repair. If dying caused this ability to  
trigger, you are dead once this effect wears off.
 

The homunculus cannot respond to novel situations or stimuli, but in a familiar setting or with familiar faces  
it can interact roughly as normal -- this trends deeply into the uncanny valley, however, and will likely not  
fool anyone into thinking that the reanimated you is “you”. 
 

UNAVOIDABLE\_VOID  
Following the opening of hostilities in the Boundary Garden sector, UIB agents in the Annamite Line began  

to note in their reports repeated instances of companion NHP “blindness” when engaging with anti-Union  
elements on New Mahangaatuamatua. Worryingly, this phenomena is analogous to anomalous entities  
described by Union elements engaged with Ascendant Chosen on Cornucopia; the similarity has lead UIB  

to conclude that HORUS has some as-yet-unidentified presence in Boundary Garden (another possibility:  
in Ascendant space) not only capable of transmitting data back from the embargoed area, but processing  
and manipulating as-yet-unworkable Ascendant technology.     

This lightweight hardsuit is of unusual make; printing one immediately induces errors into the system that  
created it. It doesn’t appear on any electronic systems, is totally immune to system attacks, cannot be  

targeted by smart weapons or drones, and cannot be seen by NHPs or AIs (they treat you as permanently  
invisible while you are wearing it).
 

Metafold Processor  

                                                                                                                 


How large is the vault of your mind? Where do you mark the boundaries of an interiority? When you dream,  
can you place a boundary on the imagined plane? Hold a vast image inside your mind’s eye -- see? The  
universe can fit inside.  

Take this. It can hold your mind, which can hold the universe, which holds all of us. Use it as you wish, but  
do not look inside.   

It is unclear exactly how this system works, but it does, and it grants a pilot hardsuit unprecedented  
processing power. A pilot can only benefit from this enhancement while wearing armor. While wearing this  

armor, a pilot gains a +2 bonus to e-defense and can make the Invasion tech action as if they were a mech  
with a +3 systems score.
 

MINE/ALL/MINE
 
Here, take this -- a code that writes itself, a sentence spiraling and spiraling. Take from it what you can  
(there is a gift hidden in the chaff, a needle you must burn the hay to find) there are evermore everalways  

more meanings and forms and shapes (so many! Ah! And to see all of them is to EXULT all of them!) and  
here is one for you: a coat to wear that will let you travel further/deeper/longer/ 
LETYOUTAKEWHATISYOURS.  

Talk soon love.   

While you’re jockeying a mech while wearing this suit, you can force it to make a systems skill check with  
1 difficulty or immediately move up to its full speed in direction of your choice.
 

WILD\_AND\_CRAZY  
A rather benign code -- as HORUS decrypts go -- WILD\_AND\_CRAZY(WITH ALL MY FRIENDS) is a simple  

program, one that neuters their greywash nanites, rendering them docile. It then uses their massed  
processing power and semi-autonomous atmospheric movement capabilities to channel systemic and  
sensor processes, effectively acting as a cloud-projector around its host.   

This pattern prints a sheet of nanites that rapidly absorb and integrate into any piece of clothing. While  
wearing this clothing, any space adjacent to your pilot counts as your mech’s sensor range for the  

purposes of making tech actions only. 
 

                                                 Miscellaneous 

 Name                Tags        Description                                                               Rarity 

 Prosocollar         Upgrade     A collar-like device that fits snugly around the mech and projects         1 
                                 a holographic image over your face and head. The collar can  
                                 change your voice and scramble or change your appearance. It  
                                 doesn’t stand up to close inspection, but it’s very easy to fool  
                                 electronic systems or people at a distance. 

                                                                                                               


Dream                 Gear         This small, puck-like system can be deployed or thrown to a point                 1 
Projector                          within range 4 as a quick action and remotely activated as another  
                                   action. While deployed and active, it can project extremely  
                                   convincing holographic images within 2 spaces of its location of  
                                   nearly any size that could fit in that space. If inspected closely, a  
                                   Tech or Swindle pilot action might be required to maintain the  
                                   illusion. 

Subjectivity          Upgrade      Cybernetic implants that allow you to hack without gear or a rig.                 1 
Enhancement                        While you have these implants, you can extrude cables or ports  
Suite                              from within your body to plug in and experience an alternate  
                                   reality interface that provides full interactivity and omninet access. 

Player\_Two            Upgrade      With this implant, you can hand complete control of your body’s                   2 
                                   motor functions over to an NHP, allowing you to sleep, rest, or  
                                   relax while it performs tasks. It’s not skilled enough to pilot a  
                                   mech in combat or perform very complex tasks, but it can pilot  
                                   your mech out of combat and perform certain tasks or work such  
                                   as cooking, administrative work, data entry, mech repair, piloting a  
                                   ship or driving, or other mundane tasks. It can also imitate you  
                                   and your personality fairly well, though not to a degree that  
                                   someone who knows you well would be fooled in the slightest. 
