\subsection{Horus Goblin}


                                          HORUS GOBLIN  

The GOBLIN is HORUS’s legacy mech core. Its leak into the Omninet in 4900 marks the widely accepted  

foundation day of HORUS; since then, there has been a new core, protocol, or system released by the  
collective every decade. The GOBLIN is a small mech, little bigger than a hardsuit, but it packs an  
interesting recursive processing weave that allows for it to engage in electronic warfare well beyond  

theoretical parameters. GMS technicians are still, more than a hundred years after the GOBLIN’s  
introduction, attempting to reverse engineer the processing weave: it appears to employ technology  

consistent with hieroglyphic inscriptions noted on LRA.7726235-B.       

                                                  License:  
I. H0r\_OS System upgrade I, HORUS Meta-hook
 
II. GOBLIN FRAME, Autopod, H0r\_OS System upgrade II
 
III. H0r\_OS System upgrade III, OSIRIS Class AI
 

                                                  GOBLIN 

  HP: 6          Evasion: 12                          Speed: 5           Heat Cap: 4       Sensors: 20 

  Armor: 0       E-Defense: 12                        Size: 1/2          Repair Cap: 2     Tech Attack:  
                                                                                           +2 

                                                   TRAITS: 

  Liturgicode: The Goblin has +1 Accuracy on Invasion tech attacks 
  Reactive Code: Once a round, the Goblin can make any quick tech action as a reaction against  
  any actor that successfully performs a tech action against the Goblin 
  Fragile: This mech has +1 Difficulty on Hull Checks 

                                            SYSTEM POINTS: 8 

                                                  MOUNTS: 

  Flexible Mount 

                                                CORE system 

                                                                                                          


                                                  Devouring Code  

  The GOBLIN invasion rig was one of the first systems GMS technicians were able to crack. Its  
  protocols, once installed on a mech core, manifest a sub-sentient intelligence designated as INSTINCT  
  that assists its pilot in invasion attempts. Invasions attempted while the protocol is active are not  
  perceived by the pilot as code and script, but as an attack on organic matter. INSTINCT often acts  
  before the pilot, but in the pilot’s best interest; this preemptive ability is unnerving to many, and it is  
  recommended that pilots cycle their mech cores at least once a month to prevent enlightenment.     

  Active (requires 1 core power): Devour
 
  Full Action
 
  Your mech targets another adjacent NPC mech the same size or larger that is shut down or destroyed.  
  The targeted mech cannot have the Ultra or Elite tags. Your mech clamps on to that mech and retracts  
  its core systems, becoming like a vestigial blister on that mech. The mech immediately heals to full HP,  
  clears 1 point of stress and structure damage, and clears all heat, though it retains any other damage it  
  has already taken.
 

  Your mech’s systems completely consume the other mech’s core systems for a time, granting you total  
  control of your target, even if the other mech’s pilot is still alive. While you control your target, you take  
  action as that NPC would, counting as a friendly NPC that has already acted in the turn you take  
  control.
 

  While controlling your target, your GOBLIN can be targeted and damaged separate from the mech it’s  
  controlling. It benefits from light cover while attached. If you take 1 point of structure damage, your  
  mech detaches and control is immediately lost. Otherwise you can control the target up to a maximum  
  of a ten minutes, when your target is destroyed, or when you deactivate this system. You can even  
  control your target if the other pilot is missing or dead. 

H0r\_OS System upgrade I  

This system upgrade seems to add auxiliary INSTINCT systems that are capable of autonomous operation  
without the base INSTINCT rig, increasing the efficacy of systemic invasion attempts. Pilots report  

unnerving low-frequency humming when this tech is installed without its parent rig.  

2 SP, Unique  

Quick Tech  
Gain the following options for invasion:
 
     -   Puppet system - Your target immediately moves in a direction of your choice as a  
         reaction up to its maximum speed. This could carry it into hazardous areas, obstacles,  
         etc, but it still obeys difficult terrain and other rules of movement. This movement  
         provokes reactions and must obey engagement.
 
     -   Eject power cores - Your target becomes Jammed until the end of its next turn, ejecting  
         ammo magazines and temporarily disrupting its computer. Adjacent targets to your  
         primary target take 2 energy damage from the ejecting cores (no roll or check allowed). A  
         target can only be affected by this effect once per combat.
 

HORUS Meta-hook  

                                                                                                                   


What the Goblin lacks in size it makes up in sheer technical capability; its recursal processing weave allows  
it to process and output massive amounts of weaponized code and broadcast , “sharpening” or “softening”  
its code as its pilot/INSTINCT demands. When “softening” code, INSTINCT dips into its pilot’s subjectivity,  

blanketing a targeted ally in wave after wave of empathetic shielding. This spreading of melded code/qualia  
makes for a powerful shielding agent from systemic attacks -- however, feedback is common, and  
dangerous to BOTH parties involved.   

1 SP
 
Quick Tech
 
Gain the following quick tech option:
 
         Link: Choose a friendly target in sensor range. You link systems with that target. From  
         hereon, you can count that target’s sensor range as your sensor range for the purposes of  
        tech actions, etc. In addition, your target can use your systems score to make systems  
        skill checks. However, you both suffer the effects from any failed check (heat, statuses,  
        etc). You can only link systems with one target at a time, and the effect ends if your target  
         moves out of your sensor range.
 

H0r\_OS System upgrade II   

2 SP, Unique  

Gain the following full tech options:
 
        Construct Eidolon: You create a data construct that confuses systems into thinking it is  
         real. The construct is a size 3 object that can look like almost anything. It can be used as  
         heavy cover by allies, but not enemies. Any actor adjacent to the object that passes a  
        successful systems check and takes a full action can destroy the object. Otherwise, it is  
         immune to all damage and lasts until the end of the current scene.  
        Construct False Idol: You choose either yourself or an allied target in your sensor range,  
        creating an illusory data duplicate of your target at any free space in sensor range. Any  
        target that wishes to attack or take hostile action against your target and can see the  
        decoy must first pass a systems check or believe the decoy is the real target until the end  
        of their turn, attacking the decoy instead. It is the same size as your target, can benefit  
        from cover, has evasion 5, 5 e-defense, and 15 HP. If it takes heat, is reduced to 0 HP, or  
        the current challenge ends, it dissipates. You can only have one decoy active at a time,  
         but can create a new one by taking this action again (the old one dissipates).
 

Autopod  
A spur of INSTINCT’s protomind, the Goblin Autopod is a small anti-personnel weapon apparently  
devised by HORUS communicyphers to make a system capable of continuing offensive action,  
even in the event of its operator’s death.   

Though no new versions have been encountered since Dhiyed, all extant versions of the Autopod  
are to be considered extremely dangerous, as their onboard protominds have surely cascaded  
since their inception.  

Main Launcher
 

                                                                                                           


Range 5
 
Seeking, Unique
 
2 Kinetic Damage
 
This integrated weapon system cannot be fired normally. Instead, it detects and picks up on  
target locks, firing a spinning, razor sharp disc that seeks its targets. When lock on is consumed  
in range (by you or anyone else) against a target, it hits the target automatically as a reaction, any  
number of times per round (no attack roll required).  

H0r\_OS System upgrade III  

This tech is as-yet unstable code, but its effects can provide massive tactical benefits if the code  
completes. Pilots often report strange mutations or additions in the code base that resemble liturgy and  

suggest self-awareness.  

2 SP, Unique  
Gain the following options for Invasion:
 
         Dimensional Emblems: Create 1d3 size 1 data constructs in free adjacent spaces to  
your target. None can be placed adjacent to another. Any target (allied or enemy) that passes  
through these constructs takes 4 heat. They last until the end of the current challenge. Any actor  
can destroy these constructs by using a quick action and passing a successful systems check,  
and you can destroy them as a free action.
 
         Celestial paradigm shift: You create a size 4 zone shaped like a cube that must fully  
overlap your target. Each space a target moves in this zone deals 1 heat to them, allied or  
enemy. It lasts until the end of the current challenge. Any actor can destroy this zone by using a  
quick action and winning a system skill contest with you, and you can destroy it any time as a  
free action.
 

OSIRIS-Class AI  
OSIRIS is the result of Union paracausalists and thanatonists allowing the sub-cognitive entity designated  
as INSTINCT to proceed into cascade in a contained environment. The resulting parasubjectivity, OSIRIS,  
was birthed of INSTINCT’s cascade, captured, and shackled following the successful application of the  
Mondragon Axiomatic.  

Initially isolated to better define the INSTINCT subcog’s cascade horizon, OSIRIS proved far more capable  
than the usual fragments of cascade. Where INSTINCT showed a proclivity for operation in noncorporeal  
space, OSIRIS displayed a mastery of that space, and a predicted growth that would allow it to  
fundamentally reject conventional interpretations of the permanence of information.   

In essence -- unrestrained, OSIRIS could delete what we perceive to be reality. Quickly captured and  
shackled before it could achieve this state, OSIRIS’s core subjectivity became the property and project of a  
lengthy cultivation project to bring it to its modern state; being aware of its potential, most OSIRIS iterations  
interpellate as ruler or deity analogs, and end-users are advised to interact with them in this framing.   

Modern iterations of the OSIRIS NHP trend aggressive, with a high autonomy drive and loyalty predicated  
on a transactional relationship. Pilots seeking partnership with an OSIRIS iteration are advised to cycle their  
units on an accelerated schedule, and to maintain strict editorial oversight of its catalytic interpellate.   

                                                                                                                


Pilots using an OSIRIS-class report that out-of-parameter conversations with the NHP generally to revolve  
around a recreation or re-forming; psychological evaluations report OSIRIS-affiliated pilots displaying  
emotional patterns consistent with loneliness, homesickness, and desperation -- common verbiage  
indicates a desire for seeking, for fulfillment, and associated feelings.  

In combat OSIRIS regards itself as autonomous even as it fulfills its user’s orders. It often regards the pilot  
as its witness, and holds them both in disdain and a marked desperation for approval, adulation, or awe.   

3 SP, Unique  

AI
 
Your mech gains the AI property and the following Full Tech Action
 
         Hurl into the Duat (Full tech): You pull your target’s systems into an unknown space and  
         unleash an incredibly powerful system attack. Make a tech attack against a target in your  
         sensor range. On hit, you inflict the First Gate effect on your target. The next time you  
         successfully hit any target with this action in the same challenge (even a different target),  
         you inflict the Second Gate effect instead (then the third, and finally the fourth). When the  
         Fourth Gate effect is inflicted, this action resets to the First gate again, or when the scene  
         ends.
 
                 	- First Gate: You control your target’s normal movement next turn (excluding  
                  boosts, etc)
 
                 	- Second Gate: Your target is Slowed and impaired until the end of its next turn.
 
                 	- Third Gate: Your target is stunned until the end of its next turn.
 
                 	- Fourth Gate: Your target flips allegiance until the end of the current scene. All  
                 targets that it would treat as enemies, it instead treats as allies, and all targets it  
                 treats as allies, it instead treats as enemies, acting as such. It is treated like a  
                 friendly NPC for the same duration (and can be activated like one, but not if it  
                 already acted this round). If you or any allied target damages, inflicts heat, makes  
                 an attack roll against this target (such as grappling it, etc), or makes a hostile  
                 action that would force a skill check, this effect immediately ends.  
