\subsection{Horus Manticore}

                                        HORUS MANTICORE  

The MANTICORE pattern-group is an experiment in HORUS//COREBREAK combat doctrine. Using  
focused, projected electromagnetics, MANTICORE pattern-group mechs attempt to neutralize enemy  

cores without conventional ammunition. A fully charged MANTICORE is an impressive sight, wreathed in  
brightly glowing nets of glowing plasma that lash out at nearby targets. The MANTICORE pattern-group is  
a relatively new p-g on the Omninet, and its combat efficacy has prompted the rest of the Big Five to  

scramble for a response. If anything gives away the MANTICORE pattern group, the tall spines of the  
lightning generator cast a clear silhouette. The spines act as heat-dispersal systems for this crude weapon,  
giving a path for its incredible thermal tax to bleed from the chassis after it projects a close-range arc whip.  

Even then, the system is not perfect; spines often slag under the tremendous heat -- a recognizable  
signature of the pattern group (beyond the spines) is a chassis covered in cooling, melted metal.    

                                                    License:
 
I. EMP Mine, Catalyst Pistol
 
II. MANTICORE FRAME, Arc Projector, Beckoner
 
III. Lightning Generator, SMITE
 

                                                MANTICORE 

 HP: 10          Evasion: 6                            Speed: 4            Heat Cap: 7        Sensors: 10 

 Armor: 2        E-Defense: 10                         Size: 1             Repair Cap: 3      Tech Attack:   
                                                                                              +1 

                                                    TRAITS: 

 Slag Carapace: The Manticore is resistant to energy damage and burn.
 
 Unstable System: When the Manticore is destroyed, it explodes immediately as though it had triggered  
 a reactor meltdown, no matter what result you rolled 

                                             SYSTEM POINTS: 6 

                                                   MOUNTS: 

 Flexible Mount                                         Heavy Mount 

                                                 CORE system 

                                                                                                               


                                             Charged Exoskeleton  
 And RA Said To Themselves: LET MY NAME ENVELOP YOU. SEEK NO SHELTER FROM THE FLAME  
 OR THE TEETH OF THE BEAST. CLOAK YOURSELF IN THE FIRE (MY WORD) AND CAST BACK TO  
 YOUR ENEMIES THAT WHICH WOULD BLACKEN YOUR FORM. 
 

 Passive: When you take heat from any source, one target in range 3 of you takes 1 energy damage.
 
 Active (requires 1 core power):
 
  Protocol
 
 Your mech crackles with energy. For the rest of this combat your mech has resistance to heat from any  
 source (round up). Set aside a charge die, starting at 1. When you take heat or energy damage (from  
 any source, even self), increase the die by 1, to a maximum of 6. You can discharge the accumulated  
 energy in a burst 2 area around you by taking an action to do so. This deals 1d6 energy damage to all  
 targets caught inside, allied or enemy, per charge on the die, and affected mechs can pass an  
 engineering check to halve the damage. This system then deactivates for the remainder of this  
 challenge, including its passive. 

EMP Mine  

Crawl away, APEP! Thou hateful serpent; thou shalt not copulate! Thou art put in chains and taken to the  
place of execution; there thy slaying shall be carried out as thy father has commanded.  

1 SP, Limited (1)  
Mine  
Once planted, EMP charges can be detonated remotely as a quick action, or activate normally  
like a mine. All affected mechs in a burst 1 around the charge when it activates must pass an  
engineering check with 1 difficulty or become stunned until the end of their next turn.
 

Catalyst Pistol
 
Lo! Thy countenance is melted
 
Auxiliary CQB
 
2 heat (self)
 
Cone 3, threat 3
 
2 energy damage
 

Arc Projector  

Fire be upon thee, APEP! Thy flesh is seared from thy stinking bones; thy shade shall never rise again. The  
Lord of the Duat will never enable thee to rise again.  

Heavy Rifle
 
1 heat (self)
 
Range 5
 
1d6+1 energy damage
 
If a target is successfully hit by this weapon, you can repeat this attack against another actor  
within range 3 of the first target (generating heat each time). This effect can chain as long as  
there are valid targets in range, but can only choose the same target once.
 

Beckoner  

                                                                                                                


I am heard in the House of Stillness, I am clad in the Magick of RA: what exists is within my grasp.  

2 SP  

Quick Tech, Unique  
Gain the following options for invasion:
 
         Beckon: On hit, you swap places with your target, teleporting
 
         Summon: On hit, all actors, allied or enemy, in range 3 of your target are pulled towards  
         your target as far as possible (into adjacency if possible)  
	          

Smite  

Go with thy face averted! The hidden ones have overthrown thy words, thy face is turned backwards, thy  
head is divided in two at the sides; thy skull is ripped from thy spine. Taste thou death!
 

3 SP  
Quick tech, Unique  
Gain the following options for invasion:
 
         	Smite: Your mech takes 1d6 AP energy damage. Your target must pass a system check  
         with 1 difficulty or become stunned until the end of its next turn. It can only be affected by  
         this option successfully once per scene.
 
         Annihilate: Your target takes +2 heat for each other mech in engagement or adjacency  
         with it (including your mech).  

Lightning Generator
 

I feed upon my own fire. I am they that protect themselves. Nothing can harm me.  

2 SP, Unique
 

Danger zone
 
At the start of your turn, you can take 1 heat (self) to deal 1d3 energy damage to all targets  
adjacent to you, no roll required.
 

While you are in the Danger Zone (the bottom half of your heat gauge), all adjacent targets to  
you, allied or enemy, take 1d3 energy damage if they begin their turn next to you or move there  
during the course of their turn.
 