\chapter{Stat and Terminology Glossary}
                          STAT AND TERMINOLOGY GLOSSARY

Armor - The amount of damage you reduce all incoming sources of damage by. For mechs,
cannot go higher than 4
Electronic Defense - The number that most electronic warfare attacks must beat to be
successful
Evasion - The number that most melee and ranged attacks must beat in order to hit with an
attack
Grit - 1/2 your level. Added to melee and ranged attacks, system points, and hp
Heat Capacity - The amount of heat your mech can take before making an overheating check.
Hit Points (HP) - The amount of damage you can take as a pilot before going down and out, and
the amount of damage a mech can take before it takes 1 point of structure damage.
Modifier - The number added to mech skill checks and attacks, equals your targeting, hull, agility,
engineering, or systems
Range - The range of your ranged attack, measured from yourself. Depends on weapon
Repair Cap - The maximum number of repairs to your mech you can make per mission
Resistance - Resistance to damage or a type of damage means it is reduced by half, rounded up,
after armor is applied. You can only have resistance to damage once (it doesn’t stack multiple
times)
Structure - When a target with structure goes to 0 HP, it makes a structure check, then takes 1
structure damage. When a target runs out of structure, it either goes into the CRITICAL state
(player mechs) or is destroyed outright.
Tech attack - Electronic Warfare attacks, modified by your systems
Threat - The range of your melee and overwatch attacks with certain weapons, measured from
yourself. Base threat for all weapons is 1, but it may be greater depending on the weapon.
Sensor Range - The range in which you can make electronic warfare attacks, lock on, and use
some systems
Size - The area that your mech takes up, rounded up for determining space. For example, a size
2 mech is an area 2 spaces on each side approximately 2 spaces high
Speed - How far your mech moves when it moves (in spaces)


