\chapter{Statuses}

  STATUSES

During combat, characters might inflict statuses on opponents, giving temporary conditions. Most
statuses indicate when they are inflicted and when they end in the weapon, system, or piece of
gear that inflicts them.

CORE BREACH
    -   You cannot cool heat or lose heat

    -   Make an overheating check each time you take heat

CRITICAL
    $$\bullet$$   You cannot gain HP or repair
    $\bullet$    Make a structure check each time you take damage
Engaged
    -   While Engaged in melee, all your ranged attacks are made with +1 difficulty

    -   If you become engaged with a target the same size or larger, you immediately stop
        moving and lose any unspent movement from that move.

Hidden
    -   You cannot be targeted by hostile attacks or actions, and enemies only know your
        approximate location. Performing any attack, taking reactions, or ending your turn out of
        cover will lose hidden.

Immobilized

    $\bullet$    Your maximum speed becomes 0. You cannot move or boost.
Impaired
    $\bullet$    +1 Difficulty on all actions, attacks, and skill checks
Invisible
    $\bullet$    All attacks against an invisible target have a 50% chance to miss outright (check before
        the attack roll).

Jammed

    $\bullet$    The only attacks a Jammed mech can make are improvised attacks, grapples, or rams

    $\bullet$    A Jammed mech cannot use comms to talk to other players (can only talk to GM)
    $\bullet$    A Jammed mech cannot make or benefit from Tech actions

    $\bullet$    A Jammed mech cannot take reactions

Lock On
    -   An attacker can consume the Lock On status on a target to gain +1 Accuracy on its next
        attack against that target. Lock On may also activate other talents or abilities.

Shut Down
    $\bullet$    Your mech is stunned, but you can still take the Boot Up action
    $\bullet$    Your mech’s evasion becomes 5
    $\bullet$    Your mech cools
    $\bullet$    You cannot be affected by tech actions or system attacks or effects
    $\bullet$    Shutting down (or being shut down) re-shackles any unshackled AI.

Shredded
    $\bullet$    A shredded mech cannot benefit from armor or resistance





Slowed
     $\bullet$    Your maximum speed becomes 2 (after all modifiers)
     $\bullet$    You cannot boost

Stunned

     $\bullet$    You cannot overcharge, take free actions, reactions, move, or take any actions with your
         mech. A pilot in a stunned mech can still mount or dismount their mech, eject, or take
         actions normally.
     $\bullet$    Attackers receive +1 Accuracy to attack you

     $\bullet$    You automatically fail all hull or agility checks

Prone

     $\bullet$    Attackers receive +1 Accuracy to attack prone targets
     $\bullet$    A mech knocked prone is Slowed while prone but can still move. A prone mech can stand
         up as its regular movement. A mech cannot stand up while immobilized.
