\section{Backgrounds}
                                               Backgrounds

Your background describes your life up until you became a mech pilot. A background does not
necessarily describe your pilot’s role in the squadron now — a background tells your GM and
fellow players a bit about what your pilot did before they enlisted. Think of backgrounds as a
prompt for you to draw from when describing your pilot’s full backstory: how did they first
become a soldier, a doctor, or a miner (or whatever your background may be), and from there
how did they become the pilot they are now?


When you make a background, you can either roll 1d20 for one of the backgrounds in the
compendium, choose a background from that same list, or simply make your own up.


At level 0, choose four skills above based on your background.

Then choose two of the four skills you just chose. You have a speciality in those skills, giving
you +1 Accuracy on top of your flat bonus. These are things you are especially good at, that
your background has given you an edge in.





Finally, choose any two other skills that you didn’t choose in your original four. These skills are
flawed for you and get +1 difficulty when you make a relevant pilot skill check that uses those
actions. These are things your character is unpracticed at or has some difficulty performing,
based on their background, personality, or personal abilities.


Your background bonuses generally never change, but if you and your GM feel like part of your
background is no longer relevant or has changed significantly, you can change the bonuses
around during downtime. Having a flawed skill does not prevent you from training that skill when
you level up, mitigating your background.