\section{Creating a Pilot}

Making a pilot at level 0 is as simple as the following:

\begin{enumerate}
\item \textbf{Create a background:} When you create a pilot at level 0, you'll need to make up a background for your pilot - where your pilot comes from. You can create your own background, or roll or choose from the list of backgrounds in the compendium.
\item \textbf{Set pilot skills:} Choose four triggers at +2
\item \textbf{Set background bonuses:} Based on your background, choose two skill triggers. You get a specialty in those skills, giving you +1 Accuracy. Then choose two others that you didn't choose in step 2. These skills are flawed, giving you +1 difficulty.
\item Write down \textbf{HP, e-defense, speed. and evasion:} Your pilot has HP (hit points), how much damage you can take before you're down and out, and \textbf{evasion} and \textbf{e-defense}, how hard it is to hit you with weapons and electronic systems in mech combat. You also have \textbf{speed} (how far you move in spaces when you move). At level 0 that's \textbf{6 HP, 10 e-defense, 10 evasion, and 4 speed.} More on the importance of these stats in the mech \textbf{combat} section.
\item \textbf{Before you embark on a mission,} you'll choose pilot \textbf{gear,} which might change your stats. More on that in the mission section. You can take clothing, armor, up to two weapons, and two other pieces of gear. Gear can be acquired from the compendium, and you can't take gear that has a total rarity greater than your level. All General Massive Systems gear is level 0, allowing any pilots (even license level 0 pilots) access to it.
\end{enumerate}

\textbf{Advancement:}
\begin{itemize}
\item Each time you level up, you can increase one of your existing skills by +2, to a maximum of +6, or gain a new skill at +2.
\item Every 3 levels, you can gain a new specialty. If you gain a specialty in a flawed skill, it cancels out, leaving it a normal skill.
\item A pilot can add 1/2 their level (grit) to their HP and attack rolls in mech combat
\item Your pilot's total gear they can bring with them on a mission is limited by license level
\end{itemize}
