\subsubsection{Armsman}

\begin{talent}
{Think of a firefight. What's your average pilot or trooper gonna sling? Jacketed lead of course. A mag or three of depleted uranium if their target's a big one. Boring. No, worse than boring -- dull. Predictable. Basic.

Dull isn't fun. Predictable gets you killed. Basic leaves a boring body. Put down the depleted uranium and pick up a magazine of anoriginary stutter-blink slugs, or at least a pack of tachyon flechettes. Lay waste in style, and live forever.}

\rank{I}{Armament}  You have an custom supply of ammunition that can be used with all your main ranged weapons. The ammo case is a limited (6) system that doesn't take any SP but can be destroyed by system damage, etc. You can load special ammo when you fire a main weapon, expending a use of this system and choosing one of the following options (you can only load one type at once). The ammo lasts for one shot.
\begin{itemize}
\item \textbf{Ripper} - The attack gains the AP tag and deals kinetic damage 
\item \textbf{Thumper} - The attack gains knockback 2 and deals explosive damage 
\item \textbf{Shock} - The attack deals energy damage. On hit, any actors adjacent to the primary target take 3 energy damage (no attack required). The primary target doesn't take this damage.
\end{itemize}
\rank{II}{Underslung}
Gain the following ammo types. They cost 2 charges instead of 1.
\begin{itemize}
\item \textbf{Hellfire} - The attack becomes kinetic damage and deals +2 burn 
\item \textbf{Jager} - The attack becomes explosive damage, gains knock back 3, and a target struck must pass a hull check or be knocked prone 
\item \textbf{Mag} - The attack deals energy damage and gains the Arcing tag
\end{itemize}
\rank{III}{Efficiency}
If you score a Critical Hit with special ammo, you don't expend it's use.
\end{talent}
