\subsubsection{Engineer}

\begin{talent}
{Pilots are creative and driven individuals, but you’re an exceptional case - some would say to the point of excess. In your spare time you’ve managed to scrape together just enough scrap, requisitioned materials, and workshop space to apply a little old fashioned ingenuity to your mech.}

\rank{I}{Spark}
On a full repair, you can, with some trial and error, install a prototype weapon system on your mech. It has the following profile -- the specifics you may choose upon installation. Roll the Limited property each full repair. You can change the profile of this weapon each time you full repair. 
\gearBox
[name = {Prototype Weapon},
fluff = {},
template = {\Main (Choose 1; \Melee, \Rifle, \Cannon, \Launcher, \CQB)\newline
\Limited{1d6+2}, \Overcharged\newline
\Threat{1} (melee) or \Range{8} (ranged)\newline
1d6 \kinetic, \explosive or \energy damage}]
This weapon does not take a mount to add to your mech, and counts as its own mount.
\rank{II}{Updated Plans}
On a full repair, you can remove and tweak essential components of your system in order to increase the effectiveness of your prototype weapon. 
Choose 1 of the following: 
\begin{itemize}
\item Tweak optics:
     You always fire your prototype weapon with +1 Accuracy. 
\item Tweak Computer 
     Your prototype weapon gains the Smart property. 
\item Removing reactor shielding 
     Your prototype weapon can fire as a cone 3 weapon, a line 5 weapon, or a blast 1 weapon (choose when you fire), but costs 2 heat to fire
\end{itemize}
\rank{III}{Final Draft}
Your prototype weapon is now limited (2d6+1) and does 1d6+2 damage.
\end{talent}
