\subsection{Exemplar}

                                                  Exemplar  

Your livery is famous, your voice brassy, your weapons polished to a sheen. Your training in certain martial  

orders has given you the power to harry and hinder even the most powerful of foes.  

Honorable Challenge (Rank I): The first time you attack an enemy on your turn, hit or miss, you  
can give it your Exemplar’s Mark. A target can only be affected by this mark from one target (the  
most recent mark replaces all others).
 
The mark lasts until the start of your next turn, and while marked, gain the following reaction:
 
         Harry  
         Reaction
 
         Once per round, when an ally attacks your target and misses, you can allow them to re- 
         roll the attack. They must use the second result, even if it’s worse.
 
Punishment (Rank II): Gain the following reaction:
 
	        Punishment  
	        Reaction
 
         Once per round, when the target of your mark makes an attack against a target other than  
         you, you may immediately make a skirmish action as a reaction against your target as  
         long as your target is within range.
 
To The Death (Rank III): When you give a target your mark, you can choose to challenge it. If  
you do so, you and your marked target gain +2 difficulty to attack any target other than each  
other until the end of your next turn. While this challenge is active, you cannot willingly make any  
movement that would move you further away from your marked target, otherwise the mark  
immediately ends. It also ends if you or your target are destroyed.