\subsection{Guardian}


                                                    Guardian  
Behind the line, there is not much to do but wait and make ready. You clean your cannons. Make  
ordered rows of your shot and shell. You pack sandbags onto earthen berms. Stitch closed tears  
in the sheathes over your chassis’ joints.   

It changes in an instant. Chatter over the omni. The percussive throb of the medivac lifting off  
from the other side of the base. Somewhere a firefight. Here is your entrance music, your call to  
join the fight: a desperate cry for help from a friend distant, as the enemy draws close.   

 The flight of your shells across the sky, and the trembling earth, and the dust that once was.
 
Covering Fire (Rank I): As a quick action, you can choose a target in range of one of your heavy  
ranged weapons. That target takes +1 difficulty on all attack rolls until the start of your next turn.  
Once before the start of your next turn, if that target starts a move that carries it more than 1  
space, it immediately ends this effect, but you can attack it as a reaction with a heavy ranged  
weapon. You can make this attack at any point during its movement (such as waiting until it exits  
cover). Only one target can be affected at once.
 
 Hammerbeat (Rank II): Your target takes +2 difficulty on all attack rolls instead of +1. Any target  
struck by your covering fire is immediately immobilized until the end of their next turn.
 
 Bracketing Fire (Rank III): You can choose two targets for your covering fire instead of 1. Each  
can trigger separately.