\subsection{Hacker}

                                                     Hacker  

The Omninet is everywhere, and so are you. Since you were a kid, you played the bandwidth, able to  
access any public node — and even a few private ones — with ease. Now, as a pilot, you dive headfirst into  

the hardcode of any mech core you come across. Firewalls, Gatekeeper Protocols, Invasion, Defence —  
nothing stands in your way. You win a fight without firing a single shot; if your enemy can’t control their own  

mech, then they sure can’t do anything to stop you.   

Snow\_Crash (Rank I): When you consume Lock On as part of a tech attack, your attack deals  
+3 heat on hit.
 
Safe\_Cracker (Rank II): Gain the following options when attempting Invasion on a mech:
 
         Jam Cockpit: Your target cannot mount or dismount their mech until they take a full  
         action and succeed on an engineering check to fix their cockpit.
 
         Disable Life Support: Your target’s life support is disabled. Their mech can function in a  
         hazardous environment for a number of minutes equal to their engineering skill before  
         consequences such as radiation or lack of air start to affect them. They can take a full  
         action and make an engineering check with 1 difficulty to reactivate it.
 
         Hack./Slash: Your target cannot benefit from or make Tech actions until they spend a  
         quick action and make a successful systems check to reboot their core computer. They  
         can also shut down their mech to gain the same effect.
 
Last Argument of Kings (Rank III): Gain the following full tech option:
 
	        Last Argument of Kings (full tech): Make a tech attack vs your target. On a successful  
attack, your target is implanted with a virus that causes their core reactor to suffer a minor  
meltdown. They immediately take Burn equal to their current heat.
 