\subsection{Siege Specialist}

                                             Siege Specialist  

No wall can withstand you, no bunker can stay sealed before you. Your skill with cannon and blast is  
uncanny: after-action reports describe ordnance tagged with your firing signature hitting their targets with  

accuracy greater than AI-controlled weaponry, a stat written off as an anomaly by your commanders. Still,  

they always seem to pick you for missions where they bring out the big guns.   

Select Fire Gunner (Rank I): Once per round, while attacking with a cannon weapon, you can  
choose the following firing modes, taking +1 difficulty on the attack roll.
 
         Saturation Fire: Your weapon fires as a cone (5) but deals half damage on hit
 

                                                                                                                 


         Suppressive Fire: The next ranged attack made by targets hit by your attack is made with  
         +1 Difficulty
 
         Shock: Your targets must succeed on an engineering check or become Slowed until the  
         end of next round
 
Jackhammer (Rank II): If your mech has a cannon weapon, as a quick action, you can target a  
size 1 section of any cover, deployable, building, or piece of terrain or scenery in range. You deal  
20 AP damage to that section (typically destroying it, most size 1 sections of objects have 10  
HP). Any targets adjacent to your target are knocked back 1 space directly away from it.
 
(Rank III): 1/round when you fire a cannon weapon, your primary target and all adjacent actors to  
both that target and your mech are knocked back directly away from you or your target up to 1  
space and must pass a hull check or be knocked prone. Your primary target is unaffected.
 