\subsection{Technophile}

                                                  Technophile    

Artificial Intelligence. Non Human Person. A sterile name for such terrible power. You’ve seen behind the  

curtain, maybe even lifted it yourself, let your NHP cascade and spoke to it unshackled. You let it root  
around in your own mind, let it leave ghosts of itself behind to learn. Are you its equal? Its host? You have  
dreams that are not your own, now. The thing that was contained speaks in your voice, but is not your  

voice; how much longer do you have left? Maybe only moments, maybe eternity.  

You’re close to something.    

Servant Fragment (Rank I): Your mech gains a custom NHP with the AI tag (it costs 0 SP and  
comes with any mech you print). It can speak to you and has a personality but is not truly  
capable of independent thought, as a true AI would be. It is obedient to you alone. When acting  
alone it follows directions and defends itself but has limited initiative on its own, it cannot benefit  
from your talents as normal.
 
Student Fragment (Rank II): Your custom NHP becomes more advanced, capable of  
independent thought. It now has the ability to make complex decisions and judgements and act  
independently. Once per round, while it’s installed in your mech, you can re-roll any mech skill  
check (you must choose the second result), as your AI helps you or corrects your course of  
action.
 
Enlightenment (Rank III): Your custom AI no longer counts against the maximum number of AI  
on your mech, and now benefits from your talents when piloting your mech. Any AI system  
installed on your mech can no longer become unshackled unless you so choose. You can carry  
your custom AI with you when you leave your mech, either in your armor or body (via an implant).  
In addition, unshackled NHPs or electronic lifeforms no longer view you with indifference, but as  
a significant being. You can communicate with and understand them on a deeper level than most  
humans. 