\subsection{Harrison Armory Barbarossa}

                           HARRISON ARMORY BARBAROSSA  

The BARBAROSSA chassis is a massive frame, built to carry the heaviest of weapons and equipment.  

Standing nearly forty feet tall at its highest point, the BARBAROSSA is a slow, unsubtle beast of a mech,  
inspiring terror in enemies and comfort in allies. The weapons it can mount are capable of going toe-to-toe  
with corvette and cutter class ships; indeed, due to its size and slow maneuverability, the BARBAROSSA is  

                                                                                                          


commonly employed in micro and zero gravity engagements where mass is less of a factor. The  
BARBAROSSA is rated for all theaters, and excels in ranged combat situations.   

                                                  License:
 
I. Siege Stabilizers, Roller Grenades
 
II. BARBAROSSA FRAME, Auto-Loader, Flak Cannon
 
III. External Ammo Feed, Siege Cannon
 

                                            BARBAROSSA 

 HP: 10         Evasion: 6                           Speed: 2           Heat Cap: 7       Sensors: 10 

 Armor:  2      E-Defense: 6                         Size: 3            Repair Cap: 4     Tech Attack:  
                                                                                          +0 

                                                  TRAITS: 

 Heavy FRAME: The Barbarossa cannot be knocked back or prone by actors smaller than itself
 
 Siege Shield: The Barbarossa has resistance to Explosive Damage
 
 Slow: The Barbarossa gets +1 Difficulty on Agility checks 

                                           SYSTEM POINTS: 5 

                                                 MOUNTS: 

 Main Mount                                          Apocalypse Rail 

                                              CORE system 

                                                                                                          


                                                Apocalypse Rail  

 The HA Apocalypse Rail is a spinal mount augmentation that adapts the weapon mounted upon it to  
 patch directly into its host mech’s coldcore. This allows for energy conservation/overcharge cycling:  
 most effective with energy weapons, this system allows a pilot to dump excess offensive energy from  
 sub-super weapons and systems into its central core, exciting the cold-burn system into an overcharge  
 state, which is then used to overpower and override inherent limiters built into the factory spec weapon  
 mounted in the Apocalypse Rail. This overcharge state allows for momentary overclocking of the AR- 
 mounted weapon, sacrificing mobility and auxiliary abilities in favor of stationary defense and attack.   

 Passive: Your mech has the apocalypse rail, a weapon mount that takes a superheavy or smaller sized  
 weapon. You can still mount smaller weapons on the apocalypse rail. You don’t need an additional  
 mount to add a superheavy weapon to this mount. This mount is not modifiable (such as from core  
 bonuses).
 

 Active (requires 1 core power): Convert to Battery  
 Quick Action
 
 Your mech converts to something more resembling a gun emplacement. While this mode is active, you  
 have the following drawbacks:
 
      -   Your mech is immobilized
 
      -   You cannot directly attack any target within range 5 of your mech
 
      -   You can only make attacks with the weapon mounted in your Apocalypse Rail
 
 However, you gain the following benefits:
 
      -   You cannot be moved (such as with a grapple) by any target smaller than you
 
      -   You have resistance to heat
 
      -   The weapon mounted in your Apocalypse Rail can be fired twice with the Barrage action  
          instead of just once. If it has the loading tag, it can still be fired twice (but must be reloaded  
          normally after) 

Siege Stabilizers  

Some weapons require further stabilization for optimal use: with Armory-sanctioned Siege Stabilizers  
installed, a chassis becomes a stable firing platform for any weapon.   

1 SP  
Quick Action
 
Extend or retract your stabilizers as a quick action. Your mech is immobilized while this system is  
active, but you can increase the base range of your ranged weapon attacks by +5. You cannot  
directly target any target within range 5 when this system is activated.
 

Roller Grenades  

2 SP, Limited (2)  
Quick Action, Grenade  
Instead of throwing these grenades normally, draw a line 15 spaces long from your mech. These  
grenades bounce over cover and objects up to size 1, and can pass through holes or areas as  
small as size 1/2. They detonate when they move through or adjacent to any actor’s space (even  
allied ones), dealing 2d6 explosive damage to that target only and knocking that actor back in  

                                                                                                                


the direction of the line 3 spaces. The target can pass an agility check to avoid the knock back  
and halve the damage.
 

Auto-Loader Drone  

Auto-Loader Drones are half-size, many-legged arthropod-analogous drone systems that assist  
sectionmate chassis in loading ordinance, maintaining powerline hookups, and cycling magazine-fed  

weapons.  

2 SP, Limited (1)  
Drone  
This drone can be deployed in an adjacent space. While deployed, once per round, any one  
adjacent mech can reload a weapon with the Loading tag as a quick action. It lasts until the end  
of the current scene, then deactivates.
 

Flak Cannon  
A quad-barreled autocannon, flak cannons are loaded with proximity-explosive shells perfect for  
blanketing fire. A perfect weapon for use against massed infantry or low-altitude flyers.   

Main Cannon
 
Reliable 1
 
Range 20
 
1d3 Kinetic Damage
 
Any flying target hit by this weapon must pass an agility check or immediately fall.  

External Ammo Feed 
 

An EAF is a general term for any manner of additional ammunition not carried in a chassis‘s integrated  
storage. Whether in magazines strapped to brachial, trunk, or ambulatory elements; battery packs attached  

to hip clasps; or massive, dorsal-mount ammunition/ charge packs, an EAF ensures that you‘ll have more  
than enough boom to get the job done.   

3 SP, Unique
 
Once on your turn, you can take 1d3+1 heat to reload any weapon with the Loading tag as a  
quick action
 

Siege Cannon  

Siege Cannons are the Armory‘s core-squadron level artillery, a howitzer-style 10“ gun fed by a self- 
contained loading system. Commonly mounted on rear-line mechs deployed in an artillery/ squad support  
role, the Siege Cannon is capable of direct fire should the necessities of dynamic combat call for it. Siege  

cannons can fire HE and canister FRAMEs, depending on the target.   

Superheavy Cannon
 
4 heat (self), Arcing, Ordnance, Loading
 
Range 30, Blast 2
 
3d6 explosive damage
 
