\subsection{Harrison Armory Core Bonuses}

                           HARRISON ARMORY CORE BONUSES  

When you choose a core bonus every 3 license levels, you can pick a bonus from this list as long  
as you have at least 3 license levels in H.A. licenses for each H.A. bonus you have. For example,  
if you have 6 points in H.A. licenses, you could take up to 2 bonuses. H.A. bonuses are focused  
on repair, heat capacity, and overcharge.
 

ARMORY SCULPTED  
Rather than simply queuing a stock chassis like any other pilot, you’ve used your reputation, contacts, or  

status in the Armory’s hierarchy to requisition a chassis that is designed, tested, and tuned by a master  
fabricator.    

Your mech takes +1 Accuracy to all engineering checks
 

HEATFALL Coolant System  

The HEATFALL system comes packaged with a stable COLDCORE power core of Armory make; when  

paired together, this suite makes for an incredibly low-tax powerplant.   

The heat cost for overcharging your mech never exceeds 1d6.
 

INTEGRATED AMMO FEEDS  

By streamlining and better integrating all automated ordinance loading modules, your chassis’ time-to- 
target minimums are greatly improved. As an added bonus, your overall carrying capacity has been  

increased, allowing you to field more ordinance than design specifications suggest.    

Your mech gains +1 use to all limited systems or deployables
 

REDUNDANT REPAIR SYSTEMS  

All Armory chassis are engineered to have multiple failsafe systems: yours has been over-engineered to  
make SURE you won’t go down fast. Your chassis comes with a ream of single-item print sheets to be  
applied to any scoring damage or hull breaches.    

You can now spend 3 repairs as part of a Stabilize action in combat to repair 1 reactor stress and  
cool your mech, or regain 1 structure and heal your mech to full.
 

STASIS SHIELDING  

A Think-Tank exercise in extending stasis beyond the capabilities of civilian utility, stasis shielding is a  
cutting edge Armory system that identifies critical systems and blankets them in HOLDFAST stasis lock,  
preventing further degradation for a limited period of time until repairs can be made.   

Your mech gains +1 repair capacity. Repairing a destroyed weapon or system during a rest now  
costs 0 repairs (only the time to rest).
 

                                                                                                                 


SUPERIOR BY DESIGN  

Even the entry-level Armory chassis are designed to be better than the competition. By flexing the sheer  
amount of resources they have at their disposal, the Armory can out design and out produce other smaller,  

boutique engineers and fabricators. Where there is resistance, the answer is simple: buy them out, or  
stamp them out. You, pilot, benefit from this -- so why worry?   

Your mech is immune to the impaired condition and gains +1 heat capacity
 