\subsection{Harrison Armory Iskander}

                              HARRISON ARMORY ISKANDER  

The ISKANDER is a specialist‘s chassis, designed to provide area-denial and breach capability to squads in  
which it is a member of. A large chassis, the ISKANDER commonly sports weapons meant to ensure  

dominance in all close-quarters situations, as well as increased blast shielding to protect its pilot from  
deadly concussive forces. 
 
                                                   License:
 
I. Stub cannon, Repulsor Field
 
II. ISKANDER FRAME, Assault Launcher, Gravity Gun
 
III. Sticky Bombs, Grounding Charge
 

                                                ISKANDER 

 HP: 8          Evasion: 8                            Speed: 3           Heat Cap: 7        Sensors: 15 

 Armor: 1       E-Defense: 10                         Size: 2            Repair Cap: 4      Tech Attack:  
                                                                                            +1 

                                                  TRAITS: 

 Mine Deployers: When the ISKANDER uses a quick action to plant a mine, it can plant up to 2 other  
 mines in free adjacent spaces as a free action.
 
 Skeleton Key: The ISKANDER never activates mines or other systems that activate by proximity unless  
 it chooses to (allied or enemy). 

                                            SYSTEM POINTS: 6 

                                                  MOUNTS: 

 Flexible Mount                    Heavy Mount 

                                               CORE system 

                                                                                                            


                                             Broad-Sweep Seeder  

 The ISKANDER’s broad-sweep area-denial/countermeasure Seeder is a HA proprietary system  
 developed during the Orrugi Occupation, where HA Acquisition Legionnaires encountered an  
 embittered, recalcitrant local guerilla movement. IEDs, VBEDs, and D/SABEDs were common weapons  
 employed by the local resistance: to counter this threat, the Armory developed a triple-use system to  
 scan, ID, and eliminate explosive threats in proximity to stationary units. This system proved successful  
 and, with minor adaptation, was tuned for use on Armory chassis.   

 The Broad-Sweep Seeder projects a hivecone of excited LIDAR that flags potential targets: mag- 
 accelerated, dull-coat flechettes then disable that target. This system may also load explosive-backed  
 hivemines.   

 Active (requires 1 core power): Death Cloud
 
 Action
 
 As an action, your mech fires an enormous expanding cloud of micro-mines across the whole  
 battlefield. Any mech of your choice on the whole battlefield (or a roughly 50x50x50 area), that  
 voluntarily moves more than 1 space takes 3 AP explosive damage. If a mech boosts, it takes 3 AP  
 explosive damage immediately. Characters are aware of the presence of the mines. They last until the  
 end of 3 rounds, counting this one, then deactivate.
 
 You do not activate mines from this system. 

Stub Cannon  
A supercompact rotary pistol, short range, but able to be integrated into hardpoints or held in a  
manipulator.  

Auxiliary Cannon
 
Limited (6), Knockback 1
 
Range 5
 
3 explosive damage  

Repulsor Field
 

1 SP, Unique
 

Quick Action
 
You can use this system as a quick action to emit a burst 2 pulse around your mech. Targets  
caught in the area (allied or enemy) must pass a hull check or be knocked back directly away  
from you 1 space. The pulse then detonates any mines or explosives caught in the field
 

Assault Launcher  

Assault launchers are universal launchers. Ammunition is loaded first into a comparable sabot, then  
electromagnetically accelerated either directly or indirectly towards its target. The sabot shatters upon  
firing, releasing the projectile to perform as designed at range far greater than factory limits.   

2 SP  
You can fire and deploy mines and grenades up to any point in range 15 and line of sight instead  
of their regular range. 
 

                                                                                                               


Gravity Gun  
The complex negotiations of gravity and time, shattered in an instant by a machine that can pluck  
a waves like a player strums a guitar string.   

We’ve weaponized the thing that holds all things in its embrace. What could go wrong?  

Heavy Rifle
 
Range 8, Blast 3
 
When you attack with this rifle, all targets caught in the area must pass a hull check or take 1d6  
energy damage and be pulled as close to the center of the blast as possible.
 

Sticky Bomb Launcher  

Sticky bombs attach to ferrous metals by means of burnout electromagnetic generators, triggered in  
proximity after firing or manually by the user.   

Main Launcher
 
Arcing
 
Range 15
 
To fire this weapon, you can attack a point on the environment within range without rolling, or  
make a regular ranged attack roll against a target within range. On a hit, the target or area does  
not take damage, but instead has a sticky bomb attached. It takes a quick action and a  
successful engineering check to remove all sticky bombs from an area or mech.
 
As a free action, you can detonate all sticky bombs fired by this weapon to deal 1d6 explosive  
damage in burst 1 area centered on all targeted mechs or areas. Mechs caught in the blast area  
can pass an agility check to halve this damage, but mechs ‘stuck’ by this weapon fail their check  
automatically.
 

Grounding Charge  

Grounding charges take the pulse/wave principle of the thumper and applies a second component: gravitic  
generation. When triggered, the initial pulse wave acts similarly to the Thumper, but immediately after the  

wave dissipates, the grounding charge triggers a gravity well that pulls all destabilized materiel towards it. A  
potent anti-positional weapon, grounding charges are commonly used to disrupt prepared positions and  
pull enemies from cover.   

2 SP, Limited (1)  
Mine  
This charge can also be detonated with a quick action. Once detonated, targets in a burst 6 area  
centered on the charge must make a successful hull check or be knocked prone and pulled as  
far as possible towards the charge as though they moved normally (starting with the closest  
target). The charge also pulls any flying mechs or vehicles within range 6 above the area that fail  
the check to the ground, taking damage as if they fell.
 
