\subsection{Engineer}

                                                   Engineer  

Pilots are creative and driven individuals, but you’re an exceptional case - some would say to the point of  

excess. In your spare time you’ve managed to scrape together just enough scrap, requisitioned materials,  
and workshop space to apply a little old fashioned ingenuity to your mech.  

Spark (Rank I)  
On a full repair, you can, with some trial and error, install a prototype weapon system on your  
mech. It has the following profile -- the specifics you may choose upon installation. Roll the  
Limited property each full repair. You can change the profile of this weapon each time you full  
repair.
 
         Prototype Weapon
 
         Main (Choose 1; Melee, Rifle, Cannon, Launcher, CQB)
 
         Limited (1d6+2), Overcharged
 
         Threat 1 (melee) or range 8 (ranged)
 
         1d6 kinetic, explosive, or energy damage
 
This weapon does not take a mount to add to your mech, and counts as its own mount.
 
Updated Plans  (Rank II)  
On a full repair, you can remove and tweak essential components of your system in order to  
increase the effectiveness of your prototype weapon.
 
Choose 1 of the following:
 
  - Tweak optics:  
         You always fire your prototype weapon with +1 Accuracy. 
 
  - Tweak Computer
 

                                                                                                                 


         Your prototype weapon gains the Smart property. 
 
  - Removing reactor shielding
 
         Your prototype weapon can fire as a cone 3 weapon, a line 5 weapon, or a blast 1  
         weapon (choose when you fire), but costs 2 heat to fire
 
Final Draft (Rank III): Your prototype weapon is now limited (2d6+1) and does 1d6+2 damage.
 