\section{Damage}
 DAMAGE

You want to avoid or mitigate incoming damage as much as possible, but know this: Sometime,
somewhere, someone is going to punch a few holes in your kit.


Damage in LANCER comes in three types: Explosive, Energy, and Kinetic, each representing a
different type of weaponry or projectile.


Armor, like with pilots, reduces all incoming damage by the amount indicated. Damage with the
AP tag ignores armor.

Resistance reduces all incoming damage by 1/2 of a particular type. Mechs can only have
resistance once (it doesn’t stack) for a particular type of damage.


Damage in LANCER resolves as follows:

             1.  Reductions from armor

             2.  Reductions from systems, talents, and reactions, such as those that grant
                 resistance. Only one reduction of a type or system can be applied at once.

Remaining damage is dealt to your HP, your HIT POINTS.


For example: Your total HP is  15. You take fire from an enemy, who scores a successful hit by
beating your mech’s Evasion. You’re dealt 12 points of kinetic damage. Lucky for you, you have
armor installed on your mech, which subtracts 2 from all incoming damage, reducing the final
amount of incoming damage to  10. Your total HP after all modifications to incoming damage
have been applied is now 5. Take cover!

                                               Heat and Burn

Some weapons also deal Heat or Burn.

    -    Heat is not affected by armor, though it can be affected by resistance. It fills up a mech’s
         heat capacity (see the section below)

    -    Mechs affected by Burn immediately take damage equal to the burn they just took,
         ignoring armor. At the end of their turn, a mech can make an engineering check. On
        success, they clear all Burn on themselves, on failure, they take damage equal to their
        current Burn. Burn can stack with itself (so being hit by Burn 3 twice would increase it to
         Burn 6). Burn is its own damage type.

\subsection{Structure}
                                                Structure

If your mech is ever reduced to 0 HP, unlike a pilot, you are not down and out. Your mech is a
powerful machine that can take multiple hits before it starts to be break down. This is
represented by structure. Player mechs have 4 structure, NPC mechs might have less.





When a mech or other actor with structure is reduced to 0 HP, it takes 1 structure damage,
makes a structure check, then resets its HP to full. It then takes any damage that ‘spills
over’ (this could cause it to lose multiple points of structure and make multiple structure checks
in a turn). Structure damage represents major damage to your mech or its systems.


If your mech takes its last point of structure damage and checks its last box, it goes into the
CRITICAL state (see below). This is a state in which your mech is so heavily damaged that it
begins falling apart with every hit. NPCs that run out of structure typically are destroyed.

\subsubsection{Structure Damage}
                                        STRUCTURE DAMAGE
When your mech is reduced to 0 HP or when it takes any damage in the CRITICAL state, you roll
on the structure damage chart. Structure damage represents the results of unusually powerful or
accurate hits, which can disable a mech rapidly if not dealt with. When you make a structure
check, roll 1d6 per point of structure damage you have marked. When rolling multiple dice,
choose the lowest result, though certain outcomes activate if you also roll multiples 1s.


                                            STRUCTURE DAMAGE

 ROLL            RESULT                   EFFECT

 5-6             GLANCING BLOW            Emergency systems kick in and stabilize your mech. However, your
                                          mech is impaired until the end of your next turn.

 2-4             SYSTEM TRAUMA            Parts of your mech are torn off (potentially limbs). All the weapons
                                          on one mount or a system chosen by you is destroyed. If a system
                                          is used up (it has the limited tag and no charges left) it’s not a valid
                                          target. If there’s nothing left to destroy, this result becomes DIRECT
                                          HIT instead.

 1               DIRECT HIT               This result has different outcomes depending on how much
                                          structure damage your mech has remaining.

                                          3+ - Your mech is stunned until the end of your next turn.

                                          2 - Your mech must pass a hull check or be destroyed.
                                          1 - Your mech is destroyed.

 Two or          CRUSHING HIT             Your mech is damaged beyond repair and is destroyed. You can
 more 1s                                  still exit it as normal.

                                              The CRITICAL state


When your mech ticks off its last point of structure (typically 4), it immediately enters the
CRITICAL state, remaining at 0 hp. While CRITICAL:

             -    Your mech cannot repair or gain Hit Points.

             -    When you take damage, you make a structure check.

This allows a mech to stay fighting at great personal risk to the pilot. A mech can exit the
CRITICAL state only by resting or taking a full repair. When a mech exits the CRITICAL state it
returns to 1 HP.

\subsection{Heat and Overheating}

  HEAT \& OVERHEATING

Heat represents the stress of combat on a mech’s electronic systems and mechanical
components. Generally a mech is equipped with heat sinks, shunts, and coolant systems and to
operate within factory defined standards without generating heat. However, combat and
activated abilities can tax your mech’s heat dispersal systems to the point of causing actual
damage. Electronic warfare attacks, environmental hazards, weaponry, and overcharging can all
cause heat buildup.


Each Mech has a Heat Capacity that determines how much heat they can handle without things
getting dangerous. It can be increased through certain systems and by improving a mech’s
engineering score. A mech with a negative bonus to heat capacity has less than a mech with no
bonus. A mech reactor also can take a certain amount of stress before its reactor core is
breached and it starts to completely melt down. Most mechs have 4.


When a mech takes Heat, mark it off. If you gain heat that puts you up to your heat capacity or
over, check 1 reactor stress, then make an overheating check on the OVERHEATING chart by
rolling 1d6 per point of stress you have. If rolling multiple dice, choose the lowest result. Then
your mech fully cools, erasing all heat from the heat gauge. You take any heat that ‘spills over’ to
your gauge again. This could cause you to overheat more than once.


                                                OVERHEATING


 ROLL       RESULT                  EFFECT

 5-6        EMERGENCY               Cooling systems recover and manage to contain the peaking heat
            SHUNT                   levels. However, your mech is impaired until the end of your next turn.

 2-4        POWER PLANT             Your mech’s power plant becomes unstable, ejecting jets of plasma.
            DESTABILIZE             Your mech is Jammed until the end of your next turn

 1          MELTDOWN                This result has different outcomes depending on how much reactor
                                    stress your mech has remaining.

                                    3+ - Your mech is immediately shut down

                                    2 - Your mech must pass a engineering check or suffer a reactor
                                    meltdown at the end of 1d6 turns after this one (rolled by the GM). You
                                    can reverse it by taking a full action and repeating this check.

                                    1 - Your mech suffers a reactor meltdown at the end of your next turn

 Two 1s     IRREVERSIBLE            Your reactor goes critical. Your mech will suffer a reactor meltdown at
            MELTDOWN                the end of your next turn.

                                               COOLING HEAT




You can reset your heat gauge by taking the Stabilize action in combat or using other systems.
You also automatically cool heat when you rest or full repair. Whenever you cool heat, your gauge
resets, clearing all heat.


                                            The DANGER ZONE

When a mech has 1/2 of its total heat capacity filled, it’s in the danger zone. Certain mech
weapons and talents only activate in this area. While a mech is in this zone, it’s visible - parts of
your mech will be glowing, smoking, or steaming. Reactor vents or other cooling mechanisms
might be visible hot or working overtime.


                                              CORE BREACH

If you check your last (typically 4th) stress box, your mech enters the CORE BREACH state. In
this state your gauge does not reset, you can no longer cool, and whenever your mech takes
heat, it makes an overheating check. You can exit this state by resting or taking a full repair.

\subsubsection{Reactor Meltdown}

                                      REACTOR MELTDOWN

Certain critical and overheating table results can cause a reactor meltdown. This can be
immediate, or involve a countdown (in which case update the countdown at the start of the
round. The meltdown triggers when specified). When a mech suffers a reactor meltdown, any
pilot inside immediately dies, the mech is immediately vaporized in a catastrophic eruption (it
becomes completely unrepairable), and any mechs inside a burst 2 area centered on the mech
must pass an agility skill check or take 4d6 explosive damage, and half on a successful save.


\subsection{Repair}

                                               REPAIR

A Repair is in or out of combat healing to your mech. Repairs represent the resilience of your
mech and its ability to continue functioning while damaged, as well as physical assets such as
parts or tools. You can spend a repair by taking the Stabilize action in combat, repairing your
mech during a rest, or using systems that allow you to repair.


In combat, you can spend 1 repair as part of Stabilize to heal your mech to full HP.


During a rest, your mech cools all heat. You can then spend any number of repairs. 1 repair can:

    -    Refill HP to maximum

    -    Repair a destroyed weapon or system.

4 repairs can be spent to repair a destroyed mech (during a rest only, see below)


A pilot’s Repair Capacity is equal to 4+ HULL. This indicates the number of repairs a pilot can
make before returning to base - so if a mech’s repair capacity is 8, it can only spend 8 repairs
before taking a full repair. If a pilot has no repairs left, they cannot repair their mech! This
capacity refreshes to full when a pilot takes a full repair.


                                                 DESTROYED

When destroyed, a mech counts as permanently stunned and shut down until it is restored to
working condition (these conditions cannot be removed in any way). It then becomes an object
on the battlefield and provides cover accordingly. The wreck can be moved and dragged around.

\subsubsection{Repairing a Destroyed Mech}
                                  Repairing a Destroyed Mech

If a mech is destroyed and the wreck is present (not melted in a reactor explosion, for example), it
can be repaired to working order by spending 4 repairs during a rest. These repairs can be spent
from the mech’s own pool or the pools of any pilots that wish to contribute, in any combination. If a
mech has 0 repairs remaining, it can still be repaired if other mechs spend repairs, for example.
This is unique to repairing a destroyed mech.

Once repaired, the mech is returned to 1 structure at full HP, no matter how much it had before.
Any weapons or systems that are destroyed remain so unless that mech spends its own repairs to
fix them.
\subsubsection{Full Repair}
                                                Full Repair

If you take at least 10 hours of downtime in a secure location, you can Full repair. You can
repair all damage on your mech unless it is completely destroyed, returning it to full HP and




clearing all stress and structure (you can also repair destroyed systems). Your repair cap
refreshes to full, your pilot heals to full (or returns from being down and out), you can reset
your CRITICAL and heat gauges, and end all statuses other than destroyed (including
CRITICAL and CORE BREACH). You also regain core power if you lost it and get back all
(limited) use weapons, that you checked off.

\subsubsection{Printing}
                                                   Printing

If your mech is destroyed, even if you don’t have the wreck with you, you can rebuild it during a
full repair as long as you have access to the proper facilities. Mechs can be printed whole-cloth
from enormous Union printing facilities, which are generally ubiquitous across civilization. A
printer and assembler will perfectly recreate any mech or gear you have licenses for. If you need
to work on a destroyed mech and don’t have a printer, it’s also possible to repair it during a full
repair without a printer, but you need the wreck.


                                            One At a Time, Please

You’re only licensed to print a single active mech at a time. Only the newest mech you printed
will function (any others repaired, etc will cease to function).

\subsubsection{Rests}
                                                     Rests

A rest is defined as at least 1 hour of uninterrupted downtime or light activity (making camp,
routine maintenance, for example). After a rest, as long as you took action to do so:

             -   Cool heat
             -    Heal 1/2 your pilot HP or return from being down and out

             -    Exit the CRITICAL or CORE BREACH state if you’re in it and return to 1 HP and
                 clear 1 heat.
             -   You can spend any number of repairs to repair your mech, as long as you don’t
                 spend over your repair cap. You can also repair a destroyed mech.
             -   You can end any statuses currently affecting your mech automatically.


\subsection{Death}
  DEATH

The destruction of a mech does not always mean the death of a pilot. Pilots can escape and exit
from shutdown, disabled, or even destroyed mechs, presuming they survived. A pilot can always
re-create a mech - the pilot is much harder.

\subsubsection{Cloning}
                                                  CLONING

Pilots are tremendous investments in hardware and training and tend to have powerful and well-
connected patrons. It should not be surprising, then, that the technologies to resuscitate dead
flesh or create imperfect, flash-grown genetic clones of pilots, though often illegal or highly
secretive, do exist, and are often utilized by powerful organizations who don’t wish to give up on
their investments.


Cloning or revivification is a costly and dangerous process. It’s always up to the player whether
they want to bring a character back or simply make a new one. Flash-cloning or revivification
is an experimental process that always creates complications. These caveats are here by
default, and can be tweaked by the GM at their discretion:


    -    A cloned or revived character can only re-join the party after a mission’s completion.

    -    A cloned or revived character knows and learns nothing of the mission that they died on

    -    A cloned or revived character always comes back with a Quirk.

             -   The quirk could be physical or mental in nature, but whatever the quirk is, it
                 should be a story hook or something narrative in design (it shouldn’t have any
                 major gameplay effects).

             -   Quirks are always complicating - though your character might adjust to them in
                 time, they are a shock to the system.
    -    If a cloned or revived character would be cloned or revived a second time, they can no
         longer be played as a player character. The trauma and personality shift from being
         brought back to life is too great. In other words, you’re one and done.


If you want to roll for a random Quirk, you can roll 1d20 or choose from the below chart. You can
use these as examples for your own quirks and are free to figure out between you and your GM
what quirk your pilot comes back with.


                                                 Random Quirk


 Roll
      Quirk
 (1d20)

 1          Part (or all) of your body was too damaged or badly cloned and needed to be amputated and
            replaced with cybernetics. These are high quality prostheses, and are not visibly synthetic to a
            casual observer. The extent of the damage is unknown to you.




2          The process required you be fitted with a visible cybernetic augment, such as an arm, leg,
           eyes, or the like. It is conspicuous and often attracts unwanted attention.

3          By accident or malintent, you have been cloned into someone else’s body. They might be
           someone noteworthy or important.

4          You are cloned or revived with a nasty, disfiguring scar, a mutation, or a hideous appearance
           that clearly marks you as vat-grown.

5          Administrative mishaps lead to complete and drastic change in appearance in your new body

6          An extra, withered limb grows out of your chest shortly after your cloning or resurrection. It
           sometimes moves on its own.

7          A conspicuous barcode is now printed on your body. The barcode has meaning to powerful
           organizations, but you are not initially privy to its meaning.

8          Under certain light conditions, it is possible to read a script or inscription printed just under
           your skin. The script is all over your body and contains a scientific formula, a map, or other
           information contested by powerful organizations or entities.

9          Your new body is too frail to survive the exposure to direct light and air and requires you wear
           an environmental suit outside of sterilized environments or your mech.

10         DNA from a non-human or possible xenobiological source was used in your resuscitation. Your
           revivers will not tell you the exact details or what effects it will have on you long term, and treat
           you more as a science experiment. You now have a useful, visible (though able to be hidden)
           cosmetic variation.

11         You are stricken with persistent dreams, visions, and images of your death in vivid detail
           whenever you try and sleep or rest. You know they are all real, but cannot reconcile the
           existential gulf between what your previous “you” experienced, and your new subjectivity.

12         You are replaced by a digital ‘homunculus’, an electronic imprint and reconstruction of your
           personality that occupies a subaltern, a kind of robotic shell.

13         You are plagued by the constant understanding or belief that the ‘real’ you is actually dead,
           and you are merely a shadow aping a dead person, implanted with the memories of someone
           else. You cannot establish the difference between the “you” that died and the “you” that exists
           now.

14         Due to a clerical mishap, you are implanted with the residual memories of an entirely different
           and powerful or influential person. This reveals very dangerous and potentially unwanted
           information to you that is contested or sought after by powerful entities.

15         The process goes awry and you are revived tabula rasa. In desperation, the techs dump a
           stock personality construction into you. Change your background (adjust your skills
           accordingly)

16         The process of revival is not without complications. Your natural lifespan is dramatically
           shortened, and you know you will have to undergo another flash-cloning in the near future.

17         Something changed you, and you have persistent and intrusive mental contact with another
           entity or entities. It could be human or non-human in nature.

18         You often are struck with searing headaches during which you see brief flashes of what you
           are pretty sure is the future. Sometimes it comes to pass, sometimes it doesn’t.




 19        Knowingly or unknowingly, you are implanted with a mental trigger that when heard or
           activated, causes you to go into a receptive state, either following a pre-programmed course
           of action (kill, lie, etc) or to listen to and follow exactly the commands of the person who
           activated you. These commands must be simple, and the person who gives them (PC or NPC)
           is determined by the GM.

 20        You are brought back with complete amnesia of the time before you were re-born, causing a
           ‘tabula rasa’ situation in which you must be re-trained and cultured, a costly process. Your
           skills completely reset. Re-assign them as if you were level 0 and just leveled up to your
           current level.
