\chapter{Mech Skills}
                                                  Mech Skills

A mech operates on an entirely different level in LANCER: a powered, armored hulk with
incredibly powerful systems, weaponry, and physical strength. A mech is capable of far more than
a pilot on foot, and can perform feats of incredible strength, speed, and resilience where skill
alone will not suffice.

Your character’s pilot skills relate to their personal aptitudes on foot, whereas your character’s
mech skill refer to their abilities piloting and building mechs. A Mech skill check can be referred to
by the name of it’s statistic, such as a Hull check, a an Agility check, etc.

Each mech skill has a primary benefit and use. Unlike pilot skills, mech skills also give your mech
bonuses while building or creating a mech.

HULL describes your ability to pilot and build mechs with high strength, structure, and frame
reinforcement. Mechs with a high hull can survive a lot of punishment and perform feats of
enormous strength.

Roll Hull when: Smashing through or pulverising an obstacle, vehicle, or building; lifting, dragging,
pushing, or hurling an enormous amount of weight; grabbing, wrestling, or grappling a mech,
starship, or mech-sized creature; resisting a huge amount of force, staying upright through
cataclysmic weather

AGILITY describes your ability to pilot and build mechs with speed, reactivity, quickness, and
dexterity. Mechs with a high agility are lightning fast for their size, and can react quickly and
accurately.

Roll Agility when: Chasing, pursuing, or fleeing with incredible speed; performing acrobatics in
your mech; hiding or moving silently; performing a feat of fine manual dexterity with your mech;
dodging out of the way of danger

SYSTEMS describes your ability to build mechs with powerful computing and electronic systems,
often aided by sentient or sub-sentient programs. Mechs with powerful Systems scores have a
mind-boggling amount of computing power, some of which may not even exist in realspace.

Roll Systems when: Infiltrating hardened and powerful electronic systems and targets, including
other mechs; boosting or suppressing a signal; performing electronic warfare; scanning or analyze
information; boosting or weakening the electronic systems of a vehicle, mech, starship, or base;
interacting safely with Non-Human Persons or electronic life forms; analyzing the nature of
unfamiliar electronic systems.




ENGINEERING describes your ability to build mechs with powerful reactors, high tech weaponry,
ammunition, and utility tools. Mechs with a high engineering score typically incorporate a lot of
advanced technology, are extremely resilient and reliable, can draw upon huge amounts of energy
and heat, and can push their systems far beyond their factory specifications.

Roll Engineering when: pushing your mech past its limits; withstanding extreme conditions such
as heat, cold, void, or radiation; keeping your mech running well past its breaking point or for
extreme amounts of time; traveling or move safely through hazardous or hostile conditions;
boosting the reactor output of another mech, starship, or base; conserving and efficiently using
ammo, power, and other resources

Collectively, these four skills are often referred to as H.A.S.E. You may add the appropriate rating
to a 1d20 roll for the total when making a skill check that calls for one of these ratings. You often
make HASE checks as a part of mech combat, and certain actions will call for checks, such as
hiding or grappling.