\section{Debrief and Downtime}

Once a mission is over (success or failure) and the players have time to recuperate, it's time for the \textbf{Debrief}. Much like the \textbf{Brief}, this step of a LANCER game doesn't have to be an actual meeting in-character, and could just be an out-of-character conversation amongst the people playing at the table. 

A mission being over or completed should be a natural stopping point in the narrative (it could even be mid-mission if the objectives have changed). Players don't necessarily need to have accomplished their goal, but something needs to have changed enough about the mission that the mission itself is functionally over. 

During the debrief:
\begin{itemize}
\item \textbf{Level up} - Characters gain 1 license level, representing their access to resources, income, or clout. Characters get more access to mech gear and increase their skills. You can find more information on leveling up at the end of the mech section, but pilots gain +1 to any skill and every 3 levels can gain additional training, allowing them to get +1 accuracy on certain skill triggers as if they had a background in it.
\item \textbf{Talk about the mission}. This is not a necessary step but can be helpful to think about what worked and what didn't during the session. If there were any notable moments that were fun, interesting, or exciting it can be helpful to talk about them here as well. Not only is it good feedback for the GM but also can help validate your fellow players. If you're going to take this step, remember to be respectful.
\end{itemize}  