\subsection{Ace}
                                                  ACE  

A pilot more comfortable the closer they get to their roots, the Ace enemy-type employs high-speed  

strafing runs, agile maneuvers, and a reckless approach to piloting their mech. Cocky and self-assured,  
Ace-type enemies relish a good duel.  
 

 ACE 

 Mech 

 Hull       Agility     Systems       Engineering 

 -2         +3          +1            +0 

 HP         Evasion     E-defense     Heat Cap. 

 16         11          9             8 

 Armor      Speed       Sensors       Size 

 0          6           10            1/2 or 1 

Base systems:
 
SS Corpro flight system  
System
 
Whenever this mech moves or boost, it can fly.
 

Missile Launcher  
Main Launcher
 
+1 vs evasion/tier
 
Seeking
 
Range 10, Blast 1
 
4/6/8 explosive damage
 

Optional systems:  
Bombing Bay  
System, Limited (6)
 
1/turn
 
When the mech flies while it moves or boosts, it can drop a bomb on one target below as a free  
action it that it passes over or adjacent to. Bombs create a blast 1 area with at least 1 square on  
their target. All affected targets must pass an agility check or take 6/9/12 explosive damage and  
be knocked prone.
 

                                                                                                       


Strafing Module  
System, Quick Action
 
1/round
 
The mech flies its speed in any direction in a strafing run, dealing 3/5/7 kinetic damage to any  
enemy it passes over or adjacent to (no roll required).
 

Burst/Dash module  
System
 
Recharge (5+)
 
The mech may activate this module instead of moving normally, engaging powerful thrusters. It  
flies its speed in a straight line in any direction. This movement doesn’t provoke reactions,  
ignores, engagement, and any mechs engaged with the target when it activates this module  
must pass an agility check or be knocked prone.
 

Chaff Launchers  
System, Reaction
 
Recharge (6+)
 
In response to any hostile tech action or attack, the mech launches chaff and engages digital  
scramblers, causing the attack to miss, and granting it immunity to tech attacks and ranged or  
melee attacks with the smart keyword until the end of its next turn.
 

Attitude Thrusters  
System, Reaction
 
1/round, Recharge (5+)
 
In response to being hit by any ranged attack, the mech does a barrel roll, flying 3 in any  
direction and gaining resistance to all the damage of that attack.
 

Tier II:
 
HP: + 2
 

          Evade    E-D    Heat    H     A     S    E        Armor       Spd       Sense 

          14       10     8       -2    +4    +2   +1       0            7        10 

All agility checks made as a response to the Ace’s attacks are made at +1 Difficulty.
 

Tier III:  
HP + 2
 

          Evade    E-D    Heat    H     A     S    E        Armor       Spd       Sense 

          18       11     8       -2    +6    +3   +1       0           8         10 
