\subsection{Aegis}

                                                 AEGIS  

Aegis-style mechs are squat, defend-and-suppress chassis built to hold ground, support their allies, and  

suppress enemies. Higher-tier Aegis mech pilots have access to hardlight and blackwall defensive  
measures - technology that makes bulwarks out of even the smallest barricade.   

 AEGIS 

 Mech 

 Hull       Agility      Systems       Engineering 

 +0         -2           +2            +2 

 HP         Evasion      E-defense     Heat Cap. 

 14         7            10            10 

 Armor      Speed        Sensors       Size 

 2          3            8             2 

Base systems:  
Light Laser  
Main cannon
 
+2 vs evasion/tier
 
Range 8
 
2 energy damage + 3 burn/tier
 

Defense Net  
System, Shield, Quick Action
 
This system spreads a powerful shimmering repulsion shield over a large area. While this system  
is active, this mech is immobilized, but all attacks against any target within a burst 3 zone around  
the mech originating outside of that zone take +1 Difficulty/tier. Attacks out of the zone or  
between targets that are both inside of the zone are unaffected. It can be deactivated as an  
action.
 

Optional systems:  
Adaptive Shielding
 
System, Reaction
 
1/round
 
The first time an allied target inside the defense net is damaged, all targets inside gain resistance  
to the damage type of the triggering attack until the end of the Aegis’s next turn.
 

Ring of Fire
 

                                                                                                          


System
 
All targets hostile to the Aegis that start their turn inside the Defense Net or enter it for the first  
time on their turns take 3 heat and become Shredded while inside the net (they can end this  
condition by leaving the net).
 

Hardlight cover system
 
System, shield, deployable, quick action
 
Recharge (5+)
 
The Aegis creates a line 3 section of hardlight, which grants light cover (1 difficulty) against  
incoming fire. Mechs adjacent to this cover have resistance to damage from line, blast, and cone  
attacks. The cover is immune to damage.
 
At tier II onwards, this cover grants heavy cover.
 

EM Shielding
 
System
 
The Aegis’ defense net also grants its difficulty to tech attacks made from outside the shield.
 

HA Blackwall system
 
System, Full Action
 
Limited (1)
 
The Aegis creates a pitch black wall of blinkspace that takes up a free line 10 zone 5 spaces high  
that must have at least one point within 5 spaces of the Aegis. The wall breaks line of sight  
between its two sides and no effect or attack can be drawn across it. Any mech that starts its  
turn on the wall or crosses it for the first time on its turn has a 50% chance to be lost in  
blinkspace momentarily. If this occurs, remove the mech from play. It returns at the end of its  
next turn, in any free space within range 10 of either side of the wall. If there is no space  
available, it returns when there is. The wall disappears when the Aegis is destroyed or it uses an  
action to deactivate it, also returning any stranded mechs.
 

Tier II:
 
HP: +4
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          8         12     10      +0   -1    +3    +3      2            3         10 

Tier III:
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          8         14     10      +0   -1    +4    +5      3            3         10 
