\subsection{Assassin}

                                                 ASSASSIN  

Assassin style mechs trend towards agility, damage, and speed. Their pilots sacrifice comfort for a chassis  

efficiency — unnecessary life-support systems, pilot care systems, communications systems, and others  
are stripped out and replaced with systems that increase processing power, run-silent ability, and increase  
chassis range.   

Assassin pilots work alone or in small groups, piloting their small, sleek mechs into territory thought  
impenetrable by their targets. One of the few doctrines to employ bladed weapons, assassin-style pilots  

train both in the cockpit and out of it to be able to fight with any weapon, in any theater, as efficiently as  
possible.   

 Assassin 

 Mech 

 Hull        Agility      Systems        Engineering 

 +1          +2           +0             -1 

 HP          Evasion      E-defense      Heat Cap. 

  15         12           8              7 

 Armor       Speed        Sensors       Size 

 0           8            12             1 

Base systems:  
Kai Bioplating  
Trait
 
This mech gains +1 Accuracy on all agility checks. It can climb with no penalty, takes no penalty  
for difficult terrain, and doesn’t make dangerous terrain tests.
 

Variable Knife  
Auxiliary Melee
 
AP
 
+1 vs evasion/tier with 1 Accuracy/tier
 
Threat 2
 
4/6/8 kinetic damage
 

Pulse Rifle  
Heavy rifle
 
+1 vs evasion/tier with 3 Accuracy
 
Range 12
 
7/9/11 energy damage
 

                                                                                                               


Optional systems:
 
Boltok Rifle  
Heavy CQB
 
Loading, Knockback 1
 
+1 vs evasion/tier
 
Range 3, Threat 3
 
10/15/20 kinetic damage
 
This heavy, archaic weapon replaces the Pulse Rifle.
 

Spinning Kick  
Trait, Quick Action
 
A target adjacent to the Assassin must pass a hull or agility check with 1 difficulty/tier or be  
knocked back 4 spaces away from the assassin and knocked prone.
 

Shroud module  
System, Quick Action
 
The Assassin creates a burst 3 zone of light cover within range 8. The zone disperses at the end  
of its next turn, or when the Assassin creates a new one. Mechs other than Assassins that enter  
the zone for the first time on their turns or start their turn there must pass a systems check with 1  
difficulty/tier or become Jammed until the end of their next turn.
 

Explosive Knives  
Quick Action
 
Limited (3)
 
A knife can be thrown at any surface or mech as a quick action. Make a ranged attack roll for +2  
vs evasion/tier, attaching on hit. At the start of the assassin’s next turn, the knife explodes,  
dealing 6/8/10 explosive damage in a burst 2 area centered on the knife or mech. A mech can  
remove and disarm the knife by passing a successful systems check as a quick action if they are  
adjacent to it.
 

Tracker Missiles
 
Quick Tech
 
+2 vs e-defense/tier
 
The Assassin makes a tech attack vs e-defense against a target in sensor range. On hit, the  
target has the missiles latch on to them. While attached, the target cannot hide or benefit from  
invisibility, and the Assassin always knows its location up to a 10 mile distance. The missiles can  
be removed during a rest or by taking a quick action and successfully repeating this check.
 

Tier II:
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          15       8       7       +2   +3    +1    -1      1            8         12 

                                                                                                                


Tier III:
 

         Evade     E-D   Heat    H    A     S     E      Armor        Spd      Sense 

          17       8     7       +3   +4    +2   -1      2            8        12 
