\subsection{Assault}
                                                ASSAULT  

Assault doctrine mechs and their pilots are the most common main battle chassis found throughout the  
galaxy. Fitted with a localized version of a main battle rifle, sidearm, and a suite of systems to enhance  

movement, targeting, and defensive systems, an Assault Doctrine chassis is a straightforward, reliable,  
hardy combatant.   

Assault doctrine pilots are the cheapest to train and outfit: this does not make them any less of a threat  
when paired with a kit of their choice.   

       ASSAULT 

       Mech 

       Hull       Agility      Systems       Engineering 

       +1         +1           +1            +1 

       HP         Evasion      E-defense     Heat Cap. 

       20         8            8             8 

       Armor      Speed        Sensors       Size 

       1          4            8             1 

Base systems:
 
Heavy Assault Rifle  
Main Rifle
 
Range 10
 
+2 vs evasion/tier with +1 Accuracy
 
7/9/11 kinetic damage
 

Combat Knife  
Auxiliary Melee
 
Threat 1
 
+1 vs evasion/tier
 
5/7/8 kinetic damage
 

                                                                                                           


Optional systems:
 
Underslung Grenade Launcher  
Auxiliary Launcher
 
Loading, Arcing
 
Range 8, Blast 2
 
4/6/8 explosive damage
 

Micro-missile Barrage
 
Quick action, Recharge (6+)
 
This mech makes a line 8 ranged attack with +1 vs evasion/tier for 6/9/12 explosive damage. The  
closest target hit by this missile barrage must pass a hull check or be knocked prone.
 
At tier II onwards, this hull check is made with 1 difficulty.
 

High Impact Rounds
 
System
 
The Heavy Assault rifle can be fired with high caliber rounds, adding +4 kinetic damage and the  
AP tag, but requiring a reload after firing it this way (as if it had the loading tag)
 

Auto-targeting  
System
 
The Heavy Assault rifle ignores the effects of light and heavy cover
 

Rank Discipline  
Trait
 
The Assault gains +1 Accuracy on all its attacks and checks as long as it’s adjacent to at least  
one friendly mech.
 

Tier II:
 
HP: +3
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          10       9      8        +2   +2    +2    +2      1            4        8 

Tier III:  
HP: +3
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          12        10    8        +3   +3    +3    +3      1            4        8 

                                                                                                               