\subsection{Barricade}
                                            BARRICADE  

 BARRICADE 

 Mech 

 Hull       Agility     Systems       Engineering 

 +0         -2          +1            +3 

 HP         Evasion     E-defense     Heat Cap. 

 16         6           9             10 

 Armor      Speed       Sensors       Size 

 1          4           10            1 

Base Systems:  
Cycle Lance  
Main Cannon
 
Range 10
 
+0 vs evasion with 1 Accuracy/tier
 
6 energy damage
 
This weapon can attack twice at tier III with the attack action
 

Mobile Printer  
Recharge (6+)  
As a free action at the start of its turn, the barricade may print a line 3 section of size 3 cover (3  
spaces high) in any adjacent and free space. The cover provides heavy cover and has evasion 5  
and 30 HP.
 

Shock Plating
 
System
 
The Barricade is resistant to kinetic damage
 

Optional Modules:
 
Drag Drone  
Quick Tech
 
+2 vs e-defense/tier
 
A target struck by this drone takes 2 AP energy damage for each 1 space that it voluntarily or  
involuntarily moves until the start of the Barricade’s next turn. The target is aware of this effect.
 

Seismic Repulsor  
Quick Action, recharge (5+)
 

                                                                                                       


All non-flying targets within a burst 3 area centered on the Barricade must pass a hull skill check  
with 1 difficulty/tier or be knocked back 3 space directly away from the barricade and knocked  
prone. The area in the blast then becomes difficult terrain permanently.
 

Rapid Extruder  
The Barricade can print twice as fast (can print two sections of cover at once)
 

Mag Mines  
Quick Action, Recharge 6+  
The Barricade rapidly prints and deploys a field of tiny mines that seek out targets and clamp on  
to them in droves, slowing them down and inhibiting movement. The mines take up a 5x5x5  
cube. The area is both difficult and dangerous terrain, and any target other than the Barricade  
that enters the area or starts its turn there must pass a systems check with 1 difficulty/tier or  
become Slowed the end of its next turn.
 

Snare Drone  
Quick Action, Drone
 
Limited (1)
 
The Barricade rapidly prints and deploys a snare drone in an adjacent space. This drone is size  
1, has 10 evasion and 10 HP. When any hostile mech moves within range 3 of the drone or starts  
its turn in range of the drone, it emits a pulse, immediately immobilizing that mech until the drone  
is destroyed (no check allowed).
 

Tier II:
 
HP: +3	
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          7         11     11      +1   -2    +1    +5      1            4         10 

Tier III:  
HP: +3
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          8         13     12      +2   -2    +2    +6      1            4         10 
