\subsection{Bastion}

                                               BASTION  

Bastion doctrine chassis trade the pure defensive edge of an Aegis doctrine chassis for one that  
allows more mobility. Blending area-denial offensive capability with hardened defense systems  
and advanced communication suites, Bastion doctrine chassis make for strong squadron  
commanders.   

 BASTION 

 Mech 

 Hull       Agility     Systems       Engineering 

 +2         -3          +0            +2 

 HP         Evasion      E-defense    Heat Cap. 

 16         6           8             8 

 Armor      Speed       Sensors       Size 

 3          4           8             1 

Base systems:
 
Rotary Grenade Launcher  
Main Launcher
 
Arcing, Loading
 
+1 vs evasion/tier
 
Range 8, Blast 1
 
8/11/14 explosive damage
 

Heavy Assault Shield  
Heavy Melee
 
Threat 1
 
+1 vs evasion/tier
 
3 kinetic damage/tier
 
As a quick action, the Bastion can deploy or retract its shield as a line 2, size 2 piece of heavy  
cover, disarming it of this weapon. The Bastion can leave the shield deployed and move away  
from it if it so wishes (it can pick it up again as a quick action). Any mech that gains the benefit of  
this cover against an attack also has resistance to all damage from that attack. The cover has  
evasion 5 and 20 HP and can be attacked and destroyed as normal.
 

Optional systems:  
Shard Launcher
 
System, Reaction
 

                                                                                                         


The first time a Bastion takes damage in a round, all mechs in a cone (3) area in front of it must  
pass an agility check or take 5/7/9 explosive damage, and half on a successful save.
 

Shieldwall  
Trait
 
As long as it’s holding its shield, the Bastion and one adjacent mech of its choice has resistance  
to all damage from a target of its choosing that it can see. It can only change this target at the  
start of its turn.
 

Immortality  
System, Full Action
 
Recharge (5+)
 
The Bastion and one adjacent mech of its choice are immune to all damage and effects until the  
start of the Bastion’s next turn, guarded by a flickering pane of Blackshield tech. The mech  
adjacent to the Bastion loses this benefit if it breaks adjacency. On the start of the Bastion’s next  
turn, it is stunned until the start of its following turn and cannot gain or benefit from resistance or  
immunity of any kind for the same duration.
 

Defender  
Trait, Reaction
 
Once a round, when an allied mech is damaged, if the mech is in movement range of the Bastion  
and the bastion is not immobilized, it can immediately move adjacent to that mech and take that  
damage instead of the targeted mech. This movement doesn't provoke reactions and ignores  
engagement.
 

Hypo-reinforcement servos
 
System, Shield, Protocol
 
Recharge (4+)
 
The bastion activates this system at the start of its turn as a free action if it has it available. While  
active, it reduces all damage from the very next melee or ranged attack it takes to 0. This effect  
can only stack once.
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H     A     S     E       Armor        Spd      Sense 

          7         8      9       +4    -3    +0   +3       3            4        8 

Tier III:  

          Evade     E-D    Heat    H     A     S     E       Armor        Spd      Sense 

          7         8      10      +6    -2    +0   +4       4            4        8 
