\subsection{Berserker}
                                            BERSERKER  

Berserker doctrine mechs build to take advantage of advanced heat cycling systems to shunt  
system heat tax into an offensive force, increasing their weapon output by orders of magnitude.   

       BERSERKER 

       Mech 

       Hull      Agility      Systems       Engineering 

       +3         +2          -2            -1 

       HP         Evasion     E-defense     Heat Cap. 

       15         10          6             6 

       Armor     Speed        Sensors       Size 

       1          4           5             1 

Base systems:  
Chain Axe  
Heavy melee
 
+2 vs evasion/tier with
 
Threat 1
 
7/10/14 kinetic damage
 
This weapon deals an extra +1d6 damage/tier on Critical Hits
 

Volcanic Re-route
 
System, Protocol
 
The Berserker can choose to activate or de-activate this system at the start of its turns. While  
this system is active, the Berserker can make two attacks with its chain axe when it takes the  
attack action, but it takes 4 heat at the end of its turn.
 

Optional systems:  
Molten Shield  
System, Shield, Reaction
 
Once per round, the Berserker can activate this dispersal shield when it takes damage from any  
melee attack. The damage is reduced by half, and the attacker must pass an engineering check  
with 1 Difficulty/tier or take Burn 2/tier
 

Harpoon 
 
Main CQB
 
+1 vs evasion/tier
 

                                                                                                         


Range 5, Threat 3
 
2/4/6 kinetic damage
 
Targets struck by this weapon the same size or smaller than the Berserker are pulled in a straight  
line adjacent to the Berserker or as far as possible. If the target is pulled adjacent to the  
Berserker, the Berserker grapples them automatically.
 

Calamity module  
System, Full Action
 
The Berserker can only activate this system against a target it is grappling. Auxiliary strength  
servos engage and the Berserker hurls its target with incredible violence. The target must make a  
hull check with 1 Difficulty/tier. On a failed check, it takes 8/12/16 kinetic damage, is knocked  
back 4 spaces away from the berserker, and is stunned until the end of its next turn. On a  
successful check it takes the damage and knockback, but is not stunned. The Berserker ends its  
grab after making this move, success or failure.
 

Nail Gun  
Main CQB
 
+1 vs evasion/tier
 
Range 5, Threat 3
 
5/7/9 kinetic damage
 
Targets struck by this weapon must pass an engineering check with 1 difficulty/tier or become  
immobilized until the end of their next turn.
 

Hunter jets  
System, Reaction
 
Once per round, as a reaction to any enemy movement, the Berserker can make the boost  
action.
 

Tier II:
 
HP: +5
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          11       6      6        +4   +4    -2    -1       1           4         5 

Tier III:  
HP: +5
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          12       6      6        +6   +4    -2    +0       1           5         5 
