\subsection{Breacher}

                                              BREACHER  

 BREACHER 

 Mech 

 Hull       Agility      Systems       Engineering 

 +2         +0           -1            +1 

 HP         Evasion      E-defense     Heat Cap. 

 18         9            7             8 

 Armor      Speed        Sensors       Size 

 1          4            5             1 

Base Systems  
Dual Shotguns  
Main CQB
 
+1 vs evasion/tier with 2 difficulty
 
Range 3, Threat 3
 
6/8/12 kinetic damage
 
The Breacher can attack twice with this weapon with the attack action, choosing the same or  
different targets.
 

BREACH Ram  
Quick action, Recharge (5+)
 
The breacher moves forward in a straight line as far as it can, up to its speed. It ignores  
engagement and obstruction (even for obstacles or mechs passed through). Obstacles or  
objects such as cover are punched or smashed through and take 10 AP kinetic damage/tier. If  
the obstacle is an especially hardy composition (such as a starship hull) the breacher can make a  
successful hull check to smash through instead. All other targets passed through must pass a  
hull check with 1 difficulty or be knocked out of the breacher’s path and knocked prone.
 

Optional Systems:
 
Unload  
Full Action
 
The breacher chooses a target in range of its dual shotguns. At the start of the breacher’s next  
turn, if the target is still in range, the breacher can attack that target with its dual shotguns with  
+3 Accuracy (for a total of +2 Accuracy by default) as a free action.
 

Loaded for Bear  
Trait
 

                                                                                                          


A target struck by both the Breacher’s Dual shotguns becomes shredded until the end of the  
Breacher’s next turn
 

Hunter Lock  
Quick Tech
 
+1 vs e-defense/tier with +1 Accuracy
 
The Breacher chooses a target in sensor range and makes a tech attack. On hit, all its attacks  
gain +1 accuracy/tier against that target, and 1/turn it can take the boost action as a Free Action,  
as long as it is made directly towards that target. The Breacher cannot change its target until it or  
the target is destroyed.
 

Thermal Charge  
Quick Action
 
Limited (1), Thrown 5
 
Blast 2
 
2/4/6 explosive damage + 5 Burn/tier
 

Hi Caliber Slugs  
The breacher takes 1 heat when its fires its dual shotguns, but they deal +3 damage
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          11        7      8       +3   +1    -1    +2       1           4         5 

Tier III:  
HP: +2
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          13        7      8       +4   +2    -1    +3       1           4         5 

                                                                                                                