\subsection{Cataphract}
                                            CATAPHRACT  

The Cataphract doctrine is common among rapid-strike kits that emphasize mobility, shock, and  
tenacity. Cataphract squadrons are feared across the galaxy for their ability to overwhelm  
defenses in moments: from an otherwise static line, a squadron of low and angular chassis burst  
overhead, heavy cannons and PDF guns carving seemingly impossible paths through a suddenly  
futile defense. 
 

 Cataphract 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         +1           +0            +0 

 HP         Evasion      E-defense     Heat Cap. 

 16         10           8             9 

 Armor      Speed        Sensors       Size 

 0          6            8             1-2 

Base systems:
 
Ram cannon  
Heavy Melee/Heavy Cannon
 
+0 vs evasion with 1 Accuracy/tier
 
Range 8, Threat 2
 
5/7/9 kinetic damage
 
This lance-like weapon can be fired with either profile (used as a melee or ranged weapon), but  
not both in the same turn.
 

Impact thrusters  
System, Full Action
 
Recharge (5+)
 
The Cataphract charges, moving 6 in a straight line in a direction of its choosing. It can ignore  
obstructions caused by enemies. Hostile targets that it passes through must pass a hull or agility  
check or take 2 kinetic damage/tier and be knocked prone.
 

Optional systems:  
Rotary Barrels  
System
 
1/round when the Cataphract hits with a Ram Cannon attack, it can repeat the attack roll against  
a different target in range with +2 difficulty.
 

                                                                                                          


Lance shot  
System, Full Action, Recharge (5+)
 
The Cataphract can fire a lance shell from its ram cannon. This changes the attack type of the  
weapon to line 10 and causes all affected mechs to pass an agility skill check to dodge the shot  
or become immobilized until the start of the Cataphract’s next turn.
 

High-speed targeting  
System
 
The Cataphract can make one Ram Cannon attack (melee or ranged) after taking the dash  
action, but takes 1 difficulty on the attack roll.
 

Point-defense shield  
System, Shield, Quick Tech
 
+2 vs e-defense/tier
 
The Cataphract makes a tech attack against a target in range. On hit, the Cataphract has  
resistance to all damage from that target. It can only have one actor effected at a time.
 

Capacitor discharge  
System
 
After the cataphract takes the boost action, all mechs it is adjacent to after the action completes  
take 2/3/4 heat.
 

Tier II:
 
HP: +4
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          11       8      9        +3   +2    +0    +0      0            7        8 

Tier III:  
HP: + 4
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          12       8      9        +4   +4    +0    +0      0            7        8 

                                                                                                                