\subsection{Commander}
                                              COMMANDER   

Commander-type enemies operate on a grand scale, controlling fleets and armies across worlds  
and in interstellar space. They might not be the best individual combatant, but they can bring out  
the best in the best of their forces.   

Making a Commander:
 
All Commanders get the following features added to their base NPC type:
 
    -    Bonus structure: The Commander gains +1 structure  
    -    Bonus stress: The Commander gains +1 reactor stress  
    -    Command: Once per round, the Commander can cause an allied target it can see to re- 
         roll any single attack roll or check as a reaction. The commander can’t use this reaction if  
         it is Jammed.  
    -    Commander Traits: The commander can choose one of the following commander traits.  
         These traits don’t function if the commander is Jammed.  

Commander Traits
 
Bolster network  
Trait  
While the commander is alive, all allies the commander can see gain the hardened target trait (+1  
difficulty on all hostile tech actions or attacks against them). The commander does not benefit  
from this trait.
 

Covering Fire  
Trait, Reaction
 
1/round, an ally the commander can see can attack with one weapon as a reaction against a  
target hostile to the commander that just made an attack against that ally or a different ally.
 

Press on!  
Trait, Free Action
 
1/round, the commander can pass a systems check as a free action to end the stunned or  
jammed conditions on a target it can see in its sensor range.
 

Reposition  
Trait, Free Action
 
1/round one ally that a commander can see can make the boost action as a reaction on the  
commander’s turn.
 

Rank and File  
Trait
 
Allied targets adjacent to the commander gain +1 Accuracy on all attacks and checks.
 