\subsection{Demolisher}

                                            DEMOLISHER  

The prolonged siege of Jadigmora City saw the development of the DEMOLISHER patten. Based  
off the long-operational berserker doctrine, DEMOLISHER tuned the chaotic heat flow to a more  
sustainable, if limited system, increasing a chassis’ heavy-lift capacity to allow for supermassive  
kinetic weapons to be used effectively in combat. Combined with the increased pilot shielding  
and system hardening made necessary by the heat tuning, pilots soon discovered more  
aggressive applications for concussion-wave ordinance. 
 

 Demolisher 

 Mech 

 Hull       Agility      Systems       Engineering 

 +2         -2           +0            +2 

 HP         Evasion      E-defense     Heat Cap. 

 16         6            7             8 

 Armor      Speed        Sensors       Size 

 2          4            8             2 

Base systems:
 
Demolisher hammer  
Superheavy Melee
 
Threat 2
 
AP, Knockback 2
 
-2 vs evasion with 1 difficulty (no difficulty at tier II, +1 Accuracy at tier III)
 
13/18/25 explosive damage
 
This weapon deals double damage against structures, objects, the environment, and cover and  
gains +2 Accuracy against them.
 

Kinetic compensation  
System
 
If the Demolisher misses with its hammer attack, it gains +1 Accuracy on subsequent attacks  
until it hits. This effect stacks.
 

Optional systems:  
Broad-sweep haft  
Full Action
 
The Demolisher’s hammer can be used to make a sweep attack instead of a regular attack,  
attacking all targets in threat range (allied or enemy) for +1 vs evasion/tier, 4/6/8 explosive  
damage. Targets struck by this attack are impaired until the start of the Demolisher’s next turn.
 

                                                                                                          


Concussion missiles  
Quick Action
 
A target in range 8 must pass an engineering check with 1 difficulty/tier or be knocked back 3  
spaces and impaired until the start of the Demolisher’s next turn.
 

Seismic Destroyer
 
System, Full Action, Recharge (6+)
 
The Demolisher’s hammer can be used to make a special attack that hits cone 3 or line 5 from  
the Demolisher instead of its regular attack. This attack cannot hit flying targets. Targets in the  
area must pass a hull or agility skill check or be stunned until the end of the Demolisher’s next  
turn.
 

Shatter module  
Trait
 
The Demolisher’s hammer strikes against prone, immobilized, or stunned targets gain the AP tag  
and can Critical Hit, dealing +1d6 bonus damage/tier on Critical Hits
 

Knockout Blow  
Trait, Quick Action, Recharge 6+  
A target adjacent to the Demolisher must pass a hull or agility check with 1 difficulty/tier or  
become stunned until the end of the Demolisher’s next turn.
 

Tier II:
 
HP: +4
 

          Evade     E-D    Heat    H     A     S     E       Armor        Spd       Sense 

          6         7      8       +4    -2    +0    +3      3            4         8 

Tier III:  
HP: +4
 

          Evade     E-D    Heat    H     A     S     E       Armor        Spd       Sense 

          6         7      8       +6    -2    +0    +4      3            5         8 
