\subsection{Hive}

                                                   HIVE  

A recent development following the Deimos Contact Event, Hive doctrine chassis are, in theory,  
not too different than their pre-Contact cousins: they establish a local, secure omninetwork,  
fabricate and deploy a century or half-century of drones, and coordinate them in achieving their  
mission. The difference between pre-Contact and post-Contact drone controllers is ease: pilots  
who pursue this doctrine establish complex handler-trainer relationships with their hives, allowing  
them to segue between direct control and autonomous operation unimpeded by tactile interface.  
Hive pilots exhibit signs of psychological trauma at one month continuous drone-strain operation,  
and it is recommended that they practice a strict two-week format cycling with their paired hive.   

 HIVE 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         -1           +2            +0 

 HP         Evasion      E-defense     Heat Cap. 

 20         8            10            8 

 Armor      Speed        Sensors       Size 

 0          5            15            1 

Base systems:  
Hunter Killer Drone Nexus
 
Main Nexus
 
Smart, Seeking
 
Range 15
 
+2 vs e-defense/tier
 
7 energy damage
 
This weapon can attack twice at tier III with the attack action
 

Drone Barrage
 
Quick Tech
 
+2 vs e-defense/tier with +1 accuracy/tier
 
The Hive directs its drones to run interference on a target of its choice. On hit, the target is  
Slowed and Impaired until the start of the hive’s next turn.
 

Optional systems:
 
Electro-Nanite Cloud  
System
 

                                                                                                          


All hostile targets that start their turn within range 3 of the Hive take 2 Burn/tier. In addition, any  
system checks they make or tech actions they make in that area suffer from +1 Difficulty/tier.
 

Grinder Drones  
Drone, System
 
Quick Tech
 
+2 vs e-defense/tier with +1 Accuracy/tier
 
The Hive releases a swarm of tiny, hard to hit drones that attach to a target within range 15,  
making a tech attack. On hit, the target takes Burn 4/6/8. The Hive can only have one target  
attacked by these drones at once.
 

Razor Swarm  
Drone, System, Quick Action, Recharge 5+
 
The Hive creates a blast 2 area within sensor range. The area remains until the end of combat or  
the Hive is destroyed. Targets allied to the hive can use the area for light cover. Otherwise, any  
target that starts its turn in the area or moves into it for the first time on its turn takes 3 Burn/tier.  
The Hive can deploy any number of Razor Swarms.
 

Swarm Shield  
Quick Action, Recharge 6+
 
The Hive releases a cloud of miniature drones that cluster around it, providing heavy protection.  
The Hive has resistance to damage from the next 1d6 attacks.
 

Seeker Cloud  
Main Nexus
 
Smart
 
+0 vs e-defense with 1 Accuracy/tier
 
Cone 5
 
3/4/5 Kinetic Damage
 
Targets damaged by this weapon gain the Lock On condition.
 

Tier II:
 
HP: +4
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

         9         12     8       +2   -1    +4   +0       0           5        20 

Tier III:  
HP: +4
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

          10       14     8       +3   -1    +6   +0       0           6        25 
