\subsection{Hornet}

                                                HORNET  

 HORNET 

 Mech 

 Hull       Agility      Systems       Engineering 

 -2         +2           +2            +0 

 HP         Evasion      E-defense     Heat Cap. 

 10         15           8             5 

 Armor      Speed        Sensors       Size 

 0          8            10            1/2  

Base Systems:  
Stinger Pistol  
Auxiliary CQB
 
Range 8, Threat 3
 
+1 vs evasion/tier with +1 accuracy/tier
 
2/3/4 energy damage
 
Targets critically hit by this pistol are impaired until the end of the hornet’s next turn.
 

SSC Total Suite  
The Hornet can fly when it moves or boosts with hover flight.
 

Impale Systems  
Quick Tech, Recharge 5+
 
+2 vs e-defense/tier
 
On hit, the target takes 3 heat/tier and becomes jammed until the end of the hornet’s next turn.
 

Optional Systems:  
Evade Suite  
Trait
 
The Hornet ignores engagement and is immune to grapples
 

Minor Basilisk  
Trait
 
The first attack a target misses against the Hornet per turn deals 2 heat/tier to the attacker.
 

Interdictor Suite
 
Reaction
 

                                                                                                           


1/round the Hornet can use a reaction to attempt to electronically jam a target in its sensor range  
that is attempting to make an attack roll. The target must pass a systems skill check or lose its  
attack roll (it can still make other attacks as normal). The difficulty of this test increases by 1  
difficulty at tier II onwards.
 

HEX missiles
 
Auxiliary Launcher
 
Smart
 
+0 vs e-defense with +1 Accuracy/tier
 
Range 10, Blast 1
 
3/4/5 heat
 

Drag Javelin  
Full Action
 
The Hornet fires a javelin at a target it can see within range 10. The target must pass a hull check  
with 1 difficulty/tier or become impaled by the javelin. Upon impact, the javelin fires a secondary  
grapple at the environment, tethering the target to the ground. While impaled this way, the target  
is immobilized and shredded. It can end this condition by repeating the check as a quick action  
on their turn to pull the javelin out.
 

Tier II:
 

          Evade     E-D    Heat    H     A     S     E       Armor         Spd      Sense 

          17        8      6       -2    +4    +3    +0      0             10       10 

Tier III:
 

          Evade     E-D    Heat    H     A     S     E       Armor         Spd      Sense 

          20        9      7       -2    +6    +4    +0       1            12       10 

                                                                                                                  