\subsection{Marker}
                                                MARKER  

Marker doctrine calls for the active, close, and aggressive application of orbital, atmospheric, and  
terrestrial fire support on identified and potential enemy positions. Equipped with more-than- 
cursory targeting systems, Marker doctrine pilots adopt an tactical/artillery commander role,  
operating on the ground with infantry, chassis, and other vehicles to build a map of the  
battlescape in order to more accurately place small arms fire, bombs, shells, missiles, beams, and  
kinetic kill clouds. They are not usually a threat in face-to-face combat, but the threat they  
represent to a combat cannot be underestimated.   

       Marker 

       Mech 

       Hull       Agility     Systems       Engineering 

       -2         +2          +3            -1 

       HP         Evasion     E-defense     Heat Cap. 

       14         12          10            8 

       Armor      Speed       Sensors       Size 

       0          6           20            1/2 - 1 

Base systems:
 
High Caliber Pistol  
Auxiliary CQB
 
+2 vs evasion/tier
 
Range 8, Threat 3
 
3/4/5 kinetic damage
 

Target Marker  
Main rifle
 
Smart
 
+1 vs e-defense/tier with 1 Accuracy
 
Range 20
 
Targets hit by this attack immediately gain Lock On and are Shredded while they suffer from  
Lock On. They then cannot turn invisible or benefit from invisibility, and cannot hide until the end  
of the Marker’s next turn. If the Marker is destroyed or this weapon is disabled, immediately end  
this condition.
 

Optional systems:  

                                                                                                          


Orbital Strike  
System, recharge 5+
 
Instead of firing the target marker at an enemy, the Marker can fire it at a point within range 30.  
At the start of the Marker’s next turn, that area is hit by an orbital strike. Any mechs still in a burst  
3 area centered on that point must pass an agility check or take 12/17/22 energy damage and be  
knocked prone, or half and no prone on a successful check.
 

HOUND missile
 
Quick Action, Recharge (6+)
 
Choose a target within range 20. The marker fires a hound missile at the target, which is size 1/2,  
has evasion 10, and 10/15/20 HP. The missile primes on the turn that it is fired, deploying in an  
adjacent space, then moves 3 at the start of each of the marker’s turns. If its target suffers from  
the Lock On condition, its movement increases to 6. The missile can benefit from cover, counts  
as flying with hover flight, and can be targeted and shot by systems and weapons. It must move  
towards its target, but can maneuver skillfully around cover, fit through holes, etc. If the missile’s  
movement causes it to collide with a hostile mech or its target, it detonates for a blast 1  
explosion. Mechs caught inside must pass an agility skill check or take 15/20/25 energy damage  
and half on a successful check.
 

Blind  
Quick Tech, Recharge (4+)
 
+2 vs e-defense with +1 Accuracy/tier
 
On hit, the target only has line of sight to adjacent squares until the end of its next turn.
 

Rebound Scan  
System, Full Action
 
All targets in range 10 of the marker must pass a systems check or immediately lose the benefit  
of all cover, hiding, and invisibility and be unable to take cover, hide, or turn invisible until the  
start of the Marker’s next turn.
 

Smart Missile Cloud  
System
 
At the start of the marker’s turn, one target suffering from Lock On in the Marker’s sensor range  
takes 4/5/6 explosive damage from the Marker, no roll required.  

Tier II:
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          15        13    8        -2   +4    +4    -1      0            7         20 

Tier III:  

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          18        16    8        -2   +5    +6    -1      0            8         20 
