\subsection{Mercenary}
                                                MERCENARY  

Mercenary-type enemies are foes that offer their services to the highest bidder. They may have  
attachments to a faith or flag, but when it comes to doing their business, they’re loyal only to  
gold.    
 
 
Making a Mercenary:
 
All Mercenaries get the following features added to their base NPC type:
 
     -   Opportunist: If an allied target is adjacent to the mercenary’s target, it gets +1 Accuracy  
         on all attack rolls against that target  
     -   Mercenary systems: A mercenary can choose from the list of mercenary systems and  
         traits below when choosing optional systems and modules  

Mercenary systems and traits:
 
Bounty Hunter
 
Trait
 
Before combat, choose a player character that there’s a bounty out for. The mercenary gains +1  
Accuracy on all attacks and checks against that character and their mech.
 

Efficient Killer
 
Trait
 
The mercenary gains +1 Accuracy on attacks and all its damage becomes AP against a target  
with 1 structure remaining.
 

Call in Favor
 
Action, Limited (1)
 
The Mercenary calls in a favor in the form of an orbital strike or artillery strike, targeting a blast 2  
area within range 30 of its position. All mechs caught in the area must pass an agility check or  
take 6/10/15 explosive damage, or half on a successful check.
 

Scout Drone
 
Action, Limited (1)
 
The Mercenary fires a scout drone to an empty space within its sensor range. The drone has  
evasion 10, 10 hp, and no armor. Within a burst 3 area centered on the drone, no target can turn  
invisible or hide from the mercenary, and the mercenary can attack targets in the area with +1  
accuracy. The mercenary can reposition the drone as a free action at the start of its turn.
 

Tactical Retreat
 
Reaction, Limited (1)
 
When the mercenary is taken below half health, this system automatically activates. All targets  
within a burst 2 area around the mercenary must pass a systems check or take 2 kinetic damage  

                                                                                                                   


and become jammed until the end of their next turns. The mercenary can then move its speed in  
any direction. This movement doesn't provoke reactions and ignores engagement.
 