\subsection{Monstrosity}
                                           MONSTROSITY  

Monstrosity-type enemies are massive or horrifying predatory wildlife. Generally wild, some kinds  
of monstrous enemies can be domesticated and trained for combat: these are in high demand in  
the distal and proximal reaches of the galaxy. 
 

       MONSTROSITY 

       Biological 

       Hull       Agility      Systems       Engineering 

       +2         +1           +0            +0 

       HP         Evasion      E-defense     Heat Cap. 

       15         10           10            - 

       Armor      Speed        Sensors       Size 

       1          6            10            1-3 

Base mutations:  
Claws
 
Main melee
 
+2 vs evasion/tier with 1 accuracy
 
6/8/12 kinetic damage
 

Optional mutations (choose 1 or more):
 

Acid Spittle  
AP  
+0 vs evasion with +1 accuracy/tier
 
Range 10
 
3/4/5 energy damage
 

Adhesive Extrusion  
Trait
 
The first target damaged by the monstrosity on a turn must pass an engineering check or  
become Slowed until it heals any amount of hit points or until the end of the current challenge.
 

Burrower  
Trait, Quick Action
 
The monstrosity can burrow into the ground as a quick action, as long as the ground beneath it  
is malleable enough. While burrowed, it counts as invisible, ignores all obstructions above  
ground, can take no other actions other than to move, boost, or emerge as a quick action. When  

                                                                                                           


it emerges, it must have a free space to emerge into. It loses these benefits and all adjacent  
mechs must pass a hull check or be knocked prone.
 

Charger  
Trait, Quick Action, Recharge (5+)
 
As a quick action, the monstrosity in a straight line as far as possible up to its speed, ignoring  
obstructions and not provoking reactions. Any targets it passes adjacent to or over must pass an  
agility check or take 4/6/8 kinetic damage.
 

Corrosive Bite  
Full Action, Recharge 5+
 
The monstrosity makes a melee attack at an adjacent target for +2 vs evasion/tier. On hit, the  
target takes 4/6/8 Burn. In addition, regardless of whether it succeeds this check, it is Shredded  
until it regains any amount of HP.
 

Grasping Claws  
Trait
 
The monstrosity gets +1 Accuracy to grapple, +1 Accuracy to attack targets it is grappling, and  
can boost and take reactions while grappling.
 

Natural Camouflage  
Trait
 
The monstrosity gains +1 Accuracy to checks made while hiding. If it’s in its natural terrain, it  
counts all terrain as being large enough to hide it (no matter the size difference).
 

Regenerator  
Trait
 
The monstrosity heals 2/3/4 HP at the end of its turn. This trait does not function if the  
monstrosity took energy damage at any point during the round.
 

Spined  
Trait
 
When the monstrosity takes damage from a melee weapon, it deals 1 AP kinetic damage to its  
attacker after the damage resolves.
 

Swift  
Trait
 
The monstrosity gains +2 speed
 

Tempered Hide  
Trait
 
The monstrosity has resistance to one of the following damage types: kinetic, energy, explosive  
damage.
 

                                                                                                                    


Winged  
Trait
 
The monstrosity can fly when it moves or boosts.
 

Increase at tier II :
 
HP +2
 
+1 optional mutation
 

         Evade    E-D     Heat    H   A   S    E   Armor     Spd       Sense 

         11       11      -       +   +   +    +   2         7         10 
                                  4   2   0    0 

Increase at tier III:  
HP +2
 
+1 optional mutation
 

         Evade    E-D     Heat    H   A   S    E   Armor     Spd       Sense 

         13       13      -       +   +   +    +   2         8         10 
                                  6   4   0    0 

All monstrosities get the following features:
 
    -    Unique Critical Chart: If the monstrosity has structure (such as an Elite or Ultra), it uses  
         the critical chart below instead of the regular one for mechs  
    -    Biological: The monstrosity has the biological tag  

                                          Monstrosity Critical Chart  

 ROLL       RESULT                   EFFECT 

 5-6         GLANCING BLOW           The monstrosity flinches in pain, giving it the impaired condition until  
                                     the end of its next turn 

 4           HEAVY BLOW              The blow knocks the monstrosity down. The attacker (or the GM)  
                                     chooses one of the following:
 
                                         -   The monstrosity is Slowed until the end of its next turn
 
                                         -   The monstrosity is knocked prone 

 3           HEAD TRAUMA             The monstrosity is stunned until the end of its next 

 2           DISMEMBERMENT           A limb or chunk is torn off the monstrosity, dealing +1d6 bonus damage  
                                     to it and permanently slowing it until it can potentially heal. 

 1           BRUTAL HIT              The monstrosity must pass a hull check or be destroyed. It gets +1  
                                     difficulty on this check per level of structure damage it has. 

                                                                                                                 


Two or     FATAL HIT              The monstrosity is destroyed and instantly killed 
more  
1s 

                                                                                                          


                                       TEMPLATES
 

These templates can be applied to any of the above enemy types to add more flavor or change  
the way they function in combat. In particular, the Ultra, Elite, Grunt, and Veteran templates can  
be used to make tougher or easier enemies. The Veteran template can be applied on top of the  
Ultra or Elite templates to make an especially tough enemy.
 