\subsection{Pirate}

                                                   PIRATE  

Pirate-type enemies live on the boundaries, in the forgotten bolt-holes of occupied space. They  
are far-ranging, operating around blink gates, interstellar shipping lanes, and near flagged but  
not-yet colonized worlds.   

Pirate-type groups are usually small, with their base of operations hidden a short-to-medium  
distance from the area that they are first encountered. Usually they are motivated by profit and  
materiel goods, not ideology or religion -- a good thing for a savvy negotiator.    

Pirate-type enemies commonly operate in mixed groups of fast, deadly subline ships, fighter/ 
bombers, and clutches of marines and mechanized chassis. They prefer hit-and-run style  
overwhelming ambush attacks, aim to capture rather than kill, and don’t like to engage in pitched  
battles  
 

Pirate-type enemies can be found across the galaxy wherever the law is spread thin, resources  
travel, and people are desperate.   

Making a Pirate
 
All pirates get the following features added to their base NPC type:
 
    -    Deadly (trait): The pirate can Critical Hit, dealing +2/3/4 bonus damage on a 20+ ranged  
         or melee attack roll  
    -    Pirate modules: The pirate can choose from the below modules when choosing optional  
         systems  

Gain the following options for optional systems/modules:
 

Boarding Clutch
 
Heavy Melee
 
+0 vs evasion with +1 Accuracy/tier
 
5/7/9 kinetic damage
 
This weapon can be used as an improvised grappling hook. It can be thrown at a target within  
range 5. The affected target must pass a hull or agility check or be pulled directly to the attacker  
and grappled.
 

Splinter Rounds  
System
 
Critical Hits from this mech deal an additional +3 bonus damage
 

Borer Missiles  
Main Launcher
 

                                                                                                              


Smart, Limited (1)
 
+1 vs e-defense with 1 Accuracy
 
Range 8
 
On hit, 1d3 miniature drones are attached to the target and begin boring into the mech’s interior.  
In 1d6+3 rounds, if there are any missiles still attached to the target, they bore inside the cockpit  
savage the pilot, reducing the pilot to 0 HP, causing them to make a Down and Out check. A  
single drone can be removed by making a successful systems or engineering skill check as a  
quick action. The drones can also be confused by shutting the affected mech down, which  
deactivates them. The pilot in the affected mech is aware of how much time they have before the  
drones bore through.
 

Prying Claws  
System, Full Action, Limited (1)
 
An adjacent target makes a hull check. On a failed check, the targeted pilot immediately exits  
their mech as if they had taken the dismount action (place them adjacent to their mech).
 

Slaver Signal  
System, Full Action
 
Recharge 5+
 
Range 10
 
This system affects one piloted vehicle or mech within range 10. The affected target must make  
a systems check with 1 difficulty/tier to shut out the signal or be affected. On failure, all the pilots  
in the target are affected by the signal, falling into an unresponsive stupor. While in this state,  
their mech is stunned. If the target takes damage, the pilots will be jolted awake, immediately  
ending this effect. Another adjacent actor can use an action on their turn to make a systems  
check to try and blot out the signal, waking the affected target up on success. If the source of  
the signal is destroyed, any targets affected will also wake up.
 