\subsection{Pyro}

                                                   PYRO  

A combat doctrine adopted following the Hercynian Crisis, the Pyro chassis-pattern is reviled  
across the galaxy as a terror instrument, though some states and organizations still choose to  
integrate them into their armies. Pyro doctrine chassis are heavily armored and insulated, built to  
manage incredible heat tax while projecting volatile mixes of irrepressible flame towards their  
enemies. Pyro chassis are sent in to root out entrenched defenders, defoliate areas rich in flora,  
and cause terror. 
 

 PYRO 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         -1           -1            +3 

 HP         Evasion      E-defense     Heat Cap. 

 12         8            8             15 

 Armor      Speed        Sensors       Size 

 3          3            8             2 

Base systems:
 
Flamethrower  
Heavy CQB
 
Cone 5
 
+1 vs evasion/tier
 
4 heat (self)
 
Burn 5/7/9 + 2/4/6 heat
 

Explosive Vent
 
System, Full Action
 
The pyro cools to 0 heat. Targets caught in a burst 1 area around it must pass an engineering  
check or take half of the heat the pyro cools as heat to themselves and be knocked prone.
 

Optional systems:  
Insulated Plating  
The pyro has resistance to heat and energy damage (including its self inflicted heat). It is immune  
to Burn
 

Unshielded Reactor  

                                                                                                           


Targets that start their turn adjacent to the pyro or become adjacent to the pyro for the first time  
on their turns take 1 heat/tier.
 

Napalm Bomb  
Main Launcher
 
Arcing, Loading
 
-1 vs evasion with +1 Accuracy/tier
 
Range 8, Blast 1
 
Burn 3/4/5 + 2/4/6 heat
 

Rigged fuel rod launcher  
Heavy Launcher
 
-2 vs evasion with +1 Accuracy/tier
 
Knockback 1
 
Range 10
 
4/6/8 heat
 

Explosive Jet  
System, Quick action, recharge (5+)
 
Enemies in a burst 2 area around the Pyro must pass a hull or agility check or be knocked back  
outside of that area and knocked prone. The Pyro then flies 5 in any direction, but it must land  
after completing that move.
 

Tier II:
 
HP: +3
 

          Evade    E-D    Heat    H     A    S     E       Armor        Spd      Sense 

          8        8      15      +2    +0   -1    +4       3           3         8 

Tier III:  
HP: +3
 

          Evade    E-D    Heat    H     A    S     E       Armor        Spd      Sense 

          8        8      15      +3    +0   +0    +5       4           3         8 

                                                                                                               