\subsection{Rainmaker}

                                             RAINMAKER  

The tongue-in-cheek designation describes a combat doctrine that patterns chassis around the  
optimal use of rockets and missiles in combat. Favored by all-theater combat units, Rainmakers  
are mobile platforms loaded with ordinance, able to handle engagements at any range, against  
any target. 
 

       RAINMAKER 

       Mech 

       Hull       Agility     Systems       Engineering 

       +0         +1          +2            -1 

       HP         Evasion     E-defense     Heat Cap. 

       15         8           10            8 

       Armor      Speed       Sensors       Size 

       1          2           15            2 

Base systems:
 
Thundershock missile pods
 
Main launcher
 
Arcing, Knockback 1
 
+2 vs evasion/tier
 
One, two, or three targets in range 15
 
3/4/5 explosive damage
 

‘Drang’ missile rack
 
Heavy launcher
 
Ordnance, Loading
 
Line 15
 
+1 vs evasion/tier
 
8/11/14 explosive damage
 

Optional systems:  
HADES missile
 
Quick Action, Recharge (5+)
 
The rainmaker targets a cone 3 area drawn in any direction from a point within range 20 of its  
location. This system tracks line of sight as if it were an arcing weapon. All targets in that area  
must pass an agility check or take 3/5/7 energy damage and 2/4/6 heat, and half on a successful  
check.
 

                                                                                                          


Rigged payload  
System
 
When the rainmaker is destroyed, it explodes in a burst 2 explosion centered on itself. Targets  
caught within must pass an agility check or take 8/12/16 explosive damage, and half on a  
successful check.
 

Volley  
System, Full Action, Recharge (5+)
 
All hostile targets within range 30 of the rainmaker must pass an agility check or take 4/6/8  
explosive damage, or half on a successful check. This system tracks line of sight as if it was a  
seeking weapon.
 

Huntsman  
Trait
 
While firing at a target suffering from the Lock On condition, the rainmaker’s weapons gain the  
Smart and Seeking tags.
 

Atlas missile  
Superheavy launcher
 
Ordnance, Arcing
 
Range 30
 
This weapon system replaces the Drang Missile rack. Instead of targeting a mech, the rainmaker  
instead targets a space on the ground within range. The targeted area is visible to all in line of  
sight. At the start of its next turn, the missile lands, targeting a burst 2 area centered on that  
space. All targets caught within must pass an agility check or take 15/20/25 explosive damage,  
and half on a successful check.
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd      Sense 

          11        11    8        +0   +2    +3    +0      1            2        20 

Tier III:  
HP: +2
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd      Sense 

          12        12    8        +0   +3    +4    +1      2            3        20 
