\subsection{Ronin}

                                                  RONIN  

Ronin doctrine chassis differ from Berserker and DEMOLISHER pattern chassis in that they have  
been purpose-built by boutique fabricators to excel in melee combat. Ronin patterns are  
common among martial cultures and event-combat firms both. Tactical applications for Ronin  
chassis are difficult in cultures where ranged weapons are preferred, but there is a certain  
prestige earned by pilots who adopt ancient weapons in the modern day and survive. That being  
said the availability of stasis and mag based defensive technology has made the Ronin doctrine  
marginally more viable in modern combat. 
 

 RONIN 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         +2           -1            -1 

 HP         Evasion      E-defense     Heat Cap. 

 18         10           7             8 

 Armor      Speed        Sensors       Size 

 0          5            12            1 

Base systems:  
Carbon Fiber Sword  
Main Melee
 
+2 vs evasion with 1 Accuracy/tier
 
Threat 1
 
6 kinetic damage
 
This weapon can attack once per tier (up to 3 times at tier 3) with the attack action
 
This weapon can Critical Hit, and deals an extra +1d6 kinetic damage on Critical Hit
 

Mag Parry  
System, Shield, Reaction
 
Once per round, when damaged by a ranged weapon, the Ronin can roll a d6. On a roll of a 5+,  
the Ronin gains resistance to all the damage from that attack, and the target must repeat the  
attack roll against itself, dealing damage on a success.
 

Optional systems:  
Charged Slash  
Full Action, recharge (5+)
 

                                                                                                          


All targets adjacent to the Ronin must make a successful agility check or take 8/12/16 kinetic  
damage, and half on a successful check.
 

Reflex Implant  
System
 
When the Ronin boosts, attackers gain +2 Difficulty to attack it until the start of the Ronin’s next  
turn.
 

Echo Edge  
System
 
When the Ronin damages a target, it marks that target (keep track of it). At the start of its turn,  
the Ronin can consume all these marks as a free action to deal 1d6 AP kinetic damage to all  
targets, no attack roll required. They last until consumed, until the Ronin is destroyed, or until the  
end of the current challenge.
 

Hyper-reflex mode  
System, Quick Action, Recharge (5+)
 
This system remains active until the end of the Ronin’s next turn. While active, the first time each  
turn (the Ronin’s turn or any other actor’s turn) the Ronin is targeted by an attack, it can  
immediately make a Carbon Fiber Sword attack against a target in range before the attack is  
made.
 

Extended Blade  
The Ronin’s Carbon Fiber Sword becomes threat 2. The first time it critically hits with a melee  
attack on a turn, all targets within its threat take 3/4/5 kinetic damage including the target of its  
attack.
 

Tier II:
 
HP: +2
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          13       7      8        +2   +4    -1    -1      0            5        12 

Tier III:  
HP: +2
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          16       7      8        +4   +5    -1    -1      0            6        12 

                                                                                                                