\subsection{Scourer}

                                              SCOURER  

SCOURER doctrine mechs mount massive-output recursive power plants in order to field deadly  
energy weapons. A common specialist-role doctrine, SCOURER chassis are found on fronts  
across the galaxy, supporting kinetic-focus ground troops with powerful lensing attacks that  
target not only corporeal enemies, but systemic threats. 
 

 SCOURER 

 Mech 

 Hull       Agility     Systems       Engineering 

 +1         +0           0            +1 

 HP         Evasion      E-defense    Heat Cap. 

 16         9            8            10 

 Armor      Speed       Sensors       Size 

 1          4            10           1 

Base systems:
 
Thermal Lance  
Heavy Cannon
 
2 heat (self)
 
+0 vs evasion with +1 Accuracy at tier II and +2 Accuracy at tier III
 
Range 8
 
6/8/12 energy damage
 

Cooling Module  
System  
If the Scourer did not move or boost at all this turn, it reduces its heat to 0
 

Optional systems:  
Crystal Lense  
Once the Scourer hits a target with the Thermal Lance, on subsequent turns it can choose to  
focus down that target instead of firing normally. As a full action from the Scourer, that target  
takes 6/9/12 Burn, no roll required. This effect breaks if the target gains cover from the Scourer,  
the scourer is stunned, this weapon is disabled or destroyed, or the target moves out of range.  
The target is aware of this effect.
 

Supercharged
 
Trait
 

                                                                                                         


Targets struck by the thermal lance are shredded until the end of the scourer’s next turn.
 

Pulse Laser
 
Main Cannon
 
+2 vs evasion/tier
 
Line 10
 
4 energy damage
 
This weapon can attack twice at tier III
 

Flash Lense  
System, Quick Action, Recharge (6+)
 
The Scourer targets a cone 5 area in a direction of its choosing. All targets in the area must pass  
a systems check or be jammed until the start of the Scourer’s next turn.
 

Melt  
System, Quick Action, Recharge (5+)
 
The scourer targets a piece of cover, terrain, or deployable, then makes an attack roll, dealing  
10/20/30 AP energy damage on hit.
 

Tier II:
 
HP: +2
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          10       8      12       +2   +1    +0    +3      1            4        10 

Tier III:
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          10       8      12       +3   +1    +1    +4      2            4        10 
