\subsection{Seeder}

                                                SEEDER  

Seeders are sapper chassis, adept at building defensive nets of mines and traps for point defense  
and aggressive area denial. Laden with ordinance, pilots who adopt Seeder doctrines operate in  
small teams to blanket the battlefield in clouds of fire and shrapnel, placing their launched  
grenades and explosive-tipped FRAMEs with pinpoint accuracy. 
 

 SEEDER 

 Mech 

 Hull       Agility      Systems       Engineering 

 +0         +0           +2            +0 

 HP         Evasion      E-defense     Heat Cap. 

 15         7            10            10 

 Armor      Speed        Sensors       Size 

 2          4            15            1 

Base systems:
 
Grav Grenade Launcher  
Main Launcher
 
Arcing
 
+2 vs evasion/tier
 
Range 10, blast 1
 
2/3/4 explosive damage
 
This weapon deals 5/7/9 damage if it catches more than 1 target in its blast
 

Mine Deployer  
System, free action, recharge (4+)
 
The seeder lays a mine in a space within range 3 of it. It cannot place a mine adjacent to another  
mine. The mine arms at the end of the round. Once armed, the next target other than the seeder  
to become adjacent to it must pass a systems check or trigger the mine. That target, and any  
caught in a burst 1 area centered on the mine must pass an agility check or take 10/15/20  
explosive damage, and half on a successful check.
 

Optional systems:  
Smart Tagging
 
System
 
The seeder’s mines only detonate automatically if there is a hostile target in range (not allied).  
Furthermore, the seeder can choose to stop their detonation as a reaction.
 

                                                                                                          


Grav Mine  
System, Quick Action
 
A target in range 5 and line of sight to the Seeder must pass a systems check or have a mine  
attached to them. They can disarm the mine by taking a quick action and successfully repeating  
this check. The seeder can detonate any grav mines at the start of its turn as a free action,  
causing any affected mech to take 3/5/7 explosive damage, no attack roll required, and be  
knocked 3 spaces in a direction of the Seeder’s choosing.
 

Anti-Infantry mine  
Trait
 
If the seeder chooses, it can lay an anti-infantry mine with its mine deployer. This mine affects a  
burst 3 area instead of burst 1 and deals 1/2/3 explosive damage, but 4/6/8 to targets with the  
biological tag.
 

Grav Lash
 
Quick Tech
 
+2 vs e-defense/tier 
 
On hit, the target is knocked back 5 spaces in a direction of the Seeder’s choosing.
 

Seeker Mines  
System, Full Action, recharge (5+)
 
The seeder fires small seeker mines at one to three targets of the seeder’s choice in range 5 and  
line of sight. Those targets must pass a systems check or have a mine latch on to them. At the  
start of the seeder’s next turn, the mines explode for a burst 1 explosion on the target for 3/5/7  
explosive damage.
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          8         10     10      +1    +0   +3    +1       2            4        15 

Tier III:  
HP: +2
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          9         11     10      +2    +0   +4    +2       2            4        15 
