\subsection{Sentinel}

                                              SENTINEL  

Sentinel doctrine chassis fill guard roles. Typically found in the retinues of commanders or posted  
in defense of batteries, Sentinel chassis employ a suite of technology that ensures their charges  
stay alive and operational, even if it means the Sentinel’s death. 
 

 SENTINEL 

 Mech 

 Hull       Agility     Systems       Engineering 

 +2         +1           +0           -1 

 HP         Evasion      E-defense    Heat Cap. 

 20         9            9            8 

 Armor      Speed       Sensors       Size 

 0          5            8            1
 

Base systems:  

Combat Shotgun  
Main CQB
 
Range 3, Threat 3
 
+2 vs evasion/tier with 1 Accuracy
 
7/9/12 kinetic damage
 

Retractable Sword  
Main Melee
 
Threat 1
 
+2 vs evasion/tier
 
4/6/9 kinetic damage
 

Eye of Midnight
 
System, Quick Action
 
This system can be activated or deactivated as a quick action, and remains indefinitely. While  
this system is active, the Sentinel is Slowed, but is not limited in the number of overwatch  
reactions it can make per round.
 

Optional systems:  

Punisher Ammunition  

                                                                                                         


System
 
The first enemy damaged by the Sentinel’s combat shotgun each round must pass a engineering  
heck with 1 difficulty or be Slowed until the end of the sentinel’s next turn.
 

Wrath-lock  
System, Full Action
 
The sentinel may arm this module as a full action. While armed, the next time it fires its combat  
shotgun, it makes 3 attacks instead of one.
 

Impaler  
System
 
The first enemy damaged by an overwatch shot from the Sentinel must pass an agility check  
with 1 difficulty or immediately stop moving and become immobilized until the end of the  
sentinel’s next turn.
 

Watchful  
Trait
 
Once per round, in response to any enemy movement, the Sentinel can make the boost action as  
a reaction.
 

Guardian protocols
 
Trait
 
At the start of its turn, the Sentinel can nominate an allied mech within range 5. Once per turn  
(but any number of times per round) when that mech is targeted by an attack, the Sentinel can  
immediately make a single attack for free against the attacker if it is in range as a reaction.
 

Tier II:
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          11        11     8       +3    +2   +1    -1       1            5        8 

Tier III:  
HP: +4
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          13        13     8       +4    +2   +4    -1       1            6        8 
