\subsection{Ship}
                                                    SHIP   

Ship-type enemies are any military or civilian vehicles that are flight capable and operate primarily  
in space, outside the bounds of atmosphere (though many can operate in-atmos if need be).
 

Making a Ship
 
You can use any of the mech classes and apply this template to convert that mech into a ship.  
They lose the mech tag and gain the vehicle tag. All ships get the following features added to  
their base NPC type:
 
    -    Flier: A ship always counts as having an EVA module in space. In atmosphere, it can fly  
        with either normal flight or hover flight (depending on type). If a ship is grounded without  
         landing, it is immobilized. If it is immobilized, knocked prone, or stunned mid-air, it  
        crashes.  
    -    Massive size: A ship is typically much larger than a mech. If its size is less than 4,  
         increase its size to 4. This template describes ships that can be engaged on a ship-to- 
         mech level about up to size 6-8. Much larger ships (size 10/20+) are usually too heavily  
        armored for mech-mounted weapons to harm  
    -   Crew: A ship might be operated by more than one crew member (typically a minimum  
         number of crew equal to 1/2 of the vehicle’s size). As long at least half the crew is alive, the  
        ship can still function.
 
    -    Bonus HP: Increase the Ship’s HP by +5  
    -    No manipulators: A ship cannot initiate a grapple, pick up, or manipulate items  
    -    Limited melee attacks: A ship cannot make melee attacks other than Ram
 

                                                                                                            


-   Transport: A transport ship can hold one squad or a number of entities whose total size  
    (added together) is less than its size  

                                              