\subsection{Sniper}

                                                 SNIPER  

Sniper pattern chassis are common throughout the galaxy’s armies. Favoring stability and  
targeting over mobility, Snipers operate extremely long-ranged kinetic weapons in small, self- 
sufficient teams well removed from any direct combat. Sniper pilots are a proud breed, who  
emphasize economy and elegance over destructive power. Their weapons are often as tuned and  
modified as much as their chassis are; the pilots themselves often exhibit unparalleled control  
over their targeting systems. Partnered NHPs are said to send boast-data between themselves,  
noting the difficulty of landed shots to allied pilots. 
 

 SNIPER 

 Mech 

 Hull       Agility      Systems       Engineering 

 +0         +1           +2            -1 

 HP         Evasion      E-defense     Heat Cap. 

 15         10           10            6 

 Armor      Speed        Sensors       Size 

 0          4            15            1 

Base systems:
 
Anti-Material Rifle  
Heavy Rifle
 
Loading, Ordnance, AP
 
+1 vs evasion/tier with +2 Accuracy/tier
 
Range 30
 
10/15/20 kinetic damage
 

Auto-pistol  
Auxiliary CQB
 
+0 vs evasion with +1 Accuracy at tier II, +2 Accuracy at tier III
 
Range 8, Threat 3
 
3/4/5 kinetic damage
 

Deathmark protocol  
System, Full Action
 
The Sniper marks a target within range 20. While marked, the Sniper’s anti material rifle attacks  
against that target causes it to take 1 structure damage on hit instead of dealing damage  
normally (causing the target to make a structure check and reset its HP). The Sniper can only  
have one mark active at a time, but can transfer it if need be. The target can avoid this effect if it  

                                                                                                          


is in any kind of cover, or if it’s prone (it is aware of this effect), and instead takes damage  
normally.
 

Optional systems:
 
Defensive Grapple  
System, Quick Action, Reaction, Recharge (4+)
 
The Sniper chooses a point within range 5 (vertical or horizontal) and pulls itself to that point with  
a grappling hook as if it had flown. It can use this as an action on its turn or a reaction to an  
enemy’s movement that it can see.
 

Climber  
Trait
 
The sniper can climb any surface with no penalty and walk or stand on such surfaces as if they  
were flat ground, even overhanging or vertical surfaces. 
 

Selective Loader  
System
 
The Sniper can fire one of several types of ammunition, choosing one before it attacks:
 
	        Impact: Targets hit by the AM rifle must pass a hull check or be knocked prone
 
         EMP: Targets hit by the AM rifle must pass a system check or be Jammed until the end of  
         their next turn
 
         Flare: Targets hit by the AM rifle cannot hide or turn invisible until the end of their next  
         turn
 
         Molten: Targets hit by the AM rifle must pass an engineering check or become Shredded  
         until the end of their next turn.
 

Over-penetrating Round  
System, protocol, recharge (6+)
 
The Sniper loads an over-penetrating round into its anti-material rifle. Its next attack with the rifle  
becomes Line 30.
 

Flash Bomb  
System, Quick action, recharge (6+)
 
The sniper fires a bomb at a blast 2 area within range 5 of it. Targets other than the Sniper caught  
inside must pass a systems check or become Slowed and jammed until the end of their next  
turn. The area counts as light cover until the start of the sniper’s next turn
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          13        10     6       +0    +2   +3    +0       0            4        15 

                                                                                                                 


Tier III:  
HP: +2
 

           Evade       E-D     Heat     H      A     S      E         Armor          Spd        Sense 

             16         12     6          +0    +3     +4    +1        0              4          15 

.  