\subsection{Spectre}

                                               SPECTRE  

Spectre doctrine chassis emphasize the ability not to be hit over pure defensive shielding.  
Employing cutting-edge optical and systemic camouflage, Spectres vanish from the battlefield  
and all active/passive scans, flickering in and out of vision and shattering their image and radar  
signatures, confusing the eye and the sweep.Their weapons do not mark their doctrine: their  
power comes from the ability to operate unseen. 
 

 SPECTRE 

 Mech 

 Hull       Agility      Systems       Engineering 

 -2         +2           +1            +1 

 HP         Evasion      E-defense     Heat Cap. 

 10         10           10            7 

 Armor      Speed        Sensors       Size 

 0          6            10            1/2-1 

Base systems:  

Machine pistol  
Auxiliary CQB
 
+2 vs evasion/tier
 
Range 5, Threat 3
 
6 kinetic damage
 
This weapon can attack twice at tier III with the attack action
 

ATHENA-class scan  
System, quick action, recharge (4+)
 
One target in range 10 of the specter’s choice must make a systems skill check (the specter can  
guess they are there and doesn’t need line of sight). If they fail, they are revealed from hiding and  
lose the benefits of hiding or invisibility and cannot hide or turn invisible until the start of the  
spectre’s next turn.
 

Tactical Cloak
 
System
 
The spectre is permanently invisible while this system is intact.
 

Optional systems:  

                                                                                                          


Combat subroutine  
Trait
 
A targets that fails their check against the spectre’s Athena-Class scan system gain the lock on  
condition.
 

Fortress  
Trait
 
The spectre gains the Fortress trait (lock on, invasion, and scans are made against it at +3  
difficulty). To electronic systems, it doesn’t appear to even be there.
 

System flayer  
Trait
 
Targets that fail their check against the spectre’s Athena-Class scan system immediately suffer  
from Lock On.
 

Weakness analyser  
System
 
The specter’s attacks from hiding gain an additional +1 Accuracy/tier and gain the ability to  
Critical Hit, dealing +1d6 kinetic damage on Critical Hit
 

Cloaking Field  
System, full action, recharge (6+)
 
The spectre deploys a cloaking field, affecting a burst 3 area around it. All allied mechs in that  
field become invisible while inside the area. The field deactivates at the end of the spectre’s next  
turn.
 

Tier II:
 

          Evade     E-D     Heat    H     A     S     E        Armor        Spd       Sense 

          11        11      7       -2    +3    +3    +1       0            6         10 

Tier III:
 

          Evade     E-D     Heat    H     A     S     E        Armor        Spd       Sense 

          12        12      7       -2    +4    +5    +1       0            6         10 
