\subsection{Squad}

                                                 SQUAD   

Squads come in two varieties: Squadrons and Infantry. A squadron represents a squad of mech- 
type enemies operating as a group, whereas an infantry squad represents a squad of  
approximately human-sized enemies operating together. They are treated like one entity.
 

All squads (squadrons and infantry) get the following features:
 
    -   Weak: Squads cannot have more than 1 structure or heat capacity. They take energy  
        damage when they take heat.  
    -   Exclusive templates: Squads cannot take the Grunt, Veteran, or Ultra templates (they  
        can still take Elite, but don’t gain structure)  
    -   Split HP: Squads have a large number of members operating together. Once a certain  
        amount of damage is done to the squad, one of the members is destroyed (indicated in  
        the profile). Once a squad is under half HP, it loses some of its attacks to represent this.  
    -   Strength in numbers: Squads have resistance to all damage that is not from line, blast,  
        or cone attacks. They are immune to grapple or ram and cannot grapple or ram.  
    -   Spread out: Squads occupy a square area equal to their size for purposes of targeting,  
        but each individual member is not represented. For the purposes of determining cover  
        and obstruction, use the size of each individual member, not the size of a squad as a  
        whole.  

       SQUADRON 

       Squad, Mech 

       Hull       Agility     Systems       Engineering 

       +1         +1          +1            +1 

       HP         Evasion     E-defense     Heat Cap. 

       16         6           8             - 

       Armor      Speed       Sensors       Size 

       1          5           10            6 (individual:  
                                            1) 

HP per member: 2
 
Number of members: 8
 

Base modules:
 
Primary squad weapon
 
Main Rifle
 
+1 vs evasion/tier
 

                                                                                                          


Range 10
 
3/4/5 kinetic, energy, or explosive damage (choose on creation)
 
This weapon can be fired three times when the squad attacks. If the squad is under 1/2 hp, it can  
only be fired once.
 

Heavy squad weapon
 
Heavy cannon
 
+0 vs evasion with 1 Accuracy/tier
 
Range 12 and blast 2, line 10, or cone 5 (choose on creation)
 
4/5/6 kinetic, energy, or explosive damage (choose on creation)
 

Tier II:
 
HP: +2 (+1 members)
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

          7        8      -       +2   +2    +2   +2       1           5        10 

Tier III:  
HP: +2(+1 members)
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

         8         8      -       +3   +3    +3   +3       1           5        10 

                                    