\subsection{Support}

                                               SUPPORT  

Support doctrine chassis focus their systems towards keeping their allies combat operational.  
Alloy cement, nanite paste, patch plates, vacuum seals — the tools vary, but the result is the  
same: you may be messed up, but you’re up, and you can keep fighting because the Support  
kept you alive. 
 

 SUPPORT 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         -1           +0            +2 

 HP         Evasion      E-defense     Heat Cap. 

 20         7            10            10 

 Armor      Speed        Sensors       Size 

 1          4            12            2-3 

Base systems:  

Suppressive cannon  
Main cannon
 
Ordnance
 
+2 vs evasion/tier
 
Range 10
 
6 kinetic damage
 
This weapon can be fired an additional time at tier III with the attack action
 
Targets damaged by this cannon suffer from the impaired condition until the end of their next  
turn
 

Latch drone  
System, Recharge (5+)
 
As a free action, the support fires a drone to a point within range 5 of its position, where it  
hovers. The drone can be attacked and destroyed. It is a size 1 drone with evasion 10 and 10 HP.  
The drone clamps on to the next allied mech to move through or adjacent to that drone’s space  
and discharges, healing that mech 5/7/10 HP.
 

Optional systems:
 
Remote reboot  
Trait, Full action
 

                                                                                                          


The support immediately ends 2 of the following conditions on an allied mech within range:  
impaired, jammed, shut down, Slowed. 
 

Nano-repair cloud  
System, Full Action, recharge (5+)
 
The support creates a blast 2 area within range 5 of its location. Allied targets that start their  
turns in the area or move through it for the first time can gain 4/5/6 HP. The cloud disperses at  
the start of the support’s next turn.
 

Defensive pulse  
System, Full action
 
The support makes a systems skill check with +1 Accuracy/tier. If it is successful, all mechs  
within range 5 of the support can immediately end the Jammed and Lock on conditions on  
themselves.
 

Manual Repair
 
System, Full Action, recharge (5+)
 
The support targets an adjacent mech or vehicle and makes an engineering skill check. If the  
check is successful, that mech can repair up to 4/6/8 HP and also to repair up to 1 destroyed  
system, returning it to functionality.
 

VULCAN drone  
System, Drone, Full Action, Recharge (6+)
 
The support chooses another mech within range 5 of its position, then fires a self-deploying  
drone at that mech. The drone is a size 1 object with evasion 10, 10 HP, and 1 armor. The drone  
clamps on to the targeted mech. At the start of each of its turns, while the drone is deployed on  
that target, that target can heal 3/4/5 HP. In addition, it gains +1 Accuracy on all checks and  
attacks. The drone can be shot off and destroyed.
 

Tier II:
 
HP: +5
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          7        11     10       +1   -1    +1    +4      1            4        10 

Tier III:  
HP: +5
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          8        12     10       +1   -1    +2    +6      1            4        10 

                                                                                                                