\subsection{Swarm}
                                                   SWARM  

A swarm represents a large, motile group of very small or weak enemies, biological, human,  
nanorobotic, or otherwise.  

All swarms get the following features:
 
    -    Weak: Squads cannot have resilience or heat capacity. They take energy damage when  
         they take heat.  
    -    Exclusive templates: Swarms cannot take the Grunt, Veteran, or Ultra templates (they  
         can still take Elite, but don’t gain resilience)  
    -    Swarms can take the Biological tag if they represent biological creatures. Otherwise a  
         swarm represents a swarm of mechanical entities.  
    -    The Many: The only actions a swarm can take are to move and boost, or those specified  
         in its profile.  
    -    Strength in numbers: Swarms have resistance to all damage that is not from line, blast,  
         or cone attacks. They are immune to the grabbed condition.  
    -    Spread out: Swarms occupy a square area equal to their size for purposes of targeting,  
         but each individual member is not represented. For the purposes of determining cover  
         and obstruction, use the size of each individual member, not the size of a squad as a  
         whole.  
    -    Swarm: A swarm’s area counts as difficult terrain, even if a mech can normally move  
         through it  

       SWARM 

       Swarm 

       Hull       Agility      Systems       Engineering 

       +1         +1           +0            +0 

       HP         Evasion      E-defense     Heat Cap. 

       15         6            8             - 

       Armor      Speed        Sensors       Size 

       -          3            6             5 (individual:  
                                             1/2, 1/4, or  
                                             smaller) 

Base modules:
 
Swarm
 
Trait
 
Targets starting their turn in the swarm’s area or entering it for the first time take 3/5/7 AP kinetic  
damage.
 

                                                                                                            


Optional modules:  
Crawl over
 
Trait
 
When a target starts its turn inside the swarm or enters that area for the first time on its turn,  
members of the swarm cover and crawl over it, inflicting the impaired condition on it until the end  
of its next turn.
 

Drag down
 
Trait, Quick Action
 
1/round, the swarm chooses one target in its area. That target must pass a hull check with 1  
difficulty/tier or be knocked prone
 

Endless Swarm
 
Trait
 
The swarm heals 2 HP/tier at the end of its turn.
 

Split
 
Trait
 
At the end of any turn when the swarm is reduced past 1/2 HP, it splits into two swarms of size 2,  
each with half the swarm’s current HP. These swarms cannot split again.
 

Tear apart
 
Trait
 
The swarm’s Endless Swarm trait also causes 3/4/5 Burn
 

Tier II:
 
HP: +5
 

          Evade     E-D     Heat    H     A     S     E        Armor        Spd       Sense 

          6         -       -       +2    +1    +0    +0       0            3         6 

Tier III:  
HP: +5
 

          Evade     E-D     Heat    H     A     S     E        Armor        Spd       Sense 

          6         -       -       +3    +1    +0    +0       0            3         6 
