\subsection{Technical}
                                              TECHNICAL  

Technicals lean into the incredible tumult of systemic warfare, operating both in realtime and  
among the omnicloud tempest that descends upon a combat theater. Technicals often pair with  
personality-clone NHPs — NHPs that structure profiles based on profiles of their pilots — to  
handle the chaotic swirl that results from realtime/omninet combat splitting.   

 Technical 

 Mech 

 Hull       Agility      Systems       Engineering 

 -1         +1           +2            +0 

 HP         Evasion      E-defense     Heat Cap. 

 12          12          12            8 

 Armor      Speed        Sensors       Size 

 0          5            10            1/2 -1 

Base systems:
 
Autogun  
Auxiliary rifle
 
Smart
 
Range 10
 
+2 vs e-defense/tier
 
6 kinetic damage
 
This weapon can attack twice at tier III with the attack action
 

HORUS hacker  
Trait
 
This mech makes tech actions with +1 Accuracy and its invasions deal +1/2/3 heat on hit.
 

Snap Fire  
Trait, Quick Action
 
This mech makes one autogun attack
 

Optional systems:  

Predatory logic
 
Quick Tech, Recharge (5+)
 
+2 vs e-defense/tier with +1 Accuracy
 

                                                                                                           


On hit, the target immediately makes an attack with a single weapon of the technical’s choice  
against any other target within range (even an allied target).
 

Puppet system  
Quick Tech
 
+2 vs e-defense/tier 
 
On hit, the target is impaired until the end of its next turn. In addition, the technical can  
immediately cause that target to move up to its speed in a direction of the technical’s choice.
 

SCORPION protocols  
System
 
The technical gains the hardened target trait (invasion, lock on, and scan are made at +1  
difficulty). In addition, any failed invasion, lock on, or scan attempt on it inflicts 2/3/4 heat to the  
attacker.
 

Illusory subroutines  
Quick Tech
 
+2 vs e-defense/tier 
 
On hit, all actors allied to the Technical count as invisible to the target until the start of its next  
turn.
 

System link  
System, Quick Action
 
The Technical links systems with an allied mech within its sensor range. It can only link with one  
mech at a time. While linked, the allied mech gains +1 Accuracy/tier, and the allied mech can use  
the Technical’s systems score for all checks it makes. However, if either linked mech becomes  
jammed or impaired, the other also suffers the same condition for the same duration as long as  
the link persists. The link is disabled if either mech is destroyed or this system is disabled or  
destroyed.
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H     A    S     E        Armor        Spd      Sense 

          14        15     8       -1    +2    +4   +0       0            5         10 

Tier III:  
HP: +2
 

          Evade     E-D    Heat    H     A    S     E        Armor        Spd      Sense 

          16        18     8       -1    +3    +6   +0       0            5         10 
