\subsection{Ultra}
                                                   ULTRA  

In Lancer, Ultra-type enemies are typically the most dangerous individual enemies a party can  
face.   

Ultra-type enemies are high-tier enemies that do not usually fill command roles. Ultras are  
champions, favored warriors, major domos: they might command a few units in a retinue or lead  
armies from the front, but they do not typically engage in grand strategy.    

Making an Ultra
 
All ultras get the following features added to their base NPC type:
 
    -    Bonus activations: The Ultra can be activated again (take another turn) each round. If  
        the Ultra is facing more than 4 players, it takes another activation (for a total of 3). It  
         regains spent reactions each time it takes a turn.  
    -    Deadly: The Ultra can Critical Hit, dealing an extra +2 bonus damage/tier on Critical Hits.
 
    -    Exclusive templates: The Ultra can’t take the Elite or Grunt templates.  
    -   Juggernaut (trait): At the start of its turn, the Ultra ends one condition affecting it. If it  
         rolls a ‘system destroyed’ result on a structure check, it is instead jammed until the end of  
         its next turn (it doesn’t lose the system or weapon).
 
    -    Legendary (trait): The Ultra can enter the CRITICAL state and is not destroyed when  
         reaching 0 HP.  
    -   Structure: The Ultra gains 4 Structure, or increases its structure up to 4 structure if it  
         already has structure
 
    -   Stress: The Ultra gains 4 reactor stress, or increases its stress up to 4 if it already has  
        stress.  
    -    Bonus module: The ultra should gain +1-2 more optional modules than normal.  
    -    Bonus HP: The Ultra gains +5 HP  
    -    Reflex (trait): The Ultra can make any number of overwatch attacks per round (instead of  
        just 1). It can only attack the same target 1/turn with overwatch.  

Then choose 1-3 Ultra Traits or modules.
 

ULTRA traits:
 

                                                                                                            


Berserker  
Trait  
The Ultra gains +1 Accuracy on all melee attacks. It can make 1 melee attack roll, grapple, or  
ram attack as a Free Action on its turn.
 

Devastator  
Trait
 
Once per turn, when the ultra hits with an attack, all targets visible to the ultra take 2 kinetic,  
explosive, or energy damage.
 

Evasive
 
Trait
 
The Ultra gains +4 evasion, up to a maximum of 20, but reduce its structure to 3.
 

Extra Deadly  
Trait  
The first Critical Hit the Ultra deals per turn does +1d6 bonus damage/tier
 

Fortress  
Trait
 
The Ultra gains the Fortress trait instead of its Hardened Target trait (lock on, invasion, and scans  
are made against it at +3 difficulty). To electronic systems, it doesn’t appear to even be there.
 

Legion  
Trait
 
The ultra gains +4 e-defense, up to a maximum of 20, can take the full tech action (like a player),  
and gains +2 accuracy to all tech actions
 

Limitless  
Trait
 
The Ultra can use overcharge.
 

Unstoppable  
Trait
 
The Ultra always cannot be knocked back, knocked prone, or moved involuntarily.
 

Sight  
Trait
 
Targets cannot hide while inside the Ultra’s sensor range and it ignores invisibility.
 

Superior Construction  
Trait
 
The ultra has resistance to one of the following damage types: kinetic, energy, explosive. It  
cannot gain resistance to more than 2 (from this trait or any other systems).
 

                                                                                                                        


Superior Frame  
Trait
 
The ultra is immune to the Slowed, Shredded, and immobilized conditions
 

Superior Reactor  
Trait
 
The ultra is immune to the stunned and shut down conditions.
 

Superior Targeting  
Trait
 
The ultra ignores light and heavy cover when making ranged attacks.
 

Supreme Maintenance  
Trait  
The ultra is immune to the Jammed condition and can reload one weapon with the loading  
property as a free action on its turn.
 

Supreme Parting Gift  
Trait  
The Ultra can use the Self Destruct action. When it takes this action, it emits an EMP pulse. All  
vulnerable targets (mechs, vehicles) in a burst 5 area around it must pass a system check or be  
shut down.
 

Supreme Skirmisher  
Trait
 
2/round the Ultra can take the boost action as a reaction to any enemy movement or action that  
it can see.
 

Ultra systems and weapons:  

ARGUS armor  
The ultra’s armor increases to 6. Each time it rolls a critical or overheating check, reduce its  
armor by 2, to a minimum of 0.
 

H.A. Siege Shield  
The ultra has resistance to all damage that originates further away than range 5
 

Hellfire Projector  
Heavy CQB
 
Cone 5
 
3 energy damage + 5 Burn/tier
 
This weapon can be fired twice with the attack action, but its areas cannot overlap.
 

                                                                                                                   


HORUS manticore repulsion field  
Hostile targets that start their turn adjacent to the Ultra or become adjacent to it for the first time  
on their turn take 2 energy damage, 2 heat, and must pass a systems check or become impaired  
until the end of their next turn.
 

Obliterator
 
Action, Ordnance, Recharge (6+)
 
Choose a direction, then draw a line 30 spaces long and 2 spaces wide in that direction. Each  
target inside that area must pass an agility skill check or take 1/2 of its current hit points in energy  
damage, or 1/4 on a successful check, rounded up. Any cover, objects, buildings, drones,  
deployables, or items smaller than size 5 in the area are completely annihilated.
 

Ravager Turret  
Heavy Cannon
 
Ultra
 
+1 vs evasion with 1 Accuracy/tier
 
Range 10
 
4/6/8 kinetic damage
 
The Ravager fires at every hostile mech in range when this weapon is fired with the attack action.
 

SSC Slivershielding  
System
 
The Ultra is permanently invisible. Reduce its structure to 2.
 

SSC Ex Hover propulsion  
System  
The Ultra can fly when it moves or boosts, and can hover (it can stop midair, doesn’t have to  
move in a straight line, and doesn’t need to land after moving).
 

Volley module
 
Full Action, System
 
The ultra goes into a stable stance. At the start of its next turn, it fires one weapon at each target  
that is in range and not in cover or prone as a Free Action. It can fire the same weapon multiple  
times for this special action, ignoring the loading tag during this attack.
 

WOLFHOUND missile  
Heavy Launcher
 
Recharge (6+)
 
Instead of firing this weapon normally, choose a target within range 30. The ultra fires a  
wolfhound missile at the target, which is size 1, moves speed 4, has evasion 10, 0 armor, and  
10/15/20 HP. The missile primes in an adjacent space when deployed, then moves 3 at the start  
of each the ultra’s turns. If its target suffers from the Locked On condition, its movement  
increases to 6. The missile can benefit from cover and can be targeted and shot by systems and  
weapons. It must move towards its target, but can maneuver skillfully around cover, fit through  

                                                                                                            


holes, etc. If the missile’s movement causes it to collide with a hostile mech or its target, it  
detonates for a blast 1 explosion. Mechs caught inside must pass an agility skill check or take  
15/20/30 energy damage, and half on a successful check.
 

The Ultra can have only one missile fired at a time. Only check for recharge if this missile has hit  
its target or been destroyed.