\section{Death}
  DEATH  

The destruction of a mech does not always mean the death of a pilot. Pilots can escape and exit  
from shutdown, disabled, or even destroyed mechs, presuming they survived. A pilot can always  
re-create a mech - the pilot is much harder.
 
\subsection{Cloning}
                                                  CLONING  

Pilots are tremendous investments in hardware and training and tend to have powerful and well- 
connected patrons. It should not be surprising, then, that the technologies to resuscitate dead  
flesh or create imperfect, flash-grown genetic clones of pilots, though often illegal or highly  
secretive, do exist, and are often utilized by powerful organizations who don’t wish to give up on  
their investments.
 

Cloning or revivification is a costly and dangerous process. It’s always up to the player whether  
they want to bring a character back or simply make a new one. Flash-cloning or revivification  
is an experimental process that always creates complications. These caveats are here by  
default, and can be tweaked by the GM at their discretion:
 

    -    A cloned or revived character can only re-join the party after a mission’s completion.
 
    -    A cloned or revived character knows and learns nothing of the mission that they died on
 
    -    A cloned or revived character always comes back with a Quirk. 
 
             -   The quirk could be physical or mental in nature, but whatever the quirk is, it  
                 should be a story hook or something narrative in design (it shouldn’t have any  
                 major gameplay effects). 
 
             -   Quirks are always complicating - though your character might adjust to them in  
                 time, they are a shock to the system.  
    -    If a cloned or revived character would be cloned or revived a second time, they can no  
         longer be played as a player character. The trauma and personality shift from being  
         brought back to life is too great. In other words, you’re one and done.
 

If you want to roll for a random Quirk, you can roll 1d20 or choose from the below chart. You can  
use these as examples for your own quirks and are free to figure out between you and your GM  
what quirk your pilot comes back with.
 

                                                 Random Quirk
 

 Roll
      Quirk 
 (1d20) 

 1          Part (or all) of your body was too damaged or badly cloned and needed to be amputated and  
            replaced with cybernetics. These are high quality prostheses, and are not visibly synthetic to a  
            casual observer. The extent of the damage is unknown to you.  

                                                                                                                 


2          The process required you be fitted with a visible cybernetic augment, such as an arm, leg,  
           eyes, or the like. It is conspicuous and often attracts unwanted attention. 

3          By accident or malintent, you have been cloned into someone else’s body. They might be  
           someone noteworthy or important. 

4          You are cloned or revived with a nasty, disfiguring scar, a mutation, or a hideous appearance  
           that clearly marks you as vat-grown. 

5          Administrative mishaps lead to complete and drastic change in appearance in your new body 

6          An extra, withered limb grows out of your chest shortly after your cloning or resurrection. It  
           sometimes moves on its own. 

7          A conspicuous barcode is now printed on your body. The barcode has meaning to powerful  
           organizations, but you are not initially privy to its meaning. 

8          Under certain light conditions, it is possible to read a script or inscription printed just under  
           your skin. The script is all over your body and contains a scientific formula, a map, or other  
           information contested by powerful organizations or entities. 

9          Your new body is too frail to survive the exposure to direct light and air and requires you wear  
           an environmental suit outside of sterilized environments or your mech. 

10         DNA from a non-human or possible xenobiological source was used in your resuscitation. Your  
           revivers will not tell you the exact details or what effects it will have on you long term, and treat  
           you more as a science experiment. You now have a useful, visible (though able to be hidden)  
           cosmetic variation.  

11         You are stricken with persistent dreams, visions, and images of your death in vivid detail  
           whenever you try and sleep or rest. You know they are all real, but cannot reconcile the  
           existential gulf between what your previous “you” experienced, and your new subjectivity.   

12         You are replaced by a digital ‘homunculus’, an electronic imprint and reconstruction of your  
           personality that occupies a subaltern, a kind of robotic shell.  

13         You are plagued by the constant understanding or belief that the ‘real’ you is actually dead,  
           and you are merely a shadow aping a dead person, implanted with the memories of someone  
           else. You cannot establish the difference between the “you” that died and the “you” that exists  
           now. 

14         Due to a clerical mishap, you are implanted with the residual memories of an entirely different  
           and powerful or influential person. This reveals very dangerous and potentially unwanted  
           information to you that is contested or sought after by powerful entities. 

15         The process goes awry and you are revived tabula rasa. In desperation, the techs dump a  
           stock personality construction into you. Change your background (adjust your skills  
           accordingly) 

16         The process of revival is not without complications. Your natural lifespan is dramatically  
           shortened, and you know you will have to undergo another flash-cloning in the near future.  

17         Something changed you, and you have persistent and intrusive mental contact with another  
           entity or entities. It could be human or non-human in nature. 

18         You often are struck with searing headaches during which you see brief flashes of what you  
           are pretty sure is the future. Sometimes it comes to pass, sometimes it doesn’t.  

                                                                                                                     


 19        Knowingly or unknowingly, you are implanted with a mental trigger that when heard or  
           activated, causes you to go into a receptive state, either following a pre-programmed course  
           of action (kill, lie, etc) or to listen to and follow exactly the commands of the person who  
           activated you. These commands must be simple, and the person who gives them (PC or NPC)  
           is determined by the GM.  

 20        You are brought back with complete amnesia of the time before you were re-born, causing a  
           ‘tabula rasa’ situation in which you must be re-trained and cultured, a costly process. Your  
           skills completely reset. Re-assign them as if you were level 0 and just leveled up to your  
           current level. 

                                                         