\section{Reactions}
                                        REACTIONS  

Reactions are special moves that can be made out of turn order in response to incoming triggers  
such as attacks or movement. Upon use, reactions are, unless specified otherwise, expended  
until the beginning of your next turn. You can only make one reaction per turn (your turn or  
another actor’s), but any number per round, as long as you have unspent reactions to perform.  
All mechs can use the Brace and Overwatch reactions once per round by default.
 
\subsection{Brace}
                                                  BRACE  

Once per round, you can choose to brace your mech’s systems in response to incoming fire. You  
can choose to brace against an attack after the attack hits you and you learn what the damage  
is.
 

If you choose to Brace, you gain resistance to all damage from the triggering attack (damage is  
halved, rounding up) and all other attacks against you are made at +1 difficulty until the end of  
your next turn. However, the stress of bracing means until the end of your next turn you cannot  
take reactions and on that turn you can only make one quick action (no regular move, no full  
actions, no free actions, and no overcharge).
 \subsection{Overwatch}

                                              OVERWATCH  

All mechs are able to perform Overwatch. Overwatch represents your mech’s ability to control  
and defend the space around it from enemy incursion, whether through pilot skill, reflex, or finely  
tuned sub-systems. By default, a mech can make 1 overwatch reaction per round.
 

If any enemy starts any movement (move, boost, etc) inside the threat of one or more of your  
weapons, you can immediately make a skirmish action as a reaction against that target using  
that weapon and any others on the same mount that count the target inside their threat.
 

Threat is 1 by default for all weapons unless listed otherwise.