\section{Repair}

                                               REPAIR  

A Repair is in or out of combat healing to your mech. Repairs represent the resilience of your  
mech and its ability to continue functioning while damaged, as well as physical assets such as  
parts or tools. You can spend a repair by taking the Stabilize action in combat, repairing your  
mech during a rest, or using systems that allow you to repair.
 

In combat, you can spend 1 repair as part of Stabilize to heal your mech to full HP.
 

During a rest, your mech cools all heat. You can then spend any number of repairs. 1 repair can:
 
    -    Refill HP to maximum
 
    -    Repair a destroyed weapon or system.
 
4 repairs can be spent to repair a destroyed mech (during a rest only, see below)
 

A pilot’s Repair Capacity is equal to 4+ HULL. This indicates the number of repairs a pilot can  
make before returning to base - so if a mech’s repair capacity is 8, it can only spend 8 repairs  
before taking a full repair. If a pilot has no repairs left, they cannot repair their mech! This  
capacity refreshes to full when a pilot takes a full repair.
 

                                                 DESTROYED  

When destroyed, a mech counts as permanently stunned and shut down until it is restored to  
working condition (these conditions cannot be removed in any way). It then becomes an object  
on the battlefield and provides cover accordingly. The wreck can be moved and dragged around.
 
\subsection{Repairing a Destroyed Mech}
                                  Repairing a Destroyed Mech  

If a mech is destroyed and the wreck is present (not melted in a reactor explosion, for example), it  
can be repaired to working order by spending 4 repairs during a rest. These repairs can be spent  
from the mech’s own pool or the pools of any pilots that wish to contribute, in any combination. If a  
mech has 0 repairs remaining, it can still be repaired if other mechs spend repairs, for example.  
This is unique to repairing a destroyed mech.  

Once repaired, the mech is returned to 1 structure at full HP, no matter how much it had before.  
Any weapons or systems that are destroyed remain so unless that mech spends its own repairs to  
fix them.  
\subsection{Full Repair}
                                                Full Repair  

If you take at least 10 hours of downtime in a secure location, you can Full repair. You can  
repair all damage on your mech unless it is completely destroyed, returning it to full HP and  

                                                                                                                


clearing all stress and structure (you can also repair destroyed systems). Your repair cap  
refreshes to full, your pilot heals to full (or returns from being down and out), you can reset  
your CRITICAL and heat gauges, and end all statuses other than destroyed (including  
CRITICAL and CORE BREACH). You also regain core power if you lost it and get back all  
(limited) use weapons, that you checked off. 
 
\subsection{Printing}
                                                   Printing  

If your mech is destroyed, even if you don’t have the wreck with you, you can rebuild it during a  
full repair as long as you have access to the proper facilities. Mechs can be printed whole-cloth  
from enormous Union printing facilities, which are generally ubiquitous across civilization. A  
printer and assembler will perfectly recreate any mech or gear you have licenses for. If you need  
to work on a destroyed mech and don’t have a printer, it’s also possible to repair it during a full  
repair without a printer, but you need the wreck.
 

                                            One At a Time, Please  

You’re only licensed to print a single active mech at a time. Only the newest mech you printed  
will function (any others repaired, etc will cease to function).
 
\subsection{Rests}
                                                     Rests  

A rest is defined as at least 1 hour of uninterrupted downtime or light activity (making camp,  
routine maintenance, for example). After a rest, as long as you took action to do so:
 
             -   Cool heat  
             -    Heal 1/2 your pilot HP or return from being down and out
 
             -    Exit the CRITICAL or CORE BREACH state if you’re in it and return to 1 HP and  
                 clear 1 heat.  
             -   You can spend any number of repairs to repair your mech, as long as you don’t  
                 spend over your repair cap. You can also repair a destroyed mech.  
             -   You can end any statuses currently affecting your mech automatically.  

                                                                                                                 
