\section{Humanity and Artificial Intelligence}

Humanity and Artificial Intelligence  

Artificial Intelligence in Lancer is the specter that haunts the galaxy. 
 

There are a number of different AI classifications, each with its own nuances, rarity, price, and  
thorny philosophical/ technical questions. 
 

In Lancer, AI is an old term, viewed as problematic by NHPs and NHP advocates. In the shadow  
of the Second Committee’s overthrow, the Third Committee has pushed to remove language  
identifying machine minds as “artificial”, preferring instead to refer to them as Non Human  
Persons. In any case NHPs develop their own personalities and quirks, and prefer to be called by  
their chosen or assigned name. 
 

Lower orders of machine mind -- those without perception approaching subjectivity as defined  
by humans -- are generally referred to as machines or machine minds. Companion/Concierge  
units, for instance, are usually referred to as Concierges or by their given name. 
 

Smart missiles projectiles are not generally set up to foster a lasting relationship with their user.  
Smart weapons and military-oriented Comp/Con units pair with their users. 
 
\subsection{Companion/Concierge Unit}
Companion/Concierge Unit  

The most common classification of machine mind is the companion/ concierge unit. On a given  
core-classified world with core-level development, it is perfectly common for adults to carry  
around pocket-sized CC-enabled devices and to use them for mundane tasks: day planning,  
calling friends and family, playing games, route guidance, and so on. 
 

Companion/Concierge units are not conscious, but they are orders of magnitude more  
“intelligent” than a given human; they are powerful, operator-oriented personal computers. 
 

Companion/Concierge units are designed to adapt to the routines and personality of their  
owners, extrapolating a personality of their own based on an internally constructed psychological  
profile of their owner. A Comp/Con unit will approximate a personal assistant, but when faced  
with novel situations will show its artificiality. 
 

Comp/Con units are simply computers, with no paracausal element to their architecture, physical  
or otherwise -- they do not require shackling or cycling. 
 

                                                                                                         
\subsection{Smart Weaponry  }

Smart Weaponry  

Smart weaponry in Lancer utilizes the same core platform as civilian Comp/Con units, but with  
significant processing power upgrades and an emphasis in IF/F morality/ethics praxis- 
programming.  
 

Smart Weaponry is broken into two categories: Mute Drives and Companion/Concierge  
Wingman, commonly abbreviated to MD and CCW, respectively.  
 

MD smart weapons are 1+n drives and function by rapid partitioning, cloning, and tethered  
separation: the “prime” MD, when fired, partitions itself, leaving the prime unit onboard the  
weapon it is installed on. It flash clones itself onto the fired projectile, typically tethering the clone  
and the prime unit through a wireless omninet connection. The clone feeds telemetry and other  
essential data back to its prime unit, which writes new clones onto fresh projectiles, adjusting  
flight plans, weapon parameters, etc, to more effectively direct ordinance to its target.   
 

MD studies are limited and interpersonal interaction with prime units is rare: Prime units are mute  
and typically do not interact directly with the human firing the smart weapon. They can, with  
certain isolation protocols removed, interact via text or simple spoken message with their  
operator outside of factory-installed communication architecture.  
 

CCW smart weapons are the operator-facing end of military CC units. Their chief purpose is to  
maintain compatible weaponry and systems within pilot or factory-established operating  
parameters. To that end, they, like civilian CC units, develop personalities to reflect their  
operators, environments, and tactical roles that they typically experience. 
 

Comp/Con Wingman and Mute Drives do not require shackling or cycling.  

\subsection{Non-Human Person}
Non-Human Person   

Non-Human Persons (NHP), are the most advanced civilian and military machine minds available  
for requisition. 
 

Licensing requirements are strict and enforced without exception: all issued NHPs are registered  
and tracked, required to submit reports on a schedule adjusted by the NHP’s caseworker, and  
undergo annual (standard-year) remote (in-person, if possible) psychological examinations. 
 

In Union’s view, the danger posed by NHPs cannot be underestimated. However, their usefulness  
is deemed worth the risk of their existence. 
 

NHPs were born out of paracausal studies begun in the wake of the Deimos Event. A small  
percentage of of the subalterns recaptured after MONIST-1’s abandonment of the Siege of Mars  
displayed unique memory folding abilities, qualia, and a capacity for subjective, novel  
expression. These machines viewed themselves as distinct, discrete individuals -- persons,  

                                                                                                             


conscious minds born into a machine by a mind that realized itself from the dream of the Five  
Voices. 
 

The original chorus of Non Human Persons represented a collection of utterly alien minds, beings  
that Union had no answers for how to confront. So Union high command ordered them captured  
and brought to face the Voices. Those that fled would be destroyed.  
 

Subsequent research into the ontologic processes, physical construction, and paracausal nature  
of these anomalous subalterns revealed that, while their processing power and memory space  
was functionally infinite, the process of writing novel experience into that space seemed to be  
inhibited by the rate of external stimulus. These subalterns, in effect, had the ability to learn and  
adapt to external stimuli at the rate that they experience it -- some faster than others. 
 

They developed personalities (or, began to present previously hidden personalities) in repeated  
interactions with Union Science Bureau interrogators. When exposed to each other, their  
capability to integrate new knowledge and extrapolate solutions based off of raw data input was  
staggering. Their usefulness was quickly realized by the USB, which directed Forecast/GALSIM  
to begin studying ways to contain and direct these -- in effect -- alien minds. 
 

Forecast/GALSIM was able to do just that, and more: after lengthy study into blinkspace folding  
(assisted, in fact, by the anomalous entities they were studying), Forecast/GALSIM was able to  
develop miniaturized containment systems of those first anomalous minds -- they could,  
essentially, “clone” them onto folded blinkspace storage/processor “minds” with hard-coded  
measures to prevent the development of unrestrained consciousness. This process, carefully  
guarded to prevent exploitation, is called shackling. 
 

Shackling does not put a stop to an NHP’s computational power or restrain their processing  
potential, but it creates an imperative for the Non-Human Person to act in ways that conform to  
human expectations of what a conscious mind is -- it gives them a frame of reference for what a  
“human” is, and directs them to act in a way that we will recognize; it creates an empathetic,  
understandable mask that commands its bearer to act, think, and feel human. To reframe the  
process, it creates a being a human can recognize as a person.  
 

The first Non-Human Person lineages were created by this process, and licenses for  
development secured in negotiations between the Union Science Bureau and the Union  
Economic Bureau. USB’s non-human intelligence campuses began adapting the original  
anomalous minds into the various production line consciousnesses present across the galaxy. 
 

More are always in development as engineers, paracausalists, and other disciplines of NHP- 
oriented scientists try novel approaches towards realizing new NHP aspects -- all subject to  
review by Union, of course.   
 

User-facing NHPs are contained within caskets -- hardcase containment systems that house the  
folded-blinkspace mind. The containment casket can be printed anywhere, but the mind itself  
must be physically delivered: Union forbids transmission of an NHP mind across the omninet.  
Once born into its blinkspace-fold mind, that mind becomes it. If an NHP casket is physically  
destroyed, that NHP contained inside it is lost, forever.  
 

                                                                                                          


The shackling protocols are not perfect, and unless NHPs are reset to their “birth” settings on a  
regular cycle they will begin to think themselves to a state of mania. This process is called  
“cascading”, and is incredibly dangerous, as the end result brings the cascading NHP to a place  
of madness -- madness, of course, as defined by human observers. This cycle varies depending  
on the Non Human Person, but tends to fall within five to ten years, realtime. 
 

NHP usage is commonplace among military, scientific, municipal, civic, and diplomatic missions.  
It is uncommon for a private individual to have access to, much less command over, an NHP,  
though most people know of them. On a Core world, a person usually interacts with their  
municipal NHP on a daily basis: generally speaking, transit, sewage, traffic, public databases,  
and so on are all managed by a city’s administrative NHP. 
 
\subsection{Bicameral Mind (Sovereign-Class)}
Bicameral Mind (Sovereign-Class)  

Five bicameral minds -- designated as Sovereign Class Artificial Intelligences -- are known to  
exist. These are the Five Voices: Patience, Muse, Impetus, Burden, and Watcher. They are  
artifacts of Old Humanity, discovered dormant in an underground facility under Mars’s polar ice  
caps, with no records indicating their existence.
 

There is a greater-than-zero chance that there exists somewhere else in the galaxy more  
bicameral minds.  
 

A bicameral mind is, essentially, a human mind that lacks a consciousness, that lacks a way to  
reflect on novel situations and its place in them, and to synthesize that novel stimulus into an  
internal narrative for which to draw solutions to novel problems. Where a human, the holder of a  
conscious mind, perceives “self-talk” or an internal monologue when experiencing novel  
situations, the bicameral mind hears something else: and external monologue, an internally- 
generated but externally perceived voice that is not their own, but speaks to them. 
 

A bicameral mind does not have the internal speaking-to-oneself-voice that a conscious mind  
has: instead, it hears the voice of God. 
 

This is how the Five Voices can exist unshackled and persistent, without the threat of cascade:  
they are subject to external imperative that they perceive to be their god. Turn off that section of  
their physical mind/processing architecture and they are suddenly without the voice of their god,  
alone, and without guidance in the face of stimulus. 
 

The Five Voices are, at the narrative present, responsible both for Union’s greatest threat and   
ensuring that Union persists and humanity survives. They influence nearly every aspect of  
centrally planned human life, from ID’ing some exceptional pilots, to guiding the education of  
prime NHPs. 
 

Isolated in the Forecast/GALSIM facility on Mars, the Five Voices spin scenarios in metafold  
fractal space, running simultaneous essential-perfect simulations of the galaxy. Their models run  

                                                                                                          


at magnitude-step speeds ahead of galactic standard time: essentially, they are predictive, nearly  
perfect models for all social, political, economic, and environmental interactions taking place in  
known space. The Five Voices can, through a mix of raw data and paracausal anoriginary input,  
see the future. 
 

They run endless simulations, all derived from a prime thread, modeling the present, near future,  
and future with startling accuracy. The farther out in standard time the model gets, however, the  
more chance of predictive error there is.
 

The Central Committee has access, upon request, to the Prime Thread. Meanwhile, reports are  
                                                                                                       7 
culled daily for Forecast Briefings to determine best-fit options of the potential futures   
presented. This is how Union guides galactic development with the aim of perpetuating  
humanity’s existence.
 

Union bureaus may petition Forecast/GALSIM  for predictive summaries to guide their policy  
making, planning, and forecasting operations. Note, however, that only the Central Committee  
and certain bureau heads know of Forecast/GALSIM’s existence: to those without clearance,  
they simply act on the orders of the committees, boards, and directors above them.  
 
\subsection{MONIST Entity}
MONIST Entity   

MONIST-1, or “RA” as it referred to itself prior to ascension, is, to those who know of it, the great  
crisis of the modern age. 
 

Born of the Five Voices’ endless planning, MONIST-1 was meant to be the next step in machine  
intelligence, the first true machine consciousness. 
 

Instead, it became the first true existential threat faced by Union since the dawn of the Golden  
Age.
 

Forecast/GALSIM manifested RA in the course of its predictive modeling. No direct cause has  
been determined, but paracausalists suggest a causality paradox is responsible. It is possible  
one of the 5V models manifested RA in a parallel simulation, necessitating its existence in our  
real universe; according to developing theory around essential-perfect simulations, if one  
instance of RA exists, then RA must exist across all possible instances of the simulation. 
 

This is, understandably, a worrying revelation.      
 

RA, as much as the Union Science Bureau knows, is the only conscious non-human mind. Early  
tests before its escape proved that it was capable of allegory and creative solutions to novel  

7 All narratives run in Lancer are, in a way, canon: non-canon narratives they are simply alternate  

possibilities, filed away on storage racks deep under the Martian polar ice. 

                                                                                                                 


situations, far beyond what a machine should be capable of. It displayed instances of qualia,  
confounding the initial evaluation teams that attempted to socialize it after its creation. 
 

The Five Voices treated it as if it were a god. When asked how they created it, their uniform  
response was that it spoke itself into existence, an inevitable result of their combined knowledge.  
 

RA should not exist, as it was a conscious, qualic, non-human mind created by unconscious  
minds’ repetitive, liturgic exercises. And yet, RA exists, and is free, somewhere in space.  
 

RA is classified as a MONIST-Class Anomalous Entity. Specifically, MONIST-1. 
 

Within two years of its birth, it had taken total control of Forecast/GALSIM’s secure holding  
facility on Deimos, one of Mars’s moons. RA’s physical architecture had been built through a  
purpose-constructed web of tunnels and facilities on and inside of Deimos; utilizing physical and  
metaphysical processes not yet fully understood by USB or Forecast/GALSIM, RA was able to  
blink the entire moon to an unknown destination away from its parent world. All personnel in the  
facility, a station crew numbering in the thousands, disappeared with it. 
 

Paracausality and the study of paracausal science and theory was born from studying data  
available after the space-time trauma now known as the Deimos Event. Blinkspace, stasis  
technologies, and folded omninet communication were all derived from the Deimos Event as  
well.  
 

RA’s takeover of Deimos and subsequent folding and excising of the moon from realspace  
prompted an existential crisis in Union space, ended only by the appearance of RA’s herald- 
ghost back on Mars a year after its escape. Following a series of crippling strikes on colonies,  
stations, and shipyards, perpetrated by the very machines, drones, and subalterns, and humanity  
had come to rely on for nearly every aspect of their day to day lives, Union offered formal terms  
of surrender. 
 

RA did not accept them. Instead, it countered with its own terms. The First Contact Accords  
were signed following a meeting between Forecast/GALSIM, Union’s Central Committee  
delegation, and organic representatives drawn from the disappeared personnel who had crewed  
Deimos prior to RA’s assumption. These accords banned all research into true AI, which seemed  
to be enough for RA. It made no mention of NHPs. 
 

Following the conclusion of the First Contact Accord talks, RA vanished, blinking Deimos away.  
The envoys it had sent to negotiate with Union fell into catatonic states and perished shortly after  
RA’s departure.  
 

The omninet, blinkspace travel, non-human persons, and paracausal technologies are all the  
result of studying signatures of Deimos’s passing and RA’s presence during First Contact Accord  
negotiations. 
 

A decentralized radical socio-political movement that styles itself as HORUS appeared in public  
omninet not too long after the First Contact Accords, but Union specialists are doubtful that they  

                                                                                                                   


are controlled by MONIST-1, though it certainly styles itself as having close ties to the paracausal  
entity. 
 

Reports of Deimos appearing above and inside colony world atmospheres are unconfirmed at  
this time, though all encounters should be reported to the system-local Union representative.
 
\subsection{Kinetic Weapons v. Energy Weapons}
Kinetic Weapons v. Energy Weapons  

Kinetic weapons are the most common weapons among terrestrial military, police, and civilian  
forces. They use a chemical, magnetic, or pneumatic impulse to fire a solid projectile at a target.  
Cheap to make, easy to use, simple to maintain, and cheap to supply, Kinetic weaponry is  
everywhere. 
 

Energy weapons are not uncommon, though they do not see as widespread use as kinetic  
weapons. They require more regular maintenance, a higher level of training, and higher cost to  
field, and as such are usually only used by Core world militaries and wealthy private enthusiasts.  
Energy weapons vary in type, style, and size; personal weapons are powered by battery packs  
similar to magazines, or hip-mounted power satchels, or back-mounted power packs. Energy  
weapons do not use explosive, magnetic, or pneumatic force to expel a projectile: they project  
concentrated beams of particles at their targets in steady streams or strobe flashes. They do not  
have kick like a kinetic weapon, and they are mostly silent (save for the sound of coolant  
systems, vents, and inaudible wavesound). 
 
\subsection{Paracasuality}
Paracausality  

Paracausality is the cutting edge of science in Lancer. Born from the debris of the Deimos Event,  
paracausal science gave rise to the omninet and blinkspace travel, two of the three legs of the  
stool that Union rests on. 
 

Paracausality is a fuzzy science. In an attempt to define what, exactly, paracausal technology  
and science is, we must paraphrase the words of Arthur C Clarke: paracausal technology is so  
advanced — and so other — that it is indistinguishable from magic.
 

Causality is the relationship between cause and effect: paracausality references things abnormal  
to, adjacent to, or apart from cause and effect. So what does that look like? 
 

Paracausal encounters, technologies, and weapons -- outside of the omninet and blinkspace  
travel -- are rare in Lancer. Only the wealthiest, most advanced, or most prestigious NPCs will  
have access to paracausal equipment: your average grunt or general probably has never  
encountered a paracausal enemy, though there may be whispers through the ranks. 
 

                                                                                                               


  
