\section{Damage}
 DAMAGE  

You want to avoid or mitigate incoming damage as much as possible, but know this: Sometime,  
somewhere, someone is going to punch a few holes in your kit. 
 

Damage in LANCER comes in three types: Explosive, Energy, and Kinetic, each representing a  
different type of weaponry or projectile.
 

Armor, like with pilots, reduces all incoming damage by the amount indicated. Damage with the  
AP tag ignores armor. 
 
Resistance reduces all incoming damage by 1/2 of a particular type. Mechs can only have  
resistance once (it doesn’t stack) for a particular type of damage. 
 

Damage in LANCER resolves as follows:
 
             1.  Reductions from armor
 
             2.  Reductions from systems, talents, and reactions, such as those that grant  
                 resistance. Only one reduction of a type or system can be applied at once.
 
Remaining damage is dealt to your HP, your HIT POINTS. 
 

For example: Your total HP is  15. You take fire from an enemy, who scores a successful hit by  
beating your mech’s Evasion. You’re dealt 12 points of kinetic damage. Lucky for you, you have  
armor installed on your mech, which subtracts 2 from all incoming damage, reducing the final  
amount of incoming damage to  10. Your total HP after all modifications to incoming damage  
have been applied is now 5. Take cover!   

                                               Heat and Burn  

Some weapons also deal Heat or Burn. 
 
    -    Heat is not affected by armor, though it can be affected by resistance. It fills up a mech’s  
         heat capacity (see the section below)
 
    -    Mechs affected by Burn immediately take damage equal to the burn they just took,  
         ignoring armor. At the end of their turn, a mech can make an engineering check. On  
        success, they clear all Burn on themselves, on failure, they take damage equal to their  
        current Burn. Burn can stack with itself (so being hit by Burn 3 twice would increase it to  
         Burn 6). Burn is its own damage type.
 
\subsection{Structure}
                                                Structure  

If your mech is ever reduced to 0 HP, unlike a pilot, you are not down and out. Your mech is a  
powerful machine that can take multiple hits before it starts to be break down. This is  
represented by structure. Player mechs have 4 structure, NPC mechs might have less.
 

                                                                                                             


When a mech or other actor with structure is reduced to 0 HP, it takes 1 structure damage,  
makes a structure check, then resets its HP to full. It then takes any damage that ‘spills  
over’ (this could cause it to lose multiple points of structure and make multiple structure checks  
in a turn). Structure damage represents major damage to your mech or its systems.
 

If your mech takes its last point of structure damage and checks its last box, it goes into the  
CRITICAL state (see below). This is a state in which your mech is so heavily damaged that it  
begins falling apart with every hit. NPCs that run out of structure typically are destroyed.
 
\subsection{Structure Damage}
                                        STRUCTURE DAMAGE  
When your mech is reduced to 0 HP or when it takes any damage in the CRITICAL state, you roll  
on the structure damage chart. Structure damage represents the results of unusually powerful or  
accurate hits, which can disable a mech rapidly if not dealt with. When you make a structure  
check, roll 1d6 per point of structure damage you have marked. When rolling multiple dice,  
choose the lowest result, though certain outcomes activate if you also roll multiples 1s.
 

                                            STRUCTURE DAMAGE  

 ROLL            RESULT                   EFFECT 

 5-6             GLANCING BLOW            Emergency systems kick in and stabilize your mech. However, your  
                                          mech is impaired until the end of your next turn. 

 2-4             SYSTEM TRAUMA            Parts of your mech are torn off (potentially limbs). All the weapons  
                                          on one mount or a system chosen by you is destroyed. If a system  
                                          is used up (it has the limited tag and no charges left) it’s not a valid  
                                          target. If there’s nothing left to destroy, this result becomes DIRECT  
                                          HIT instead. 

 1               DIRECT HIT               This result has different outcomes depending on how much  
                                          structure damage your mech has remaining.
 
                                          3+ - Your mech is stunned until the end of your next turn.
 
                                          2 - Your mech must pass a hull check or be destroyed.  
                                          1 - Your mech is destroyed. 

 Two or          CRUSHING HIT             Your mech is damaged beyond repair and is destroyed. You can  
 more 1s                                  still exit it as normal. 

                                              The CRITICAL state
 

When your mech ticks off its last point of structure (typically 4), it immediately enters the  
CRITICAL state, remaining at 0 hp. While CRITICAL:
 
             -    Your mech cannot repair or gain Hit Points.
 
             -    When you take damage, you make a structure check.
 
This allows a mech to stay fighting at great personal risk to the pilot. A mech can exit the  
CRITICAL state only by resting or taking a full repair. When a mech exits the CRITICAL state it  
returns to 1 HP.
 

                                                                                                                   

