\section{Debrief and Downtime}

                      DEBRIEF and DOWNTIME
 

Once a mission is over (success or failure) and the players have time to recuperate, it’s time for  
the Debrief. Much like the Brief, this step of a LANCER game doesn’t have to be an actual  
meeting in-character, and could just be an out-of-character conversation amongst the people  
playing at the table. 
 

A mission being over or completed should be a natural stopping point in the narrative (it could  
even be mid-mission if the objectives have changed). Players don’t necessarily need to have  
accomplished their goal, but something needs to have changed enough about the mission that  
the mission itself is functionally over.
 

During the debrief:
 
	        1. Level up - Characters gain 1 license level, representing their access to resources,  
income, or clout. Characters get more access to mech gear and increase their skills. You can find  
more information on leveling up at the end of the mech section, but pilots gain +1 to any skill and  
every 3 levels can gain additional training, allowing them to get +1 accuracy on certain skill  
triggers as if they had a background in it.
 
	        2. Talk about the mission. This is not a necessary step but can be helpful to think about  
what worked and what didn’t during the session. If there were any notable moments that were  
fun, interesting, or exciting it can be helpful to talk about them here as well. Not only is it good  
feedback for the GM but also can help validate your fellow players. If you’re going to take this  
step, remember to be respectful.
 

\subsection{Downtime}
                                             DOWNTIME
 

Pilots are individuals (exceptional individuals, perhaps), with lives to live outside of their mechs.  
It’s assumed in LANCER that your pilot has a lot to do outside of a mission. What exactly that is  
depends on the GM, the narrative, and the players involved in the game. 
 

Your story might not include much downtime - maybe the character are on a planet under siege  
and have little time to pursue other projects. It might include a lot of downtime - maybe there’s a  
time skip in between missions of several months, allowing characters many opportunities to  
pursue their other goals.
 

What’s important for the game of LANCER is there must be at least SOME downtime between  
missions, even if that’s only a few hours. This allows players to prepare for the next mission and  
take actions that will impact the story going forward.
 

                                           TIME AND DOWNTIME
 

Downtime is almost purely narrative and doesn’t have to follow strict moment-to-moment action.  
You can allow one roll in downtime to cover any amount of time, from an hour to a few months  

                                                                                                                


worth of activity. Generally it is better to let the outcomes of rolls follow the narrative  
circumstances, ie the impact of rolls that cover several months of activity should be  
consequently more.
 

                      REWARDING DOWNTIME: FREEFORM VS STRUCTURED
 

Downtime can be used to accumulate reserves by taking certain actions in order to prepare for  
the next mission. During downtime, players can take one downtime action, or two if downtime is  
especially long. If the players are under siege, for example, they probably only have time for one.
 

The purpose of downtime is not merely to prepare for the next mission, however - it’s also to  
progress personal stories, advance plots, or flesh out characters. You can do freeform  
roleplaying as much as you like during downtime with absolutely no intent (as it is during any  
mission), but the GM can still feel free to reward this kind of play with similar rewards if it  
feels appropriate. For example, even if Pan and Penny are role-playing a scene of them drinking  
at a bar together with no intent to prepare anything, gain reserves, or take downtime actions, the  
GM might decide to give them +1 Accuracy on skill checks to help each other during the next  
mission because of their bond.
 

\subsection{Reserves}
                                                 RESERVES  

During downtime, you might want to prepare reserves for the next mission. This is a catch all  
term for extra supplies, gear, support, bonuses, allies, etc that you accumulate during downtime.  
The GM can give you reserves at any time as a result of the story (for example, granting you  
reserves as part of a mission). You can also typically ask for reserves by using the power at a  
cost tool below, or by successfully taking downtime actions.
 

You establish reserves you are taking on a mission before you embark on that mission. There’s  
no limit to what you can take along other than what the GM and your own actions are willing to  
grant you.
 

Here’s some examples of reserves. Don’t take these examples as set in stone, but as ideas for  
the kind of reserves that could be available to you. Abstractly speaking, reserves is anything  
you are holding as an advantage for the next mission. The reserves available to characters  
should be dependent on the GM, your own actions, and the story. Some of these are relevant to  
mechs (See the mech section for more details), some for pilots, and some for the story.
 

Before a mission, if the GM is using a list of reserves, it can help for it to be visible for all  
players so players have a good idea of what is potentially available for them. When rewarding  
reserves, the GM doesn’t necessarily have to pick from this list.
 

TABLE: Narrative Reserves  

                                                                                                                 


 d20       Narrative	Reserves 

  1-2      Access: Gain a keycard, invite, bribes, or insider access to a particular location 

  3-4      Backing: Political support from someone powerful for this mission - you can invoke it  
           as leverage 
  5-6      Supplies: Cross a hazardous or hostile area without having to make a skill check 

  7-8      Disguise: Prepare a disguise or cover identity, allowing you to sneak into a location  
           uncontested 
 9-10      Diversion: Prepare or arrange for a diversion, giving you time to take action without  
           fear of consequence 
   11-12   Blackmail: Gain blackmail or sensitive information on a particular person 

   13-14   Reputation: Make a good name for yourself for the next mission, starting you off on a  
           good position with everyone you meet 
   15-16   Safe Harbor: Gain a guaranteed safe location where you can convene, plan, or  
           recuperate 
   17-18   Tracking: Know the location of important objects or people for this mission 

   19-20   Knowledge: Gain important knowledge of local history, customs, or culture etiquette  

TABLE: Mech Equipment and gear reserves  

 d20       Mech	reserves 

  1-2      Ammo: Get extra uses (+1 or +2) to a (limited) weapon or system 

  3-4      Rented gear: Get access to a weapon or piece of mech gear you don’t normally have  
           access to for the mission only 
  5-6      Extra repairs: Start the mission with +2 repairs on your mech. 

  7-8      CORE battery: Consume this to gain core power on your mech, allowing it to use its  
           most powerful ability again (you can’t get more than 1 core power at a time) 
 9-10      Deployable Shield: Gain a 1-use deployable shield generator, a size 1 deployable that  
           grants all allied actors in a burst 2 radius around it light cover 
   11-12   Redundant repair: 1/mission make the stabilize action as a free action 

   13-14   Systems reinforcement: Get +1 accuracy to hull, agility, systems, or engineering  
           checks, this mission only (choose one) 
   15-16   Smart ammo: All weapons become smart, this mission only 

   17-18   Boosted servos: Become immune to the slowed condition, this mission only 

   19-20   Jump jets: Your mech can fly when it makes its regular move, this mission only 

TABLE: Tactical reserves  

                                                                                                                


 d20       Tactical	Reserves 

 1-2       Scouting: Get detailed information on the kinds of mechs and threats you will be  
           facing soon, such as number, type, and statistics 
 3-4       Vehicle: Gain use of a transport vehicle or starship for this mission only (a tier 1 NPC  
           with the vehicle or ship tag) 
 5-6       Reinforcements: Call in an NPC mech ally, once per mission (choose a tier 1-3 NPC  
           from the NPC section). 
 7-8       Environmental Shielding: Ignore a particular battlefield hazard or dangerous terrain,  
           such as extreme heat or cold 
 9-10      Accuracy: Gain +1 accuracy on a particular skill or action due to training or  
           enhancement, this mission only 
 11-12     Bombardment: Call in a artillery or orbital bombardment once during mech combat  
           (Full Action, range 30 within line of sight, blast 2, 3d6 explosive damage). 
 13-14     Extended Harness: Carry an extra pilot weapon and two pieces of pilot gear into this  
           mission 
 15-16     Ambush: Choose exactly where your next battle will take place, including the terrain  
           and cover set up, etc 
 17-18     Orbital Drop: Start the mission dropping from orbit into a heavily fortified or hard to  
           reach location 
 19-20     NHP assistant: Gain an NHP, controlled by the GM, that can give you advice on the  
           current situation 

Here’s some examples of reserves in play:
 

Xi Xiaoyun  

During downtime, Xi negotiates with the powerful boss of the Red Dog Triad local crime  
syndicate. He knows their next mission might take them through their territory. He makes some  
checks (and some promises) and gets in the boss’s good graces. The GM tells his player he can  
write down the following for reserves:
 
	        Weaponry: I’ve borrowed a Coldcore sniper rifle from the triad (from the Smith Shimano  
Corpro gear catalogue) just for this mission
 
	        Backing: I have the backing of the triad. If someone messes with me, I can invoke that.
 
	        Information: I can ask the GM what kind of enemies we might run into on the mission  
due to the Triad’s spy networks
 

Pard Landover  

Pard decides to do some scouting during downtime, scavenging a strange, abandoned derelict  
in his mech for supplies. After some harrowing exploration and a few skill checks, the GM asks  
him to write the following down:
 
	        Ammo: I’ve recovered extra ammo cases, giving me +1 use to all limited weapons
 
	        Nanomaterials: I’ve recovered some strange nano materials, giving me +2 repairs to my  
mech this next mission  

                                                                                                                 

\subsection{Downtime Actions}

                                           Downtime Actions
 

You can use these story actions below to represent what your pilot gets up to during a stretch of  
downtime. You can also use them to fill gaps in the story where you want to speed things up,  
‘montage’, or cover a greater stretch of time.
 

Unlike a regular skill check, these downtime actions have specific outcomes depending on  
whether you hit, miss, or excel, and usually ask you to choose from a list. The actual skill used is  
dependent on context. For example, the Get a Damn Drink action could be rolled using Survive  
(for alcohol tolerance, most likely), or Getting Word on the Streets (charming the locals).
 

Each outcome is dependent on the roll, but is up to the GM and the player making the action to  
establish the details, using the prompts given. You can go into as much detail about the ins and  
outs of the action as you want - the outcome is the only thing that’s important.  

As a good rule, a pilot can do only one of these during downtime, and one or two if the downtime  
is especially long. You can always keep the outcomes of these actions as reserves for the next  
mission.  

You can easily write your own downtime actions that are more dependent on your particular  
narrative or story, using them modeled ones below.  

To start, let’s look at the Power at a Cost action.  

\subsection{Power at a Cost}
POWER AT A COST  

This is a really simple downtime action for gaining rewards, opportunities, or additional  
resources (such as reserves). You might want reserves, or something more abstract, like time,  
safety, information, allies, support, a base of operations, materials, shelter, food, a damn  
pack of cigarettes.
 

Name what you want. You can always get it, but:  

BUT (the GM chooses one or two of the following and fills in details, depending on how  
outlandish the request is):
 
    -    It’s going to take a lot more time than they anticipated  
    -    It’s going to be really damn risky  
    -    You have to have to give something up or leave something behind (wealth, resources,  
         allies)  
    -    You’re going to piss someone or something important and powerful off to get it  
    -    It’s going to involve going WILDLY off the plan  
    -    You’ll need more information to proceed safely  
    -    What you put together is going to fall apart damn soon  

                                                                                                                  


    -    You’ll need to gather more resources first (you know where to find them, however)  
    -    You can’t EXACTLY get what they want, just approximately what you want, a lesser  
         version, or less of what you want
 

You can also use the power at a cost action mid-mission for similar effects (not necessarily  
during downtime). The rest of the downtime actions are typically for use only in downtime, but  
you could adapt them mid mission if they fit.
 

BUY SOME TIME  
You try and stave off some reckoning, extend your window of opportunity, or merely buy more  
time and breathing room for you and your group to act. You might be trying to dodge some heat,  
survive stranded in the wilderness, or cause a distraction so another plan can go off. You can use  
that distraction or bought time as reserves for the next mission.  

On a total result of 9 or lower, you’re out of time, and whatever you’re trying to stall catches up  
with you unless drastic measures are taken right now.  
On a total result of 10-19, you can buy enough time, but the situation becomes precarious or  
desperate. Next time you get this result with the same situation, treat it as a 9 or lower.  
On a total result of 20+, you buy just enough time as you need for now, until the next mission. If  
you’ve already gotten this result, it becomes a 10-19 for the same situation next time.  

GET A DAMN DRINK  
You can only make this action where there’s a drink to actually get (in town, a station, a city, or  
some other populated area). You blow off some steam, carouse, and generally get into trouble.  
You could be doing this to make connections, collect gossip, forge a reputation, or maybe just to  
forget what happened on the last mission. Drinks don’t have to be involved, but vice usually is.  
There’s usually trouble.  

On a total result of 9 or lower, you can decide whether you had good time or not. However, you  
wake up in a gutter somewhere with only one of the following (choose!):  
    -    Your dignity  
    -    Most of your possessions  
    -    Your memory  
On a total result of 10-19, you get one of the following as reserves and lose one of the following:  
    -    A good reputation  
    -    A friend or connection  
    -    A useful item or piece of information  
    -    A convenient opportunity  
On a total result of 20+, you get two of the above and don’t lose anything  

GET CREATIVE  
You tweak something or attempt to make something new, either a physical project, or a piece of  
software. It doesn’t have to be something on the a gear list, but it generally can’t be something as  
impactful as a piece of mech gear. Once finished, you can use it as reserves.  

                                                                                                                  


On a total result of 9 or lower, you don’t make any progress on your project for now. If you already  
got this result on the same project, treat it as a 10-19 next time.  
On a total result of 10-19, you can make progress on your project, but can’t finish it. You can finish  
it next time you have downtime without a roll if you get some things before then (pick 2):  
    -    Quality materials  
    -    Specific knowledge or techniques  
    -    Specialized tools  
    -    A good workspace  
On a total result of 20+, you can finish your project during this downtime. If it’s complicated, treat  
this result as a 10-19, but only choose 1.  

GET FOCUSED  
You focus on increasing your own skills, training, and self-improvement. You might practice, learn,  
meditate, or call on a teacher. Before you make this action, name one thing you’d like to learn or  
improve on (a skill, technique, an academic subject or language). This could be something like  
starship piloting, cooking, chess, boxing, history, or etiquette. It should generally be a non-combat  
action.  

The GM will give you a new trigger for a skill, giving you +1 Accuracy when you undertake your  
new action (you need to work out which skill to use). For example, the trigger could be +1  
Accuracy to roll sharp when playing chess, or +1 Accuracy to roll cool when dancing.  

GET ORGANIZED  
You start, run, or improve an organization, business, or other venture. Describe it when you start it  
up: it’s purpose or goal, mode of operation, and primary business. Track your organization’s  
efficiency and influence, from 1-6 (they each start at 1). When you want to make a narrative role  
where your organization could help, you can roll your organization’s efficiency or influence like a  
skill check. Efficiency is how effective your organization is at what it does (a military organization  
with high efficiency would be good at combat, for example). Influence is your organization’s size,  
reach, and reputation. An organization with high influence can easily acquire assets or create  
opportunities, transport people, or sway public opinion. You can use these advantages as  
reserves.  

On a total result of 9 or lower, your organization folds immediately unless:  
    -    It lowers in efficiency and influence by 1, to a minimum of 1. If it’s already at 1 for both of  
         these, you can’t choose this option.  
    -    It takes one of the following actions: pay debts, prove worthiness, get bailed out, make an  
         aggressive move  
On a total result of 10-19, your organization is stable. It gains +2 influence or efficiency, to a  
maximum of +6.  
On a total result of 20+ your organization gains +2 influence and efficiency, to a maximum of +6  

GATHER INFORMATION  

                                                                                                                   


You poke your nose around, perhaps where it doesn’t belong. You’re investigating something,  
doing research, following up on a mystery, tracking a target, or keeping an eye on something. You  
might be doing research in a library, or go undercover in an organization to learn what you can.  
Whatever you’re doing, you’re generally trying to gather information on a subject of your choosing.  
You can use this information as reserves.  

On a total result of 9 or lower, you can choose to get out now, or treat this result as a 10-15. If you  
choose the latter, you get your information but you are immediately found out, noticed, captured,  
or discovered by an organization that either controls or seeks that information.  
On a total result of 10-19, you find the information you’ve looking for. However, (choose one):  
    -    You leave clear evidence of your rummaging  
    -    You have to dispatch, harm, or implicate someone innocent  
On a total result of 20+, you get your information cleanly, no complications  

GET CONNECTED  
You try and make connections, call upon favors, ask for help, or drum up support for a particular  
course of action. You need access to communications or just good old fashioned face to face  
conversation to take this action. You can use your connection’s resources or aid as reserves for  
the next mission.  

On a total result of 9 or lower, you’ve got to do a favor or make good on a promise for your  
connection right now. Otherwise, they won’t help you at all. If you take action right away, however,  
they’ll go along with what you want.  
On a total result of 10-19, your connection will help you, but you’ve got to do a favor or make good  
on a promise after they help you. If you don’t, treat any result as a 9 or lower next time with the  
same organization.  
On a total result of 20+, your connection will help you out, no strings attached.  

SCROUNGE AND BARTER  
You try and get your hands on some gear or asset for your group by dredging the scrapyard,  
chasing down rumors, bartering in the local market, hunting around, or through good old  
fashioned force of will. You could try and get some better pilot gear that could help you, a vehicle,  
narcotics, goods, or other sundries. It’s got to be something physical that you can acquire, but  
doesn’t necessarily have to be on the gear list. If you get it, you can take it on the next mission as  
reserves.  

On a total result of 9 or lower, you can get what you’re looking for, but (choose one):  
    -    It was stolen, probably from someone who’s looking for it  
    -    It’s degraded, old, filthy, or malfunctioning  
    -    Someone else has it right now and won’t give it up without force or convincing  
On a total result of 10-19, you can get what you’re looking for, as long as you trade in a little  
(choose 1):  
    -    Time  
    -    Dignity  
    -    Reputation  

                                                                                                                   


     -   Health, comfort and wellness  
On a total result of 20+, you get what you’re looking for, no problems at all.  

\subsection{Putting it all Together}
                                    PUTTING IT ALL TOGETHER  

After downtime naturally wraps up, the game should loop right back into the next mission,  
following the same structure (Brief, Preparation, Mission, Debrief, Downtime).  

Of course, narrative play doesn’t cover everything in a game of LANCER. There’s inevitably  
always conflict, and that conflict is probably going to involve mechs, which brings us to the next  
section.
 

                                                                  