\section{An Endless Generator, An Unquiet Forge}

An Endless Generator, An Unquiet Forge   

Generator Tools for GMs and Players   

\subsection{Deep Field Survey }

Deep Field Survey   

Iterative worldbuilding, courtesy of the Union Astrocartography Department.   

World Type   
     1.  A barren world, with no atmosphere, few valuable resources, no water, under a ceaseless  
         barrage of terrible radiation.   
     2.  A barren world, with little atmosphere, and a distant sun. It is a cold, dead place, where  
         lonely wind blows perpetual across flat planes of dark ice and stone.   
     3.  A barren world rich in mineral wealth, cooling after a long period of tectonic activity.  
         Massive thunderstorms lash the world, and methane ice storms accumulate into world- 
         sculpting glaciers.  
    4.   A barren world encased in ice, with a deep subglacial sea. The surface trembles with  
         asteroid impacts, and the world’s orbit trails ice and dust behind it.   
     5.  A barren world, old and close to its sun, where the mountains have eroded to sand, and  
         the dunes are endless and white.   
     6.  A temperate world, lush, forever hazy under a thick mist that all but blocks out the sun.    
     7.  A temperate world, with myriad biomes, and skies piled high with columnar clouds.   
     8.  A temperate world, dry across great swathes of plainsland and desert, where vast alluvial  
         deposits speak of rivers that once were.   
     9.  A temperate world of archipelagos scattered across a salton sea  
     10. A temperate world with a mild climate, rich in native flora and fauna, and old, stable  
         biomes.   
     11. An inhospitable world, whose atmosphere is thick and choking, with deep valleys that hold  
         pockets of breathable air.  
     12. An inhospitable world of storm-tossed nitrogen oceans and wind-polished cadmium  
         islands, where tides surge and recede for years and no land is safe from the flood or  
         retreat.    
     13. An inhospitable world of lava and lightning, a new world, where there is no life to be found.  
     14. An inhospitable world, scoured by a distant gamma ray burst, where the life that once was  
         there has long since died off, and the land simmers with fires that never stop.   
     15. An inhospitable world, cracked open by an ancient impact, its core bleeding heat into  
         vacuum as it slowly dies.    
     16. A temperate moon with a stable atmosphere, the curve of its horizon visible from even a  
         modest mountaintop. Its parent world looms massive above it, ever-present in its day and  
         night sky.   
     17. An icy moon, cold and dim, one of many around its parent world. It absorbs the impacts of  
         asteroids that would otherwise hit its counterpart.   
     18. An ocean world, where there is no land.  

                                                                                                                 


    19. A barren world with a stable, if thin atmosphere. Massive geometric features and perfectly  
        flat metal planes create an uncanny landscape; deep canals funnel moaning wind around  
        the world.   
    20. An ancient world, star red and swollen in its sky, where all things have a terrible symmetry,  
        as if nature itself had oriented -- or been oriented -- around something now absent.   

Defining Natural Feature  
    1.  100 year storms with increasing regularity -- typically manifests as massive hurricanes.   
    2.  Very active tectonics -- earthquakes are more common on this world than others. On  
        ocean worlds, this means a higher prevalence of tsunamis.   
    3.  Inert core -- this world’s core has stopped spinning, and as a result it has shed its  
        magnetic field. Compasses do not work on this world, and UV exposure is dangerous  
        without significant protection.   
    4.  Monobiome -- this world is an oddity among worlds, in that has a single, global biome with  
        a single, global climate. It could be a forest that spans the world, or a desert, a swamp,  
        and so on.    
    5.  Worldscar - the world has suffered a recent (within a million years) impact from a massive  
        stellar body. Its climate has leveled, but the scar of the impact is still a massive, visible  
        feature on the world’s surface.   
    6.  Royal Court - the world has hundreds of terrestrial moons, ranging from hundreds of yards  
        in diameter to thousands of kilometers. The night sky is bright, and the day is marked by  
        gentle, dappled light.   
    7.  Under Twin Suns - the world orbits a binary star.  
    8.  Ringed -  the world is banded in a series of planetary rings, visible as a thin white line  
        across the night sky. It is an especially beautiful world to view from afar.    
    9.  Remote - this world was a remote colonial, industrial, or scientific prospect. It is far  
        removed from any other civilization, and takes great effort and time to reach.  
    10. Cosmopolitan - this world is located close to interstellar shipping lanes, and is a frequent  
        landmark, resupply point, or pit stop for interstellar travellers, who ether remain in orbit or  
        have an easy route down to the surface of the world.   
    11. Hecatoncheires - The world is marked by a series of massive mountains, sheer peaks  
        rising kilometers into the sky.   
    12. Epochal Sunset - the world is gripped by the transition between eras -- ice to temperate,  
        temperate to ice, and so on. Expect a varied climate.   
    13. A Monument of Shame - the world is a dumping ground for passing ships, for a local CS,  
        or abandoned following massive climate destabilization.   
    14. Quarantined - the world has been hidden behind Union red tape, for reasons unknown or  
        known.     
    15. Breathable Atmosphere - the world, unless already noted, has a breathable atmosphere. A  
        human can breathe without relying on an EVA, scrubbers, or other assistance or  
        augmentation.   
    16. High Gravity - the world, in addition to any other features, has higher than standard gravity,  
        ranging from +1-2G greater than Cradle standard.    
    17. Low Gravity - the world, in addition to any other features, has lower than standard gravity,  
        ranging from .1-.99G less than Cradle standard.   

                                                                                                         


    18. Hard Sun - in addition to any other features noted in its description, this world’s  
        atmosphere provides little to no UV protection. Venturing outside in the daylight is a risk  
        without proper optical and dermal shielding.   
    19. Dreamland - in addition to any other features noted in its description, this world has  
        something, well, otherworldly about it that makes it stand out. Islands that float suspended  
        in the air, or oceans of liquid mercury, or motile fauna, and so on.   
    20. Dust and Echoes - the world has ancient, pre-collapse ruins on it, with no indication as to  
        their origin or nature.  

Defining Anthropocentric Feature   
    1.  Colonial Settlement - initial. There is a settlement here, but it was only recently seeded.  
        Drones and subalterns work tirelessly, clearing space and assembling the initial colony  
        footprint. A small cluster of buildings house the landfall team -- they are likely welcoming,  
        as they’ve probably not seen anyone else for years. The population numbers in the  
        dozens.   
    2.  Colonial Settlement - first generation. The colony settlement here is young, with its first  
        generation of native-born colonists now of-age and set to the work of building their future  
        home. The population numbers in the hundreds to thousands.   
    3.  Colonial Settlement - stable. The colonial settlement here is in its second or third  
        generation, stable, with a population in the tens of thousands.   
    4.  Outpost - Union Far Field Team Mission. There is a FF Team outpost on this world, but  
        nothing else in the way of human population.   
    5.  Outpost - Omninet Relay Node. The world is empty save for a lone omninet relay node. A  
        small team crews the node, providing security and on-site technical support. They rotate  
        on a regular schedule.   
    6.  Outpost - Union Navy SigInt Station. The UN maintains a small signals and intelligence  
        station on this world. There may or may not be other populations here -- that is up to you --  
        but the SigInt station is in a remote, high-altitude part of the world.   
    7.  Outpost - Union Astrocartography Station. The world is marked with an orbital  
        astrocartography station -- a suite of automated telescopes, sensors, and observational  
        equipment used to map more distant stars and worlds.   
    8.  Outpost - Checkpoint/ Forward Post -- The world hosts a small Union garrison, most likely  
        auxiliaries who report to a remote Union officer. Their duty is to scout, stand watch, and  
        await further orders. They spend most of their time exercising, cleaning, maintaining their  
        gear, and waiting for something to happen.   
    9.  Installation - Research Facility - The world hosts a Union, Corpro-State, or other state or  
        private entity’s research facility. It may be a secure, top secret site, or it may not.   
    10. Installation - Proving Ground. The world, or a significant part of it, is given over to a  
        proving ground, test field, ordnance firing range, or other large-area hazardous testing,  
        training, measuring, or dumping installation. Run by a small long-term skeleton crew, there  
        typically is a larger short-term crew or population present during a given season or  
        exercise.   
    11. Installation - Deep Field Relay Installation. The world features a secure, long-range,  
        planet-based sensor installation, typically located in a remote, high-altitude location.  
        Populated by a small crew, the installation can be privately run or Union.   

                                                                                                          


     12. Installation - Union Embassy. Generally only found on more developed worlds  
         approaching or at Core status, Union Embassies are modest, centrally-located buildings  
         typically sited in capital cities on capital worlds. They function as embassies do.   
     13. Installation - Corpro-State Campus. This world features a publicly-accessible or off-limits  
         CS campus with a large permanent population. This can be an enclave, an exclave, or  
         integrated into a larger urban environment, and typically is an administrative center with  
         some level of public exposure (even just notariety)   
     14. Base - Union Naval System Command. The world is the site of a regional system  
         command center for the Union Navy. Part base, part garrison, part shipyard, part  
         recruitment center, part medical center, a UN SysComm facility is a large, removed,  
         military base with a defensive perimeter, sunken launch pads, and hardened buildings and  
         bunkers. It has a massive permanent population and a garrison numbering in the  
         thousands, usually with a complement of ships in orbit with (at minimum) global strike and  
         delivery capacity  
     15. Base - Capital. This world is the capital world of a system, and hosts the physical center of  
         the system’s government, generally a campus, estate, block, or other large collection of  
         hardened buildings charged with ministering to the state’s population. Generally speaking,  
         there is some level of public access to this building, but only in more liberal states.   
     16. Base - Uplift. This world has a spaceport, a sprawling launch facility open to the public  
         (access subject to local laws, of course, beyond the basic ability to purchase a ticket  
         offworld).    
     17. Civic - Municipalities. The population of this world live in modest towns and cities scattered  
         across biomes. The population numbers in the hundreds of millions. There may be one or  
         two signature cities, but there are vast stretches of wilderness between them, and each  
         municipality has developed their own take on global cultures.    
     18. Civic - Arcology. The world’s population lives in one or more arcologies -- unified, self- 
         contained ecosystem-cities -- in harmony with the world around and inside of them. They  
         may be strictly monitored and walled-off from the larger world, or not. Worlds with  
         arcologies as the primary urban centers tend to be well developed, with a history at least  
         centuries long. The global population numbers in the hundreds of millions to single-digit  
         billions.   
     19. Civic - Metroswathe. Unlike an arcology or municipality, a world marked by metroswathes  
         is heavily developed, with a significant percentage of the landmass given over to a single,  
         amalgamated urban environment (<10-15%) that is home to billions. That it functions --  
         and there are likely large chunks of it that doesn’t -- is a miracle. A metroswathe is usually  
         not planned to be a swathe, but there are certainly large sections of it that have been  
         developed intentionally, rather than just metastasizing. There are usually vast, baroque  
         criminal, bureaucratic, and community organizations working both above and below board  
         (and street level!).   
    20. Union - Administrator’s Residence. This world, if it wasn’t previously, is habitable, and has  
         a stable population of millions. A Union Administrator makes their residence here.    

COMBAT AND ROLEPLAYING ENVIRONMENTS  

Roleplaying and combat can take place anywhere in the galaxy. Most human affairs occur in one  
of three locations: on a terrestrial world (or moon, asteroid, comet, etc), on a satellite station, or  
onboard a spaceship. 
 

                                                                                                                    


Habitable worlds are terrestrial worlds, moons, asteroids, or comets that are tectonically stable  
enough to support structures; these worlds do not need to have an atmosphere in order to be  
considered habitable -- in Lancer, “habitable” means a world on which humans can live, not  
necessarily live comfortably or independently of life-sustaining systems. 
 

Habitable worlds that are stable and have a breathable atmosphere that protects and sustains  
human life are called Terran worlds. These are rare and precious, usually the site of stellar  
nations’ capitals or preservation worlds. 
 

Satellite stations orbit larger stellar bodies: orbital habitats, shipyards, blink stations, omninodes,  
orbital science stations, orbital military installations, and others all fall into this category. 
 

Typically, civilian stations have a large permanent populations and act as galactic transit hubs.  
Travellers pass through these stations on their way to their berths or while their ships are  
refueled, resupplied, and rearmed; the civilian population on the station typically works around  
this transient population at cafes, bars, shops, and entertainment venues, and in maintenance,  
logistical, engineering, and harbor navigation roles. 
 

Military stations typically have small populations posted on a semi-permanent basis, usually for a  
period of months or years before being rotated out.   
 

Example environments:  
 

    $\bullet$    A lush jungle world, thick with kilometer-tall trees and layered canopies thick enough to  
        support buildings. The light fades to a darkness complete the deeper you dare venture.  
    $\bullet$    A dead moon with a thin skein of atmosphere, just enough to form and hold clouds at  
        ground level. The wind is terrible and constant, and carves strange shapes from the  
        moon’s soft grey rock.    
    $\bullet$    In borean fields of polar ice, a crashed Far-Field Shuttle broadcasts its lonely SOS. A band  
        of slavers makes across the permafrost, their flyers beating low over the white landscape.  
        A blizzard approaches.        
    $\bullet$    On the metal and stone flanks of a rocky world, where unique magnetic properties hold  
        iron pillars suspended in the air. Buildings here must be made of wood and plastic, and  
        your mechs struggle to adapt to the interference.    
    $\bullet$    Aboard an abandoned station in decaying orbit, its inertial gravity fluctuating in response  
        to the decay. The station lists to the side as distal components begin to break away. The  
        station’s NHP is firm in its declaration of intent: it wants to see the night sky from the  
        world below.     
    $\bullet$    On a massive blink station thronging with travellers, merchants, and all manner of people  
        in transit. Thousands travel the station’s main concourse, some characters less savory  
        than others, and hundreds of alleyways lead to chambers and venues that showcase the  
        wonders of the galaxy.   

                                                                                                         


$\bullet$    Among the dunes of an arid world, a nomad’s camp crouches on the banks of an oasis,  
    indigo in the shadows. They are hunting something grand in the sky, tracking it by its  
    droppings.   
$\bullet$    In the hive-like streets of a neon-drenched capital world, under a driving artificial rain in  

    the commerce district. NHPs in armature bodies consort with human partners, dealing in  
    business, trade, and secrets. The city is endless.    
$\bullet$    In the deep black of space, aboard a capital ship as its main guns thunder away at the  
    enemy fleet. Outside, vacuum and silence, as the debris and the dead float cold and still.    
$\bullet$    Outside the hull of a titanic generation ship, under the shield of its bow guard as it  
    accelerates through an asteroid field.    
$\bullet$    On an atmospheric moon of a gas giant, in the fields under the planet-rise as day slips to  
    oversky. The people of this moon have never seen night, as the world their moon orbits  
    only brings a dimmer day.     
$\bullet$    In a lonely colony on a nondescript Terran world, as snow falls on the fledgling habitat  
    during the celebration of their first year settled. It is a time of celebration, and a time of  
    worry: what happens if it never stops snowing?    
$\bullet$    In the gilded palace of an interstellar king, as his hosts march in formation below the  

    viewing plaza. Your shuttle waits on a distant landing pad and you think to yourself, are  
    you guests, or are you prisoners?    

                                                                                                     


HAZARDOUS ENVIRONMENTS  

It is possible (and likely) for mechs to operate in hazardous environments such as being  
submersed in hostile atmosphere, vacuum, or water. To operate without killing its pilot, a mech in  
these circumstances needs life support -- if a mech’s life support system is active and running,  
it can run essentially indefinitely (a pilot will likely die of dehydration/starvation before they run  
out of oxygen, thanks to the efficiency of standard 02 scrubbers). A mech in a hazardous  
environment without life support has enough residual support for a number of hours equal to its  
engineering score, or 30 minutes if that score is less than 1.
 

                                                 ZERO -G  

A Mech operating in zero-g, underwater, or space is impaired unless it has a propulsion system  
or a system allowing it to Fly. Mechs in space or zero-g cannot fall.
 

Mechs without a propulsion system or flight are Slowed in space or zero-g, but can fly when  
they move or boost.
 

                                              Environments:
 

 Roll    Name                                Description/Effect 

 1       Dangerous Flora or Fauna            The planet has a high amount of dangerous animal or  
                                             plant life, some of it perhaps titanic, predatory, or  
                                             particularly hostile. You can represent this by using the  
                                             Monstrosity NPC type from the NPC toolkit. You can  
                                             also represent the presence of hostile flora on a  
                                             battlefield as size 1 or 2 static entities with evasion 10,  
                                             5 hp. Any target that moves adjacent to them must  
                                             pass a hull check or take 3 kinetic damage and become  
                                             immobilized by sticky sap, webbing, a pit trap, or the  
                                             like until the flora is destroyed. 

 2       Extreme Cold                        Mechs and pilots will quickly freeze without a source of  
                                             heat nearby, and culture on this world accommodates  
                                             this. Any mech that does not move or boost on its turn  
                                             becomes immobilized at the end of its turn. It can end  
                                             this condition by taking an action and a successful hull  
                                             check to break out of the ice.
 
                                             All mechs have resistance to heat. 

 3       Extreme Heat                        Civilization has retreated mostly underground in this  
                                             blistering atmosphere. All systems and weapons that  
                                             generate or inflict heat generate +1 more heat than  
                                             normal. 

 4       Thin Atmosphere                     All targets gain resistance to explosive damage. 

                                                                                                          


5       Extreme Sun                         Mechs take 1d6 heat at the end of any turn that they  
                                            are not standing in the shade 

6       Corrosive Atmosphere               The thick atmosphere on this world corrodes armor. All  
                                            weapons gain the AP tag. 

7       Particulate Storm                  This planet is swept by brutal, scouring storms of sand,  
                                            rock, or metal. While one of these storms is active,  
                                            mechs treat all terrain as heavy cover. Pilots cannot  
                                            step outside without great personal risk if they are not  
                                            in their mech. 

8       Electric Storm                     This planet is swept by unusually strong electrical  
                                            storms. While one of these storm is active, at the end of  
                                           the round, choose a target at random. That target must  
                                            pass a systems check with 1 difficulty per size or be  
                                            stunned until the end of their next turn by a bolt of  
                                            lightning. 

9       Disruptive Storm                   The storms on this planet are so thick that electronic  
                                            systems cannot function. All tech actions and system  
                                            checks are made at +1 difficulty. 

10      Dangerous Storm                    This planet is swept by storms of fire, meteors, acid  
                                            rain, ice, or other destructive particles. While one of  
                                           these storms is active, all mechs not in cover at the end  
                                            of the round take 3 AP kinetic damage. 

11      Earthquakes                        At the end of each round, while earthquakes are active  
                                            on this world, roll a 1d6. On a 1, all mechs on the  
                                            battlefield must pass a hull check or be knocked prone. 

12      Ocean World                        This entire world is covered in water, with less than 5%  
                                            of the surface being solid ground. The water is a  
                                            hazardous environment. Mechs with Flying or EVA can  
                                            move normally, otherwise mechs without will sink to the  
                                            bottom and count movement as difficult terrain. They  
                                            can walk perfectly normally on the bottom (if slowly)  
                                            and most mechs are pressure rated to extremely high  
                                            specifications. 

13      Molten World                        Parts of this world’s crust pokes through in showers  
                                            and pools of liquid rock. Any mech that enters a zone of  
                                            molten rock or lava for the first time on its turn or starts  
                                            its turn there takes 5 AP energy damage and 1d6 heat. 

14      Primordial World                   This world is mostly a bubbling soup of semi-organic  
                                            mud and gases. The atmosphere is toxic and humans  
                                            must use a breathing apparatus or sealed suits outside  
                                            of their mechs. Boiling mud covers this world, creating  
                                            zones of both difficult and dangerous terrain. 

15      Low Gravity                        All mechs gain the ability to fly when they boost on this  
                                            world, as if they had jump jets. Mechs don’t take  
                                            damage from falling, and only fall 3 spaces a round. 

                                                                                                        


 16      High Gravity                        Mechs cannot boost on this high gravity world and are  
                                             immobilized instead of Slowed 

 17      Tomb World                          This world has extremely high radiation, possibly as a  
                                             result of nuclear war, atmospheric degradation, or  
                                             something more sinister. Humans not wearing a sealed  
                                             hard suit or some other kind of environmental suit lose  
                                             5 HP/hr on this world. 

 18      Spire World                         This world is made up of a large number of islands or  
                                             spires held aloft in a gaseous substrate and suspended  
                                             through magnetic force. Perhaps it was a world  
                                             shattered by a superweapon or natural disaster. Most of  
                                             the land is not connected, but a loose collection of  
                                             floating rocks, some of them large enough to hold  
                                             cities. Navigation systems go haywire on this world. 

 19      Sinking World                       This world is covered in fine sand or thick mud. While  
                                             on the surface, mechs that move 1 space or less during  
                                             their turn are Slowed. Mechs that are Slowed and move  
                                             1 space or less are immobilized and start sinking,  
                                             eventually becoming completely engulfed. A mech can  
                                             take a full action and make a hull check to end this  
                                             effect on itself or another adjacent mech. 

 20      Holy World                          This world is beautiful and has no particular dangerous  
                                             features, but held sacrosanct by the local population.  
                                             Damaging its rocks, trees, and pristine grasslands will  
                                             incur the ire or wrath of the locals 

Generally speaking, tune the environmental hazards to the world(s) that your campaign takes  
place on: jungle worlds will have hazards that are appropriate for jungle worlds, aquatic worlds  
will have hazards appropriate for aquatic worlds, and so on. 
 

                                                                                                          
\subsection{In The Pipe, 9 To 5 }

In The Pipe, 9 To 5   

What work do mech pilots encounter, and what types of organizations do they work for?   

What kind of constraints might get put on them depending on a) the work that they do and b) the  
people/orgs that they work for? What are common complications that they might encounter on a  
job/mission/assignment?  

These tables below will help develop mission structures in a pinch, further complications can be  
added as necessary. These reflect the more mundane missions, typically encountered by  
mercenary groups, Union DoJ/HR liberation teams, Union Navy regulars or auxiliary troopers,  
private militaries, and other conventional fighters.    

Source  
    1.  A Union Administrator in need of a team of fixers.  
    2.  A mercenary company, known for its upstanding reputation.   
    3.  An upstart mercenary company with a lot to prove, few resources, but this one golden  
        contract.  
    4.  A Union Far Field team manager in need of extended security.  
    5.  A local ruler, whose own soldiers can’t finish the job.  
    6.  A board member of a corpro-state, who needs this job done off-book.   
    7.  The heir to a throne, in need of a team of champions.  
    8.  A local crime boss, who needs extra muscle for this job.  
    9.  The mouthpiece for a mysterious figure, who needs a disposable team for a covert  
        mission.  
    10. A system administrator NHP, who needs to procure an asset from one of its distant  
        colonies.  
    11. Your commanding officer, who orders you to complete a necessary mission.   
    12. A sudden burst of code that overwhelms your chassis’ onboard computers, depositing  
        mission parameters in a window on your HUD that won’t go away  
    13. A familiar dead drop, unused for years but active now, with your orders scrawled on  
        hardcopy inside.   
    14. The dying wish of a comrade or loved one.   
    15. A system administrator NHP, who has issued an SOS and requires immediate, Union- 
        sanctioned aid.   
    16. A HORUS cell leader -- you think -- who speaks to you through a remote-piloted subaltern.    
    17. An NHP, just prior to cycling, who would whisper a single name over and over  
    18. Of your own volition, out of desire  
    19. Of your own volition, out of a sense of duty  
    20. Of your own volition, out of a need for revenge  

Hook  
    1.  Escort a VIP from a compromised location to a new safe one  
    2.  Respond to an SOS from an unknown source, location noted in message.   
    3.  Retrieve a valued or strategic object, item, or information from a secure, hostile location  

                                                                                                          


    4.  Investigate a tip from a valued informant, which could go south.   
    5.  Escort a long-flight weapon or ordinance to its target   
    6.  Run security for a secure location expecting an attack   
    7.  Head into a derelict to retrieve important data    
    8.  Bring down a piece of massive infrastructure (bridge, skyhook, dam, etc)  
    9.  Go loud to provide cover for a covert mission of utmost importance  
    10. Assassinate a VIP in broad daylight, to send a message  
    11. Attack a hostile defensive position in order to destroy a key objective  
    12. Board a hostile ship or station and take it over; or, destroy it   
    13. Be first on the ground on a world hostile to human life; create a beachhead  
    14. Deal with hostile local fauna or megafauna plaguing a colony.   
    15. Hunt down a team of notorious, feared, or respected mech pilots, and kill them.   
    16. Provide cover for an evacuation.  
    17. Rescue and extract a downed pilot from a warzone.   
    18. During a massive attack, strike the enemy’s critical weak point to make a breakthrough.  
    19. Liberate a people held hostage from their cruel ruler, with Union’s backing.  
    20. Intervene in a desperate attempt to stop an incoming missile or attack.   

Location  
    1.  On a habitable, terrestrial, populated world, with a few large cities, a capital with a  
        spaceport, and outlying towns. Vast stretches of unexploited, but explored wilderness.   
    2.  On a terrestrial world with little to no atmosphere. Rocky, uninhabited, with a smattering of  
        automated sig/int, omni, and navigational stations.   
    3.  On a high-traffic, low-orbit civilian station, full of travellers bound for distant stars and  
        Cosmopolitans waiting to clear quarantine.   
    4.  Inside a massive arcology, thick with life, an oasis on an otherwise grim world.     
    5.  In hard vacuum, near a dorsal monitoring terminal of a Blink station’s Dyson panel,  
        thousands of kilometers above the city decks.   
    6.  Aboard a capital ship, all decks vented of air and ready for combat.   
    7.  On an arid terrestrial world close to its sun, in a white sand desert of massive marching  
        dunes and glass spires.   
    8.  On a cold, distal world of black stone and vast, geometric planes of nitrogen ice.   
    9.  Inside the upper atmosphere of a massive gas giant, where long-flight hydrogen refineries  
        scrape the valuable fuel from impossible blue depths.   
    10. Among the teeming streets, bazaars, and boulevards of an ancient, persistent  
        metroswathe, laden with millennia of histories, both personal and public.   
    11. On a ocean world, landmasses covered by glaciers and the mountains they’ve carved as  
        they march to the sea. Storms marble the world’s grey skies, and turbulent tectonic activity  
        sends world-sweeping tidal waves to crash into glacial faces.   
    12. On a rocky world defined by massive craters, whose skies are lit by the brilliant passage of  
        frequent meteor showers.   
    13. On a hot, terrible world of choking gases and thick atmospheres, where light is eaten by  
        deep yellow fog, and the ground is a barren mix of oily green stone and rotting metals.   
    14. Aboard a vibrant Cosmopolitan space station, a hub of intergalactic trade and art, with  
        constituant asteroidal states leashed in its orbit.   
    15. In the arcadian planes of a temperate world, distant from any human habitation, but  
        marked by the promise of future colonization.  

                                                                                                         


    16. On the storied land of an old Core world, once a thriving metropole, now long since scaled  
         back. Empty cities collect sand and creeping vines; the world’s population resides in a  
         single valley, content.     
    17. On a bucolic temporal reserve, a neo-pastoral world with a population that has no  
         knowledge of Union or the politics and current events of the galaxy at large.   
    18. In the hard vacuum of space, among the ruins of the fleet.  
    19. In the hard vacuum of space, between the ink-black hulls of capital ships on long patrol  
    20. On the hardpack surface of a comet, whose horizon is never far away, whose chasms and  
         valleys are picked out in sharp relief by the hard light of a nearby star.   

Complication  
    1.   The local leader is hostile to Union, and will send their agents, military, or assassins to try  
         and stop you.  
    2.   The location of the mission is under local quarantine, due to the presence of a virulent,  
         deadly illness.   
    3.   The location of this mission is secret, and your presence there will be deniable: expect no  
         support or public reward for completing your objectives.   
    4.   The local gravity is much higher than you’re used to, making movement and breathing  
         more difficult.   
    5.   The atmosphere is corrosive and thick, rendering all but the most powerful energy  
        weapons useless.   
    6.   The world is marked by odd, unnatural geometries -- certain features, when the wind  
         blows over them, “sing”, and the world is never silent.   
    7.   The world is a frequent (enough) target of meteorite impacts: one is forecasted within the  
         mission window, and its impact will plunge the world into a decade of dust-night and  
         storms.   
    8.   The world is in turmoil, roiling with political discontent, and you’ve just stepped in the  
         middle of it.   
    9.   The station is a common type among long-term-residency stations: a cylinder, whose  
         population lives on the gentle curve of the cylinder’s interior. You’ll need to take that into  
         account when the mission gets hot.    
    10. The weapon, VIP, ship, etc, that you’re escorting will intersect with an opposing weapon,  
        VIP, ship, etc, that the enemy is escorting: you must ensure that your objective remains  
         secure, while theirs is done away with.    
    11. The station you’re on begins to break apart after the shooting starts.  
    12. The forces employed by your enemy are unwilling combatants, coerced into fighting you.   
    13. Your mission runs counter to the mission of another arm of your state, company, or  
         agency; you may encounter internal resistance.   
    14. Your way in is incapacitated or made unavailable, leaving you without a clear way out.   
    15. Your intel was wrong -- the objective you seek is not where you were told it would be.   
    16. The city’s (or station’s) administrative NHP dislikes you, for reasons unknown, and seeks  
         to impede your progress.    
    17. The world has a much longer day/night cycle, lasting on the order of standard months or  
         more -- you’re approaching the end of one period and the beginning of the other, with  
         significant cultural meaning placed on the transition, and wide variance in how the local  
         biome reacts.   

                                                                                                               


    18. Completing the mission requires some interstellar transit, which would divorce you from  
        the subjective timeline of your friends and family back home.   
    19. This mission is set up to fail, but you don’t know that yet. Someone higher up in your  
        organization wants you dead.   
    20. The world has been visited previously by RA, and it bears markings of the MONIST entity's  
        passing.  

\subsection{Identifty Friend/Foe}

Identify Friend/Foe  
Force generator for NPC factions.   

Faction Type   
    1.  Union Regulars, Regiment   
    2.  Union Auxiliary, Regiment  
    3.  Union Department of Justice and Human Rights, Liberator Team   
    4.  Union Intelligence Bureau, Field Team  
    5.  Union Naval Intelligence, Field Team  
    6.  Union Far Field Team, Security   
    7.  Harrison Armory, Acquisition Team  
    8.  Harrison Armory, Colonial Legion  
    9.  Harrison Armory, Board Intelligence Field Team  
    10. IPS-N, Marine Security Detachment   
    11. IPS-N, Company Trunk Security  
    12. SSC, Diplomatic Corps Detachment - Security Team    
    13. HORUS, Local Cell   
    14. Ungratefuls, Local Cell    
    15. MSMC, Company Detachment   
    16. Voladores, Sparri Espadas   
    17. Sparri Mercenaries, Free Band   
    18. Local, Planetary Defense Force (Ground, Navy, or both)   
    19. Local, Honor Guard  
    20. Local, Opposition Group   

Signature  
    1.  Survivors. Loosely organized, scattered in groups of twos and threes, with broken, or  
        empty small arms. No anti-armor.   
    2.  Ready partisans, with civilian weapons and the capacity to produce improvised explosive  
        devices and lightly armored vehicles (technicals, motorcycles). Small to medium numbers.   
    3.  Resistance fighters. Scavenged or stolen military-grade small arms and explosives, light  
        anti armor, provisions and scavenging ability. Lightly armored vehicles, few stolen military  
        grade vehicles. Small to medium numbers.   
    4.  Light infantry, with light anti-armor, a few light vehicles (motorcycles, armored cars, etc),  
        and provisions for long field deployment. Medium numbers.   
    5.  Mobile, mechanized infantry, light to medium anti-armor, military grade small arms and  
        explosives. Mounted in armored personnel carriers. Provisions for field repairs and long  
        travel. Some APCs devoted to medium anti-armor. Medium to large numbers.    

                                                                                                         


    6.  Line infantry. Medium armored infantry, with military grade small arms and explosives.  
        Supported by medium armored vehicles, typically with artillery behind their line. Typically  
        supported by medium/line mechs. Provisioned for long-term deployments, garrisons, and  
        battles. Large numbers.   
    7.  Heavy infantry. Medium to heavy armor, military small arms and explosives, medium to  
        heavy anti-armor, uncommon/exotic weapons and systems. Powered armor is common,  
        typically operate in support of line and heavy mechs. Medium numbers.   
    8.  Shock infantry. Light to medium armor, military small arms and explosives, medium anti- 
        armor. Often employ light, mobile power armor, commonly in support of scout and mobile  
        line mechs. Typically mounted in armored personnel carriers or all-theater dropships.  
        Medium to large numbers.   
    9.  Drop infantry. Light to medium armor, military small arms and explosives, often equipped  
        with light powered armor. Commonly in support of scout ot medium mechs. Commonly  
        provisioned for long-term deployments. Typically deployed behind enemy lines or in close  
        proximity to priority targets via orbital drop or atmospheric insertion. Small to medium  
        numbers.   
    10. Scout Mechs. Half-size to size 1. Emphasis on speed, range, and sensors. Light armor.  
        Small numbers. Military grade weapons. Rapid infiltration and exfiltration. Small numbers.   
    11. Medium/Line Mechs. Size 1 to size 2. Emphasis on all-round ability, light to medium armor,  
        small numbers. Military grade weapons, with some exotic or uncommon. Rapid infiltration  
        and exfiltration. Small numbers, unless operating in a line capacity. Versatile roles.   
    12. Heavy/Siege Mechs. Size 2+. Emphasis on powerplant and fire output. Light to heavy  
        weapons, some exotic, medium to heavy armor. Small numbers, operate protected by  
        lighter mechs, armor, or infantry. Slow infiltration and exfiltration.   
    13. Armored Division - Light. Emphasis on speed and offensive ability, usually operate alone  
        or with light aerial support.    
    14. Armored Division - Medium. Emphasis on all-round capability and staying power. Usually  
        operate in support of or supported by infantry and light-to-line mechs.   
    15. Armored Division - Heavy. Emphasis on armor and offensive capability. Usually operate in  
        support of infantry, specifically meant to eliminate enemy armor or mechs.   
    16. GM choice.  
    17. GM choice.  
    18. GM choice.  
    19. GM choice.  
    20. GM choice.   

Strength   
    1.  Patrol. 1 to 5 soldiers, whose goal it is to observe and report, avoid engagements at all  
        cost, and correctly identify the location and strength of the enemy.   
    2.  Patrol. 1 scout mech, light atmospheric flyer, pair of light armored cars, pair of motorbikes,  
        or other patrol vehicle.    
    3.  Squad. At least 10 to 20 soldiers, on foot.   
    4.  Squad. At least 10 to 20 soldiers, supporting a single scout or line mech, or a single  
        medium armored unit.   
    5.  Squad. At least 10 to 20 soldiers, mounted in a single dropship, or two APCs.   

                                                                                                           


6.  Company. At least 100 to 200 soldiers, with support personnel and fire support (artillery,  
    mortars, air support, or orbital). They will occupy ground, provide relief, engage in combat,  
    and operate as an efficient unit.   
7.  Company. At least 100 to 200 soldiers, mounted 10:1 in armored personnel carriers  
    (APCs), or 20:1 in dropships.  
8.  Company. At least 10 to 20 light mechs, operating in teams of 2-4. Scout configuration,  
    some carrying heavy precision weapons.  
9.  Company. At least 50 heavy soldiers, operating 10:1 in support of 5 medium or heavy  
    mechs.   
10. Company. At least 20-40 armored vehicles, operating in teams of 5.   
11. Regiment. 5 to 8 companies, organized under an on-site, (typically) rear echelon   
    regimental commander. Usually supported by significant off-site fire support, well- 
    provisioned, outfitted with broad range of small arms and heavy weaponry, and operational  
    from a fortified static base or orbital carrier.    
12. Regiment. 5 to 8 companies organized under an on-site commander, who travels in an up- 
    armored, command-suite version of the same APC or dropship as their soldiers. Some of  
    the APCs or dropships are up-armored, anti-armor/gunship variants.    
13. Regiment. 5-8 companies of light mechs, organized into teams of 5-10, operating as  
    flankers, hussars, pickets, and/or first recon. Tip of the spear tactics, with more specialized  
    weapons and systems seeded throughout.  
14. Regiment. 5-8 companies of soldiers operating in support of medium or heavy assault  
    mechs at a 10:2 ratio.   
15. Regiment. 5-8 companies of armored vehicles, operating in teams of 5. Supported by a  
    rear echelon or orbital motor pool.   
16. Battalion. 2-4 Regiments organized under an offsite, high-ranking commander, typically  
    operating well behind the lines in a hardened site or orbital. Significant logistic, tactical,  
    and fire support. Continental reach and response time within a day.   
17. Battalion. 2-4 regiments organized under an on-site commander, who pilots a high-license  
    mechanized chassis and is attended by a retinue of similarly grizzled, ranking veterans. At  
    least 1 regiment is composed of medium or heavy assault mechs.   
18. Battalion. 2-4 regiments of armored vehicles, supported by an off-site battalion  
    commander with significant tactical, strategic, logistic, and fire support. Multiple motor  
    pools and/or heavy-lift shuttles allow for for sustained operations and rapid insertion.   
19. Army. 2-5 battalions, with significant material, logistic, strategic, tactical, systemic, and fire  
    support. Usually matched with an orbital/aerial presence, multiple forward operating  
    bases, a main operating base, and well-resourced. Will contain a mix of infantry, armor,  
    and mechanized chassis. Has a global reach.   
20. Army. 2-5 battalions Mobile, organized around a mix of medium and heavy chassis, with  
    support from regiments of mechanized infantry, dropships, and heavy shuttles. Supported  
    by an orbital battlegroup, has a global reach.    

                                                                                                        
