\section{Example Character Creation}

 EXAMPLE CHARACTER CREATION  

Let’s put it all together and see a pilot in action. Our sample pilot’s name is Taro Oda.
 
\subsection{Building Oda: The Pilot}
                                       Building Oda: The Pilot  

To create Oda, his player will have to choose a background, and assign some skills and skill  
points.
 

Oda’s player decides that Oda grew up in the colonies, so he writes down Colonist for Oda’s  
background. Oda’s player decides Oda is pretty astute and good at gunplay, so they decide to  
give him skill bonuses to read a situation, spot, take someone out, and survive, at +2 each.
 

They decide Oda is especially good at spot and take someone out, giving him specialties and  
+1 accuracy in each. Then they decide he is not very well connected and bad in social situations,  
so they give him +1 difficulty flaws to charm and get a hold of something.  

Next, Oda’s player writes down some gear that Oda always brings with him on missions to save  
some time. He can change this during preparation. Looking at the GMS gear list, Oda’s player  
chooses a signature weapon (his hunting rifle), a light hardsuit for maneuverability, and extra  
rations.  

At level 0, here’s what our pilot looks like. Note that at level 0, Oda only has GMS licenses.
 

Taro Oda  
License level 0
 
Background: Colonist  
Skills: Get bonuses to read a situation (+2), spot (+2 with +1 accuracy), take someone out (+2  
with +1 accuracy) and survive (+2). Roll +1 difficulty to charm someone or get a hold of  
something.
 
Gear: Signature weapon (Hunting Rifle), Light hardsuit, Extra Rations, Cooking Gear
 

Let’s get to Oda’s mech.  

At Rank 0, Oda, like all other pilots, only has access to GMS licenses.
 

To build his mech, Oda chooses the GMS Standard Pattern I Everest FRAME, the only one he  
has access to. To fill his weapon mounts, Oda can choose from GMS weapons. He chooses the  
Anti Material Rifle for his heavy mount, an assault rifle, a main size weapon, for his main mount,  
and two tactical knives for his auxiliary mount.
 

                                                                                                              


                                             RAIJIN (EVEREST) 

  HP: 10          Evasion: 8                             Speed: 4            Heat Cap: 6        Sensors: 10 

  Armor: 0        E-Defense: 8                           Size: 1             Repair Cap: 4      Tech Attack:  
                                                                                                +0 

                                                     TRAITS: 

  Initiative: The very first turn the Everest takes in any combat, it can take an extra Quick Action as a free  
  action 

                                               SYSTEM POINTS: 6 

                                                    MOUNTS: 

  Tactical Knife
                    Assault Rifle                           Anti Material Rifle 
  Tactical Knife 

                                                  CORE system 

                                         GMS Hyperspec Fuel Injector 

He has 6 system points to spend and chooses to spend them on the following:  
(2) GMS Pattern A “Apple” HE Grenades x4  
(1) GMS Burst type Jump Jet system  
(1) Personalizations  
(2) GMS Shield Type I
 

For Talents, at rank I Oda chooses Crack Shot (rank I), Infiltrator (rank I), and Leader (Rank ) 
 
That’s it! But let’s look at Oda at License level 3 to show how Oda and his mech with a couple  
levels would look.
 

Leveling from 0-3 (completing 3 missions), Oda looks very similar. However, he gets +3 talent  
points to spend on talents, 3 license points to spend on licenses, +6 pilot skill points, +3 mech  
skill points, a new pilot specialty, a CORE bonus, and access to advanced pilot gear, and his grit  
goes up to 2.
 

If this seems a little overwhelming, remember Oda’s player will pick up each of these one at a  
time!
 

                                                                                                                


Taro Oda 
License level 3 
Background: Colonist 
Pilot Skills: Get bonuses to read a situation (+6), spot (+2 with +1 accuracy), take someone out 
(+4 with +1 accuracy) and survive (+2 with +1 Accuracy). Roll +1 difficulty to charm someone or 
get a hold of something. 
Gear: Signature weapon (Hunting Rifle), “Peacekeeper” R35, Light hardsuit, Extra Rations, 
Cooking Gear 

Mech Skills: +3 hull (+6 HP, +2 repair) 
Talents: Crack Shot (Rank II), Infiltrator (Rank I), Leader (Rank III) 
CORE Bonuses: Reinforced Frame (IPS-N),  +6 HP 
Licenses: GMS, IPS-N Raleigh Rank I-III 

Since Oda has a rank III license (Raleigh), he gets the Raleigh FRAME (rank II) and can choose a 
+5 HP CORE bonus from IPS-N since he has 3 points in that manufacturer. He can also take any 
of the systems or weapons in the Raleigh license now. Here’s what Raijin, his mech, looks like at 
rank III. Oda chooses to mount two hand cannons instead of his knives, a new system from his 
new licenses. 

                                            RAIJIN (RALEIGH) 

 HP: 22 (+6      Evasion: 8                            Speed: 4            Heat Cap: 5        Sensors: 10 
 from core 
 bonus, +6 
 from Hull, 
 +1 from grit) 

 Armor: 1        E-Defense: 8                          Size: 1             Repair Cap: 6      Tech Attack:  
                                                                           (+2 from hull)     +0 

                                                    TRAITS: 

 Full Metal Jacket: If the Raleigh makes no attack rolls during its turn, it can re-load all weapons with  
 the loading tag at the end of its turn as a free action.
 
 Shielded Magazines: The Raleigh can still make ranged attacks if it is Jammed. 

                                     SYSTEM POINTS: 6 (+1 from Grit) 

                                                   MOUNTS: 

 Hand Cannon
                       Assault Rifle                           AMR 
 Hand Cannon 

                                                FRAME system 

                                                                                                               


                                          IPS-N M35 ‘Mjolnir’ cannon 

He has 6 system points to spend (5+1 from GRIT) and chooses the following:  
(2) GMS Pattern A “Apple” HE Grenades x2  
(2) GMS Shield Type 1  
(2) IPS-N Breaching Charge
 