\section{Foundation Day}

Foundation Day  

         “Work stops at sunset. Darkness falls over the building site. The sky is filled with stars.   

         ‘There is is the blueprint,’ they say.”  

                      -    Italo Calvino, Invisible Cities  

Union began as a way to build a new world from the ashes and ice. 
 

In the 3500’s CE, -5500U by Union’s dating system, Earth sent the first wave of her children out  
to seed the stars. The world, Humanity’s only home save for distant, fledgling colonies, was  
dying. An accumulation of fatal blows, a thousand cuts on the world by the people that called it  
home, had rendered it all but inhospitable. 
 

The Fall, as it is now called, was not concluded in a single, cataclysmic blow. There was time --  
not enough of it, but time enough -- for acts of desperate hope. 
 

The Ten were one such act. 
 

In the twilight of the Fall, Ten massive colony ships launched from orbital shipyards that ringed  
Earth. They were slow ships, their titanic hulls pushed along by conventional sublight drives, but  
they marked the crowning achievement of a species: a second chance.
 

These generation ships were humanity’s last hope. They would travel for thousands of realtime  
years, accelerating nearly to lightspeed before flipping over and slowing down as they  
approached their destinations. Generations of passengers would live, die, and procreate,  
sustaining the ship and the remnants of humanity on board until they arrived at their destination:  
a world able to sustain human life.
 

This was humanity’s second chance, a handful of stones cast out into the night. Back on Earth,  
the billions left behind watched the Ten burn away into the night, tracking their progress through  
choking clouds of smog, dust, and smoke from raging, unstoppable wildfires. 
 

Humanity on Earth fought for what was left, erupting into a pandemonium, a violent crescendo.  
Climate change choked the atmosphere, disease scoured the cities, and war ravaged the rest.  
Lonely colony outposts and stations throughout the solar system — established when Earth was  
terminal and not yet dying — watched their homeworld go dark. Most withered on the vines, a  
rare few managed to hang on. 
 

Thousands of years of real time passed. For the ten ships, relative time passed slower. 
 

Earth spun, silent and unresponsive to the desperate calls for help from her dying colonies. Cities  
sank under rising water, wildfire and stinking fog swept the equator. The poles thawed, while  

                                                                                                                  


storms thrashed the tropics. Ash fell over the whole of the world. Satellites and stations decayed  
in their orbits. Shipyards fell quiet. Great habitats on the moon and Mars cascaded into failure.  
 

Thousands more of years of silence followed. The First Anthropocene, the age of Humanity,  
faded, buried under ash and water. 
 

Yet Earth was not empty, nor lost: billions had died, but humanity is a resilient race. Some  
hundreds of thousands had survived. Persevering through the new long dark. 
 

This was the Fall. The end of it, and the beginning of a new Dark Age. 
 

In time, the global population began to stabilize, then grow as the world’s climate evened out.  
Long-dead crops began to grow as hearty survivors. Trees, forgotten at the Fall, grew back from  
gnarled shrubs. The oceans receded, cooled. The fires dimmed, then died. The sky, once a  
greasy smear of black and orange, lightened, blued.   
 

Humanity, too, began to grow back. First, small rulers and tyrants laid claim to the ruins of the  
past, organizing themselves around altars of scavenge and scrap. Wandering machines were  
tamed or followed, venerated and hunted. Farms grew from small plots. Once again, lines and  
borders were drawn, land claimed, loyalty pledged. Scraps of cloth and paint and feathers and  
flags grew to mean, to divide. The rulers gave way to nations. Nations, to empires. 
 

And then, the first of three great traumas humbled the healing world: Old vaults, stores of  
information from the pre-collapse era, were discovered and reopened. The survivors, so far  
removed from Old Humanity, had grown through the dark ages thinking that their cultures were  
the first on Earth, the first people to walk under the Sun. 
 

They discovered otherwise. They were not the first: they were the last. 
 

Reeling from this discovery and the wealth of pre-collapse humanity unleashed upon a healing  
world, the fledgling states of Earth backed into their corners. Ultimately, a reckoning followed the  
revelation, and a new war began: a global war. This was the second trauma: a global war, a bitter  
fight over the scraps of the long-dead. 
 

War scarred the world, and when it was done the survivors gathered together and pledged  
peace. The tools of war and capital were thrown aside, as they had nearly killed Earth again.  
Humanity pledged peace, and came together under a single banner, which would be the last to  
fly over Earth: 
 

Union. 
 

Union’s foundation reset the clock, changing the calendar and myriad dating systems to one  
single metric. Year 0 marked the beginning of a new age of humanity, a people redeemed,  
bruised stewards of an old and aching world. In peace, and with the help of the wondrous  
technology of their predecessors, the people of Union began to dream of greater things.
 

                                                                                                           


Flight and clean power spread across the world. Linked, networked communications further  
bound Union together. Sudden, exponential advancement in medications, computational power,  
hard and soft sciences — all gifts from the data stored in seed vaults around the world. 
 

We discovered and translated the story of the collapse, of the desperate rush of old humanity to  
preserve what it could so that future generations could begin anew, with all the plenty and  
knowledge of those who came before. We found technologies that could have saved the world,  
but were discovered too late, or kept from Humanity by their inventors and owners. 
 

Union began to look beyond: out, towards the depths of space. The first rockets were launched,  
and on Luna we found dusty colonies, empty but for mummified remains of the people who once  
lived there. We found dormant satellites strung in orbit, ancient shipyards hanging in space. We  
found charts, logs, flight plans, trajectories showing that some of us, some of our ancestors, had  
escaped. 
 

We found and thawed the old telescopes, radio towers, and laser communication suites,  
preserved in ice on mountaintops and high places all over the world. We pointed them to the  
stars, turned them on, and waited.  
 

The first messages arrived almost immediately. This was Union’s third great trauma. 
 

Ancient calls from distant, lonely outposts and hardscrabble colonies. Voices, thousands of years  
old and long dead, on radio waves garbled by radiation, time, and transit, crying out to their  
home for help. Lost souls that begged for aid, for guidance, for their loved ones. Thousands of  
years of messages, recorded and playing on endless, decaying loops for the survivors to hear. 
 

This was the voice of humanity from the stars: a desperate cry for help, a lonely gasp as the air  
ran out. A plea, unanswered, as the light grew dim.  
 

Union now had a new purpose: to answer those calls, and to ensure the event that caused them  
would never happen again.
 

The old orbitals were retaken and reactivated. Machine minds greater than humanity’s — the first  
artificial intelligences — were discovered and set to puzzle out solutions we could not. The first  
new ships were launched towards those old signals, along ancient charted paths, and out  
towards new worlds. 
 

Union could not bring their dead back home, but they would choke the stars with the living.
 

                                         