\section{Basic Full Actions}BASIC FULL ACTIONS  
\subsection{Barrage}
                                               BARRAGE  

When you take the barrage action, you can attack with two weapons, or one superheavy  
weapon. You can choose the same target or different targets when you make these attacks.
 
        	- When you attack with a weapon, you can also attack with another auxiliary weapon in  
        the same mount. That weapon can’t deal bonus damage.
 
        	- The barrage action takes your mech’s full attention and the engagement of all its  
        systems, so it requires Full Action to use. 
 
        	- Superheavy weapons can only be fired as part of a barrage action, as they require the  
        full attention of your mech’s systems.  
\subsection{Full Tech}
                                              FULL TECH  

Choose and perform two options from the Quick Tech list (or choose from other systems that  
would take a quick tech action to use). You can repeat options, but must choose different targets  
for each option.
 

Alternately, use a system or tech option that takes a Full Tech action to activate.
 \subsection{Improvised Attack}

                                      IMPROVISED ATTACK  

If your mech is unarmed or does not have a melee weapon, it can use an action to make an  
improvised attack action with a rifle butt, fist, or other improvised melee weapon against a target  
in melee. You may use the butt of a weapon, a slab of concrete, a length of hull plating, etc, to  
complete this improvised attack. How you flavor the attack is up to you!
 

An improvised attack costs a full action by itself to perform, and is separate to the skirmish or  
barrage actions above. It counts as a melee attack. An improvised attack is a melee attack that  
deals 1d6 kinetic damage on hit.  
\subsection{Stabilize}
                                              STABILIZE  
During a heated battle or prolonged mission, it may become necessary to enact emergency  
protocols in order to purge your mech‘s systems of excess heat, to repair your chassis where you  
can, and/or buy your system time to eliminate hostile code.  

To that end, a pilot may spend a Full Action to Stabilize and do one of the following:  
•  Cool your mech, resetting the heat gauge  
•  Spend 1 Repair to refill HP to maximum.  

And one of the following:  
•  Reload all weapons with the Loading Tag  

                                                                                                           


•  End all Burn currently affecting your mech  
•  Perform an Engineering Check. If successful, end one of the following conditions on yourself  
  or an adjacent ally.  
             •  Jammed  
             •  Impaired  
             •  Lock On  
             •  Immobilized  
             •  Slowed  
\subsection{Disengage}
                                            DISENGAGE  

When you disengage, you attempt to move safely. Until the end of your turn, your movement  
ignores engagement and does not provoke reactions, such as overwatch.
 
