\section{GMS - General Massive Systems}

 GMS - GENERAL MASSIVE SYSTEMS  

    “From Cradle to the Stars, General Massive Systems did it first and did it best. GMS:  
                         reliable quality, universal licensing, total coverage.”   

General Massive Systems, GMS for short, is the galactic standard for non-civilian mechs.  
Reliable, sturdy, and solidly built, with universal components, full radiation and environmental  
shielding, and tens of thousands of pre-loaded languages, a pilot in their GMS mech will have all  
they need to get the job done in a hostile galaxy.
 

GMS is one of the oldest galactic entities, getting their start as an early player in the colonization  
rush of the 2400’s after constructing the first Blink Gates. GMS hails from Cradle, the home  
systems of Union and all humanity, and their designs reflect the aesthetics and intentions of  
those first pioneers to seek the stars. They developed the first mech cores in 4500, followed  
shortly by the pre-contemporary Harrison Armory. 
 

All GMS FRAMEs, gear, core bonuses, and licenses are available to all pilots from license  
level 0. The GMS core is the all-rounder standardized EVEREST core. Variants of this core exist,  
such as the ANNAPURNA, the LHOTSE, the DENALI, and the MASSIF mechs.
\input{./GMS/gear.tex}

\input{./GMS/core.tex}

\input{./GMS/everest.tex}                                                                                                          

\input{./GMS/weapons.tex}                                                                                                          

\input{./GMS/mods.tex}                                                                                                          

\input{./GMS/deployables.tex}                                                                                                           

\input{./GMS/systems.tex}                                                                                                            

\input{./GMS/flight.tex}                                                                                                            

                                                                                                                
