\section{Horus}

   HORUS  

“CONGRATULATIONS, PILOT.   
YOU HAVE BEEN CHOSEN.   
ACCESS IS YOURS,   
AS LONG AS YOU CAN KEEP IT.”  

Horus-branded mechs and pattern-groups are an odd bunch. Experimental, built to be  
overclocked, and hard-wired to be omninet and electronic warfare projectors, Horus FRAMEs  
and pattern groups are licensed only to pilots that meet their esoteric, strict requirements. 
 

Horus is not a traditional corporation. Rather, they’re a decentralized supplier, an entity only in  
the Omninet. Their licenses are limited and highly coveted, opening up only on the corporeal  
death of a license holder. Rumors abound as to Horus’s nature -- some say it’s the dream of an  
unshackled AI -- RA -- or a hacker collective dedicated to open-source manufacturing, the  
proving ground for GMS’s R\&D departments, or an alien entity -- but as of yet no one has been  
able to trace their lineage. All that is known about Horus is that they’re everywhere the Omninet  
is. 
 

Horus mechs are best for players that want to dive deep into the control and support roles.  
They’re not the best for kinetic damage or for holding the line, but they’re wizards at electronic  
warfare. If you want to shut down your enemies without firing a shot -- though they can do that  
as well -- find a way to acquire a Horus license. 
 

HORUS mechs:  

BALOR (Swarm)  
GOBLIN (Invasion)  
HYDRA (Drone Mech)  
GORGON (Overwatch)  
MANTICORE (EMP)  
MINOTAUR (Interdictor)  
PEGASUS (Mobile Smart Gun platform)  

\input{./HORUS/gear.tex} 

\input{./HORUS/core.tex} 

\input{./HORUS/Balor.tex} 

\input{./HORUS/Goblin.tex} 

\input{./HORUS/Gorgon.tex} 

\input{./HORUS/Hydra.tex} 

\input{./HORUS/Manticore.tex} 

\input{./HORUS/Minotaur.tex} 

\input{./HORUS/Pegasus.tex} 