\chapter{LANCER}
\punch{It’s 5014, and our arm of the galaxy is home to trillions.} It is not a safe place,
but it burns bright, and for some there are gentle lands.

Out from our humble beginnings, humanity has colonized the darkness. We have set empty
worlds and barren moons alight with civilization, have tamed asteroids and gas giants, have even
built homes in the hard vacuum of space itself. We have taken root throughout our arm of the
Milky Way galaxy. In every situation and setting, humanity has made their home; life, however it
expresses itself, continues. Stories begin and end across the stars, though most never leave the
worlds they were born to.

But for some, their life is as a river, ever-moving, with the land of their birth left somewhere far
behind. Traders and smugglers, refugees and immigrants, miners, pirates, scientists, volunteers,
colonists, soldiers and conscripts: humanity on the move, always. Wars pull hundreds of
thousands into the current, trade and migration yet more. For every ten stable homes, there is
one family’s worth that has been uprooted, for good or ill.

Blink gates dot the galaxy. These massive, star-bound stations - gatehouses - tap into an
unknowably vast and strange plane known as the Blink and facilitate safe, instant travel, opening
all corners of the Deep to the daring. These portals are open and common to those with the
permission, money, or clearance to enjoy it: Thousands of ships travel through the Blink each
standard day for trade, migration, travel, war, or any myriad other purposes, so long as they have
clearance.

The Omninet connects all of humanity to one another, a decentralized network that links every
computer, every server, every thing to everything. More than just a way to communicate, more
than just a way for far-flung worlds to read of the galaxy’s news and listen to the music of the
spheres, the Omninet facilitates government and industry. Data is the new wealth, and the
Omninet allows for the sharing of the wealth of all worlds.

Manna, the universal currency, unites all the disparate nations of the human diaspora. A single
currency — based on a combination of material wealth, labor, intellectual property, experience,
and data — that any market on any planet will accept as fair currency. When a galaxy’s wealth of
raw resource is available for exploitation, what becomes valuable is not gold but data.

This vast spread of humanity, these trillions of souls, can only be administered by one body:
Union, the hegemonic council that rules from Cradle, the ancestral home of the human diaspora.
Earth and Mars, Mercury and Venus. Saturn, Jupiter, Neptune, and Uranus. Io. Titan. Europa.
Phobos and Deimos. Sol. These worlds and moons around this warm yellow star form Cradle,
the seat of Union’s power, and the very heart of humanity. Union controls the triumvirate of
progress: the Blink Gates, the Omninet, and Manna. Without the triumvirate, without Union, the
galaxy falls into chaos.

All that being so, Union, Cradle -- and far more so Earth herself -- are things and places of myth
to the vast majority of humanity, fictionalized in Omninet dramas and novels, dreamt about by
children and wanderers, idealized as the promised land or damned as the pit from whence we
came by religions across the galaxy. Few have ever seen a Union administrator, or suffered a
Union naval campaign. For all its control over human affairs, Union prefers to rule from a
distance.

The galaxy, despite its interconnectedness, is a dangerous place. Rebellion, insurrection, piracy,
civil wars -- even wars between worlds -- flare up and burn their way through Union space,
though only the most desperate or dangerous of conflicts require Union’s direct attention.
Disputes between Union’s subject states are common enough that there is a need for individual
militaries and militias: Five major suppliers have permeated the galaxy to offer arms and armor to
those with Manna enough to afford them and an Omninet connection with enough bandwidth to
download them.

Into this broad and dangerous environment come the players. You take on the role of a lancer --
a mech pilot, or simply pilot for short -- in a squadron with your fellow players. Whatever the
conflict, whatever the scale, you can bet that lancers will be involved; together, you and your
squadron will run missions as the tip of the spear, fighting in only the most dangerous and
important engagements. You’re the backbone, the heroes, the knights in shining armor, the
decorated aces sent in when all hope seems lost and victory must be assured.

In short, you, the players, are the cavalry.