\section{IPS-Northstar}

  IPS-NORTHSTAR   

                              “YOUR FRIEND IN AN UNFRIENDLY SEA”  

IPS-Northstar is the child company born from the merger of civilian cargo lines  
Interplanetary Shipping and Northstar.  

Space piracy and rogue state actors remain the greatest threat to interstellar shipping lines,  
costing ship owners trillions in Manna and countless more in their local currencies. After incurring  
tremendous capital losses due to piracy, IPS and Northstar decided to announce a collaborative  
merger in order to ensure the safety of all civilian and corporate shipping.   

Initially utilizing late-model GMS line mechs, the new IPS-Northstar corporation quickly  
developed their own makes and models of versatile, durable, modular mech chassis that mount  
weapon and engineering systems in equal measure. IPS-Northstar mechs are a good choice for  
pilots who want a tough chassis that’s built for close quarters and melee combat where breaching  
a ship hull might be a possibility. IPS-N mech chassis are built sturdy, meant to take as much  
damage as they can deal, and then some.    

IPS-N is most closely associated with The Albatross, a Cosmopolitan anti-piracy/peacekeeping  
force known across the galaxy for their long and storied history of humanitarian intervention. IPS- 
N supports the Albatross materially, providing them with chassis, ships, and cutting edge IPS-N  
tech -- the relationship between the two groups is mutually beneficial, and IPS-N makes a point  
to emphasize their close relationship to the Albatross in marketing campaigns and PR materiels.   

IPS-N Mech FRAMEs: 
 
IPS-N DRAKE (Heavy Assault)  
IPS-N BLACKBEARD (Melee)  
IPS-N TORTUGA (CQB)  
IPS-N NELSON (Mobile Melee)  
IPS-N LANCASTER (Repair/Support)  
IPS-N VLAD (Special Assault)  
IPS-N RALEIGH (Line mech)  

\input{./IPS-N/gear.tex}                                                                                                          

\input{./IPS-N/core.tex}                                                                                                          

\input{./IPS-N/BlackBeard.tex}                                                                                                                    

\input{./IPS-N/Drake.tex}                                                                                                                    
                                                                                                                       
\input{./IPS-N/Lancaster.tex}                                                                                                                    

\input{./IPS-N/Nelson.tex}                                                                                                                                                                                                                                         

\input{./IPS-N/Raleigh.tex}                                                                                                                                                                                                                                                                                                                                                              

\input{./IPS-N/Tortuga.tex}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  

\input{./IPS-N/Vlad.tex}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             
