
\section{Unique Locations}
Unique Locations   
\subsection{Cradle}
Cradle  

                                                                                                                  


Cradle refers to both the home system and home world of Union, what we call the Solar System  
and Earth, respectively. 
 

Cradle -- the system and the world -- is highly developed, heavily populated, and dedicated to  
the daily and long term maintenance, planning, and running of Union. Humanity's homeworld is  
the beating heart of the galactic hegemony, Union, part memorial, part privileged residence, part  
central hub of bureaucracy. 
 

The terrestrial worlds of Cradle -- Mercury, Venus, Cradle, and Mars, are developed and  
populated. These worlds, like their gaseous sisters, are proving grounds as well for technologies  
developed by GMS and Union. 
 

Mercury is, largely, a world given over to generate and manage the incredible amounts of solar  
power emitted by the Sun and transmit it to Venus, Cradle, and Mars. Mercury is the anchor  
point for solar nets hundreds of thousands of kilometers long that expand, weblike, from the  
world to absorb solar power. It was Humanity’s first Dyson Panel, and Union continues to work to  
perfect and grow the massive, ancient engineering. 
 

Venus is an archive world. Populated stations scatter the surface, but are meant more for  
rotational work than long-term occupation. The world has not been terraformed, and is hostile to  
humans outside of the vast subterranean archives. Here the the bulk of Union’s prime non- 
human persons are kept in reserve, shuttled and entombed in the world for study since the  
Deimos Event of 3000U.  
 

Cradle is the administrative and cultural heart of Union. It is humanity’s birthplace -- once called  
“Earth” -- and the capital of the populated galaxy. Cradle has a fixed population of two billion,  
mostly administrative and support staff for CentComm, the Second Committee,  and the various  
archives on-world. Cradle herself is home to a massive transient population of Cosmopolitans  
and Diasporans engaged in trade, diplomatic, scientific, religious, and other missions to and from  
the galaxy.
 

Cradle is a world healing from the terrible effects of the Anthropocene. Pre-Fall, humanity  
crippled the world in its development: even as they cracked the wonders of the universe, they  
grew in the heart of the world a cancer that, in the end, scoured life nearly entirely from its  
surface. As such, Union’s Cradle bears the markings of that global, epochal trauma. The waters  
have lowered, the fires have quieted, and the seasons have becalmed, and in the wake of their  
recession Humanity has slowly, carefully repopulated the world. They have explored the ruins of  
their ancient cities, reopened old vaults of wonders, and built a new society, one that is strict in  
its stewardship. 
 

To that end, Cradle is off-limits for most. Despite being the ancestral home of Humanity and the  
administrative heart of the power that controls the galaxy, the world itself is calm. It is rare that  
one hears the roar of a jet high overhead. Off the clock, life, generally speaking, is slow. The  
people there are peaceful. Great parks preserve some old wonders and remains of the pre-Fall  
world, reminders to those that live now of the dangers of hubris, of consumption, of rapidity. 
 

                                                                                                           


There are still wonders, tucked away in the lost corners of our ancient homeworld, and some  
terrors locked even deeper. Union may have lived through turbulent times as central committees  
are dissolved and cobbled together, but its bureaucracy has a long memory; none more  
important than which depths one should take care in exploring. 
 

Mars is linked by terrestrial blink to Cradle and is a satellite campus to the larger world’s  
administrative heart. Mars is the location of Forecast/GALSIM and the Union Navy’s FLEETCOM  
center. It has been partially terraformed, an artifact from pre-collapse humanity left to its own  
devices. Life flourishes in Mars’s deep canyons, where air, flora, and fauna is vibrant and hardy;  
the world, like Cradle before her, is healing from the ancient loss of its atmosphere. Outside of  
these oasis, Mars is still a windswept desert, with barely a gasp of air to be had, on vast, terribly  
cold planes of ice and sand.
 

Beyond the terrestrial worlds, humanity has hardpoint bases on a number of moons orbiting  
Saturn, Jupiter, Uranus, and Neptune. These are science stations, R\&D stations, quarantine  
holds, drydocks, mining stations, pilot houses, and so on. The Jovian moons, in particular, play  
host to a large naval population; Callisto and Ganymede are home to important ready-posture  
fleets and terrestrial training facilities, Io and Europa feature important bases and facilities as  
well.    
 

More information on Cradle can be found scattered throughout this rulebook, namely under the  
sections Foundation; Union: The Tyrant, The Watcher, The Guiding Hand; and elsewhere.    

\subsection{Deimos}
Deimos  

Deimos, a moon of Mars, is missing. The circumstances of its disappearance gives name to the  
Deimos Event that lead to the discovery of paracausality, blinkspace, and non-human persons. 
 

Deimos -- wherever it may be -- is assumed to be home to the physical architecture of RA, if  
such physical architecture is necessary for the MONIST entity’s function. At the time of the  
Event, Deimos was home to humanity’s most advanced artificial intelligence research and  
development campus, built following RA’s manifestation at ORACLE CHORUS. 
 

To date, there is no accurate or reliable way to track the location of Deimos, as it appears to be  
able to slip into blinkspace without the use of a stable gate; furthermore, RA is able to manifest a  
suite of anomalous phenomena inconsistent with (or ignorant of) current understandings of  
causality.    
 

Distal and proximal worlds have omni’d in panicked reports of the moon appearing both in orbit  
and, most distressingly, in their atmosphere. When this phenomenon occurs above population  
centers, there is no corresponding damage that, by all logic, should occur.
 

Missing persons reports do spike after such an appearance, as do anomalous paracausal  
events. 
 

                                                                                                                  

\subsection{Hercynia}
Hercynia  

Hercynia is, to date, the location of the only known sentient, sapient, and conscious alien  
civilization. Further information detailed in No Room For A Wallflower.  
 
\subsection{Bastion (Aun’Ist)}
Bastion (Aun’Ist)  

Bastion is the translated name of the homeworld of the Aun Ecumene, an advanced, powerful  
religious order at the distal edge of Union space. The descendants of Old Humanity settled  
Bastion well after Earth had plunged into is Dark Age, having discovered the world seeded by a  
Union nearlight ship and ready for them. They developed in isolation for thousands of years  
before Union made first contact, after a second nearlight arrived with another wave of contracted  
Unionite colonists. 
 

Bastion is a holy world, and the Aunic people make pilgrimage to it, mirroring (in a way) the  
migrations that humans make to Cradle in Union. The Aun were peaceful, initially, but following  
diplomatic friction as a result of Union’s strict hegemonic impositions, a war (to the Aun, a  
crusade) began. 
 

Questions abound in Union FLEETCOM as to why the Aun, a single people, were in need of as  
competent and numerous military ships and ground forces as they possess.   
 
\subsection{Cornucopia}
Cornucopia  
   
Cornucopia is the capital world of the Autumn People’s Republic, a state created following the  
successful revolution and overthrow of its previous monarchist masters. Being the most proximal  
Union territory to the Aun Ecumene, and the home of the system-local blink gate it has borne the  
brunt of the Aun’s crusade against Union.  
 

Isolated following the Aun’s surprise attack on the system, the APR and a single Union MEF in- 
system fight a desperate stand against the Aun crusade, holding out as long as they can for  
Union reinforcements. 
 
\subsection{Karrakis}
Karrakis  

A palace world, Karrakis is the capital of the Karrakin Trade Baronies, an oligarchic interstellar  
state in close proximity to Cradle.   

Karrakis is home to Throne Karraka, the original palace-city of the Baronies, a sprawling estate- 
city now grown to encompass roughly 8 million square kilometers. The original palace, the first  
colony of Karrakis, was seeded pre-fall -- it is now a living royal museum, an enclave set inside  
the crown district of Throne Karraka.    

                                                                                                               


Karrakis is a temperate world, a Gaia planet seeded pre-Fall and left isolated during the dark age.  
It has developed divergent from Union for thousands of years and under the assumption that it  
alone had survived the fall: re-contact with Karrakis and the Baronies occurred first via comm-data  
packet transmissions sent from Union to ID’d pre-Fall colony sites. Karrakis, having flourished for  
nearly 7 millenia, responded rapidly. It would be another two hundred years before physical  
contact was established, then in the form of conventional nearlight drone ships sent from Union to  
Karrakis.   

But for the Deimos Event and Union’s meteoric technological ascendancy, Karrakis would have  
been the seat of humanity’s power. Unencumbered by the events of the Fall, the colony on  
Karrakis was well-rooted on the world, and for thousands of years its people developed at  
conventional rates. By the time of first contact with Union, the Baronies had made landfall on  
nearby worlds; by the time of the Deimos Event, the Baronies had developed mass industries and  
megastructural engineering. However, by the time Union’s first ships arrived in-system, the  
Baronies were far outstripped in offensive and defensive capabilities. Recontact occured in the  
3200s under the Second Committee: fearing significant resistance -- which, indeed, they faced --  
the Second Committee sent a fleet before their diplomats. The war, such that it was one, between  
the Baronies and Union was short. The Union Navy smashed aside the Baronic fleet and secured  
the Baronies’ surrender without making landfall on Karrakis.    

Their fleet eliminated and faced by Union’s singular control over paracausal entities and  
technology, burdened with a baroque monarchy crippled by conventional interstellar  
communications and transportation, the Baronies took the unprecedented step -- by their history  
and internal mythology -- of ceding galactic sovereignty to Union.    

In return, Karrakis became the raw heart of Union’s industrial base, providing the hegemon with  
the vast boon of resources and extraction techniques that ensure Cradle and her colonies -- by  
extension, the rest of the Core worlds in the galaxy -- never want for any material good. The  
Barons, suddenly united by the Blink and the Omninet, chose not to demand rule over the galaxy,  
but to fund the people who did. In time, their economic sway has become inextricable from  
Union’s galactic dominion.   

It is a grim truth of Union -- and an uncomfortable tension among the Terrans that sit the Central  
Committee -- that whoever holds Karrakis has at least one hand on the levers of Union’s power.  
The Karrakin embassy on Cradle is constantly trafficked by Union diplomats and officials, as is the  
Union campus on Karrakis inundated by nobles and magnates.   

Karrakis is the heart of the Baronies and now home to the galaxy’s premier naval and finishing  
college, the Royal Karrakin Admiralty. Pro-Union Houses view attendance at the Admiralty as a  
necessary path for their children, and service as an honorable achievement. They are happy to  
send their children to the college, often at great temporal cost to their families, as local blink is far  
less developed in the Baronies than in Cradle -- this, some barons grumble, by design.   

Following the introduction of mechanized chassis as a warfighting machine, the Karrakin Cavalry  
College adapted the new technology, and is now known for the quality of officer and machine its  
cohorts produce. While attendance and service in the Admiralty is still viewed as the most  

                                                                                                           


prestigious track for a Barony youth, attendance and service in the Cavalry is a parallel honor --  
one more martial than mental.   
\subsection{Ras Shamra}
Ras Shamra  

Ras Shamra is a world of hard contrast. It has a severe beauty, one that Ras Shamrans take a  
fierce pride in and seek to emulate in their architecture, style, and culture in general.   

Tidally locked, Ras Shamra is divided between a “hot” side, ever-exposed to its sun, and a “cold”  
side, ever turned away from the light. The only temperate zone is a comparatively small strip of  
land and thawed sea where the two sides meet: the terminator line, bordered on one side by  
boiling desert, and on the other by frozen tundra.   

This terminator line is a global oasis, a band of life-sustaining tropical jungles, warm river-oceans,  
and balmy valleys. It is in this stormy, humid equatorial region that the first colonists of what would  
become Harrison Armory’s homeworld made their landfall. Now, the terminator line is a globe- 
circling arcology home to roughly 300 million permanent residents.   

The arcology -- the eponymous Harrison Armory -- is the habitable stripe of Ras Shamra; from the  
world’s surface to many thousand meters below, the arcology combines natural landscape with  
cultivated landscape, inorganic with organic, blending world and building together into one  
homeostatic, cultivated biome. Its surface levels are lush, varied climates that seamlessly  
integrate Armory habitats into the natural environment. If a building is exposed, it is meant to be  
exposed, to serve a mechanical, technical, aesthetic, or other official purpose. The surface level is  
widely regarded as home to the finest domiciles, offices, and campuses; the Armory’s capital is  
located on the surface level, at the heart of a pan-galactic botanical park that sprawls for  
hundreds of square kilometers.   

The lower levels of the arcology is where the bulk of the “clean” technical, mechanical, mercantile,  
political, and administrative work that sustains the Armory is done. The arcology underground is  
defined by hundred-meter tall airlight wells that funnel light from the surface down, wide  
concourses packed with shops and office fronts, and vast strips of cultivated biomes meant to  
emulate the surface. Circumnav hyperloops ring the world, forming the backbone of Ras  
Shamra’s global transport network. Here, in the arcology underground, one can find the finest of  
the Armory’s Distant-Classical architectural signature, marked by titanogeometric features,  
achromatic-primary/primary-secondary color schemes, and play with the contrast between airy  
open space and brutalist inclination towards the subterranean massive.   

Outside the safety of the Armory itself, Ras Shamra’s day and night sides are home to the  
Armory’s “dirty” work: research, development, and implementation of the Armory’s catalog. RDI  
Campuses are metropolises in their own right, oases in unrelenting desert or deep, perpetual- 
winter night, where Armory personnel live and work in project-rotation. Thousands of technicians,  
engineers, scientists, and support personnel live and work in RDI campuses for the duration of  
their project and, when it is done, they are rotated out.   

                                                                                                           


The day and night sides of Ras Shamra and the RDI campuses that populate them serve as  
proving grounds for the Armory’s massive field equipment catalog -- civilian and military. The day  
and night sides of the world also serve as proving grounds for the Armory’s colonial officers,  
where both infantry and mechanized cavalry are trained and tested in extreme terrestrial  
environments.    

Currently the Armory is engaged in a massive project of installing a new subterranean hyperloop  
ring to serve the scattered RDI campuses, one that would ring perpendicular to the arcology loop.  
The circadian loop is still a century at minimum away from completion; in the meantime, regular  
shuttle flights serve the RDI campuses.   

Ras Shamra is also home to the Armory’s Special-Exception Persistent-Cultivation Legionspace  
Environment -- colloquially known as the Think Tank. Its location is classified, though suspected to  
be buried somewhere on the night side of the world.   

In local Ras Shamran space, the Armory maintains a number of lunar bases where on-duty  
legions prepare and specialize for distant colonial missions. Massive orbitals process the wealth  
of empire that flows daily into Ras Shamran space -- tithes and tributes, colonial tax from the  
Armory’s holding -- via its local blink gate, Capitol Peak Station.    
\subsection{Carina}
Carina   

Carina, an ocean world in the Argo Navis system, is the jewel of IPS-N and home to its largest  
corporate campus, Northstar, where IPS-N’s master shipbuilders live and work alongside the top  
corporate brass and Cosmopolitan scholars.   

With only 10% of the world’s surface not covered by ocean water, Carina’s terrestrial population is  
far outnumbered by its orbital population, where IPS-N’s vast shipyards produce the galaxy’s most  
ubiquitous freight, civilian, and military hulls. Local space around Carina is a mesh network of  
slingshot gravitational shipping lanes, proving grounds, and ejecta-orbit racing courses, where the  
wealthy IPS-N board and officers enjoy easy access to the stars and the newest vessels that  
cross them.    

Settled soon after the opening of the Blink, Carina was selected by IPS-N’s planners as the  
primary site for the newly merged corpro state; an ocean world ringed by rich terrestrial moons,  
Carina would be the jewel of the old Cradle corporation.   

The great project of relocating IPS-N’s physical infrastructure from Cradle and environs to Carina  
and the Argo Navis system was a centuries-long project. Planners laid out a design for the world’s  
land masses and began converting the raw earth to arcologies akin to Harrison Armory’s  
equatorial installation. Meanwhile, back in Cradle, pilots and engineers set about the massive  
work of making IPS-N’s shipyards ready for flight, breaking up the great manufactories by section  
and setting them on course to Argo Navis: their passage through the blink would set the initial  
calibrations that would become Union-standard for ships across the galaxy.   

                                                                                                           


Carina is a campus-world, unscarred by war or a deep history of human occupation. The bulk of  
the time, Carina is a temperate, mediterranean world, with warm oceans and shallow, high-salinity  
seas -- typically no deeper than two to three meters.   

A notable feature of Carina’s endless oceans are a series of polar “wells”, underwater pits where  
the ocean floor drops to titanic depths of tens of thousands of meters. These wells render the  
polls of Carina uninhabitable; they pierce nearly to the core of the world and act as geyser-spout  
generators, boiling the sea in off-years as trapped gasses build underwater. Typically a decade  
between interruptions, these trapped gasses release in a colossal gout of steam, venting high into  
the atmosphere and plunging the world into a steamy, months-long wet season of hazy  
circumglobal rain and elevated temperatures.  

Save for this once-a-decade phenomenon, Carina is often described as a beautiful, if boring,  
world. Though to the mariner, or the Cosmopolitan, boring isn’t necessarily a thing to be avoided.   

Carina’s local blink gate is Galan Station.    

                                                                                                            
