\section{Movement}
MOVEMENT  

Characters move a number of spaces equal to their speed value. They can freely move through  
(but not end their turn in) the space of friendly targets, but treat hostile targets as obstructions. 
 
\subsection{Engagement, size, and movement}
                             Engagement, Size, and Movement   

All characters have to worry about engagement. If you move adjacent to a hostile target, you  
become engaged. Being engaged gives penalties to ranged attacks (+1 difficulty), and if you  
become engaged with a target the same size or larger than you, you must stop moving and lose  
any additional movement you have left. Targets smaller than you cannot stop you from moving,  
so larger mechs can move around more easily.
 

An actor that is larger than another actor does not count the smaller actor as an obstruction and  
ignores engagement from that smaller actor. For example, a size 1 mech can freely pass through  
the space of a size 1/2 human, and a size 2 mech can freely pass through the space of that size 1  
mech. Mechs can always move through pilots or human NPCs on foot.
 

Typical sizes:  
1/2: A human, a hard suit, small mechs, an EVA suit
 
1: Typical light mechs, assault mechs, line mechs
 
2: Battle tanks, many vehicles, heavy mechs
 
3: Siege mechs, heavy vehicles
 
4-5: Titanic mechs, mech-oriented flyers
 
\subsection{Disengage}
                                               Disengage  
A character can spend a full action to disengage, allowing them to ignore engagement when  
moving and allowing their movement to not trigger reactions (such as overwatch).  
\subsection{Involuntary movement}
                                      Involuntary movement  
Some actions or attacks push, pull, or shove a character in a certain direction. Involuntary  
movement such as pushing, pulling, or knocking a character forces them to move in a direct line  
in a direction specified by the triggering action or attack. Mechs that are pushed, pulled, or  
knocked around do not provoke reactions and ignore engagement with their movement, though  
they must still obey obstructions.  
                                                        
 
\subsection{Traversal and the enviorment}
                          TRAVERSAL AND THE ENVIRONMENT  

Mech combat takes place on many types of worlds with many hostile and hazardous  
environments. Here’s what you need to worry about:
 

                                                                                                             


Difficult Terrain reduces a mech’s speed. 1 space of movement through Difficult Terrain costs 2  
spaces worth of movement speed. Difficult terrain could be rough, marshy or swampy ground,  
icy landscape, or treacherous, rocky scree. What constitutes difficult terrain for pilots and mechs  
might be different.
 

Dangerous Terrain prompts an engineering check to navigate the first time on a turn an actor  
enters it on their turn, or if they start their turn there. Should a player fail that check, they take 5  
kinetic, energy, explosive, or burn damage on failure, depending on the hazard. Intense radiation,  
boiling gases, lava, or falling rocks are good examples of dangerous terrain. An actor only needs  
to make one check a turn for dangerous terrain.
 

Obstructions block passage. Obstructions are typically environmental, but can include NPCs  
and other players. Obstacles smaller than the moving object do not block movement, and  
can be passed through freely. Friendly NPCs or allied players never cause obstruction, but  
you can’t end your movement in their space.
 

Lifting and  Dragging  
A mech can drag another character or item up to 2x its size (but is Slowed while doing so), and  
lift a character or item overhead that’s its size or smaller, but remain immobile. While dragging or  
lifting another object or character, a mech cannot take reactions. Pilots follow the same rules but  
cannot drag or lift objects larger than size 1/2.
 

Climbing like difficult terrain, costs 2 spaces of movement for every space moved. Climbing  
especially difficult surfaces might require a successful hull or agility skill check not to fall.
 

A mech can jump half its speed horizontally in a straight line, ignoring ground based obstacles  
that it could jump over (such as pits, gaps, etc), and cannot jump higher than its size (so a size 1  
mech can jump up to 1 space high during that movement).
 
 
 
Falling causes damage if a character falls 3 or more spaces and cannot recover before it hits the  
ground. A character takes 3 AP kinetic damage for each 3 spaces it falls, up to a maximum of 12  
AP kinetic damage. Typically a character falls about 10 spaces a round, but a mech cannot fall in  
a zero-g environment (or even a low-g environment) and speeds may differ depending on where  
you are.
 
\subsection{Cover}
                                                     COVER  

Cover is obscurement from observation or gunfire. In narrative terms, cover refers to smoke  
screens, hard cover (a building, a wall, a bulkhead, etc) between the attacker and the target, soft  
cover (trees, earthen mounds, etc) between the attacker and the target, obscured vision,  
electronic countermeasures, or any other obstruction physical, mental, electronic, etc, between an  
attacker and their target.  

                                                                                                                    


Smoke, foliage, trees, blinding light, dust clouds, low hills, low walls, etc are all examples of light 
cover. Light cover is typically not solid enough to reliably block fire, but causes enough visual 
interference or reduces profile enough to make aiming difficult. 

Tall walls of buildings, ruined buildings, bulkheads, reinforced emplacements, destroyed mechs 
or vehicles, spacecraft, etc are all examples of heavy cover. Heavy cover is solid enough to 
block shots and hide behind. 

Light Cover adds +1 Difficulty to an attacker’s roll to hit for ranged weapon attacks. 
Heavy Cover adds +2 Difficulty to an attacker’s roll to hit for ranged weapon attacks. 

If a character has a better form of cover, it is not superseded by a weaker form of cover unless 
specifically mentioned. For example, a mech gains light cover from a talent. If a mech fires at that 
mech in heavy cover, they will still treat that target as in heavy cover, as that cover is better than 
the light cover granted to that target by their talent. 

\subsection{Splitting up movement and action}
                              Splitting up movement and action 

A character may take its actions at any point during its movement, and complete that movement 
after that action completes. However, each action itself cannot be split into several parts. 

For example, a mech with 3 weapons and 6 movement can move 3 spaces, then attack, then 
move 3 more spaces. However, if that mech takes the barrage action, its action must complete 
before it can move further, i.e. it must fire all weapons at once (it can’t move 2 spaces, fire a 
weapon, move two spaces, fire a weapon, etc). 

Actions and reactions themselves cannot be split into parts, and each action must resolve before 
the next takes effect. For example, a reaction typically interrupts and resolves before the action 
that triggered it resolves. 

\subsection{Teleport}
                                                TELEPORT 

Some experimental mechs have the ability to teleport. When a mech teleports, it instantly moves 
to a point within the specified range (it needs free space that will fit the whole of its body to be 
able to do so). Teleporting does not provoke reactions and ignores engagement. It ignores 
obstructions entirely and ignores line of sight. A mech can attempt to teleport to a space it can’t 
see, but if that space is already occupied, the teleport fails. The mech loses their action and takes 
5 AP kinetic damage. 

\subsection{Flight}
                                                   FLIGHT 

Some characters have the ability to Fly. When you Fly: 

                                                                                                                


    -    You ignore ground-based terrain, and you can totally ignore obstruction from ground  
         based targets while flying. You only become engaged with targets if you move physically  
         adjacent to them while you’re flying.
 
    -    You ignore obstructions while flying at all points while you’re flying. If you need to pass  
         over a a size 3 obstacle to get to the other side, feel free to do that (it’s assumed you just  
         juke around). However, you can only ignore obstructions if it’s physically possible for you  
         to do so (you can’t go right through a wall).
 
    -    You can end your movement anywhere within a vertical or horizontal range of you equal  
         to your fly speed, in any combination. For example, a mech with a fly speed of 6 could  
         end its movement anywhere within 6 spaces of its location, up to 6 spaces high.
 
    -    You cannot be knocked prone while flying
 

Flying also has some downsides:
 
             -    Flight movement must start and end along a straight line, though the direction  
                 can be changed for each separate movement. For example, a flying mech could  
                  move in one direction, then boost in another. 
 
             -    If a flying character is ever immobilized, stunned, shut down, or otherwise cannot  
                  move, it falls.
 
             -    If a flying mech takes structure damage, it must pass an agility check or fall.
 

                                                  Hover Flight  

Some very advanced mechs have Hover. Hover mechs do not need to move in a straight line,  
and can remain still while airborne (they don’t have to move on their turn and can move any  
distance).
 