\section{Narrative Play}
                                  NARRATIVE PLAY
 

Once you’ve made your engagement roll, prepared your gear and supplies, set your goal and  
your stakes, you’re officially on a mission. A mission could last one session or several sessions.  
You might abandon your original goal in favor of a new one, or encounter a twist in the story that  
throws your mission into disarray. Playing a mission out is mostly a matter of the GM - there’s no  
strong guidelines here as to how to structure it! However, here’s some tools, advice, and aid for  
running a mission.  

                                      Narrative play vs. mech combat  

The following section deals with narrative play, typically when you’re using your pilot skills. This  
is the bit of the mission outside of mech combat, which is a lot more structured. Generally in  
narrative play each roll accomplishes much more, scenes can cover large stretches of time, and  
the outcome of individual rolls is more important.   

Mech combat is turn based, tactical combat. Cutting to mech combat is as simple as declaring  
it’s started, drawing a map out, and picking who goes first. When you want each roll to accomplish  
more and want to play out turn based, tactical combat, you can swap to mech combat.   

These are two different modes of play and the rules work slightly differently for each, especially  
combat. If you’re in narrative play and get into combat, you do combat with skill checks, and don’t  
make attack rolls. NPCs don’t get their own turns (nobody gets a ‘turn’ in narrative play), but their  
actions are narrated by the outcome of player rolls. If you’re doing mech combat, you use turn  
based, tactical play, make attack rolls and track hit points, and NPCs will take their own turns.  

The rules for mech combat (and the difference from narrative play) are found right after the mech  
section.  

\subsection{Making Skill Checks}
                                          Making Skill Checks  

Skill checks are only required when there is a tense narrative situation or when the check  
would move the story forward. You don’t need to make a skill check to open a door, to cook a  
meal, or to talk to a superior, unless that situation is tense or would add to the story. You should  
generally always succeed on mundane tasks, especially if they relate to your background. A  
barroom brawl, a tense escape, decoding an encrypted message, hacking a computer, talking  
down a pirate, picking someone’s pocket, distracting a guard, hunting alien wildlife, or flattering  
the planetary governor are all situations that have some degree of tension and consequence, and  
might require a skill check.
 

Skill checks can cover as much or as little as the narrative requires. For example, you could have  
one skill check cover an entire day’s worth of infiltration into a covert facility if you so desire. Or,  

                                                                                                                  


you could instead cover the moment to moment action - sneaking into vents, hacking doors,  
disabling guards, etc.  

When making a skill check:
 
    -    First name your goal. 
 
    -    The target number is always 10, and the check is a simple 1d20 roll. You then add any  
         accuracy or difficulty from your skills, and then any accuracy or difficulty the GM imposes  
         to get the total accuracy or difficulty on the roll.
 
    -    You should only roll once to accomplish your goal (the GM can’t require extra rolls of  
         you), though the GM could tweak the difficulty if you’re asking something very hard or  
         complicated, or declare that given your goal or circumstances the roll would be  
         impossible.
 
    -    On a 9 or below, you don’t accomplish your goal. On a 10-19, you accomplish your goal.  
         On a 20+, you excel on your goal.
 
    -    On a 19 or lower, the GM can choose to add complications.
 

Complications or consequences from failing or succeeding pilot skill checks always follow the  
fiction and stakes established.
 

A failure doesn’t necessarily mean outright failure, but that you don’t directly accomplish your  
goal. Additionally, if you fail a check, you cannot attempt the same activity again until you change  
the narrative circumstances or approach (it’s a new day, you try something different). For  
example, you try to climb back up that cliff bare-handed, but fail. You could only make another  
skill check to climb the cliff again if you try it with a grappling hook, or get some other help.
 

                                                 Complications  

On any result less than a 20+, the GM can throw additional complications or costs into the mix,  
as established. The GM doesn’t have to throw a complication in every time, and can just let the  
action play out - however rolling less than 20+ gives them the ability to do so.
 

Complications are typically chosen from the categories of Harm, Time, Resources, Collateral,  
Position, Effect. This can never nullify your success if you roll a 10+ or cause you to not  
accomplish your goal, but can add additional nuance to the outcome of your skill check. 
 

It’s important to note that the GM can only inflict complications if it makes sense to do so - in  
other words it must be established clearly before the roll. If you’re trying to take someone out  
with a sniper rifle at 500 meters and they have no way to see you or shoot back, you probably  
can’t take harm as a complication. If you’re trying to knock out a soldier from hiding that soldier  
probably doesn’t have a good way to fight back right away, even if you miss. If that soldier is  
alerted and looking for you, however, she might get a shot off.
 

    -    Harm is damage, injury, or bodily harm, as established. If someone is pointing a gun at  
         you, you attempt to take control of that gun and you fail, you will probably take harm.
 

                                                                                                                  


     -   Time means the activity takes more time than normal
 
     -   Resources means something must be used up, lost, or temporarily expended. This could  
         be something concrete like running out of ammunition, losing a map, or your gun  
         jamming, or could be something like political influence.
 
     -   Collateral means someone or something else takes harm or injury instead of you or your  
         intended target, like an innocent bystander, the whole building, your organization or an  
         ally
 
     -   Position means you are put in a worse position through your actions, like right in the line  
         of fire, clinging to the edge of a cliff, in the bad graces of the Baron, or under a spotlight
 
     -   Effect means your action has less effect than you intend. If you were trying to take  
         someone out cleanly, you make a lot more noise than you intended. If you try to fix a  
         broken door, it will only open for a few people at a time.
 

Narratively, complications are probably much worse if you fail (since you failed to accomplish  
your goal and got a complication).
 

Example complications:
 
         	- Harm: A player rolls to knock someone out who just drew a knife on them by applying  
         fists to faces. They don’t manage to knock their target out however, and they get a knife  
         in the gut for 2 damage.
 
         - Time: A player rolls to charm the baron into granting them an audience, succeeding.  
         The baron lets them stew for a few hours, but gives them the audience.
 
         	- Resources: A player rolls to patch up an NPC’s wounds, and fails. The NPC not only  
         bleeds out, but the player runs out of medical supplies trying to treat them.  
         - Collateral: A player rolls to blow up a door and fails. The whole building starts to  
         collapse
 
         	- Position: A player rolls to take out an assassination target in a hidden base with a  
         sniper rifle and succeeds. They kill their target, but they have to fire multiple times,  
         exposing their position to the entire base.
 
         	- Effect: A player rolls to wreck a security system. It only shuts it down for 5 minutes,  
         however, giving the players limited time to act.
 

                                                       Excel  

If you excel on a skill check (get a 20+), tell the GM how you surpass your initial goal. The GM  
can moderate this if it’s not within reason. In addition, the GM can’t throw complications at you -  
you did that well.
 

Examples:
 
         	- Bruja excels when making a skill check to hack a door control. She suddenly finds  
         herself with access to the whole network
 
         	- Penny excels when making a skill check to threaten a royal guard to stand down. The  
         guard not only surrenders, but offers to help her get an audience with the king
 

                                                                                                                    


         	- Xi excels when making a skill check to get to the extraction point quickly. He decides  
         is able to find a shortcut to get the whole party there instead of just himself.
 
         - Raja excels when making a skill check to get a hold of transport off world for his party.  
         He decides that he manages to talk the shuttle pilot to walk off the job and hand the  
         whole ship to his party
 
\subsection{Player Initiative and NPC Action}
                                 Player initiative and NPC action
 

Players always have initiative when making skill checks or taking action in narrative play. That’s  
a fancy way to say that the GM can never ask for a roll unless prompted by the players. Players  
must name their goal or aim of their action, then GMs can ask for a roll and set difficulty. When  
the roll is made, initiative turns back to the players (probably with a ‘what do you do?’ from the  
GM). What this does in practice is let players decide the course of action and make sure that  
each roll has clearly established stakes and parameters - it’ll help the game feel more fair and  
prevent unnecessary rolling.
 

If the players don’t take action, stall, or pass off responsibility for action, then they are  
effectively turning initiative over to the GM!
 

In addition, NPCs (non-player characters) don’t take actions or make rolls by themselves. Their  
actions are based on player rolls. For example, if a player lies to an NPC, the NPC doesn’t roll to  
see if the player is lying. If the player is successful, the NPC doesn’t see through their deception  
- if they fail, the NPC sees they are clearly lying. If the GM feels like the particular NPC is astute  
or insightful and can easily see through lies, they might add 1-2 difficulty to the roll.
 

There’s a little more on this in the GM section if you need examples. In practice you probably  
won’t even think about this that much.
 
\subsection{Skills in Detail}
                                               Skills in detail
 

Each skill has basic triggers that allow you to easily decide which skill to use and which  
bonuses from backgrounds or training apply to a roll. You don’t have to track or know all of  
them (just the ones which you have +accuracy or +difficulty in from backgrounds or training). If  
you’re stuck as to which skill you should be using, you can quickly refer to the triggers to get a  
good idea.
 

Here’s a little more detail on each skill and when they might trigger. There’s intentionally a little  
overlap between some of the triggers, and each is designed to be somewhat flexible.  
Remember, you don’t need to track all the skills, just the ones you are good or bad at!
 

Applying fists to faces  

                                                                                                                   


Punch someone in the face, or alternately fight in open, brutal unarmed combat, whether it’s a fist  
fight, martial arts duel, or a huge brawl. This is probably not the smoothest or cleanest fist fight  
and probably causes a lot of noise.  

Assault  
Take part in or direct an open or pitched battle, like a corridor gunfight, a huge shootout, fighting  
your way across a battlefield, or undertaking a boarding action. When you assault, you’re always  
assaulting something (a position, a rival pilot, an enemy force, a group of guards), and it’s always  
loud, open, direct action.  

Blow something up  
Use explosives (improvised or otherwise), weapons, or maybe just good old fashion brawn to  
totally wreck something or turn it into an enormous fireball (maybe a wall, sensor array, outpost,  
reactor core - the good stuff). Whenever you’re totally destroying an object, building, etc, you can  
use this. Probably not to be used against people unless they’re incidentally in the way.  

Threaten  
Use force or threats of force to get someone to do what you want them to do. Name what you  
want someone to do and what you’re going to do to them if they don’t listen to you. This could  
also be blackmail, leverage, or something similarly nasty. Threatening someone can be very high  
risk but very effective if successful. If you threaten someone unsuccessfully, your threats have no  
further effect on them unless you change something about the situation (like all other skill checks).  

Take control  
Use force, violence, presence of will, or direct action to take control of something. This is often  
something concrete, like an object someone is holding. You could take control of someone’s gun  
or a keycard they have on their person. You can additionally can take control of a situation to force  
those present to listen, calm down, stop moving, or stop what they’re doing, though you can’t  
necessarily force them to do anything further without threatening them. Taking control is never  
subtle and always direct and dangerous.  

Survive  
Persevere through harsh, hostile, or unforgiving environments, such as the vacuum of space,  
frozen tundra, a pirate enclave, a crime-ridden colony, untamed wilderness, or scorching desert.  
You most often use survive when you want to take a journey through wilderness environments,  
navigate, or avoid natural hazards such as carnivorous wildlife, rockfalls, thin ice, or lava fields.  
Alternately you could use it to avoid man-made hazards, such as navigating a city safely, or  
avoiding dangerous areas of a space station. You could also use it when testing personal  
endurance, such as shaking off poison or alcohol.  

Stay cool and collected  
Do something that requires concentration, speed, or intense precision under pressure, like picking  
a lock, finding the right frequency for your omnihook, carefully disarming an explosive, or  
unjamming a gun. If you’ve got to do something complicated in a high stress situation without  
messing up (and possibly not even breaking a sweat) this is the action to use.  

                                                                                                                   


Take someone out  
Kill or disable someone quickly, quietly, effectively or from a distance, probably before they even  
notice. This is probably a single person but could be two people relatively close together (any  
more is sort of stretching it). If you’re looking down a sniper scope at a target, preparing to nerve  
pinch a guard to knock them out instantly, quick-drawing during a gun duel, or dropping from a  
ceiling to slit a throat, this is the action to use.  

Flash  
Do something flashy, cool, or impressive with your weapon other than killing, like shoot a very  
small or rapidly moving target, shooting someone’s hat off or their weapon out of their hand,  
knocking someone out by throwing a gun at them, performing an acrobatic flourish with a sword,  
throwing a spear to pin a fleeing target to the ground, or something similar.  

Get somewhere quickly  
Get somewhere without complications and with speed, but not necessarily quietly. Climb, swim, or  
perform acrobatic maneuvers. Fall safely from a great height. Move gracefully in zero-g. Chase or  
flee from, outrun or out pace a target. Get somewhere faster than anyone else. You can also use  
this when you want to drive or pilot a vehicle.   

Act unseen or unheard  
Get somewhere or do something without being detected, but not necessarily with speed. Hide,  
sneak, or move quietly. Infiltrate a facility while avoiding security, patrols, or cameras. Perform a  
quick action or maneuver without being seen or heard, such as picking a pocket, unholstering  
your gun, or cheating at cards. Wear a disguise.  

Fix, hack, or wreck   
Repair a device or faulty system. Alternately, hack it wide open, or totally wreck, disable or  
sabotage it. You can use this for hacking or safeguarding electronic systems, such as electronic  
door locks, computer systems, omninet webs, or NHP coffins.  

Patch  
Apply your medical knowledge to administer medication, bandage, staunch bleeding, suture,  
cauterize, neutralize poison, or resuscitate. Alternately, you could use it to diagnose or study  
disease, pathogens, or illness.  

Invent or create  
You need tools and supplies to invent or create something successfully. Use this with many  
downtime actions to work on projects. You can also use it in the spur of the moment to invent new  
devices, tools, or approaches to something (improvised explosives, gear, disguises, or some  
similar).  

Read a situation  

                                                                                                                    


Look for subtext, motive, or threat in a situation or person, often social situations. Use your  
intuition to learn someone’s motivation, who is really in charge, or who is about to do something  
rash or stupid. Get a gut feeling about a situation or person. Sense if someone is lying to you.  

Spot  
Spot hidden or difficult to make out details, objects, or people. Spot ambushes, hidden  
compartments, or disguised individuals. Spy on a target from a distance, or make out the details,  
shape, and number of objects, vehicles, mechs, or people clearly at a distance. Track people or  
vehicles.  

Investigate  
Research a subject, or look at something in great detail. If you can’t find information directly, you  
learn how you can get access to that information. Learn about a subject of historical relevance, or  
become well-read on a subject. Investigate a mystery or solve a puzzle. Locate a person or object  
through research or investigation.  

Charm   
To charm, you need a receptive audience, or some kind of promise of leverage (money, power,  
personal benefit, etc). You can use it when trying to smooth talk your way past guards, get  
someone on your side, sway a potential benefactor, talk someone down, perform diplomacy  
between two parties, or blatantly lie to someone. You can also use it when trying to impersonate  
someone. Charm won’t work on people that aren’t receptive (such as soldiers you are in a  
gunfight with) or that you don’t have leverage over (promises of safety, money, power,  
recompense, help, etc). These promises don’t necessarily have to be true but they have to have  
some weight with your target.  

Pull Rank  
Pull rank on a subordinate, getting information, resources, or aid from them, even unwillingly. You  
can use this on anyone your social status (noble, celebrity, etc) or military rank would have weight  
with. Failing this might be risky and could be seen as abusive. You typically can’t pull rank on  
hostile targets. You could also use this to pull rank and pretend you are a higher rank than you  
are, but it’s even riskier.  

Word on the streets  
Get gossip, news, or hearsay from the streets. What you get depends on what ‘streets’ you are  
getting word from (high society, low society, hearsay, military chatter, etc). This probably takes a  
lot less time than investigating something in detail, but the information might be more qualitative  
or colored by opinion (sometimes that might be useful). You can always learn where the  
information came from or who to go to next.  

Get a hold of something   
Acquire useful allies, assets, or connections through wealth or social influence. This could be  
permanent (buying it or receiving it) or temporary (renting or borrowing help or supplies, etc), and  
might be harder or easier depending on how much you want to use it. This can’t be used for  
something that’s normally gated by license level (like mech parts) but could be used for aid,  

                                                                                                                    


supplies, information, food materials, soldiers, or anything else that has more narrative impact.  
Typically this is acquired by buying it from a market or requisitioning it from a parent organization.  

Lead or inspire  
Give an inspiring speech, or motivate a group of people into action. Administer or run an  
organization efficiently or effectively, such as a company, a ship’s crew, a group of colonists or a  
mining venture. Effectively command a platoon of soldiers in battle, or (perhaps) an entire army.  

\subsection{Skill Challenges}
                                         SKILL CHALLENGES  

A skill challenge is a simple way to test an entire group for a particular activity. Everyone makes a  
relevant check, and the success of the challenge depends on the overall result of the skill checks  
from the entire group, not just one player. If more players succeed than fail, the challenge is a  
success. If equally as many succeed as fail, the challenge has a 50% chance of success (roll a  
die or flip a coin), representing the razor’s edge of the situation. If more players fail than succeed,  
the challenge is a failure.  

Here’s some example challenges:  
    -    Sneaking into a guarded facility: All players roll a skill check (example skills that could  
         trigger: move unseen, spot the cameras, charm the guards into thinking they are a  
         superior). Success means they all get in unnoticed, failure means the guards are alerted.  
    -    Gaining the favor of the Baron: All players roll a skill check (example skills that could  
         trigger: charm, but could also be to threaten the baron, or perhaps read the situation)  
         Success means the players gain a private audience with the Baron, failure means the  
         players’ meddling is noticed by rival nobility and they are thrown out.  
    -    Traversing the Wastes: All players roll a skill check (example skills that could trigger:  
         survive, spot water, or get across the waste quickly). Success means they cross the  
         wastes unharmed. Failure means they cross the wastes, but it is a harrowing journey and  
         they arrive there with no repairs or supplies left and lacking food and water.  

Challenges are good when you want to extend the narrative impact of rolls.   

You can also have extended challenges that have 3 rounds of rolling and calculate the outcome  
based on rounds ‘won’ by the players. For example, the players may have to gain the favor of the  
baron, then plant information in the baron’s castle, and sabotage the gate. They are only truly  
successful if the majority (2/3) of these tasks are accomplished.  

\subsection{Combat in Narrative Play}
                                      Combat in Narrative Play
 

When running combat narratively, use the normal rules for skill checks. That means when the  
individual actions in combat doesn’t matter that much or you want a combat scene to play out  
more like a movie than a tactical game. If there’s not a mech involved (and you’re just playing on  
the pilot scale), it’s almost always preferable to use narrative combat.
 

                                                                                                                   


You don’t need to track turns or make attack rolls, and you might only need to make a few rolls  
for the whole combat (one roll for each action or goal, as normal!). Turn-based combat in  
LANCER is usually reserved for mech combat.
 

You can also use a skill challenge to run narrative combat if you want it to be a bit more  
structured.
 

Here’s a couple examples:
 
	        - Bruja and Penny are negotiating with the Black Star Bandits to try and get them to  
release a hostage. The negotiations go sour (Penny fails her skill check to charm the bandit  
captain), and the bandits draw on them. Bruja decides to take out the bandits quickly with her  
Sidekick. She rolls a skill check, getting a 15. She kills the bandits and the GM decides to add  
position as a complication, so the rest of the bandit camp is alerted and they will need to get out  
quickly.
 
	        - Pan is in a pitched battle, on foot. He sees a gun emplacement raining hell down upon  
his allies and decides to take control of it. He rolls and gets a 7, failing. The soldiers defending  
the emplacement turn the gun on him, preventing him from getting any closer. The GM adds  
collateral as a complication. Pan looks behind him and sees some members of his squad get  
gunned down in the ill-advised assault.
 
	        - Raja is commanding a platoon of troops to board an enemy ship and take control of the  
command center. He rolls to lead the charge, getting a 22, (he excels). There’s no complications,  
and when his group successfully fights their way to the command center, they immediately  
surrender and hand control over.  

                                                                                                                    
\subsection{Hit Points, Damage, and Injury}

                                 Hit Points, damage, and injury 

Pilots normally only care about Hit points, also called HP (how much damage your pilot can take 
before they are out of the action!) during mech combat, but they might also take damage as a 
result of complications during skill checks. 

At level 0, pilots have 6 Hit Points, representing not only bodily health, but also the ability to 
duck, dodge, avoid damage, or just sheer luck. At higher levels, they add their grit (1/2 level) to  
calculate their base HP (leading to a total of 6 + grit). A pilot that takes damage doesn’t neces- 
sarily take bodily harm, but might be using up their stamina, luck, or ability to avoid that incom- 
ing damage. 

If a consequence deals damage, it’s enough to hurt or kill. Taking things like minor grazes, 
bruises, etc doesn’t deal damage but could cause other complications. 

Here’s what damage looks like for pilots in narrative play: 
Minor damage is 1-2 damage. This could be something like getting shot at by small arms fire, 
stabbed, unarmed combat, hit by a flying rock, etc 
Major damage is 3-4. This is getting shot at by assault or heavy weapons, a long fall, breathing 
in toxic gas, etc 
Lethal damage is 6+. This is something like having a mech fall on you, getting hit by a mech 
scale weapon, having a grenade blow up right under you or something similar. 

Pilots might have 1 or 2 armor. Subtract armor from all damage taken as a pilot, unless that 
damage has the armor piercing (ap) tag. Some weapons have the ap tag, but damage outside of 
that might also (falling a long distance, being immersed in lava, etc). 

                                                 Down and out 

                                                                                                                 


If you’re reduced to 0 HP or lower as a pilot roll a 1d6. On a 6, you miraculously shrug off the hit  
(or its a close call), returning to 1 HP. If you roll a 1, your luck has run out, and you’re immediately  
dead. If you roll a 2-5, you are down and out, at 0 HP. You’re knocked out, pinned, bleeding out,  
or otherwise unable to act. Your evasion (how hard it is to hit you in mech combat) becomes 5  
and if you take any more damage, you’ll die (if someone comes over and shoots you in the head,  
for example).
 

You can die instead of being down and out, if you choose so. Typically you’d just bleed out and  
wake up in prison, a field camp, a hospital, or buried under a pile of dead bodies somewhere.
 
\subsection{Rests and Full Repair}

                                         Rests and Full Repair  

If a character takes an hour and rests with no strenuous activity, they can regain 1/2 their HP, and  
recover from Down and Out, coming back to consciousness. When you take at least 10 hours to  
rest and full repair, you can recover all your hp.
 

Rest and repair also help your mech (you can see more in the mech section on damage).
 

If you’re dead, it might not be the end for you. See the rules on cloning in the Death section in  
mech combat.
 