\section{Non Player Characters}  
      NON PLAYER CHARACTERS  

This section contains the rules for running non-player characters in combat in LANCER. As a  
large part of your role as a GM is running those characters, we’ve included a lot of rules and  
resources here to help you create those characters as fully as you can. 
 

The rules for NPCs can look intimidating, but it’s more useful to think of this section as a toolbox  
for you to put together the NPCs that you want to include in your game, whether that’s a horde of  
enemy mechs, a powerful and devious adversary, biological monstrosities, or rebel raiders. It’s  
more like a catalogue for you to pick, choose, and create. If you don’t feel like getting too deep  
into this, you can take all the basic NPCs presented here and put them in your combats without  
any additional work. However, we have also tried to provide a comprehensive and flexible outline  
for you to fill in your own details or make your own creations.
 

                                              Running NPCs  

Non-player characters (NPCs) act by slightly differently rules in LANCER than player characters.  
Player characters are assumed to be exceptional individuals, whether through ability, training, or  
just sheer luck. The rest of everyone else has to follow in their wake, so to speak.
 
In narrative play, NPC actions typically depend on the rolls of player characters. In other words,  
the player’s rolls do double duty for both PC and NPC actions. For example, a player failing a  
combat roll is cue for the NPCs to tackle them, punch them in the face, or open fire. A player  
failing a roll to infiltrate causes NPCs to notice them, or sound the alarm, or call reinforcements.  
NPCs, and the GM generally don’t make rolls for themselves. Some very basic statistics are  
given for pilot-scale NPCs if you need to include them in mech combat, or want to run turn- 
based pilot combat.
 

In mech combat, NPCs act much like player characters, with some notable exceptions. NPCs  
can be heroic individuals, but they typically don’t have access to the full range of options that  
players do.
 

                                         NPCs in mech combat  

NPCs follow the same rules for players in Mech combat. By default, they take one turn per  
round, and can make a single move and two quick actions or full action on their turns, like  
player characters. However, NPCs act with the following exceptions:
 

NPCs, unless specified, never act first on the very first turn, and only take a turn when they  
are activated. A player will always act first in the round, then the GM gets to activate a hostile  
NPC. A friendly NPC can be activated by player characters and acts in lieu of a player turn.  
Player/friendly NPC turns and hostile NPC turns will always alternate until one side has  
completely activated, at which point the remaining actors can take their turns in any order.  

                                                                                                         


NPCs are limited in the actions they can take on their turn. They can also take actions that  
are slightly different to player actions.
 
NPCs can take the following quick actions:
 
             -   Boost - Move again, similar to the player action  
             -   Hide or Search - As the player action  
             -   Quick Tech - Invade, Lock on, Bolster, or another action in their profile
 
             -   Grapple - As per the player action  
             -   Ram - As per the player action
 
             -   Reload - Reload one weapon with the loading tag
 
             -   Skirmish - The NPC attacks with one weapon in its profile of size heavy or smaller
 
And the following full actions:  
             -   Recover - The NPC ends 2 conditions on themselves - Impaired, Jammed,  
                 Stunned, Slowed, Immobilized, Lock On.
 
             -   Boot up - The NPC ends the shut down condition on themselves (they can make  
                 this action even if shut down)  
             -   Cool - Reduce heat to 0  
             -   Barrage - Enemies attack once with each weapon in their profile. They may  
                 choose the same or different targets.  

You will notice that NPCs cannot overcharge or take the Stabilize action (they cannot repair by  
default).
 
                                                   Recharge  

Many NPC modules and weapons have the recharge tag. Once an NPC uses a system or  
weapon with this tag, they can’t use it again until it recharges. At the start of each of their turns,  
roll 1d6 and check to see if they gain the use of their system or weapon back. This is listed in the  
profile of the weapon or system. For example, a recharge (5+) system can be used again once a  
5 or 6 is rolled.
 

Check only once for all recharge modules per NPC, but roll separately for each NPC.
 

                                             NPCs and damage.
 

NPCs, are destroyed when they reach 0 HP by default. By default an NPC has 1 point of  
structure, and cannot enter the CRITICAL state (they are just destroyed when reaching 0 HP). An  
NPC with more than 1 point of structure follows the same rules for taking structure damage as  
players (but still can’t go CRITICAL). When they’re reduced to 0 hp and check their last point of  
structure, they are destroyed.
 

NPCs mostly deal flat damage instead of rolling for their attacks.
 

                                                                                                              


NPCs cannot Critical Hit unless specified. They rely less on luck than players, who are more  
traditionally ‘heroic’ characters. Some NPCs, such as veterans, or Ultras can Critical Hit, which  
makes them quite dangerous.
 

                                                 NPCs and heat  

Some NPCs (such as mechs) have a heat capacity like players. By default, NPCs have 1 reactor  
stress and are shut down when they reach full heat capacity and reactor stress (and cool all heat  
when they shut down). If an NPC has more than 1 reactor stress, it takes heat like a player and  
can also enter the CORE BREACH state like a player instead of shutting down when it reaches  
full stress.
 
If an NPC has no heat capacity, it instead takes heat as energy damage.
 

                                                        Tier  

NPCs are split into tiers for ease of estimating difficulty. Higher tier NPCs have increased  
statistics and deal more damage. Tier 1 is levels 1-4, tier 2 levels 5-8, and tier 3 levels 9-12.
 

The damage and bonuses of NPCs often scales per tier. This is written as X/tier. For example, an  
attack with +2/tier vs evasion +1 accuracy/tier would roll the following per tier:
 

Tier 1: +2 with 1 Accuracy
 
Tier 2: +4 with 2 Accuracy
 
Tier 3: +6 with 3 Accuracy
 

Damage is written as Tier 1/Tier 2/Tier 3 damage
 

For example, an NPC might have an attack that looks like this:
 

Assault Rifle
 
Main Rifle
 
+2 vs evasion/tier with +1 Accuracy
 
Range 10
 
4/6/8 kinetic damage
 

At tier 1, the weapon will attack at +2 targeting, +1 Accuracy for 4 kinetic damage
 
At tier 2, the weapon will attack at +4 targeting, +1 Accuracy for 6 kinetic damage
 
At tier 3, the weapon will attack at +6 targeting, +1 Accuracy for 8 kinetic damage
 

Player characters of a lower level than the tier of NPC they are fighting will generally have a much  
harder time. For example, you shouldn’t generally match up players of license level 3 against tier  
II NPCs.
 

                                                                                                                 


You can mix and match tier to give players a harder or easier challenge if you want (especially if  
you want to ease players into a higher tier so the jump isn’t as severe).
 

                                                 NPC Tags  

NPCs use the same tags as players, but have a few additional tags they can use that change the  
way that they work in combat. Some of these tags indicate that NPCs have one or more  
templates applied to them, which are explained in the following section (and you can find at the  
end of this section).
 

Grunt - The grunt tag indicates an NPC with the grunt template (a weak and numerous enemy)
 
Elite - The Elite tag indicates an NPC with the Elite template. A elite NPC is generally tougher  
and more dangerous than a regular enemy.
 
Ultra - The Ultra tag indicates an NPC with the Ultra template. An Ultra is meant to be fought by  
an entire group of players and has vastly increased toughness and destructive power.
 
Veteran - A Veteran NPC has greater abilities than a normal NPC and is a more unique or  
standout character
 

Mech - An NPC with the mech tag is an ambulatory, mechanized cavalry unit (like the players)
 
Vehicle - An NPC with the vehicle tag is a vehicle of some kind
 
Biological - An NPC with the biological tag has no heat capacity, cannot take or benefit from  
tech actions unless specified, and is immune to all tech actions except Scan and Lock On.
 
Squad - An NPC with the Squad tag indicates a large squad of biological or mechanical enemies  
or a squadron of mechs or vehicles. Rules for squads are found in the squad class.
 
Swarm - An NPC with the swarm tag indicates a large swarm of drones or smaller NPCs. Rules  
for swarms are found in the swarm class.
 

                                           Traits and systems  

Traits are components of an NPC that can’t be described by a system, such as general qualities,  
pilot experience, or training. They cannot be disabled by system damage.
 

                                         Classes and Template  

LANCER doesn’t have a set ‘catalogue’ or manual of NPCs, but instead presents a list of basic  
NPC classes and templates you can use to customize an NPC the way you want them. 
 

An NPC class describes the basic statistics and abilities of an NPC, and usually describes their  
function. For example, if you want an NPC mech that functions like a mobile artillery piece, you  
should use the Bombard class. If you want an NPC mech that flies and strafes its targets, you  
should use the Ace class.
 

                                                                                                          


An NPC template can be applied on top of the base class to further customize an NPC by  
adding more unique flavor (such as the pirate template), more unique modules, or changing the  
NPC into a tougher enemy meant to be fought by many players.
 

There are a few important templates that change the function of an NPC fairly drastically:
 

The Grunt template makes an NPC into a weak, easily dispatched enemy. Grunts have 1hp and  
deal reduced damage, but otherwise function like a regular NPC of their type. Grunts can be  
used when you want to throw numerous enemies at your players to make the experience more  
cinematic or increase the size of an encounter without totally overwhelming your players.
 

The Elite template makes NPCs tougher and more durable, and can be used when you want to  
make a standout or especially powerful NPC. Elites gain more HP and structure which gives  
them the ability to take critical damage like players.
 

The Ultra template makes an NPC into a very powerful foe that should be fought by an entire  
group of players. It drastically increases the toughness and durability of an NPC, as well as  
giving them access to powerful Ultra traits and systems. Ultras can gain additional activations  
(turns) that they can take per round, making them deadly unless they are tackled by multiple  
players at once.
 

The Veteran template makes an NPC into a more characterful, durable NPC. You can use it  
when you want an NPC to stand out or have a notable or memorable ability. You can apply it on  
top of other templates such as Elite to make a very tough or dangerous foe.
 

                                      Base and Optional modules  

All NPC classes come with base modules (system, weapons, and traits) common to all of that  
particular class. Under the entry for each NPC class is a list of optional modules for that class.  
Adding multiple optional modules can make a more tactically interesting but more complex and  
dangerous enemy and is up to your discretion.
 

                                             Building an NPC  

Building an NPC is a pretty simple process:
 

    1.  Choose NPC class from the section below  
    2.  Choose 0-2 optional modules  
    3.  Pick a tier and set the stats for your NPC.  
    4.  Choose and apply a template to your NPC, if applicable  
    5.  Re-flavor, re-name, and customize  

You should always feel free to re-name or re-flavor, modules, or classes as you see fit. For  
example, your Ace NPCs in a particular encounter might not be called ‘Aces’ but ‘Royal Guard’.
 

                                                                                                          


                                            Adding complexity  

Think about how your NPC functions. Most NPCs should have base systems and 1 optional  
system unless otherwise noted. However:
 

If you want a very basic NPC, don’t choose any optional modules or templates. You can very  
easily run NPCs without adding any extra complexity to a fight by just choosing the basic NPCs  
with their stats and base modules.
 

If you want a weak NPC you can throw at players en-masse, choose the Grunt template. If you  
want to give the impression of a true horde of enemies, use the Squad template.
 

If you want a slightly more complex, advanced, or dangerous NPC, choose additional optional  
modules. Generally adding 1-2 more will be sufficient, but you can add more or less as you see  
fit. The more optional modules you add, the more complicated the NPC will be to run during a  
game.
 

If you want a unique, strong, standout, or memorable NPC, apply the Veteran, or Elite templates.
 

If you want a ‘boss’ type NPC, something that is able to fight the entire group at once, choose  
the Ultra template
 

If you’re feeling confident, you can even swap systems around from enemy class to enemy class.  
For example, you could give the Spectre’s cloaking field to an Assault-type enemy. To push it  
even further, if you want to change the Assassin NPC into a nasty example of alien wildlife, you  
could give it the biological tag, re-name its variable knife to ‘slashing claws’, then give it the ‘Acid  
Spittle’ option from the Monstrosity class.
 

                                            Balancing Combat
 

A ‘normal’ difficulty combat should be (per player) any mix of:
 
    -   1 Ultra/4 players  
    -   4 grunts/1 player  
    -   1-2 normal enemies/1 player
 
    -   1 elite/1 player  

These enemies should be of the same tier as players. You can mix and match this, for example, if  
you have four players, you could mix in 4 grunts and three regular enemies.
 

You can decrease combat difficulty by lowering the number of enemies or lowering their tier  
relative to players, and you can increase combat difficulty by adding enemies with more optional  
systems, elite enemies, higher tier enemies, enemies with more templates (such as veteran), or  
adding more enemies.
 

                                                                                                          


This is something up to you to figure out with your particular group of players. Don’t take the  
above advice on balancing encounters as a rigid set of rules, but rather a starting point or  
guideline. Every group is going to want different levels of challenge.
 

                                          Number of Combats  

In an optimal situation, players should have 1-2 combats between rests, and should fight in 3-4  
combats before getting a full repair. As GM this is up to your discretion, especially if you’re  
throwing harder combats at players. Remember the GM agenda - you are not there to punish  
players, but to help tell a good story.
 

                                                                                                          
