\section{NPC Classes}

        NPC Classes  
\subsection{Ace}
                                                  ACE  

A pilot more comfortable the closer they get to their roots, the Ace enemy-type employs high-speed  

strafing runs, agile maneuvers, and a reckless approach to piloting their mech. Cocky and self-assured,  
Ace-type enemies relish a good duel.  
 

 ACE 

 Mech 

 Hull       Agility     Systems       Engineering 

 -2         +3          +1            +0 

 HP         Evasion     E-defense     Heat Cap. 

 16         11          9             8 

 Armor      Speed       Sensors       Size 

 0          6           10            1/2 or 1 

Base systems:
 
SS Corpro flight system  
System
 
Whenever this mech moves or boost, it can fly.
 

Missile Launcher  
Main Launcher
 
+1 vs evasion/tier
 
Seeking
 
Range 10, Blast 1
 
4/6/8 explosive damage
 

Optional systems:  
Bombing Bay  
System, Limited (6)
 
1/turn
 
When the mech flies while it moves or boosts, it can drop a bomb on one target below as a free  
action it that it passes over or adjacent to. Bombs create a blast 1 area with at least 1 square on  
their target. All affected targets must pass an agility check or take 6/9/12 explosive damage and  
be knocked prone.
 

                                                                                                       


Strafing Module  
System, Quick Action
 
1/round
 
The mech flies its speed in any direction in a strafing run, dealing 3/5/7 kinetic damage to any  
enemy it passes over or adjacent to (no roll required).
 

Burst/Dash module  
System
 
Recharge (5+)
 
The mech may activate this module instead of moving normally, engaging powerful thrusters. It  
flies its speed in a straight line in any direction. This movement doesn’t provoke reactions,  
ignores, engagement, and any mechs engaged with the target when it activates this module  
must pass an agility check or be knocked prone.
 

Chaff Launchers  
System, Reaction
 
Recharge (6+)
 
In response to any hostile tech action or attack, the mech launches chaff and engages digital  
scramblers, causing the attack to miss, and granting it immunity to tech attacks and ranged or  
melee attacks with the smart keyword until the end of its next turn.
 

Attitude Thrusters  
System, Reaction
 
1/round, Recharge (5+)
 
In response to being hit by any ranged attack, the mech does a barrel roll, flying 3 in any  
direction and gaining resistance to all the damage of that attack.
 

Tier II:
 
HP: + 2
 

          Evade    E-D    Heat    H     A     S    E        Armor       Spd       Sense 

          14       10     8       -2    +4    +2   +1       0            7        10 

All agility checks made as a response to the Ace’s attacks are made at +1 Difficulty.
 

Tier III:  
HP + 2
 

          Evade    E-D    Heat    H     A     S    E        Armor       Spd       Sense 

          18       11     8       -2    +6    +3   +1       0           8         10 

                                                                                                               
\subsection{Aegis}

                                                 AEGIS  

Aegis-style mechs are squat, defend-and-suppress chassis built to hold ground, support their allies, and  

suppress enemies. Higher-tier Aegis mech pilots have access to hardlight and blackwall defensive  
measures - technology that makes bulwarks out of even the smallest barricade.   

 AEGIS 

 Mech 

 Hull       Agility      Systems       Engineering 

 +0         -2           +2            +2 

 HP         Evasion      E-defense     Heat Cap. 

 14         7            10            10 

 Armor      Speed        Sensors       Size 

 2          3            8             2 

Base systems:  
Light Laser  
Main cannon
 
+2 vs evasion/tier
 
Range 8
 
2 energy damage + 3 burn/tier
 

Defense Net  
System, Shield, Quick Action
 
This system spreads a powerful shimmering repulsion shield over a large area. While this system  
is active, this mech is immobilized, but all attacks against any target within a burst 3 zone around  
the mech originating outside of that zone take +1 Difficulty/tier. Attacks out of the zone or  
between targets that are both inside of the zone are unaffected. It can be deactivated as an  
action.
 

Optional systems:  
Adaptive Shielding
 
System, Reaction
 
1/round
 
The first time an allied target inside the defense net is damaged, all targets inside gain resistance  
to the damage type of the triggering attack until the end of the Aegis’s next turn.
 

Ring of Fire
 

                                                                                                          


System
 
All targets hostile to the Aegis that start their turn inside the Defense Net or enter it for the first  
time on their turns take 3 heat and become Shredded while inside the net (they can end this  
condition by leaving the net).
 

Hardlight cover system
 
System, shield, deployable, quick action
 
Recharge (5+)
 
The Aegis creates a line 3 section of hardlight, which grants light cover (1 difficulty) against  
incoming fire. Mechs adjacent to this cover have resistance to damage from line, blast, and cone  
attacks. The cover is immune to damage.
 
At tier II onwards, this cover grants heavy cover.
 

EM Shielding
 
System
 
The Aegis’ defense net also grants its difficulty to tech attacks made from outside the shield.
 

HA Blackwall system
 
System, Full Action
 
Limited (1)
 
The Aegis creates a pitch black wall of blinkspace that takes up a free line 10 zone 5 spaces high  
that must have at least one point within 5 spaces of the Aegis. The wall breaks line of sight  
between its two sides and no effect or attack can be drawn across it. Any mech that starts its  
turn on the wall or crosses it for the first time on its turn has a 50% chance to be lost in  
blinkspace momentarily. If this occurs, remove the mech from play. It returns at the end of its  
next turn, in any free space within range 10 of either side of the wall. If there is no space  
available, it returns when there is. The wall disappears when the Aegis is destroyed or it uses an  
action to deactivate it, also returning any stranded mechs.
 

Tier II:
 
HP: +4
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          8         12     10      +0   -1    +3    +3      2            3         10 

Tier III:
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          8         14     10      +0   -1    +4    +5      3            3         10 

                                                                                                                
\subsection{Assassin}

                                                 ASSASSIN  

Assassin style mechs trend towards agility, damage, and speed. Their pilots sacrifice comfort for a chassis  

efficiency — unnecessary life-support systems, pilot care systems, communications systems, and others  
are stripped out and replaced with systems that increase processing power, run-silent ability, and increase  
chassis range.   

Assassin pilots work alone or in small groups, piloting their small, sleek mechs into territory thought  
impenetrable by their targets. One of the few doctrines to employ bladed weapons, assassin-style pilots  

train both in the cockpit and out of it to be able to fight with any weapon, in any theater, as efficiently as  
possible.   

 Assassin 

 Mech 

 Hull        Agility      Systems        Engineering 

 +1          +2           +0             -1 

 HP          Evasion      E-defense      Heat Cap. 

  15         12           8              7 

 Armor       Speed        Sensors       Size 

 0           8            12             1 

Base systems:  
Kai Bioplating  
Trait
 
This mech gains +1 Accuracy on all agility checks. It can climb with no penalty, takes no penalty  
for difficult terrain, and doesn’t make dangerous terrain tests.
 

Variable Knife  
Auxiliary Melee
 
AP
 
+1 vs evasion/tier with 1 Accuracy/tier
 
Threat 2
 
4/6/8 kinetic damage
 

Pulse Rifle  
Heavy rifle
 
+1 vs evasion/tier with 3 Accuracy
 
Range 12
 
7/9/11 energy damage
 

                                                                                                               


Optional systems:
 
Boltok Rifle  
Heavy CQB
 
Loading, Knockback 1
 
+1 vs evasion/tier
 
Range 3, Threat 3
 
10/15/20 kinetic damage
 
This heavy, archaic weapon replaces the Pulse Rifle.
 

Spinning Kick  
Trait, Quick Action
 
A target adjacent to the Assassin must pass a hull or agility check with 1 difficulty/tier or be  
knocked back 4 spaces away from the assassin and knocked prone.
 

Shroud module  
System, Quick Action
 
The Assassin creates a burst 3 zone of light cover within range 8. The zone disperses at the end  
of its next turn, or when the Assassin creates a new one. Mechs other than Assassins that enter  
the zone for the first time on their turns or start their turn there must pass a systems check with 1  
difficulty/tier or become Jammed until the end of their next turn.
 

Explosive Knives  
Quick Action
 
Limited (3)
 
A knife can be thrown at any surface or mech as a quick action. Make a ranged attack roll for +2  
vs evasion/tier, attaching on hit. At the start of the assassin’s next turn, the knife explodes,  
dealing 6/8/10 explosive damage in a burst 2 area centered on the knife or mech. A mech can  
remove and disarm the knife by passing a successful systems check as a quick action if they are  
adjacent to it.
 

Tracker Missiles
 
Quick Tech
 
+2 vs e-defense/tier
 
The Assassin makes a tech attack vs e-defense against a target in sensor range. On hit, the  
target has the missiles latch on to them. While attached, the target cannot hide or benefit from  
invisibility, and the Assassin always knows its location up to a 10 mile distance. The missiles can  
be removed during a rest or by taking a quick action and successfully repeating this check.
 

Tier II:
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          15       8       7       +2   +3    +1    -1      1            8         12 

                                                                                                                


Tier III:
 

         Evade     E-D   Heat    H    A     S     E      Armor        Spd      Sense 

          17       8     7       +3   +4    +2   -1      2            8        12 

\subsection{Assault}
                                                ASSAULT  

Assault doctrine mechs and their pilots are the most common main battle chassis found throughout the  
galaxy. Fitted with a localized version of a main battle rifle, sidearm, and a suite of systems to enhance  

movement, targeting, and defensive systems, an Assault Doctrine chassis is a straightforward, reliable,  
hardy combatant.   

Assault doctrine pilots are the cheapest to train and outfit: this does not make them any less of a threat  
when paired with a kit of their choice.   

       ASSAULT 

       Mech 

       Hull       Agility      Systems       Engineering 

       +1         +1           +1            +1 

       HP         Evasion      E-defense     Heat Cap. 

       20         8            8             8 

       Armor      Speed        Sensors       Size 

       1          4            8             1 

Base systems:
 
Heavy Assault Rifle  
Main Rifle
 
Range 10
 
+2 vs evasion/tier with +1 Accuracy
 
7/9/11 kinetic damage
 

Combat Knife  
Auxiliary Melee
 
Threat 1
 
+1 vs evasion/tier
 
5/7/8 kinetic damage
 

                                                                                                           


Optional systems:
 
Underslung Grenade Launcher  
Auxiliary Launcher
 
Loading, Arcing
 
Range 8, Blast 2
 
4/6/8 explosive damage
 

Micro-missile Barrage
 
Quick action, Recharge (6+)
 
This mech makes a line 8 ranged attack with +1 vs evasion/tier for 6/9/12 explosive damage. The  
closest target hit by this missile barrage must pass a hull check or be knocked prone.
 
At tier II onwards, this hull check is made with 1 difficulty.
 

High Impact Rounds
 
System
 
The Heavy Assault rifle can be fired with high caliber rounds, adding +4 kinetic damage and the  
AP tag, but requiring a reload after firing it this way (as if it had the loading tag)
 

Auto-targeting  
System
 
The Heavy Assault rifle ignores the effects of light and heavy cover
 

Rank Discipline  
Trait
 
The Assault gains +1 Accuracy on all its attacks and checks as long as it’s adjacent to at least  
one friendly mech.
 

Tier II:
 
HP: +3
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          10       9      8        +2   +2    +2    +2      1            4        8 

Tier III:  
HP: +3
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          12        10    8        +3   +3    +3    +3      1            4        8 

                                                                                                               

\subsection{Barricade}
                                            BARRICADE  

 BARRICADE 

 Mech 

 Hull       Agility     Systems       Engineering 

 +0         -2          +1            +3 

 HP         Evasion     E-defense     Heat Cap. 

 16         6           9             10 

 Armor      Speed       Sensors       Size 

 1          4           10            1 

Base Systems:  
Cycle Lance  
Main Cannon
 
Range 10
 
+0 vs evasion with 1 Accuracy/tier
 
6 energy damage
 
This weapon can attack twice at tier III with the attack action
 

Mobile Printer  
Recharge (6+)  
As a free action at the start of its turn, the barricade may print a line 3 section of size 3 cover (3  
spaces high) in any adjacent and free space. The cover provides heavy cover and has evasion 5  
and 30 HP.
 

Shock Plating
 
System
 
The Barricade is resistant to kinetic damage
 

Optional Modules:
 
Drag Drone  
Quick Tech
 
+2 vs e-defense/tier
 
A target struck by this drone takes 2 AP energy damage for each 1 space that it voluntarily or  
involuntarily moves until the start of the Barricade’s next turn. The target is aware of this effect.
 

Seismic Repulsor  
Quick Action, recharge (5+)
 

                                                                                                       


All non-flying targets within a burst 3 area centered on the Barricade must pass a hull skill check  
with 1 difficulty/tier or be knocked back 3 space directly away from the barricade and knocked  
prone. The area in the blast then becomes difficult terrain permanently.
 

Rapid Extruder  
The Barricade can print twice as fast (can print two sections of cover at once)
 

Mag Mines  
Quick Action, Recharge 6+  
The Barricade rapidly prints and deploys a field of tiny mines that seek out targets and clamp on  
to them in droves, slowing them down and inhibiting movement. The mines take up a 5x5x5  
cube. The area is both difficult and dangerous terrain, and any target other than the Barricade  
that enters the area or starts its turn there must pass a systems check with 1 difficulty/tier or  
become Slowed the end of its next turn.
 

Snare Drone  
Quick Action, Drone
 
Limited (1)
 
The Barricade rapidly prints and deploys a snare drone in an adjacent space. This drone is size  
1, has 10 evasion and 10 HP. When any hostile mech moves within range 3 of the drone or starts  
its turn in range of the drone, it emits a pulse, immediately immobilizing that mech until the drone  
is destroyed (no check allowed).
 

Tier II:
 
HP: +3	
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          7         11     11      +1   -2    +1    +5      1            4         10 

Tier III:  
HP: +3
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          8         13     12      +2   -2    +2    +6      1            4         10 

                                                                                                                
\subsection{Bastion}

                                               BASTION  

Bastion doctrine chassis trade the pure defensive edge of an Aegis doctrine chassis for one that  
allows more mobility. Blending area-denial offensive capability with hardened defense systems  
and advanced communication suites, Bastion doctrine chassis make for strong squadron  
commanders.   

 BASTION 

 Mech 

 Hull       Agility     Systems       Engineering 

 +2         -3          +0            +2 

 HP         Evasion      E-defense    Heat Cap. 

 16         6           8             8 

 Armor      Speed       Sensors       Size 

 3          4           8             1 

Base systems:
 
Rotary Grenade Launcher  
Main Launcher
 
Arcing, Loading
 
+1 vs evasion/tier
 
Range 8, Blast 1
 
8/11/14 explosive damage
 

Heavy Assault Shield  
Heavy Melee
 
Threat 1
 
+1 vs evasion/tier
 
3 kinetic damage/tier
 
As a quick action, the Bastion can deploy or retract its shield as a line 2, size 2 piece of heavy  
cover, disarming it of this weapon. The Bastion can leave the shield deployed and move away  
from it if it so wishes (it can pick it up again as a quick action). Any mech that gains the benefit of  
this cover against an attack also has resistance to all damage from that attack. The cover has  
evasion 5 and 20 HP and can be attacked and destroyed as normal.
 

Optional systems:  
Shard Launcher
 
System, Reaction
 

                                                                                                         


The first time a Bastion takes damage in a round, all mechs in a cone (3) area in front of it must  
pass an agility check or take 5/7/9 explosive damage, and half on a successful save.
 

Shieldwall  
Trait
 
As long as it’s holding its shield, the Bastion and one adjacent mech of its choice has resistance  
to all damage from a target of its choosing that it can see. It can only change this target at the  
start of its turn.
 

Immortality  
System, Full Action
 
Recharge (5+)
 
The Bastion and one adjacent mech of its choice are immune to all damage and effects until the  
start of the Bastion’s next turn, guarded by a flickering pane of Blackshield tech. The mech  
adjacent to the Bastion loses this benefit if it breaks adjacency. On the start of the Bastion’s next  
turn, it is stunned until the start of its following turn and cannot gain or benefit from resistance or  
immunity of any kind for the same duration.
 

Defender  
Trait, Reaction
 
Once a round, when an allied mech is damaged, if the mech is in movement range of the Bastion  
and the bastion is not immobilized, it can immediately move adjacent to that mech and take that  
damage instead of the targeted mech. This movement doesn't provoke reactions and ignores  
engagement.
 

Hypo-reinforcement servos
 
System, Shield, Protocol
 
Recharge (4+)
 
The bastion activates this system at the start of its turn as a free action if it has it available. While  
active, it reduces all damage from the very next melee or ranged attack it takes to 0. This effect  
can only stack once.
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H     A     S     E       Armor        Spd      Sense 

          7         8      9       +4    -3    +0   +3       3            4        8 

Tier III:  

          Evade     E-D    Heat    H     A     S     E       Armor        Spd      Sense 

          7         8      10      +6    -2    +0   +4       4            4        8 

                                                                                                                 

\subsection{Berserker}
                                            BERSERKER  

Berserker doctrine mechs build to take advantage of advanced heat cycling systems to shunt  
system heat tax into an offensive force, increasing their weapon output by orders of magnitude.   

       BERSERKER 

       Mech 

       Hull      Agility      Systems       Engineering 

       +3         +2          -2            -1 

       HP         Evasion     E-defense     Heat Cap. 

       15         10          6             6 

       Armor     Speed        Sensors       Size 

       1          4           5             1 

Base systems:  
Chain Axe  
Heavy melee
 
+2 vs evasion/tier with
 
Threat 1
 
7/10/14 kinetic damage
 
This weapon deals an extra +1d6 damage/tier on Critical Hits
 

Volcanic Re-route
 
System, Protocol
 
The Berserker can choose to activate or de-activate this system at the start of its turns. While  
this system is active, the Berserker can make two attacks with its chain axe when it takes the  
attack action, but it takes 4 heat at the end of its turn.
 

Optional systems:  
Molten Shield  
System, Shield, Reaction
 
Once per round, the Berserker can activate this dispersal shield when it takes damage from any  
melee attack. The damage is reduced by half, and the attacker must pass an engineering check  
with 1 Difficulty/tier or take Burn 2/tier
 

Harpoon 
 
Main CQB
 
+1 vs evasion/tier
 

                                                                                                         


Range 5, Threat 3
 
2/4/6 kinetic damage
 
Targets struck by this weapon the same size or smaller than the Berserker are pulled in a straight  
line adjacent to the Berserker or as far as possible. If the target is pulled adjacent to the  
Berserker, the Berserker grapples them automatically.
 

Calamity module  
System, Full Action
 
The Berserker can only activate this system against a target it is grappling. Auxiliary strength  
servos engage and the Berserker hurls its target with incredible violence. The target must make a  
hull check with 1 Difficulty/tier. On a failed check, it takes 8/12/16 kinetic damage, is knocked  
back 4 spaces away from the berserker, and is stunned until the end of its next turn. On a  
successful check it takes the damage and knockback, but is not stunned. The Berserker ends its  
grab after making this move, success or failure.
 

Nail Gun  
Main CQB
 
+1 vs evasion/tier
 
Range 5, Threat 3
 
5/7/9 kinetic damage
 
Targets struck by this weapon must pass an engineering check with 1 difficulty/tier or become  
immobilized until the end of their next turn.
 

Hunter jets  
System, Reaction
 
Once per round, as a reaction to any enemy movement, the Berserker can make the boost  
action.
 

Tier II:
 
HP: +5
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          11       6      6        +4   +4    -2    -1       1           4         5 

Tier III:  
HP: +5
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          12       6      6        +6   +4    -2    +0       1           5         5 

                                                                                                                
\subsection{Bombard}

                                             BOMBARD  

The Bombard doctrine calls for unending salvos of punishing artillery bombardments. Chassis  
tuned to this style of combat are found miles behind the line in fortified positions, or otherwise  
removed from combat: one common strategy for prolonged area-denial bombardment is to place  
a battery of bombard chassis on a world’s local moon(s). From that movable satellite, the battery  
can rain FRAMEs down upon the world below, well removed from the dangers of combat. 
 

       BOMBARD 

       Mech 

       Hull      Agility     Systems       Engineering 

       +0        -1          +1            +2 

       HP        Evasion     E-defense     Heat Cap. 

       20        7            12           8 

      Armor      Speed       Sensors       Size 

       0         2            11           2 

Base systems:  
Bombard cannon  
Superheavy cannon  
Ordnance, Arcing, Loading
 
+2 vs evasion/tier with 1 difficulty
 
Range 20, Blast 2
 
10/14/18 kinetic damage
 

Stabilizers  
System, Full Action
 
As a full action, this mech can engage or disengage its stabilizers. While they are active, the  
mech cannot move or be knocked prone, but it gains +1 accuracy and +10 range on its attacks  
and cannot fire any weapons at a target within range 5 of itself. If this system is destroyed, the  
mech is immobilized.
 

Molded Armor  
System
 
The Bombard has resistance to explosive damage
 

Optional systems:  
H.A. Siege Shield  

                                                                                                       


System, Shield, Passive
 
The mech has resistance to all damage that it takes from attacks further away than range 5.
 

High-Impact shells  
Trait
 
The Bombard cannon gains knock back 3
 

LMG
 
Main Cannon
 
One or two targets
 
Range 10
 
+1 vs evasion/tier
 
4/6/8 kinetic damage
 

Cluster-seeker Bombs  
System
 
After the artillery fires its bombard cannon, 3 additional targets within range 10 of the primary  
target take 2 explosive damage/tier (no check or roll required).
 

Devastator Protocol  
Trait, Full Action, recharge (6+)
 
Choose 1d3 points within range of the mech, and mark them (so they are clearly visible to all  
players). The bombard must be activated last next round. At the start of its next turn, the mech  
fires at each of those points with its bombard cannon, as a free action, attacking all targets and  
structures within. It cannot choose these points so that the blast area from these attacks overlap  
in any way.
 

Tier II:
 
HP: +5
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          8        14     8        +1   -1    +2    +3      0            3        11 

Tier III:  
HP: +5
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          8        16     8        +1   -1    +3    +5      0            3        11 

                                                                                                                
\subsection{Breacher}

                                              BREACHER  

 BREACHER 

 Mech 

 Hull       Agility      Systems       Engineering 

 +2         +0           -1            +1 

 HP         Evasion      E-defense     Heat Cap. 

 18         9            7             8 

 Armor      Speed        Sensors       Size 

 1          4            5             1 

Base Systems  
Dual Shotguns  
Main CQB
 
+1 vs evasion/tier with 2 difficulty
 
Range 3, Threat 3
 
6/8/12 kinetic damage
 
The Breacher can attack twice with this weapon with the attack action, choosing the same or  
different targets.
 

BREACH Ram  
Quick action, Recharge (5+)
 
The breacher moves forward in a straight line as far as it can, up to its speed. It ignores  
engagement and obstruction (even for obstacles or mechs passed through). Obstacles or  
objects such as cover are punched or smashed through and take 10 AP kinetic damage/tier. If  
the obstacle is an especially hardy composition (such as a starship hull) the breacher can make a  
successful hull check to smash through instead. All other targets passed through must pass a  
hull check with 1 difficulty or be knocked out of the breacher’s path and knocked prone.
 

Optional Systems:
 
Unload  
Full Action
 
The breacher chooses a target in range of its dual shotguns. At the start of the breacher’s next  
turn, if the target is still in range, the breacher can attack that target with its dual shotguns with  
+3 Accuracy (for a total of +2 Accuracy by default) as a free action.
 

Loaded for Bear  
Trait
 

                                                                                                          


A target struck by both the Breacher’s Dual shotguns becomes shredded until the end of the  
Breacher’s next turn
 

Hunter Lock  
Quick Tech
 
+1 vs e-defense/tier with +1 Accuracy
 
The Breacher chooses a target in sensor range and makes a tech attack. On hit, all its attacks  
gain +1 accuracy/tier against that target, and 1/turn it can take the boost action as a Free Action,  
as long as it is made directly towards that target. The Breacher cannot change its target until it or  
the target is destroyed.
 

Thermal Charge  
Quick Action
 
Limited (1), Thrown 5
 
Blast 2
 
2/4/6 explosive damage + 5 Burn/tier
 

Hi Caliber Slugs  
The breacher takes 1 heat when its fires its dual shotguns, but they deal +3 damage
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          11        7      8       +3   +1    -1    +2       1           4         5 

Tier III:  
HP: +2
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          13        7      8       +4   +2    -1    +3       1           4         5 

                                                                                                                

\subsection{Cataphract}
                                            CATAPHRACT  

The Cataphract doctrine is common among rapid-strike kits that emphasize mobility, shock, and  
tenacity. Cataphract squadrons are feared across the galaxy for their ability to overwhelm  
defenses in moments: from an otherwise static line, a squadron of low and angular chassis burst  
overhead, heavy cannons and PDF guns carving seemingly impossible paths through a suddenly  
futile defense. 
 

 Cataphract 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         +1           +0            +0 

 HP         Evasion      E-defense     Heat Cap. 

 16         10           8             9 

 Armor      Speed        Sensors       Size 

 0          6            8             1-2 

Base systems:
 
Ram cannon  
Heavy Melee/Heavy Cannon
 
+0 vs evasion with 1 Accuracy/tier
 
Range 8, Threat 2
 
5/7/9 kinetic damage
 
This lance-like weapon can be fired with either profile (used as a melee or ranged weapon), but  
not both in the same turn.
 

Impact thrusters  
System, Full Action
 
Recharge (5+)
 
The Cataphract charges, moving 6 in a straight line in a direction of its choosing. It can ignore  
obstructions caused by enemies. Hostile targets that it passes through must pass a hull or agility  
check or take 2 kinetic damage/tier and be knocked prone.
 

Optional systems:  
Rotary Barrels  
System
 
1/round when the Cataphract hits with a Ram Cannon attack, it can repeat the attack roll against  
a different target in range with +2 difficulty.
 

                                                                                                          


Lance shot  
System, Full Action, Recharge (5+)
 
The Cataphract can fire a lance shell from its ram cannon. This changes the attack type of the  
weapon to line 10 and causes all affected mechs to pass an agility skill check to dodge the shot  
or become immobilized until the start of the Cataphract’s next turn.
 

High-speed targeting  
System
 
The Cataphract can make one Ram Cannon attack (melee or ranged) after taking the dash  
action, but takes 1 difficulty on the attack roll.
 

Point-defense shield  
System, Shield, Quick Tech
 
+2 vs e-defense/tier
 
The Cataphract makes a tech attack against a target in range. On hit, the Cataphract has  
resistance to all damage from that target. It can only have one actor effected at a time.
 

Capacitor discharge  
System
 
After the cataphract takes the boost action, all mechs it is adjacent to after the action completes  
take 2/3/4 heat.
 

Tier II:
 
HP: +4
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          11       8      9        +3   +2    +0    +0      0            7        8 

Tier III:  
HP: + 4
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          12       8      9        +4   +4    +0    +0      0            7        8 

                                                                                                                
\subsection{Demolisher}

                                            DEMOLISHER  

The prolonged siege of Jadigmora City saw the development of the DEMOLISHER patten. Based  
off the long-operational berserker doctrine, DEMOLISHER tuned the chaotic heat flow to a more  
sustainable, if limited system, increasing a chassis’ heavy-lift capacity to allow for supermassive  
kinetic weapons to be used effectively in combat. Combined with the increased pilot shielding  
and system hardening made necessary by the heat tuning, pilots soon discovered more  
aggressive applications for concussion-wave ordinance. 
 

 Demolisher 

 Mech 

 Hull       Agility      Systems       Engineering 

 +2         -2           +0            +2 

 HP         Evasion      E-defense     Heat Cap. 

 16         6            7             8 

 Armor      Speed        Sensors       Size 

 2          4            8             2 

Base systems:
 
Demolisher hammer  
Superheavy Melee
 
Threat 2
 
AP, Knockback 2
 
-2 vs evasion with 1 difficulty (no difficulty at tier II, +1 Accuracy at tier III)
 
13/18/25 explosive damage
 
This weapon deals double damage against structures, objects, the environment, and cover and  
gains +2 Accuracy against them.
 

Kinetic compensation  
System
 
If the Demolisher misses with its hammer attack, it gains +1 Accuracy on subsequent attacks  
until it hits. This effect stacks.
 

Optional systems:  
Broad-sweep haft  
Full Action
 
The Demolisher’s hammer can be used to make a sweep attack instead of a regular attack,  
attacking all targets in threat range (allied or enemy) for +1 vs evasion/tier, 4/6/8 explosive  
damage. Targets struck by this attack are impaired until the start of the Demolisher’s next turn.
 

                                                                                                          


Concussion missiles  
Quick Action
 
A target in range 8 must pass an engineering check with 1 difficulty/tier or be knocked back 3  
spaces and impaired until the start of the Demolisher’s next turn.
 

Seismic Destroyer
 
System, Full Action, Recharge (6+)
 
The Demolisher’s hammer can be used to make a special attack that hits cone 3 or line 5 from  
the Demolisher instead of its regular attack. This attack cannot hit flying targets. Targets in the  
area must pass a hull or agility skill check or be stunned until the end of the Demolisher’s next  
turn.
 

Shatter module  
Trait
 
The Demolisher’s hammer strikes against prone, immobilized, or stunned targets gain the AP tag  
and can Critical Hit, dealing +1d6 bonus damage/tier on Critical Hits
 

Knockout Blow  
Trait, Quick Action, Recharge 6+  
A target adjacent to the Demolisher must pass a hull or agility check with 1 difficulty/tier or  
become stunned until the end of the Demolisher’s next turn.
 

Tier II:
 
HP: +4
 

          Evade     E-D    Heat    H     A     S     E       Armor        Spd       Sense 

          6         7      8       +4    -2    +0    +3      3            4         8 

Tier III:  
HP: +4
 

          Evade     E-D    Heat    H     A     S     E       Armor        Spd       Sense 

          6         7      8       +6    -2    +0    +4      3            5         8 

                                                                                                                  

\subsection{Engineer}
                                              ENGINEER  

Engineer doctrine chassis are common throughout the galaxy, their patterns unique to the world  
or theater in which they operate, but their charge the same: defend, maintain, secure. Engineers  
operate best in the mid to rear of the line, coordinating the defense of important positions and  
ensuring total operational deployment of all mission assets. Remember: if your chassis can’t  
make it to the line, you lose.
 

 Engineer 

 Mech 

 Hull       Agility      Systems       Engineering 

 -1         -1           +1            +3 

 HP         Evasion      E-defense     Heat Cap. 

 20         7            11            12 

 Armor      Speed        Sensors       Size 

 0          3            15            1 

Base systems:
 
Flak Cannon  
Heavy Cannon
 
Smart
 
+1 vs e-defense/tier
 
Range 15
 
5/7/9 kinetic damage
 
This weapon gains +1 Accuracy against flying targets. Flying targets damaged by this weapon  
must pass an agility check or fall.
 

Deployable turret  
System, Drone, Quick Action, Recharge (4+)
 
The engineer deploys a self-building turret in an adjacent, open space. The turret is an immobile  
size 1 drone with simple AI that attacks the nearest hostile target. It has evasion 10, 10 HP, and 1  
armor. It attacks on the Engineer’s turn for +1/tier vs evasion, range 10, 2/3/4 kinetic damage,  
but can take no other actions.
 

Ablative Shielding
 
System
 
The Engineer has resistance to energy damage
 

                                                                                                          


Optional systems:  
Power deployer  
System
 
The Engineer can deploy two turrets when it uses its deployable turret system
 

Arsenal  
The Engineer can deploy stronger turrets, and three different types of turrets, and can choose  
which to deploy when it uses its system. Each have the same statistics as a base turret, with the  
following changes:
 
         Inferno: The turret’s weapon becomes +1/tier vs evasion, cone 5, Burn 3/4/5
 
         Hellstorm: The turret’s weapon becomes +1/tier vs evasion, range 15, blast 1, 2/3/4  
         explosive damage
 
         Hunter: The turret’s weapon gains the smart tag
 
         Primed: When the turret or the engineer is destroyed, it explodes in a burst 1 area around  
         it. Targets caught inside must pass an agility check or take 7/9/11 explosive damage
 

Skyshield protocol  
System
 
The Engineer’s deployable turrets gain +1 accuracy against flying targets.
 

Point Defense Drone  
System, Drone, Quick Action, Recharge (5+)
 
The engineer deploys a drone in an adjacent space which creates a burst 1 zone around it. The  
engineer can only deploy one drone at a time. While inside this zone, targets allied to the  
engineer are immune to weapons with the Seeking and Smart tags. The drone can be attacked  
and destroyed, though it benefits from its own zone.
 

Tracking Computer  
System, Reaction
 
Once per round, the Engineer’s Flak Cannon can be fired once as a reaction to any boost action  
or movement outside of regular movement by a hostile mech it can see.
 

Tier II:
 
HP: +2
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

          9        12     12      -1   +0    +2   +4       0           3        15 

Tier III:  
HP: +2
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

          11       12     12      -1   +0    +3   +6       1           4        15 

                                                                                                             
\subsection{Hive}

                                                   HIVE  

A recent development following the Deimos Contact Event, Hive doctrine chassis are, in theory,  
not too different than their pre-Contact cousins: they establish a local, secure omninetwork,  
fabricate and deploy a century or half-century of drones, and coordinate them in achieving their  
mission. The difference between pre-Contact and post-Contact drone controllers is ease: pilots  
who pursue this doctrine establish complex handler-trainer relationships with their hives, allowing  
them to segue between direct control and autonomous operation unimpeded by tactile interface.  
Hive pilots exhibit signs of psychological trauma at one month continuous drone-strain operation,  
and it is recommended that they practice a strict two-week format cycling with their paired hive.   

 HIVE 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         -1           +2            +0 

 HP         Evasion      E-defense     Heat Cap. 

 20         8            10            8 

 Armor      Speed        Sensors       Size 

 0          5            15            1 

Base systems:  
Hunter Killer Drone Nexus
 
Main Nexus
 
Smart, Seeking
 
Range 15
 
+2 vs e-defense/tier
 
7 energy damage
 
This weapon can attack twice at tier III with the attack action
 

Drone Barrage
 
Quick Tech
 
+2 vs e-defense/tier with +1 accuracy/tier
 
The Hive directs its drones to run interference on a target of its choice. On hit, the target is  
Slowed and Impaired until the start of the hive’s next turn.
 

Optional systems:
 
Electro-Nanite Cloud  
System
 

                                                                                                          


All hostile targets that start their turn within range 3 of the Hive take 2 Burn/tier. In addition, any  
system checks they make or tech actions they make in that area suffer from +1 Difficulty/tier.
 

Grinder Drones  
Drone, System
 
Quick Tech
 
+2 vs e-defense/tier with +1 Accuracy/tier
 
The Hive releases a swarm of tiny, hard to hit drones that attach to a target within range 15,  
making a tech attack. On hit, the target takes Burn 4/6/8. The Hive can only have one target  
attacked by these drones at once.
 

Razor Swarm  
Drone, System, Quick Action, Recharge 5+
 
The Hive creates a blast 2 area within sensor range. The area remains until the end of combat or  
the Hive is destroyed. Targets allied to the hive can use the area for light cover. Otherwise, any  
target that starts its turn in the area or moves into it for the first time on its turn takes 3 Burn/tier.  
The Hive can deploy any number of Razor Swarms.
 

Swarm Shield  
Quick Action, Recharge 6+
 
The Hive releases a cloud of miniature drones that cluster around it, providing heavy protection.  
The Hive has resistance to damage from the next 1d6 attacks.
 

Seeker Cloud  
Main Nexus
 
Smart
 
+0 vs e-defense with 1 Accuracy/tier
 
Cone 5
 
3/4/5 Kinetic Damage
 
Targets damaged by this weapon gain the Lock On condition.
 

Tier II:
 
HP: +4
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

         9         12     8       +2   -1    +4   +0       0           5        20 

Tier III:  
HP: +4
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

          10       14     8       +3   -1    +6   +0       0           6        25 

                                                                                                             
\subsection{Hornet}

                                                HORNET  

 HORNET 

 Mech 

 Hull       Agility      Systems       Engineering 

 -2         +2           +2            +0 

 HP         Evasion      E-defense     Heat Cap. 

 10         15           8             5 

 Armor      Speed        Sensors       Size 

 0          8            10            1/2  

Base Systems:  
Stinger Pistol  
Auxiliary CQB
 
Range 8, Threat 3
 
+1 vs evasion/tier with +1 accuracy/tier
 
2/3/4 energy damage
 
Targets critically hit by this pistol are impaired until the end of the hornet’s next turn.
 

SSC Total Suite  
The Hornet can fly when it moves or boosts with hover flight.
 

Impale Systems  
Quick Tech, Recharge 5+
 
+2 vs e-defense/tier
 
On hit, the target takes 3 heat/tier and becomes jammed until the end of the hornet’s next turn.
 

Optional Systems:  
Evade Suite  
Trait
 
The Hornet ignores engagement and is immune to grapples
 

Minor Basilisk  
Trait
 
The first attack a target misses against the Hornet per turn deals 2 heat/tier to the attacker.
 

Interdictor Suite
 
Reaction
 

                                                                                                           


1/round the Hornet can use a reaction to attempt to electronically jam a target in its sensor range  
that is attempting to make an attack roll. The target must pass a systems skill check or lose its  
attack roll (it can still make other attacks as normal). The difficulty of this test increases by 1  
difficulty at tier II onwards.
 

HEX missiles
 
Auxiliary Launcher
 
Smart
 
+0 vs e-defense with +1 Accuracy/tier
 
Range 10, Blast 1
 
3/4/5 heat
 

Drag Javelin  
Full Action
 
The Hornet fires a javelin at a target it can see within range 10. The target must pass a hull check  
with 1 difficulty/tier or become impaled by the javelin. Upon impact, the javelin fires a secondary  
grapple at the environment, tethering the target to the ground. While impaled this way, the target  
is immobilized and shredded. It can end this condition by repeating the check as a quick action  
on their turn to pull the javelin out.
 

Tier II:
 

          Evade     E-D    Heat    H     A     S     E       Armor         Spd      Sense 

          17        8      6       -2    +4    +3    +0      0             10       10 

Tier III:
 

          Evade     E-D    Heat    H     A     S     E       Armor         Spd      Sense 

          20        9      7       -2    +6    +4    +0       1            12       10 

                                                                                                                  

\subsection{Marker}
                                                MARKER  

Marker doctrine calls for the active, close, and aggressive application of orbital, atmospheric, and  
terrestrial fire support on identified and potential enemy positions. Equipped with more-than- 
cursory targeting systems, Marker doctrine pilots adopt an tactical/artillery commander role,  
operating on the ground with infantry, chassis, and other vehicles to build a map of the  
battlescape in order to more accurately place small arms fire, bombs, shells, missiles, beams, and  
kinetic kill clouds. They are not usually a threat in face-to-face combat, but the threat they  
represent to a combat cannot be underestimated.   

       Marker 

       Mech 

       Hull       Agility     Systems       Engineering 

       -2         +2          +3            -1 

       HP         Evasion     E-defense     Heat Cap. 

       14         12          10            8 

       Armor      Speed       Sensors       Size 

       0          6           20            1/2 - 1 

Base systems:
 
High Caliber Pistol  
Auxiliary CQB
 
+2 vs evasion/tier
 
Range 8, Threat 3
 
3/4/5 kinetic damage
 

Target Marker  
Main rifle
 
Smart
 
+1 vs e-defense/tier with 1 Accuracy
 
Range 20
 
Targets hit by this attack immediately gain Lock On and are Shredded while they suffer from  
Lock On. They then cannot turn invisible or benefit from invisibility, and cannot hide until the end  
of the Marker’s next turn. If the Marker is destroyed or this weapon is disabled, immediately end  
this condition.
 

Optional systems:  

                                                                                                          


Orbital Strike  
System, recharge 5+
 
Instead of firing the target marker at an enemy, the Marker can fire it at a point within range 30.  
At the start of the Marker’s next turn, that area is hit by an orbital strike. Any mechs still in a burst  
3 area centered on that point must pass an agility check or take 12/17/22 energy damage and be  
knocked prone, or half and no prone on a successful check.
 

HOUND missile
 
Quick Action, Recharge (6+)
 
Choose a target within range 20. The marker fires a hound missile at the target, which is size 1/2,  
has evasion 10, and 10/15/20 HP. The missile primes on the turn that it is fired, deploying in an  
adjacent space, then moves 3 at the start of each of the marker’s turns. If its target suffers from  
the Lock On condition, its movement increases to 6. The missile can benefit from cover, counts  
as flying with hover flight, and can be targeted and shot by systems and weapons. It must move  
towards its target, but can maneuver skillfully around cover, fit through holes, etc. If the missile’s  
movement causes it to collide with a hostile mech or its target, it detonates for a blast 1  
explosion. Mechs caught inside must pass an agility skill check or take 15/20/25 energy damage  
and half on a successful check.
 

Blind  
Quick Tech, Recharge (4+)
 
+2 vs e-defense with +1 Accuracy/tier
 
On hit, the target only has line of sight to adjacent squares until the end of its next turn.
 

Rebound Scan  
System, Full Action
 
All targets in range 10 of the marker must pass a systems check or immediately lose the benefit  
of all cover, hiding, and invisibility and be unable to take cover, hide, or turn invisible until the  
start of the Marker’s next turn.
 

Smart Missile Cloud  
System
 
At the start of the marker’s turn, one target suffering from Lock On in the Marker’s sensor range  
takes 4/5/6 explosive damage from the Marker, no roll required.  

Tier II:
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          15        13    8        -2   +4    +4    -1      0            7         20 

Tier III:  

          Evade     E-D    Heat    H    A     S     E       Armor        Spd       Sense 

          18        16    8        -2   +5    +6    -1      0            8         20 

                                                                                                                
\subsection{Operator}

                                              OPERATOR  

Operator doctrine chassis are a known-unknown. Operators typically field smaller chassis not  
commonly encountered on the front lines; do not mistake this for fragility. Pilots who are recruited  
and trained into this doctrine, regardless of culture, are dangerous, deadly, the best of their  
state’s armed forces or martial tradition. They operate alone or in small teams under the auspices  
of black-site state agencies, engaging in the most sensitive and dangerous AMNESIAC-tier  
missions. Their chassis — and their bodies — are loaded with some of the most advanced tech  
available; if they die in combat, it is not uncommon for their bodies and their chassis to self- 
immolate, rendering what technology and data they had into waste and ash. 
 

 OPERATOR 

 Mech 

 Hull       Agility      Systems       Engineering 

 +2         +2           +2            +2 

 HP         Evasion      E-defense     Heat Cap. 

 14         10           10            9 

 Armor      Speed        Sensors       Size 

 0          4            10            1 

Base systems:
 
‘Raptor’ plasma rifle  
Heavy Rifle
 
+2 vs evasion/tier
 
Range 15
 
8 energy damage
 
This weapon can attack twice at tier III with the attack action
 

‘Nightcloak’ type omnishield  
System, Shield
 
While this system is active, the operative has resistance to one of the following types of damage:  
kinetic, explosive, energy, heat. The operative must decide which when it starts combat (setting it  
is a Free Action) and cannot change it during combat.
 

Self-erasing  
Trait
 
When this mech is destroyed, it immediately self-immolates into superheated plasma. All targets  
adjacent to it when it is destroyed must pass an agility check or take 4/6/8 energy damage or  

                                                                                                           


half on a successful check. This mech is then removed from the battlefield - it is utterly  
annihilated.
 

Optional systems:  
Fade generator  
System
 
While this system is intact, at the end of its turn, the Operative becomes invisible until the start of  
its next turn. This effect is immediately disabled if the Operative takes damage until the start of  
the Operator’s next turn.
 

Refractive shield  
System, Shield
 
This system is permanently disabled if the operative overheats. While it is active, the operative  
gains the Hardened Target trait (scans, lock on attempts, and invasions against it are made at +1  
difficulty).
 

Skirmisher implant  
System
 
Once at any point on its turn, the operative can make a boost action as a free action.
 

Nova missile  
Auxiliary Launcher
 
Smart, Seeking
 
+1 vs e-defense with 1 Accuracy/tier
 
Range 30, blast 1
 
4/6/8 energy damage
 

Trace Drive  
System
 
Once on its turn, when the Operative moves or boosts, it instead teleports up to 8 spaces away,  
as long as its target destination is a free space. This movement does not provoke reactions and  
ignores engagement, such as overwatch.
 

Tier II:	
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          12       12     9       +3    +3    +3    +3      1            4        10 

Tier III:
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          14       14     9       +4    +4    +4    +4      2            5        10 

                                                                                                               
\subsection{Pyro}

                                                   PYRO  

A combat doctrine adopted following the Hercynian Crisis, the Pyro chassis-pattern is reviled  
across the galaxy as a terror instrument, though some states and organizations still choose to  
integrate them into their armies. Pyro doctrine chassis are heavily armored and insulated, built to  
manage incredible heat tax while projecting volatile mixes of irrepressible flame towards their  
enemies. Pyro chassis are sent in to root out entrenched defenders, defoliate areas rich in flora,  
and cause terror. 
 

 PYRO 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         -1           -1            +3 

 HP         Evasion      E-defense     Heat Cap. 

 12         8            8             15 

 Armor      Speed        Sensors       Size 

 3          3            8             2 

Base systems:
 
Flamethrower  
Heavy CQB
 
Cone 5
 
+1 vs evasion/tier
 
4 heat (self)
 
Burn 5/7/9 + 2/4/6 heat
 

Explosive Vent
 
System, Full Action
 
The pyro cools to 0 heat. Targets caught in a burst 1 area around it must pass an engineering  
check or take half of the heat the pyro cools as heat to themselves and be knocked prone.
 

Optional systems:  
Insulated Plating  
The pyro has resistance to heat and energy damage (including its self inflicted heat). It is immune  
to Burn
 

Unshielded Reactor  

                                                                                                           


Targets that start their turn adjacent to the pyro or become adjacent to the pyro for the first time  
on their turns take 1 heat/tier.
 

Napalm Bomb  
Main Launcher
 
Arcing, Loading
 
-1 vs evasion with +1 Accuracy/tier
 
Range 8, Blast 1
 
Burn 3/4/5 + 2/4/6 heat
 

Rigged fuel rod launcher  
Heavy Launcher
 
-2 vs evasion with +1 Accuracy/tier
 
Knockback 1
 
Range 10
 
4/6/8 heat
 

Explosive Jet  
System, Quick action, recharge (5+)
 
Enemies in a burst 2 area around the Pyro must pass a hull or agility check or be knocked back  
outside of that area and knocked prone. The Pyro then flies 5 in any direction, but it must land  
after completing that move.
 

Tier II:
 
HP: +3
 

          Evade    E-D    Heat    H     A    S     E       Armor        Spd      Sense 

          8        8      15      +2    +0   -1    +4       3           3         8 

Tier III:  
HP: +3
 

          Evade    E-D    Heat    H     A    S     E       Armor        Spd      Sense 

          8        8      15      +3    +0   +0    +5       4           3         8 

                                                                                                               
\subsection{Rainmaker}

                                             RAINMAKER  

The tongue-in-cheek designation describes a combat doctrine that patterns chassis around the  
optimal use of rockets and missiles in combat. Favored by all-theater combat units, Rainmakers  
are mobile platforms loaded with ordinance, able to handle engagements at any range, against  
any target. 
 

       RAINMAKER 

       Mech 

       Hull       Agility     Systems       Engineering 

       +0         +1          +2            -1 

       HP         Evasion     E-defense     Heat Cap. 

       15         8           10            8 

       Armor      Speed       Sensors       Size 

       1          2           15            2 

Base systems:
 
Thundershock missile pods
 
Main launcher
 
Arcing, Knockback 1
 
+2 vs evasion/tier
 
One, two, or three targets in range 15
 
3/4/5 explosive damage
 

‘Drang’ missile rack
 
Heavy launcher
 
Ordnance, Loading
 
Line 15
 
+1 vs evasion/tier
 
8/11/14 explosive damage
 

Optional systems:  
HADES missile
 
Quick Action, Recharge (5+)
 
The rainmaker targets a cone 3 area drawn in any direction from a point within range 20 of its  
location. This system tracks line of sight as if it were an arcing weapon. All targets in that area  
must pass an agility check or take 3/5/7 energy damage and 2/4/6 heat, and half on a successful  
check.
 

                                                                                                          


Rigged payload  
System
 
When the rainmaker is destroyed, it explodes in a burst 2 explosion centered on itself. Targets  
caught within must pass an agility check or take 8/12/16 explosive damage, and half on a  
successful check.
 

Volley  
System, Full Action, Recharge (5+)
 
All hostile targets within range 30 of the rainmaker must pass an agility check or take 4/6/8  
explosive damage, or half on a successful check. This system tracks line of sight as if it was a  
seeking weapon.
 

Huntsman  
Trait
 
While firing at a target suffering from the Lock On condition, the rainmaker’s weapons gain the  
Smart and Seeking tags.
 

Atlas missile  
Superheavy launcher
 
Ordnance, Arcing
 
Range 30
 
This weapon system replaces the Drang Missile rack. Instead of targeting a mech, the rainmaker  
instead targets a space on the ground within range. The targeted area is visible to all in line of  
sight. At the start of its next turn, the missile lands, targeting a burst 2 area centered on that  
space. All targets caught within must pass an agility check or take 15/20/25 explosive damage,  
and half on a successful check.
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd      Sense 

          11        11    8        +0   +2    +3    +0      1            2        20 

Tier III:  
HP: +2
 

          Evade     E-D    Heat    H    A     S     E       Armor        Spd      Sense 

          12        12    8        +0   +3    +4    +1      2            3        20 

                                                                                                                
\subsection{Ronin}

                                                  RONIN  

Ronin doctrine chassis differ from Berserker and DEMOLISHER pattern chassis in that they have  
been purpose-built by boutique fabricators to excel in melee combat. Ronin patterns are  
common among martial cultures and event-combat firms both. Tactical applications for Ronin  
chassis are difficult in cultures where ranged weapons are preferred, but there is a certain  
prestige earned by pilots who adopt ancient weapons in the modern day and survive. That being  
said the availability of stasis and mag based defensive technology has made the Ronin doctrine  
marginally more viable in modern combat. 
 

 RONIN 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         +2           -1            -1 

 HP         Evasion      E-defense     Heat Cap. 

 18         10           7             8 

 Armor      Speed        Sensors       Size 

 0          5            12            1 

Base systems:  
Carbon Fiber Sword  
Main Melee
 
+2 vs evasion with 1 Accuracy/tier
 
Threat 1
 
6 kinetic damage
 
This weapon can attack once per tier (up to 3 times at tier 3) with the attack action
 
This weapon can Critical Hit, and deals an extra +1d6 kinetic damage on Critical Hit
 

Mag Parry  
System, Shield, Reaction
 
Once per round, when damaged by a ranged weapon, the Ronin can roll a d6. On a roll of a 5+,  
the Ronin gains resistance to all the damage from that attack, and the target must repeat the  
attack roll against itself, dealing damage on a success.
 

Optional systems:  
Charged Slash  
Full Action, recharge (5+)
 

                                                                                                          


All targets adjacent to the Ronin must make a successful agility check or take 8/12/16 kinetic  
damage, and half on a successful check.
 

Reflex Implant  
System
 
When the Ronin boosts, attackers gain +2 Difficulty to attack it until the start of the Ronin’s next  
turn.
 

Echo Edge  
System
 
When the Ronin damages a target, it marks that target (keep track of it). At the start of its turn,  
the Ronin can consume all these marks as a free action to deal 1d6 AP kinetic damage to all  
targets, no attack roll required. They last until consumed, until the Ronin is destroyed, or until the  
end of the current challenge.
 

Hyper-reflex mode  
System, Quick Action, Recharge (5+)
 
This system remains active until the end of the Ronin’s next turn. While active, the first time each  
turn (the Ronin’s turn or any other actor’s turn) the Ronin is targeted by an attack, it can  
immediately make a Carbon Fiber Sword attack against a target in range before the attack is  
made.
 

Extended Blade  
The Ronin’s Carbon Fiber Sword becomes threat 2. The first time it critically hits with a melee  
attack on a turn, all targets within its threat take 3/4/5 kinetic damage including the target of its  
attack.
 

Tier II:
 
HP: +2
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          13       7      8        +2   +4    -1    -1      0            5        12 

Tier III:  
HP: +2
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          16       7      8        +4   +5    -1    -1      0            6        12 

                                                                                                                
\subsection{Scourer}

                                              SCOURER  

SCOURER doctrine mechs mount massive-output recursive power plants in order to field deadly  
energy weapons. A common specialist-role doctrine, SCOURER chassis are found on fronts  
across the galaxy, supporting kinetic-focus ground troops with powerful lensing attacks that  
target not only corporeal enemies, but systemic threats. 
 

 SCOURER 

 Mech 

 Hull       Agility     Systems       Engineering 

 +1         +0           0            +1 

 HP         Evasion      E-defense    Heat Cap. 

 16         9            8            10 

 Armor      Speed       Sensors       Size 

 1          4            10           1 

Base systems:
 
Thermal Lance  
Heavy Cannon
 
2 heat (self)
 
+0 vs evasion with +1 Accuracy at tier II and +2 Accuracy at tier III
 
Range 8
 
6/8/12 energy damage
 

Cooling Module  
System  
If the Scourer did not move or boost at all this turn, it reduces its heat to 0
 

Optional systems:  
Crystal Lense  
Once the Scourer hits a target with the Thermal Lance, on subsequent turns it can choose to  
focus down that target instead of firing normally. As a full action from the Scourer, that target  
takes 6/9/12 Burn, no roll required. This effect breaks if the target gains cover from the Scourer,  
the scourer is stunned, this weapon is disabled or destroyed, or the target moves out of range.  
The target is aware of this effect.
 

Supercharged
 
Trait
 

                                                                                                         


Targets struck by the thermal lance are shredded until the end of the scourer’s next turn.
 

Pulse Laser
 
Main Cannon
 
+2 vs evasion/tier
 
Line 10
 
4 energy damage
 
This weapon can attack twice at tier III
 

Flash Lense  
System, Quick Action, Recharge (6+)
 
The Scourer targets a cone 5 area in a direction of its choosing. All targets in the area must pass  
a systems check or be jammed until the start of the Scourer’s next turn.
 

Melt  
System, Quick Action, Recharge (5+)
 
The scourer targets a piece of cover, terrain, or deployable, then makes an attack roll, dealing  
10/20/30 AP energy damage on hit.
 

Tier II:
 
HP: +2
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          10       8      12       +2   +1    +0    +3      1            4        10 

Tier III:
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          10       8      12       +3   +1    +1    +4      2            4        10 

                                                                                                                
\subsection{Seeder}

                                                SEEDER  

Seeders are sapper chassis, adept at building defensive nets of mines and traps for point defense  
and aggressive area denial. Laden with ordinance, pilots who adopt Seeder doctrines operate in  
small teams to blanket the battlefield in clouds of fire and shrapnel, placing their launched  
grenades and explosive-tipped FRAMEs with pinpoint accuracy. 
 

 SEEDER 

 Mech 

 Hull       Agility      Systems       Engineering 

 +0         +0           +2            +0 

 HP         Evasion      E-defense     Heat Cap. 

 15         7            10            10 

 Armor      Speed        Sensors       Size 

 2          4            15            1 

Base systems:
 
Grav Grenade Launcher  
Main Launcher
 
Arcing
 
+2 vs evasion/tier
 
Range 10, blast 1
 
2/3/4 explosive damage
 
This weapon deals 5/7/9 damage if it catches more than 1 target in its blast
 

Mine Deployer  
System, free action, recharge (4+)
 
The seeder lays a mine in a space within range 3 of it. It cannot place a mine adjacent to another  
mine. The mine arms at the end of the round. Once armed, the next target other than the seeder  
to become adjacent to it must pass a systems check or trigger the mine. That target, and any  
caught in a burst 1 area centered on the mine must pass an agility check or take 10/15/20  
explosive damage, and half on a successful check.
 

Optional systems:  
Smart Tagging
 
System
 
The seeder’s mines only detonate automatically if there is a hostile target in range (not allied).  
Furthermore, the seeder can choose to stop their detonation as a reaction.
 

                                                                                                          


Grav Mine  
System, Quick Action
 
A target in range 5 and line of sight to the Seeder must pass a systems check or have a mine  
attached to them. They can disarm the mine by taking a quick action and successfully repeating  
this check. The seeder can detonate any grav mines at the start of its turn as a free action,  
causing any affected mech to take 3/5/7 explosive damage, no attack roll required, and be  
knocked 3 spaces in a direction of the Seeder’s choosing.
 

Anti-Infantry mine  
Trait
 
If the seeder chooses, it can lay an anti-infantry mine with its mine deployer. This mine affects a  
burst 3 area instead of burst 1 and deals 1/2/3 explosive damage, but 4/6/8 to targets with the  
biological tag.
 

Grav Lash
 
Quick Tech
 
+2 vs e-defense/tier 
 
On hit, the target is knocked back 5 spaces in a direction of the Seeder’s choosing.
 

Seeker Mines  
System, Full Action, recharge (5+)
 
The seeder fires small seeker mines at one to three targets of the seeder’s choice in range 5 and  
line of sight. Those targets must pass a systems check or have a mine latch on to them. At the  
start of the seeder’s next turn, the mines explode for a burst 1 explosion on the target for 3/5/7  
explosive damage.
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          8         10     10      +1    +0   +3    +1       2            4        15 

Tier III:  
HP: +2
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          9         11     10      +2    +0   +4    +2       2            4        15 

                                                                                                                 
\subsection{Sentinel}

                                              SENTINEL  

Sentinel doctrine chassis fill guard roles. Typically found in the retinues of commanders or posted  
in defense of batteries, Sentinel chassis employ a suite of technology that ensures their charges  
stay alive and operational, even if it means the Sentinel’s death. 
 

 SENTINEL 

 Mech 

 Hull       Agility     Systems       Engineering 

 +2         +1           +0           -1 

 HP         Evasion      E-defense    Heat Cap. 

 20         9            9            8 

 Armor      Speed       Sensors       Size 

 0          5            8            1
 

Base systems:  

Combat Shotgun  
Main CQB
 
Range 3, Threat 3
 
+2 vs evasion/tier with 1 Accuracy
 
7/9/12 kinetic damage
 

Retractable Sword  
Main Melee
 
Threat 1
 
+2 vs evasion/tier
 
4/6/9 kinetic damage
 

Eye of Midnight
 
System, Quick Action
 
This system can be activated or deactivated as a quick action, and remains indefinitely. While  
this system is active, the Sentinel is Slowed, but is not limited in the number of overwatch  
reactions it can make per round.
 

Optional systems:  

Punisher Ammunition  

                                                                                                         


System
 
The first enemy damaged by the Sentinel’s combat shotgun each round must pass a engineering  
heck with 1 difficulty or be Slowed until the end of the sentinel’s next turn.
 

Wrath-lock  
System, Full Action
 
The sentinel may arm this module as a full action. While armed, the next time it fires its combat  
shotgun, it makes 3 attacks instead of one.
 

Impaler  
System
 
The first enemy damaged by an overwatch shot from the Sentinel must pass an agility check  
with 1 difficulty or immediately stop moving and become immobilized until the end of the  
sentinel’s next turn.
 

Watchful  
Trait
 
Once per round, in response to any enemy movement, the Sentinel can make the boost action as  
a reaction.
 

Guardian protocols
 
Trait
 
At the start of its turn, the Sentinel can nominate an allied mech within range 5. Once per turn  
(but any number of times per round) when that mech is targeted by an attack, the Sentinel can  
immediately make a single attack for free against the attacker if it is in range as a reaction.
 

Tier II:
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          11        11     8       +3    +2   +1    -1       1            5        8 

Tier III:  
HP: +4
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          13        13     8       +4    +2   +4    -1       1            6        8 

                                                                                                                 
\subsection{Sniper}

                                                 SNIPER  

Sniper pattern chassis are common throughout the galaxy’s armies. Favoring stability and  
targeting over mobility, Snipers operate extremely long-ranged kinetic weapons in small, self- 
sufficient teams well removed from any direct combat. Sniper pilots are a proud breed, who  
emphasize economy and elegance over destructive power. Their weapons are often as tuned and  
modified as much as their chassis are; the pilots themselves often exhibit unparalleled control  
over their targeting systems. Partnered NHPs are said to send boast-data between themselves,  
noting the difficulty of landed shots to allied pilots. 
 

 SNIPER 

 Mech 

 Hull       Agility      Systems       Engineering 

 +0         +1           +2            -1 

 HP         Evasion      E-defense     Heat Cap. 

 15         10           10            6 

 Armor      Speed        Sensors       Size 

 0          4            15            1 

Base systems:
 
Anti-Material Rifle  
Heavy Rifle
 
Loading, Ordnance, AP
 
+1 vs evasion/tier with +2 Accuracy/tier
 
Range 30
 
10/15/20 kinetic damage
 

Auto-pistol  
Auxiliary CQB
 
+0 vs evasion with +1 Accuracy at tier II, +2 Accuracy at tier III
 
Range 8, Threat 3
 
3/4/5 kinetic damage
 

Deathmark protocol  
System, Full Action
 
The Sniper marks a target within range 20. While marked, the Sniper’s anti material rifle attacks  
against that target causes it to take 1 structure damage on hit instead of dealing damage  
normally (causing the target to make a structure check and reset its HP). The Sniper can only  
have one mark active at a time, but can transfer it if need be. The target can avoid this effect if it  

                                                                                                          


is in any kind of cover, or if it’s prone (it is aware of this effect), and instead takes damage  
normally.
 

Optional systems:
 
Defensive Grapple  
System, Quick Action, Reaction, Recharge (4+)
 
The Sniper chooses a point within range 5 (vertical or horizontal) and pulls itself to that point with  
a grappling hook as if it had flown. It can use this as an action on its turn or a reaction to an  
enemy’s movement that it can see.
 

Climber  
Trait
 
The sniper can climb any surface with no penalty and walk or stand on such surfaces as if they  
were flat ground, even overhanging or vertical surfaces. 
 

Selective Loader  
System
 
The Sniper can fire one of several types of ammunition, choosing one before it attacks:
 
	        Impact: Targets hit by the AM rifle must pass a hull check or be knocked prone
 
         EMP: Targets hit by the AM rifle must pass a system check or be Jammed until the end of  
         their next turn
 
         Flare: Targets hit by the AM rifle cannot hide or turn invisible until the end of their next  
         turn
 
         Molten: Targets hit by the AM rifle must pass an engineering check or become Shredded  
         until the end of their next turn.
 

Over-penetrating Round  
System, protocol, recharge (6+)
 
The Sniper loads an over-penetrating round into its anti-material rifle. Its next attack with the rifle  
becomes Line 30.
 

Flash Bomb  
System, Quick action, recharge (6+)
 
The sniper fires a bomb at a blast 2 area within range 5 of it. Targets other than the Sniper caught  
inside must pass a systems check or become Slowed and jammed until the end of their next  
turn. The area counts as light cover until the start of the sniper’s next turn
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H    A     S     E        Armor        Spd      Sense 

          13        10     6       +0    +2   +3    +0       0            4        15 

                                                                                                                 


Tier III:  
HP: +2
 

           Evade       E-D     Heat     H      A     S      E         Armor          Spd        Sense 

             16         12     6          +0    +3     +4    +1        0              4          15 

.  

                                                                                                                                  
\subsection{Spectre}

                                               SPECTRE  

Spectre doctrine chassis emphasize the ability not to be hit over pure defensive shielding.  
Employing cutting-edge optical and systemic camouflage, Spectres vanish from the battlefield  
and all active/passive scans, flickering in and out of vision and shattering their image and radar  
signatures, confusing the eye and the sweep.Their weapons do not mark their doctrine: their  
power comes from the ability to operate unseen. 
 

 SPECTRE 

 Mech 

 Hull       Agility      Systems       Engineering 

 -2         +2           +1            +1 

 HP         Evasion      E-defense     Heat Cap. 

 10         10           10            7 

 Armor      Speed        Sensors       Size 

 0          6            10            1/2-1 

Base systems:  

Machine pistol  
Auxiliary CQB
 
+2 vs evasion/tier
 
Range 5, Threat 3
 
6 kinetic damage
 
This weapon can attack twice at tier III with the attack action
 

ATHENA-class scan  
System, quick action, recharge (4+)
 
One target in range 10 of the specter’s choice must make a systems skill check (the specter can  
guess they are there and doesn’t need line of sight). If they fail, they are revealed from hiding and  
lose the benefits of hiding or invisibility and cannot hide or turn invisible until the start of the  
spectre’s next turn.
 

Tactical Cloak
 
System
 
The spectre is permanently invisible while this system is intact.
 

Optional systems:  

                                                                                                          


Combat subroutine  
Trait
 
A targets that fails their check against the spectre’s Athena-Class scan system gain the lock on  
condition.
 

Fortress  
Trait
 
The spectre gains the Fortress trait (lock on, invasion, and scans are made against it at +3  
difficulty). To electronic systems, it doesn’t appear to even be there.
 

System flayer  
Trait
 
Targets that fail their check against the spectre’s Athena-Class scan system immediately suffer  
from Lock On.
 

Weakness analyser  
System
 
The specter’s attacks from hiding gain an additional +1 Accuracy/tier and gain the ability to  
Critical Hit, dealing +1d6 kinetic damage on Critical Hit
 

Cloaking Field  
System, full action, recharge (6+)
 
The spectre deploys a cloaking field, affecting a burst 3 area around it. All allied mechs in that  
field become invisible while inside the area. The field deactivates at the end of the spectre’s next  
turn.
 

Tier II:
 

          Evade     E-D     Heat    H     A     S     E        Armor        Spd       Sense 

          11        11      7       -2    +3    +3    +1       0            6         10 

Tier III:
 

          Evade     E-D     Heat    H     A     S     E        Armor        Spd       Sense 

          12        12      7       -2    +4    +5    +1       0            6         10 

                                                                                                                     
\subsection{Support}

                                               SUPPORT  

Support doctrine chassis focus their systems towards keeping their allies combat operational.  
Alloy cement, nanite paste, patch plates, vacuum seals — the tools vary, but the result is the  
same: you may be messed up, but you’re up, and you can keep fighting because the Support  
kept you alive. 
 

 SUPPORT 

 Mech 

 Hull       Agility      Systems       Engineering 

 +1         -1           +0            +2 

 HP         Evasion      E-defense     Heat Cap. 

 20         7            10            10 

 Armor      Speed        Sensors       Size 

 1          4            12            2-3 

Base systems:  

Suppressive cannon  
Main cannon
 
Ordnance
 
+2 vs evasion/tier
 
Range 10
 
6 kinetic damage
 
This weapon can be fired an additional time at tier III with the attack action
 
Targets damaged by this cannon suffer from the impaired condition until the end of their next  
turn
 

Latch drone  
System, Recharge (5+)
 
As a free action, the support fires a drone to a point within range 5 of its position, where it  
hovers. The drone can be attacked and destroyed. It is a size 1 drone with evasion 10 and 10 HP.  
The drone clamps on to the next allied mech to move through or adjacent to that drone’s space  
and discharges, healing that mech 5/7/10 HP.
 

Optional systems:
 
Remote reboot  
Trait, Full action
 

                                                                                                          


The support immediately ends 2 of the following conditions on an allied mech within range:  
impaired, jammed, shut down, Slowed. 
 

Nano-repair cloud  
System, Full Action, recharge (5+)
 
The support creates a blast 2 area within range 5 of its location. Allied targets that start their  
turns in the area or move through it for the first time can gain 4/5/6 HP. The cloud disperses at  
the start of the support’s next turn.
 

Defensive pulse  
System, Full action
 
The support makes a systems skill check with +1 Accuracy/tier. If it is successful, all mechs  
within range 5 of the support can immediately end the Jammed and Lock on conditions on  
themselves.
 

Manual Repair
 
System, Full Action, recharge (5+)
 
The support targets an adjacent mech or vehicle and makes an engineering skill check. If the  
check is successful, that mech can repair up to 4/6/8 HP and also to repair up to 1 destroyed  
system, returning it to functionality.
 

VULCAN drone  
System, Drone, Full Action, Recharge (6+)
 
The support chooses another mech within range 5 of its position, then fires a self-deploying  
drone at that mech. The drone is a size 1 object with evasion 10, 10 HP, and 1 armor. The drone  
clamps on to the targeted mech. At the start of each of its turns, while the drone is deployed on  
that target, that target can heal 3/4/5 HP. In addition, it gains +1 Accuracy on all checks and  
attacks. The drone can be shot off and destroyed.
 

Tier II:
 
HP: +5
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          7        11     10       +1   -1    +1    +4      1            4        10 

Tier III:  
HP: +5
 

          Evade    E-D    Heat     H    A     S     E       Armor        Spd      Sense 

          8        12     10       +1   -1    +2    +6      1            4        10 

                                                                                                                

\subsection{Technical}
                                              TECHNICAL  

Technicals lean into the incredible tumult of systemic warfare, operating both in realtime and  
among the omnicloud tempest that descends upon a combat theater. Technicals often pair with  
personality-clone NHPs — NHPs that structure profiles based on profiles of their pilots — to  
handle the chaotic swirl that results from realtime/omninet combat splitting.   

 Technical 

 Mech 

 Hull       Agility      Systems       Engineering 

 -1         +1           +2            +0 

 HP         Evasion      E-defense     Heat Cap. 

 12          12          12            8 

 Armor      Speed        Sensors       Size 

 0          5            10            1/2 -1 

Base systems:
 
Autogun  
Auxiliary rifle
 
Smart
 
Range 10
 
+2 vs e-defense/tier
 
6 kinetic damage
 
This weapon can attack twice at tier III with the attack action
 

HORUS hacker  
Trait
 
This mech makes tech actions with +1 Accuracy and its invasions deal +1/2/3 heat on hit.
 

Snap Fire  
Trait, Quick Action
 
This mech makes one autogun attack
 

Optional systems:  

Predatory logic
 
Quick Tech, Recharge (5+)
 
+2 vs e-defense/tier with +1 Accuracy
 

                                                                                                           


On hit, the target immediately makes an attack with a single weapon of the technical’s choice  
against any other target within range (even an allied target).
 

Puppet system  
Quick Tech
 
+2 vs e-defense/tier 
 
On hit, the target is impaired until the end of its next turn. In addition, the technical can  
immediately cause that target to move up to its speed in a direction of the technical’s choice.
 

SCORPION protocols  
System
 
The technical gains the hardened target trait (invasion, lock on, and scan are made at +1  
difficulty). In addition, any failed invasion, lock on, or scan attempt on it inflicts 2/3/4 heat to the  
attacker.
 

Illusory subroutines  
Quick Tech
 
+2 vs e-defense/tier 
 
On hit, all actors allied to the Technical count as invisible to the target until the start of its next  
turn.
 

System link  
System, Quick Action
 
The Technical links systems with an allied mech within its sensor range. It can only link with one  
mech at a time. While linked, the allied mech gains +1 Accuracy/tier, and the allied mech can use  
the Technical’s systems score for all checks it makes. However, if either linked mech becomes  
jammed or impaired, the other also suffers the same condition for the same duration as long as  
the link persists. The link is disabled if either mech is destroyed or this system is disabled or  
destroyed.
 

Tier II:
 
HP: +2
 

          Evade     E-D    Heat    H     A    S     E        Armor        Spd      Sense 

          14        15     8       -1    +2    +4   +0       0            5         10 

Tier III:  
HP: +2
 

          Evade     E-D    Heat    H     A    S     E        Armor        Spd      Sense 

          16        18     8       -1    +3    +6   +0       0            5         10 

                                                                                                                 


                                     GENERIC OPTIONAL MODULES:  

Any of the above NPCs can choose one of these modules when choosing an optional module.
 

Armored  
Trait  
This mech gains +1 armor, up to a maximum of +4
 

Boosted Reactor  
Trait
 
This mech gains +2 heat capacity
 

Jump Jets  
System
 
This mech can Fly when it boosts
 

Reinforced  
Trait
 
This mech gains +5 HP
 

SSC Core Flight System  
System
 
This mech can Fly when it moves or boosts and has perfect flight (it doesn’t need to land). It  
generates 2 heat/turn while this module is active at the end of each of its turns.
 

Tactical Cloak  
System, Quick Action
 
This mech becomes invisible. If it takes an action, reaction, or overheats it loses this invisibility  
until the start of its next turn.
 

                                                                                                                
