\section{Pilot Actions}
   PILOT ACTIONS  

Pilots can take the following actions : BOOST, HIDE, SEARCH, ACTIVATE, DISENGAGE,   
PREPARE, OVERWATCH, BOOT UP, SHUT DOWN, MOUNT/DISMOUNT  
These are the same as the mech actions.
 

They also get the following actions:
 
\subsection{Fight}
                                      FIGHT (FULL ACTION)  
Make a melee or ranged attack with one weapon against a target in line of sight and range.
 
\subsection{Jockey}

                                    JOCKEY (FULL ACTION)  
It is possible (though very foolhardy) to aggressively attack an enemy mech while on foot. To  
jockey a mech as a pilot, you must be adjacent to it. You must make a contested check with the  
mech, using GRIT (your GM could allow another skill, such as maneuver, flash, or brawl if you  
argue for it). The mech contests with hull. If you win the contest, you’re now riding the mech,  
sharing its space and moving when it moves. The mech you’re riding can shake you off by  
repeating the contest successfully as an action, and you can jump off as part of your movement  
any time. 
 

Attempting to jockey takes a full action. The turn you successfully jockey, you can choose one of  
the below for free, and repeat one each turn after that you continue to jockey as a full action.
 

Distract: You inflict the Impaired or Slowed condition on your target until the start of your next  
turn.
 
Shred: Deal 2 heat to your target by ripping at wiring, paneling, etc
 
Damage: Deal 4 kinetic damage to that mech by firing or slashing at joints, hatches, etc
 

                                                                                                           

