\section{The Pilot}
  THE PILOT   

Your pilot is the person inside the machine, and who you will be playing as for your entire career.  
A pilot’s general skill and access to gear is tracked by License Level (from 0-12). Your pilot  
typically starts at level 0, an inexperienced rookie, and levels up once they complete a  
mission.  

                                                                                                         
\subsection{Pilot Skills}

                                                   Pilot Skills  

A pilot’s skills refer to a pilot’s general experience, proficiency, personal ability, and aptitude with  
particular approaches or courses of action. They don’t have to necessarily describe physical  
qualities of your pilot.  

They go from +0 to +6. This number is a flat bonus applied to a pilot skill check (a check used to  
describe your pilot’s personal abilities or aptitudes) to get the final result when the skill triggers.  

A skill trigger (or just the skill itself) tells you when you can get that bonus. This is pretty simple in  
practice. If your pilot gets +2 when blowing something up, if your goal ever involves setting off  
explosives, throwing grenades, setting charges, etc, you get that skill bonus.   

Your pilot skills are used for narrative actions and generally don’t get used during mech combat.  

                                                Tracking Bonuses
 

You don’t actually have to write down skills you don’t have any sort of bonus to. It’s just a flat  
1d20 vs 10 roll with situational accuracy or difficulty applied otherwise. For example, at level 0, a  
pilot might write down ‘+2 to threaten, get somewhere fast, assault, and spot’. There’s no reason  
to write down or track the rest!
 

                                                        Skills  

Here’s the list of skills, which are thematically grouped here to help you choose. Each bolded  
word or group of words describes a skill and when that skill would trigger, giving you a bonus on a  
skill check. You get 4 of these at level 0, each at +2.  

Your pilot’s ability to use, resist, and apply direct force, physical or otherwise:  

Get a bonus when:  
          - You’re applying fists to faces  
          - You’re assaulting a position, person, or group of people (in battle or otherwise), hard,  
         fast, and up close  
          - You want to blow something up  
          - You’re forcing someone’s hand by threatening them  
          - You want to take control of something (an object, a captive, the situation)  
          - You want to survive through harsh or unforgiving conditions  

Your pilot’s ability to perform skillfully and accurately under pressure:  

Get a bonus when:  
         - You want to stay cool and collected while performing an action that takes skill or                          
         precision  

                                                                                                                      


         - You want to take someone out, cleanly  
         - You want to perform some flashy action, like shooting an apple off someone’s head  
         - You want to get somewhere fast, on foot or in a vehicle  
         - You want to act unseen and unheard  

Your pilot’s ability to notice details, think creatively, and prepare:  

Get a bonus when:  
         - You want to fix, hack, or wreck a system or device or patch a bleeding wound  
         - You want to invent or create something with tools and supplies  
         - You want to read a situation for subtext, motive, or threat  
         - You want to spot hidden details, track a target, make out distant objects, or observe with   
         an eagle eye  
         - You want to investigate, research a subject, or look at something in great detail  

Your pilot’s ability to talk, lead, change minds, make connections, and requisition  
resources  

Get a bonus when:  
         - You want to charm an audience with your words or actions  
         - You want to pull rank on someone  
         - You want to get word on the streets  
         - You want to get a hold of useful allies, assets, or connections  
         - You want to lead or inspire allies, troops, or a whole organization  

There’s a little more detail on each of these uses in the Narrative Play section below  

\subsection{Backgrounds}
                                               Backgrounds  

Your background describes your life up until you became a mech pilot. A background does not  
necessarily describe your pilot’s role in the squadron now — a background tells your GM and  
fellow players a bit about what your pilot did before they enlisted. Think of backgrounds as a  
prompt for you to draw from when describing your pilot’s full backstory: how did they first  
become a soldier, a doctor, or a miner (or whatever your background may be), and from there  
how did they become the pilot they are now? 
 

When you make a background, you can either roll 1d20 for one of the backgrounds in the  
compendium, choose a background from that same list, or simply make your own up.
 

At level 0, choose four skills above based on your background. 
 
Then choose two of the four skills you just chose. You have a speciality in those skills, giving  
you +1 Accuracy on top of your flat bonus. These are things you are especially good at, that  
your background has given you an edge in.
 

                                                                                                                 


Finally, choose any two other skills that you didn’t choose in your original four. These skills are  
flawed for you and get +1 difficulty when you make a relevant pilot skill check that uses those  
actions. These are things your character is unpracticed at or has some difficulty performing,  
based on their background, personality, or personal abilities.
 

Your background bonuses generally never change, but if you and your GM feel like part of your  
background is no longer relevant or has changed significantly, you can change the bonuses  
around during downtime. Having a flawed skill does not prevent you from training that skill when  
you level up, mitigating your background.
 
\subsection{Creating a Pilot}
                                              Creating a pilot  

Making a pilot at level 0 is as simple as the following:
 

     1.  Create a background: When you create a pilot at level 0, you’ll need to make up a  
         background for your pilot - where your pilot comes from. You can create your own  
         background, or roll or choose from the list of backgrounds in the compendium.
 
    2.   Set pilot skills: Choose four triggers at +2
 
    3.   Set background bonuses: Based on your background, choose two skill triggers. You get  
         a specialty in those skills, giving you +1 Accuracy. Then choose two others that you didn’t  
         choose in step 2. These skills are flawed, giving you +1 difficulty.
 
    4.   Write down HP, e-defense, speed. and evasion: Your pilot has HP (hit points), how much  
         damage you can take before you’re down and out, and evasion and e-defense, how  
         hard it is to hit you with weapons and electronic systems in mech combat. You also have  
         speed (how far you move in spaces when you move). At level 0 that’s 6 HP, 10 e- 
         defense, 10 evasion, and 4 speed. More on the importance of these stats in the mech  
         combat section.  
    5.   Before you embark on a mission, you’ll choose pilot gear, which might change your  
         stats. More on that in the mission section. You can take clothing, armor, up to two  
         weapons, and two other pieces of gear. Gear can be acquired from the compendium, and  
         you can’t take gear that has a total rarity greater than your level. All General Massive  
         Systems gear is level 0, allowing any pilots (even license level 0 pilots) access to it.
 

Advancement:  
          - Each time you level up, you can increase one of your existing skills by +2, to a maximum  
         of +6, or gain a new skill at +2.  
          - Every 3 levels, you can gain a new specialty. If you gain a specialty in a flawed skill, it  
         cancels out, leaving it a normal skill.  
         - A pilot can add 1/2 their level (grit) to their HP and attack rolls in mech combat  
         - Your pilot’s total gear they can bring with them on a mission is limited by license level  

                                                                                                                  


                                                                                            
 