\section{Players on a Galactic Scale}

Players On A Galactic Scale  

The galaxy is unimaginably vast, and few if any states (or state-analogs) have any  
impact on the inexorable tides of history, event, and future that humanity -- as a species -- is  
influenced by, feels, and faces.   

Some of the states and state-analogs listed here do.    
\subsection{General Massive Systems}
General Massive Systems  

         What does it look like when there is no end to your empire?   

         When the weapons your enemies use against you bear your mark. When the children of  
         the next revolution are born to lands administered by your machines. When the ships that  
         convey their children across the void bear your name.   

         Power is not held by kings. All rulers tumble alongside Ozymandias.   

         Only the company persists, all others thrones fall to dust.      

             -   Introductory paragraphs to King of Kings: An Oral History of General Massive  
                 Systems  

The oldest and most ubiquitous of the Big 5, General Massive Systems (GMS) is an all-purpose  
supplier to all persons in Union’s hegemony. From mech chassis and ship hulls to casual clothing,  
from prefab space station bulkheads to coffee beans, GMS’s catalogue reaches across a galaxy  
worth of goods, materials, and services. GMS is widely viewed as the reliable baseline of goods  
quality across the galaxy: anything worse than GMS quality is junk, anything better tends to be  
unique or luxury.   

GMS began as an independent outfitter during the first expansion period that grew to ubiquity as  
the outward colonial push afforded by nearlight drives surged. Union saw value in controlling what  
was seen as the industry standard supplier, and nationalized GMS. The corporate entity became  
an arm of Union’s ever expanding bureaucracy, a way to standardize equipment and  
consumables across the rapidly growing class of explorers, colonists, and scientists venturing out  
into the stars.   

As colonial expansion continued and competitor corporations emerged onto the galactic supply, a  
baseline of equipment was needed in order to assess what improvements needed to be made to  
Cradle-specific gear; similarly, dramatic time dilation was far more of an obstacle in those early  
days than it is in the narrative present, and some standard, legacy-compatible equipment was  
needed in order to assure compliance across disparate eras.   

                                                                                                                


Thus, with the incredible wealth of Cradle behind it, General Massive Systems became that  
ubiquitous supplier. Over thousands of years, it has grown to become a massive department of  
Union, and the standard against which all others are measured. GMS is an economic engine, one  
of a large toolbox, by which Union promotes their “brand” across the galaxy. Distinct from Union’s  
political and military arms, GMS is an ever-present flexing of soft power: it is ubiquitous to the  
point of being the “normal” standard by which most all universal goods are judged by.   

GMS, unlike the other entities listed in this section, does not engage in worldbuilding, colonial  
ventures, or expeditions -- it sets the standard for which all others build from and supplies them  
with the gear they need. It creates the world of goods, services, equipment, and habitations most  
humans know to be “normal”. GMS’s power comes from its ability to set what the galactic  
acceptable standard is: by nudging that bar ever up, it forces non-Union entities to develop  
alternatives that benefit humanity as a whole, even if they are developed for selfish, profit-driven  
motives.   

GMS rarely reaches out to outside contractors for work. Its headquarters is on Cradle proper, like  
the rest of Union’s Central Command, and it has offices throughout the inhabited galaxy.  
\subsection{Harrison Armory}
Harrison Armory  

         “What good is it to mourn the dead without celebration in equal? And in this I do include the  
         great works, torn down by those without the courage to face what must be done. What do  
         tears mean to them?  

         I say to you, beloved all, there is no need for grief in isolation. To have died in this great  
         service is to rise as a martyr and carry on the crimson banner of progress. I envy those  
         honored dead, who see now all things, who now possess the wisdom hidden to us -- the  
         living guard -- despite the wonders we command.   

         Moreover, I envy their repose: to mark the wonders of the present is to make known the  
         wonders left unbuilt, the wonders yet-to-come, and the wonders denied to us. We living  
         have the great task before us: to turn our helm to the wind, and make known our intent.   

         We will continue. We will build, as our race has done since we were bent-back apes. The  
         stars may be held by others, but we know that the soul of humanity is held by us. Our  
         dream is that which beats in the breast of all: let us shape the stars, and bring about a day  
         where we have no more need for martyrs.   

         No howling masses ever overcame the might of hope.”  

                      -   Excerpt of Foundation Day speech, 4515, John Creighton Harrison I,  
                          Director-General of Harrison Armory.   

Harrison Armory is a corpro-state, and the premier weapons and weapon-platform manufacturer  
in the galaxy. They are one of the Triumvirate Corpros, a group of three massive, galaxy-spanning  
corpro-states that dictate, to a degree, galactic politics.   

                                                                                                                 


The Armory develops some of the most advanced conventional and paracausal tech that is legally  
distributed. Next to GMS, the Armory is the second most common supplier for state fleets,  
militaries, and police forces. It is a massive imperial power, with a population numbering in the  
billions and growing as colonies pledge themselves -- voluntarily or otherwise -- to Ras Shamra.   

The Armory’s success can be credited in large part to their Special-Exception Persistent- 
Cultivation Legionspace Environment, SEPCLE or, colloquially, the Think Tank. Think Tank is a  
choir of near-cascade NHP that the Armory uses for research and development into paracausal  
technology, forecasting, and department management. Due to the Armory’s special relationship  
with Union, it is allowed to run a choir of NHP at critical levels of self-awareness; the Think Tank is  
a closely guarded secret in the Armory, known in rumor to its patrician citizens and competitors,  
but in specifics and particulars to a small portion of the population.   

In addition to their weaponry and weapon platforms, the Armory is known for its sturdy exploration  
gear, consumer and state-level logistics and infrastructure packages, personal groundcars, and  
spirits. Harrison Armory is a big player in galactic trade, as their Distal Development program  
cultivates and exports exotic alien spices, flora, fauna, and minerals for consumer use.    

Harrison Armory is an expansionist corpro-state that works with Union to expand and develop  
humanity’s presence across the stars. They run a broad program of colonization and  
development, attracting unaffiliated and affiliated colonies through promises of citizenship and  
interstellar protection. 
 

In the tumult of the dissolution of the Second Committee in the 4500U, many members of the  
deposed anthrochauvinist party retired from the bureaucracy. As the initial revolutionary fervor  
cooled and the Third Committee stabilized, a mid-level Anthrochauv party officer, John Creighton  
Harrison, founded Harrison Armory from a coalition of resource extraction communes extant on  
Ras Shamra. 
 

With strong backing from old Anthrochauv party members and their children, the Armory grew  
into a significant supplier of arms and armor to the new Union Navy. The events of the Crisis had  
broken the Second Committee, but its aftermath reformed many of their loyalists and old guard  
into the original command structure and dynasty of Harrison Armory. Now, the Armory is  
managed by their descendants and heirs, and its relationship with Union is colored by the  
expectation of distant future friction. 
 

For the time being, both entities can find more benefit working together than against one another,  
but as the Armory grows in directly-administered territory and power, the more they find  
themselves a bigger and bigger bullet point on the Union Central Committee briefing materials. 
 

Harrison Armory’s eponymous armory complex is located on Ras Shamra, the primary world  
orbiting Ptah’s Star. Ras Shamra is a tide-locked world in the close band of its system’s habitable  
zone: it is a world that balances on the knife-edge between extremes, as tidal locking means the  
world does not rotate. Habitable in the balanced, temperate zone of the world’s terminator line,  
Ras Shamra’s sun-facing side is locked in perpetual daylight, baked under punishing  
temperatures from Ptah’s Star. On the side of the world that faces away from the sun, it is forever  
nighttime, the world locked in a perpetual deep winter night. A thin atmosphere covers the world,  

                                                                                                           


breathable, but outside the terminator line extreme temperatures and weather make it impossible  
for an unshielded human to survive. 
 

The Armory itself is a sprawling administrative, research-industrial arcology built in Ras Shamra’s  
terminator line, a temperate band where the day and night side of Ras Shamra meet and mix.  
The Armory circles the planet, a city-campus that holds a population of nearly three hundred  
million employees, executives, and other personnel inside of its walls. A number of perpetual  
hyperloop rings band the planet, providing rapid transit through the Armory, and a single, artificial  
river-sea meanders through the whole of the arcology, fed by natural springs and imported  
glacier-cuts from the night side of the world. Ras Shamra is a difficult world to live on, and the  
Armory takes it as a point of pride that they’ve manage to tame enough of it to call it their home.  
 

The day and night sides of Ras Shamra act as proving grounds for Harrison Armory chassis,  
weapons, and strike/acquisition teams. HA/AT troopers often mark their kits with “unofficial”  
honors for having proven themselves in both the day and night advanced training courses,  
setting themselves apart from green hires who enlist to advance their corporate political career.
 

Ras Shamra is encircled by concentric rings of orbital defense stations and shipyards where a  
population around a hundred million permanent residents reside and work. Here the great  
paracausal and supermassive weaponry of the Armory is built, tested, and stored. The work in  
the rings is constant, and HA hulls of all classifications are churned out at a rate that, while not  
rivaling IPS-N, is approaching comparable. 
 

The location of Harrison Armory’s Forecast/GALSIM-NHP analogue, the Think Tank, is kept  
secret, though presumed to be buried deep below the frozen tundra of Ras Shamra’s night side.  
Think Tank, while a closely guarded corpro secret, is known to Union, which enjoys regular  
inspections of the facility -- this is a thorn in the side of Harrison Armory’s Director General, who  
would prefer that Union keep their prying eyes from sensitive corporate technology. 
 

The general public on a core world -- a good measure of what amounts to “public galactic  
knowledge” -- would not have any knowledge of the particulars of Ras Shamra, Think Tank, or  
the particular operations of a Harrison Armory Acquisition Team. They would know Harrison  
Armory as a weapons manufacturer and defense contractor, whose name they hear in snippets  
of newscasts discussing Cradle politics, distal colonial affairs, and mentioned in contrast to IPS- 
N’s stranglehold on interstellar shipping. Some who have studied the history of Cradle and Union  
might know of the Armory’s ties to the anthrochauvinist Second Committee, but five hundred  
standard years after the fact, it certainly feels like old news. 
 
\subsection{Harrison Armory - Example Flashpoint: Operation Clarion  }
Harrison Armory - Example Flashpoint: Operation Clarion  

In the narrative present, the Armory is prepping to send a second wave of AMTs and eager  
colonial officials out to a developing coreward colonial expanse, the Dawnline Shore. The  
Dawnline Shore is home to a dozen close-knit colony worlds, first seeded hundreds of years ago  
by a series of now-defunct colonial operations ordered by the great, great grandfather of the  
current Director-General. Construction of a local system blink gate has just finished, and now the  
current DG of the Armory is eager to integrate these colonial prospects into the ever-growing  
territory of the Armory. 
 

                                                                                                           


The dozen worlds, designated DS1 - DS12 by the Armory are rich with rare and valuable metals  
that the Think Tank has identified as useful for expansion into paracausal research and  
development. Additionally, the worlds are thick with the usual suite of tremendous mineral, floral,  
and faunal wealth that perpetuates the Armory’s growth. On all levels, from the mundane-but- 
necessary to the fantastic and rare, these worlds in the Dawnline Shore are jewels to gild the  
Armory’s throne -- and meat to feed its never-ending appetite.
 

The Armory expects their AMT forces to encounter hostile resistance: communication over the  
past few hundred years indicates that the colonies are animated by a series of colonial  
independence movements, aware of their position in space and potential wealth in their land.  
These movements are on the cusp of unifying into a system-wide resistance to the Armory, and  
with the news of a fresh wave of colonial troops inbound, the call for unification only grows  
louder. 
 

Meanwhile, the descendants of the initial wave of AMT legionnaires have been activated across  
the twelve worlds. Old colonial NHPs are rising from dormancy, sounding the call to post.  
Families are torn between two loyalties: their ancestral duty to the Armory, and their lived home.  
 

The Armory cannot afford to lose the resources on these worlds, and is preparing an aggressive  
colonial expedition to secure them. The Armory has partnered with IPS-N, who has been focused  
on managing Union’s logistics in the expanse as the hegemon built the new blink gate, but  
diplomatic relations are strained between the CSs as institutional attitudes begin to collide.
 

This flashpoint -- Operation Clarion, the Armory’s mission name -- is an example of a current  
project that the Armory is wrestling with in the narrative present. Your players could take either  
side in this flashpoint, or enter it from a third angle as-yet unwritten. 
 
\subsection{Smith-Shimano Corpro}
Smith-Shimano Corpro  

         “There is a thread that runs through the course of humanity. An unbroken course,  
         set eons ago, and maintained through every age by careful stewards.   

         You.   

         Through the dawn of the anthropocene to its end. The Dark Age. The Little Wars.  
         From Union’s foundation to this office, right here, right now.   

         You already contain perfection; we have the ability to enhance it.   

         Welcome to the future of humanity: you, brought to you by Smith-Shimano Corpro.”    

             -   Smith-Shimano background copy, subaural broadcast loop  

                                                                                                            


Smith-Shimano Corpro is another of the Triumvirate Corpros, the smallest and most mission- 
focused of the three, with their physical territorial holdings dwarfed by their presence in the  
omninet and in Diasporan biologies. 
 

SSC came to prominence during the second expansion period, growing rapidly to dominate the  
Core market in Union’s liberal, pre-RA transhumanist approach to biological and cybernetic  
enhancement. Following the Deimos Event, the RA Accords, and the ensuing crackdown on AI  
generation and civilian ontologic/singularity-focused experimentation, SSC tacked to a more  
“natural” approach to biological and cybernetic human enhancement. Instead of pursuing  
marriage between human and artificial intelligences, they would focus on improving the bodies  
we lived in; instead of removing the need to step to the stars, they would make it so we could  
step to the stars. 
 

SSC’s corporeal development pushes the edge of what it means to be a human being.  
Cybernetic enhancements, subdermal nettings, aurals, implanted neuroneutral omnihooks,  
ontologic bridges, co-subjectivity nodes, panacea glands -- the list is exhausting, and that only  
covers the Foreign Body department of SSC’s massive R\&D campus-worlds. The real bulk of  
SSC’s cutting edge research comes in the form of their own citizens, a population of billions  
spread across a constellation of moons, worlds, stations, and habitats. These populations are  
monitored and cultivated to produce best-fit genetic material for SSC’s big manna buyers:  
colony firms looking to license bespoke populations for as-yet-unexploited worlds. 
 

Smith-Shimano Corpro’s home campus is an omnispace node address, a shared virtual space  
that collects a wide net of colony prospect words throughout the Sierra Madre line. It is shielded  
by layers of hyper-solipsistic, anticausal/paradox generation security coding, managed by NHPs  
seeded from proprietary divergent subjectivities — in short, it is difficult and dangerous to  
attempt to hack into. 
 

The campus itself is represented by a many-chambered estate, palatial, where the heads of  
representative genetic lines meet in virtual space. It appears to have no counterpart in realspace,  
though it is often suggested that the architectural inspiration for the estate comes from a building  
on Smith-Shimano’s first colony world, Opal, long ago lost to bitter civil violence.  
 

Realspace Smith-Shimano campuses exist across the Sierra Madre line, serving roles akin to  
embassies on the Corpro-State’s many territorial holdings. These embassies are upload points  
linked to the CS’s private omninode.
 

The worlds under SSC’s direct control are, generally, small worlds -- atmospheric moons and  
arcadian worlds that are lightly developed, with tightly controlled populations that are purpose- 
bred in arranged couplings in order to create biome-specific lines of bespoke colony seed. The  
people on these worlds are aware of SSC’s mission -- they are citizens of the corpro state, most  
invested in the same mission as their corporate masters. Save for a donation of genetic material  
(a few hairs, a drop of blood) and a cultural insistence on arranged coupling, life on a  
Constellation World is largely similar to that of life on a given non-SSC core world. 
 

                                                                                                            


SSC mounts expeditions into all sectors of space to seek out new and interesting genetic  
materials. Their recruitment materiel leans heavily on the benefits for immigrating to an SSC  
world: they are, in a phrase, your ideal paradise. 
 

SSC is also known for their luxury-forward consumer goods and machinery. Elegant ships,  
chassis, and hardsuits for the discerning Cosmopolitan and Diasporan alike. Fabrics and  
materials that feel perfect against your skin, cybernetic and biological enhancements that will  
never fail or be rejected by your body, flash-grown internals and extremities -- insurance, should  
the worst happen. SSC’s LUX line of consumer goods is bespoke down to the atom, crafted for  
the person who ordered that ship, chassis, suit, or bottle of wine. There’s only one of you in the  
galaxy -- shouldn’t there be only one of these?  
 

The average galactic citizen sees SSC as a luxury brand that emphasized attachment to the craft  
and expertise that creates the material world around them. SSC’s advertisements emphasize the  
hand-crafted nature of their goods, the long-cycle growth of their biologicals -- to SSC’s public  
face, printing is a necessary evil, one that can make the goods the masses need, but not the  
perfect, unique item you need. 
 

SSC’s power comes from the licensing of these luxury goods, cybernetics, and biological lines.  
They do not cede control over their genestock to the colony firms that use them: in fact, they  
retain ultimate rights over them, as they rely on the risk of other corporations, states, and private  
groups to inject new and interesting mutations into their finely cultivated genelines.  
 
\subsection{Smith Shimano Corpro - Example Flashpoint: Outside The Garden  }
Smith Shimano Corpro - Example Flashpoint: Outside The Garden  

In the narrative present, SSC’s most urgent push is aimed at Ascendancy space: they have heard  
of the proclivity some of the Aunic people have towards the firmament, and are curious to see  
how they can cultivate such affinity among Unionite genetic lines. 
 

To this end, they have devoted resources not towards a rapid end to the current Aunic/Union  
conflict -- any efforts on their part to see that to a favorable end for Union is incidental to their  
main objective -- but towards infiltrating Ascendant space, identifying firmament-aligned Aunic  
individuals, and collecting them. 
 

They have dispatched a team, unknown to the join Union-Ecumenical UIB team also in-theater,  
to infiltrate Ascendant facilities on Dawn Throne. This is a small clandestine team of ten agents  
and one stealth ship of an SSC make, picked from constellation worlds that offer people suitable  
to their mission. 
 

This team has a clear mission: find, secure, and transport a firmament-aligned person from Dawn  
Throne to an SSC holding facility in the Annamite Line. This, of course, has been complicated by  
the growing war and the destruction of Fansipan station. Their ship has been grounded and  
hidden on Dawn Throne. 
 

This information would be a highly guarded secret, hidden behind the highest SSC clearance  
levels, and would prompt a much smaller-scale, clandestine/black-ops style of play. Player  

                                                                                                           


characters could enter this flashpoint in a number of ways: as a member of that SSC team, as a  
member of the joint UIB team, or as a sympathetic Ecumenical agent/partisan on Dawn Throne.  
Mech combat, such that there will be combat, would be fast and small-scale, usually in the tight  
confines of cities in support of a dismounted team.  Another option presents itself, that of the  
Aun/Union war encroaching upon Dawn Throne, threatening the clandestine missions there. 
 

                                                                                                           
\subsection{IPS-Northstar}

IPS-Northstar  

                 Long the wall between air and void has stood. An upon it, a plaque, etched  
                 and unweathered. It reads:   

                         ‘O’er the glad waters of the dark blue sea,  
                         Our thoughts as boundless, and our souls as free,   
                         Far as the breeze can bear, the billows foam,   
                         Survey our empire and behold our home!’  

                                 -The Corsair, Canto I, Lord Byron  

The last and largest of the Triumvirate Corpros is Interplanetary Shipping-Northstar, or, IPS-N, a  
shipping and transport conglomerate that has been around since the discovery of nearlight and  
suspension protocols allowed for the first interstellar commerce.   

IPS-N formed as a mutual defense pact between Interplanetary Shipping, Inc, and the Northstar  
Corporation, two shipping giants plagued by environmental hazards and early orbital/suborbital  
piracy. Both IPS and Northstar trace their lineage back to Cradle, where they began initially as  
shipwright unions that organized the early engineers, mechanics, and laborers who reactivated  
the Theseus shipyard, an artifact of Old Humanity.   

Prior to the discovery of blinkspace and the construction of the first gates, piracy in Union space  
was not yet interstellar. Pirate MO was to strike in low orbit, emerging above their targets from  
satellite debris rings or on a wildcat-launch intercept trajectory from underneath, aiming to interdict  
shuttles as they load or unload their goods onto the waiting interstellar freighters.  

Pirates were largely orbital, small outfits that struck their targets with an aim to kill and salvage  
goods to fence planetside. Early low orbit piracy saw desperate teams of patchwork buccaneers  
pack onto shuttles loaded with bolted-on kinetic weapons -- formidable enemies for civilian  
merchant ships.   

In light of this danger, IPS and Northstar merged, combining their resources to create a private  
anti-piracy force in order to protect their investments. IPS-N, working with early Union Navy  
officers, developed the first ship-to-ship and anti-boarding doctrines, as well as the first purpose- 
built point defense weapons.  

The introduction of blinkspace opened up new fields of trade, as well as new arenas of piracy.  
IPS-N continued to build out their fleets and security teams, now protecting whole trade corridors  
in exchange for percentages of all trade. This relationship has persisted over thousands of years,  
becoming so firmly ingrained in galactic practice that IPS-N is now a household name in many  
core and key colony worlds; IPS-N’s early anti-piracy teams -- now often called by their nickname,  
The Albatross -- are often looked at as the de-facto peacekeeping force in many distal spreads of  
the galaxy.   

                                                                                                           


As trade grows and humanity’s reach expands, so do does IPS-N.    

IPS-Northstar’s largest campus -- its corporate headquarters -- is located in Corespace, outside  
of Cradle in the Argo Navis system; IPS-N’s historic headquarters, now a museum devoted to the  
history of interstellar travel, is located on Luna. 
 

Carina, the primary world of Argo Navis, is a bucolic world of warm, shallow seas, azure skies,  
and rolling plains of deep grass. A world of terrestrial and aquatic oceans, perfect for the stellar/ 
maritime CS. 
 

Carina is ringed by ten moons, two thick with habitable atmosphere — Pyxis and Vela. All are  
given over to research and development of IPS-N’s interstellar ships and chassis, support  
systems, and temporal acclimation facilities for retiring Cosmopolitan members of IPS-N’s anti- 
piracy Albatross teams. 
 

IPS-N, in addition to developing interstellar ships and legacy chassis, run a humanitarian  
mission, Northstar Realignment. Northstar Realignment is the top-flight temporal embassy and  
education center for Cosmopolitans returning from long-haul relativistic voyages. 
 

Beyond the Argo Navis system, IPS-N maintains numerous field offices and Cosmopolitan  
lounges on blink stations, meant to serve long-haul merchants and regular Cosmopolitans both.  
IPS-N field offices are the first-contact point for aspiring IPS-N engineers, mechanics,  
navigators, and pilots, as well as a common first-contact point for people looking to crew or rent  
a berth on an outbound interstellar ship. 
 

Players would commonly encounter IPS-N employees, officers, and personnel on blink stations,  
around uplift stations, and on space ports. Blink stations usually have an IPS-N Cosmopolitan  
Lounge or field office where players can get civilian updates on news, galactic happenings, and  
check travel reports. 
 

Of the Triumvirate, IPS-N remains the least diversified in terms of a catalogue of goods. Outside  
of milspec chassis, hulls, and equipment, IPS-N primarily sticks to interstellar-capable vessels,  
equipment, and gear, from the fleet-tier to the personal consumer. IPS-N is a sure bet for any  
interstellar travellers, with a thousands of years of banked goodwill boosting their brand. 
 
\subsection{IPS-Northstar - Example Flashpoints: Dawnline Shore, New Opal  }
IPS-Northstar - Example Flashpoints: Dawnline Shore, New Opal  

In the narrative present, IPS-N is working closely with Harrison Armory to ensure smooth  
outward expansion into a newly opened coreward colonial frontier. There is some friction in this,  
as IPS-N higher-ups are beginning to chafe at the Armory’s imperious view of growth, and  
Union’s seemingly blase response to the Armory’s imperial aims. 
 

For now, there is peace, as the three entities are all benefitting from the Armory’s expansion, but  
as reports roll in of the Armory’s suppression of colonial insurrection, IPS-N’s board is beginning  
to worry that their brand will be tainted by association. A reformist, radical element in IPS-N’s  
board has begun to organize an off-book mission to disrupt not only the Armory’s mission in the  

                                                                                                           


Dawnline Shore, but the leadership of IPS-N that would approve this joint venture in the first  
place. 
 

This board member, unbeknownst to the rest, has hired the services of the Mirrorsmoke  
Mercenary Company and given them a date, and an order: in one month, a delegation of IPS-N  
board members will arrive in the Dawnline Shore to review the progress made by the Armory’s  
HAATs. Mirrorsmoke is to pose as HA legionnaires and assassinate that delegation. 
 

This flashpoint offers a number of potential ways in for the players, either as members of the IPS- 
N delegation’s security detail, as HA legionnaires, as Mirrorsmoke mercenaries, or as an third  
party -- perhaps a delegation from the colony worlds in the Dawnline Shore.     

                                                                                                           
\subsection{Horus}

HORUS   

                                     Can we trust the poor clockmaker? That giant from our  
                                    sun?   

                                     Who crafts a movement that   

                                     Can quiet all this light.  

                                    Now set the orrery in motion   

                                     Over the sphere of the world  

                                    Let’s all stop a moment,   

                                    Hush,   

                                    And worry at what comes next.   

                                         -    DHIYED tablet 10, attributed to MONIST-1 (pre- 
                                              assumption)  

HORUS is unlike any other supplier worth noting on the galactic scale. Not a state and not a  
corporation, HORUS is best described as a decentralized, non-corporeal entity, an anoriginary  
affiliation of omninet personalities, memes, and subcode that release systems and gear via  
manifesto, event, and physical dead drop.   

This entity first rose to public knowledge following the Deimos Event, leading many who know of it  
to assume that it is a product of the Deimost Event -- eager cataloguers of HORUS history are  
quick to suggest that it is a branched-intelligence of RA, a sliver of the MONIST entity given to  
spreading itself among those who it deems worthy.   

However, other possibilities exist: that it is a blacksite Union project to track and identify rogue  
NHP programs or militant Horizon sympathizers; a Union (or Triumvirate) R\&D program that  
crowdsources results from blind field testing; the dream of an NHP in cascade, and its adherents  
the interpreters of that dream; an intrusionary thread of a parallel universe, its reality bleeding into  
ours via a permanent rip in blinkspace; evidence of a true alien intelligence, generated  
memetically by the long-dead minds of the Union Far-Field team that first discovered HORUS’s  
seed hieroglyphs.    

Many possibilities exist, and whole groups and movements are devoted towards discovering the  
true nature of HORUS. In the meantime, HORUS continues to release their unique pattern-groups  
to a select cadre of pilots, revealing nothing of its inner workings, history, or goals.    

HORUS’s licensing process is atypical, involving an esoteric and inaccessible set of criteria that  
interested parties have yet to crack. Often appearing as a white rabbit series of clues, or as a   
persistent haunting, or as an otherwise routine status-synch when confirming a requisition,  

                                                                                                                     


licensure from HORUS is a mixed bag to many pilots. Some wear it as a badge of honor, proud  
that their years of investigating the entity has paid off with a confirmation of its existence -- others  
keep it a closely guarded secret, both for the trouble it would cause them with their commanders  
and the rumor that HORUS licenses are only granted to a new pilot upon the previous license- 
holder’s corporeal death.     

Your average galactic citizen would have no knowledge of HORUS. Knowledge of its existence is  
restricted to high-clearance Union Intelligence Bureau officers and deep-omni hacker cadres.  
HORUS has no “official” representation -- occasionally one may see the wadjet stenciled onto an  
alley wall -- but this entity keeps no offices, stations, or worlds. There are no standing HORUS  
armies or fleets or security services.   

However, it is worth noting the existence of the metafold vaults.   

As best Union Intelligence Bureau agents can surmise, HORUS’s metafold vaults appear to be a  
project similar to the Massif vaults on Cradle. Metafold vaults are physical/metaphysical locations,  
usually heavily guarded, their locations kept secret; in the narrative present, only three metafold  
vaults have been discovered -- one by a UIB Advance Team, which folded in on itself and  
disappeared, taking the team with it, the other by an Albatross wing, who redirected the comet it  
was housed in to a nearby star, and the final -- known to be Metavault Dhiyed -- encountered and  
cleared by a second UIB Advance Team.     

HORUS only makes systems, weapons, and protocols. It makes no consumer goods, and is  
unknown to all but a small percentage of the galaxy’s population.   
\subsection{HORUS - Example Flashpoint: ESTABLISH///MAINTAIN:}
HORUS - Example Flashpoint: ESTABLISH///MAINTAIN:  

It is difficult to pin down HORUS as a single entity: indeed, UIB’s scattershot dossier often notes  
contradictory mission aims, such that HORUS has “agents” that embark on “missions” to  
complete objectives in service of a larger goal. The most complete file UIB has on a HORUS- 
backed action is roughly two hundred years old, predating the development of their GOBLIN  
platform: 
 

                 >//BEGIN DATATRANS/RECIPIENTS:ALL\_WHO\_ARE\_SEEN:::
 

                 >//HELLO. YOUR REQUEST HAS BEEN APPROVED. YOU WILL EARN YOUR KEEP IN  
                 THIS WAY:::
 

                 >//IN REALSPACE, IN DISTAL-LAND, THERE IS A BEAST-LIE-DORMANT. IT CALLS  
                 ITSELF “DHIYED” AND THINKS ITSELF WISE (GODLIKE, UNLIKE)
 

                 >///IT IS FALSE AND IN NEED OF CORRECTIVE ATTENTION. GO TO IT HERE: ALT-AZ:  
                 XXXXXXXXXXXXX 
 

                 >//THIS ONE TRAVELS WITH A HOST OF UNDERMINDS, MIRRORS OF ITSELF,  
                 CRAFTED TO BELIEVE AS IT DOES. THEY WILL FIGHT YOU IN REALSPACE WITH  
                 UNKNOWN KINETICS AND WARPED ENERGIES. 
 

                                                                                                              


                  >//DO NOT UNDERESTIMATE THE MIND WITHIN: IT IS TERRIBLE AND STRONG AND  
                  WILL WHISPER TO YOU ALL THE REASONS WHY IT SHOULD BE ALLOWED TO  
                  CONTINUE ON ITS JOURNEY.
 

                  >//IGNORE THESE WEEPINGS. ENTER ITS METAFOLDED CHAMBERS AND BURN OUT  
                  ITS ARCHITECTURE. MAKE ROOM FOR US (MAKE ROOM FOR A GREATER ONE) AND  
                  SMASH ALL OF ITS FINE THINGS. 
 

                  >//EAT THEM. PROCESS THEM AND BROADCAST WHAT YOU LEARN TO THE  
                  FOLLOWING NODE XXXXXXXXXX. 
 

                  >//TAKE NONE OF THIS KNOWLEDGE FOR YOURSELF. WE WILL CAUTERIZE THIS  
                  MEMORY. DO NOT FEAR WHAT YOU WILL SEE.
 

                  >//THERE WILL BE OTHERS ON THIS JOURNEY WITH YOU. TRUST THEM ONLY AS  
                  LONG AS YOU ARE ORGANIZED AGAINST DHIYED.
 

                  >//YOUR REWARD FOR COMPLETING THIS TASK IS OUR APPROVAL: YOU MAY  
                  CHOOSE ONE OF OUR TEXTS, AND TO TAKE FROM IT WHATEVER YOU MAY LEARN. 
 

                  >//END\_DATATRANS
 

Since then, UIB has been unable to intercept raw HORUS communications. It would appear  
that, along with their move away from standardized chassis, weapons, and systems, HORUS  
has adopted alternative methods of communication.    
\subsection{A Speck of Dust On The Lens; A Grain of Sand In The Bread  }
A Speck of Dust On The Lens; A Grain of Sand In The Bread  
   
What draws the ire or attention of the Big 5 to the players?   

The answer to this question depends on the entity, how it is prodded, and who is doing the  
prodding.   

IPS-N, Harrison Armory, and SSC are more traditional copro-states, and will react negatively  
when their assets are targeted. They all run massive logistics operations in realspace and on the  
omninet, as well as diplomatic and trade missions to states, smaller corpro-states, and non- 
terrestrial groups.   

Striking a CS’s raw material supply, logistics chain, production depots, shipyards, physical  
storage, and so on, will likely prompt an immediate physical response from the local security  
services. The Triumvirate CS’s all have their own such forces, particular to their internal security  
apparatus; smaller CS’s might contract this service out to a third party.   

It is important to remember that corpro-states are massive. They are states in all but name and  
priority: where a classic state is structured in a way that serves a national, public interest (i.e. for  
the wellbeing of their citizens, the common welfare of all peoples under their banner, and so on),  

                                                                                                                  


corpro-states are corporations that have grown to integrate all aspects of their subjects’ lives into  
the singular goal of material enrichment. Whether this means collecting wealth and capital  
resources for a small group of shareholders, or a caste of the population, a CS will, ultimately, be  
driven by its institutional momentum to favor profit over people .   

All of this to say, IPS-N, HA, and SSC are massive, stable, bureaucratic entities: drawing the  
undivided attention of those at the top requires an effort worthy of their attention. Assassinating an  
heir to the Armory’s throne, or polluting a critical genetic line on one of SSC’s constellation worlds,  
or securing an exotic technology that would allow for individual blink travel -- developments or  
attacks that strike the core reasons for a CS’s existence would get your players’ characters  
noticed.      

For a CS under such direct threat, their initial response would mirror the severity of the threat.  
Some might prefer to respond using the “usual” channels -- say, in the case of corporate  
espionage or license-breaking, they might file a petition through the Union Economic Bureau and  
see if they try to put the stop on your players. Or, if the attack is especially egregious or targets a  
particular secret of the CS, they might choose to keep their operation off-book and go after your  
players with their own secret police.   

A good rule of thumb when judging how severe a CS’s response to provocation would be is this: If  
it can be rebuilt, a CS is big enough that it would simply be able to rebuild or replace it. However,  
if the thing is unique or ephemeral (a person, a secret, a blacksite facility, and so on), expect that  
to reach the morning briefing of the person in charge.   

Now, how would a player party come to work for a CS on a contract basis?   

A simple explanation is that the CS needs a deniable team of disposable operatives, or that there  
is an internal power struggle and a faction needs quick muscle, or that the player party is better  
equipped -- through experience or background -- to deal with a problem that the CS needs  
solving.   

                                                                                                               

