\section{SITREP}


                                              SITREP   

Many battles in LANCER will be simple affairs, with one side facing off against the other until one  
or the other is broken or destroyed. However, there are times when, as a GM, you might want to  
add additional objectives or make combat scenarios more interesting or engaging. This is a tool  
for creating combat scenarios featuring deployment zones, objective zones, and predicted enemy  
approaches (for more tactical mech combat, akin to a wargame).   

You can use these scenarios to represent key parts of a mission or adjust them to fit them to your  
story.  

Key terms:  

Player Deployment Zone - Where the players deploy at the start of the mission, unless otherwise  
noted.   
Extraction Zone - Where the players need to be or enter to end certain missions and  
successfully extract.   
Enemy Deployment Zone - Where the hostile NPC forces can deploy initially  
Reserves - NPC forces that are held in reserve. They don’t start on the map but can appear as  
reinforcements in later rounds in an Ingress zone.  
Ingress Zone - Where the hostile NPC forces can reinforce from  
Objective - Any key location or thing that the players need to interact with. Could be a zone or  
object. If it’s a zone, a character contests it if they are at least 1 space inside.  

Most of these missions assume you have a roughly rectangular map no longer than about 40  
spaces on its longest side. You should also fill the map with terrain or cover - some missions  
explicitly ask you to do this in certain areas, but the rest is up to you.  

                                                SCENARIOS:  
Random Scenario
 

 D6                                                     Scenario 

 1                                                      Escort 

 2                                                      Control 

 3                                                      Extract 

 4                                                      Hold Out 

 5                                                      Gauntlet 

 6                                                      Recon 


\subsection{Escort}                                          


                                                               ESCORT  
                                                               “Listen up, Administrator: when we open these  
                                                               doors, you need to stay with us, and you need to  
                                                               do exactly what we tell you to do. If I go down,  
                                                               don’t help me -- listen to Monk. If Monk gets hit,  
                                                               listen to Cross. If Cross gets hit, listen to Crown.  
                                                               If Crown dies, keep running and don’t stop, and  
                                                               remember: if you make it out of the city, we win  
                                                               the war. Ready?”   
                                                               -Archived audio, Captain Pyotr “Pat” Malov,  
                                                               Cornucopian Revolutionary Guard (KIA)  

                                                               An ESCORT mission requires bringing an  
                                                               Objective safely to the Extraction Zone and  
                                                               extracting all player characters safely.  

                                                               Objective: The Objective is a size 1/2 - size 2  
                                                               object, person, or NPC. It has 10 HP/size,  
                                                               evasion 10, e-defense 10, and no armor. The  
                                                               enemy forces want the objective and will not  
                                                               willingly damage it. If any actor starts adjacent  
                                                               to the Objective, they can move the objective  
                                                               with them when they make their regular move  
                                                               on their turn, maintaining adjacency. If the  
                                                               objective is adjacent or becomes adjacent to  
                                                               two actors of opposing sides, it immediately  
                                                               stops moving and can’t move until there is only  
                                                               one side in adjacency to it. Otherwise it does  
                                                               not move on its own.  
                                                               Enemy Forces: The GM should hold about 2x  
                                                               the enemy forces for a normal encounter. They  
                                                               can deploy up to 1x initially and hold the rest in  
                                                               reserve.  
                                                               Deployment: The players deploy first, placing  
                                                               both their characters and the Objective in the  
                                                               deployment zone, then the GM deploys in the  
enemy deployment zone.  
Reserves: The GM can bring in 1 NPC (or up to 4 grunts) at the start of any new round in one of  
the Ingress Zones. They cannot choose the same zone twice in a row.  
Extraction: Any player character can extract as a free action at the end of their turn while in the  
extraction zone. This removes them from the battlefield (they have gotten away safely). If they  
extract with the objective adjacent to them and no other actor is contesting it, they take the  
objective with them.  
Victory conditions:   
          - The players win if they extract the objective.  
          - At the end of the 6th round, if the objective hasn’t been extracted, the enemy forces win.   
          If any players are left on the battlefield after the 6th round ends, they are captured or  
         overrun.  

                                                                                                                      


          - Nobody wins if the objective is destroyed. The players must still extract to leave safely.  

CONTROL  

         “Take the hill.”  
                      -    Common final order  

A CONTROL mission requires maintaining control of four objective zones for six rounds. The  
zones could be important mission points like transmission towers or gun batteries, terminals or  
hangars.  

Objectives: There are 4 objective zones (by default you can use roughly 4x4 areas), each placed  
anywhere in one quadrant of the map. If they are not roughly symmetrical, the map will be  
unbalanced.  
Deployment: Roll off (1d6) between the players and enemy forces. The loser deploys first in their  
appropriate zone. The GM can hold enemy forces in reserve if they want but doesn’t have more  
than normal available.  
Zone control: If only actors of one side are inside a zone, they control that zone. If there are  
actors from two or more sides inside a zone, the zone is contested.  
Objective Scoring: At the end of each round, for each zone a side controls, give them 1 point. If  
they control all four zones, give them a bonus +1 point.  
Victory conditions: The side with the highest score at the end of round 6 wins.
 

                                                                                                                  

\subsection{Extract}
   

                                                                     EXTRACT  

                                                                     “Catapult Actual, this is Catapult-2:  
                                                                     requesting immediate evac from current  
                                                                     GRIDCOR”  
                                                                            “Cat-2 confirm GRIDCOR.”  
                                                                     “Confirming… Confirmed, Catapult Actual.  
                                                                     Air-ground clear and holding. We, uh, have  
                                                                     multiple down. KIA and wounded.”  
                                                                            “Heard, Cat-2. Lifeflight on the way.  
                                                                     Confirm: VIP secure.”  
                                                                     “VIP --”  
                                                                            “Say again Cat-2.”  
                                                                     “VIP secure -- We’ve got more company  
                                                                     down here, Actual -- going dark, respond to  
                                                                     GRIDCOR.”  
                                                                            “Confirmed, 2. We’re on our way,   

                                                                     An extraction mission is similar to an escort  
                                                                     mission, though different in a couple of key  
                                                                     areas.   

                                                                     Objective: The Objective is a size 1/2 - size  
                                                                     2 object, person, or NPC. It has 10 HP/size,  
                                                                     evasion 10, e-defense 10, and no armor.  
                                                                     The enemy forces want the objective and  
                                                                     will not willingly damage it. If any actor starts  
                                                                     adjacent to the Objective, they can move the  
                                                                     objective with them when they make their  
                                                                     regular move on their turn, maintaining  
                                                                     adjacency. If the objective is adjacent or  
                                                                     becomes adjacent to two actors of opposing  
                                                                     sides, it immediately stops moving and can’t  
                                                                     move until there is only one side in  
                                                                     adjacency to it. Otherwise it does not move  
                                                                    on its own.  
Enemy Forces: The GM should hold about 2x the enemy forces for a normal encounter. They  
hold them all in reserve (round 1 there will be no enemy forces).  
Deployment: The players deploy first, placing their characters in the deployment zone. The GM  
places the Objective in the objective zone.  
Reserves: The GM can bring in 2 NPCs (or up to 4 grunts) at the start of any new round in two of  
the Ingress Zones.  
Extraction: Any player character can extract as a free action at the end of their turn while in the  
extraction zone, which is the same as the deployment zone. This removes them from the  

                                                                                                                           


battlefield (they have gotten away safely). If they extract with the objective adjacent to them and  
no other actor is contesting it, they take the objective with them.  
Victory conditions:   
         - The players win if they extract the objective.  
         - At the end of the 8th round, if the objective hasn’t been extracted, the enemy forces win.   
         If any players are left on the battlefield after the 8th round ends, they are captured or  
        overrun.  

                                                                                                          
\subsection{Holdout}

HOLDOUT  

          MJ sat in his open cockpit, chewed his gum, and ignored the briefing. Was for the local Oxes, kids  
          and eagers who needed a pep talk, not him and his Emancipators. They got the real story.   

          Real story wasn’t a pretty pic.     

          Extract was six hours out and burning hard. The Crown horse guards got a hundred mix ‘n match  
          middle-tier Armory shells, couple thou’ cavalry -- poor damn horses.   

          MJ had a thousand rounds of hardpoint EX, two racks of Kodandams, and his MC-TB for when the  
          real mess came.  

          “Yo MJ,” his comms squawked. “Button up. We got company, four hundred meters out and closing.  
          Horses.”   

          “Uh huh,” MJ said. He slapped the cabin seal without looking and got comfortable. Helm on, haptics  
          on. Mag loaded. Feel bad for the horses, because they didn’t know what they were getting into.   

          Six hours to extract, clock starting now.     

A desperate mission type. When ordered to Hold Out, players will have to defend an area against  
an onslaught of enemies -- in a best-case scenario, this is to buy time for allies to complete an  
objective elsewhere. In a worst-case scenario, it is to the death.   

                                                                                                                               


Enemy Forces: The GM should hold about 2x the enemy forces for a normal encounter. They  
hold half in reserve  
Deployment: The players deploy first, then the GM deploys half their total forces.  
Fortifications: The area around the objective zone should have size 1-2 heavy cover  
Objective: The objective zone is a roughly 10 spaces by 5 spaces area in the middle of the map  
(you can adjust this as needed). Players start with 4 points. For every enemy inside of the  
objective zone, the players get -1 points (the score could go negative).  
Victory conditions:  If at the end of round 6 the player characters are alive and their score is 1 or  
greater, they win, otherwise they are captured or overrun.  

                                                                                                          

\subsection{Gauntlet}
                                                              

                                                             GAUNTLET  

                                                             >// [WHITEOUT CONTINGENCY:: REAR  
                                                             ECHELON HAS FALLEN. ALL UNITS AT  
                                                             MINIMUM/NEGATIVE EFFICACY]   

                                                             >//[ALL-BAND ORDER::PROCEED AT TOTAL  
                                                             STRIKE CAPACITY TO ID EXTRACT AREA]  

                                                             >//[THIS IS A IMPERATIVE COMPLY ORDER.  
                                                             YOU ARE ON YOUR OWN++OUR POSITION  
                                                             IS OVERRUN++HURRY]   

                                                             Generally a mission done under duress, or  
                                                            when no other options are available to the  
                                                             players. Commonly engaged in unfriendly  
                                                            terrain. A Gauntlet mission demands the  
                                                             player party move from their deployment zone  
                                                             across unfriendly territory to secure an enemy  
                                                             position.  

                                                             Enemy forces: The GM should have a  
                                                             normal amount of enemy forces, but hold half  
                                                             in reserve.  
                                                             Deployment: The GM deploys half their  
                                                            forces first, then the players deploy  
                                                             Fortifications: The area around the enemy  
                                                             deployment zone is fortified with size 1 and 2  
                                                             heavy cover  
                                                             Reserves: At the end of round 1, the GM  
                                                             deploys the rest of their forces in any of the  
                                                             Ingress zones  
                                                            Victory conditions: The players win if there  
                                                             are more player characters inside the  
                                                             objective zone at the end of turn 6 than enemy  
                                                            characters (count ultras for 4 players, elites for  
2, and grunts for 1/4). Otherwise the enemies win.  

                                                                                                                
\subsection{Recon}

RECON  

         Aurelia whistled low, taking in the fresh coat of matte on their chassis.   

          “Optical camo overlay primary, Inkwell secondary,” Engineer Coates said, finishing her walkaround.  
          “Even if they scramble your anoptics, it’s going to be a nightmare to sight her.”   

         Aurelia reached up to touch their chassis’ brachial mount. Their sylph spilled across their arm,  
         touched the chassis. An inkbloom of the midnight color clouded through it.  

         Aurelia grinned. They would be a nightmare.   

A recon mission is, generally speaking, a dangerous endeavor, where a small team enters hostile  
territory to identify targets or retrieve key information  

Objectives: The GM marks 4 4x4 objective zones on the map. The GM secretly chooses one of  
the objectives to be the real objective (from A-D). Characters can control an objective by being the  
only side inside the objective zone at the end of the round. They can determine whether the  
objective is real or not by being inside the zone and taking a full action (this information is freely  
shareable once discovered). They don’t need to control the zone to investigate it.  
Enemy Forces: The GM has normal enemy forces, and can hold any number in reserve  
Deployment: The players deploy first, then the NPCs  
Reserves: The GM can bring in 1 NPC or up to 4 grunts in the ingress zone at the start of any  
new round.  

                                                                                                                        


Victory conditions: The players win if they are in control of the real objective at the end of round  
6. Otherwise, the enemy forces win.  

                                                                                                          
