\section{Skill Checks and Attacks}
   Skill Checks and Attacks  

There are two types of rolls in LANCER:
 

A skill check is required in a challenging or tense situation that requires some effort to  
overcome. To make a skill check, first name your goal (break down the door, hack the computer),  
then roll 1d20, and add any relevant bonuses. On a total result of 10 or higher, you accomplish  
your goal. On a 20+ you excel at your goal, giving you better results than you expected. a total  
result of 9 or lower, you don’t accomplish your goal. A failed roll doesn’t necessarily mean you  
fail completely, but further complicates the situation. The GM cannot change the target number  
(10) of a skill check, but can add additional Difficulty (see just below) to the check if it’s harder  
than normal.
 

                                                                                                                 


An Attack is an offensive roll against another actor in mech combat, such as firing a weapon,  
attempting to hack a target, or wrestle them to the ground. An attack roll is made the same way  
as a skill check (1d20 + relevant bonuses), but the target number can differ from 10, and usually  
depends on the numerical defensive statistic of your target, such as evasion, or electronic  
defense. An attack is successful if it equals or exceeds the target defense. Some attacks can  
deal a Critical Hit on a 20+, allowing you to deal more damage or trigger extra effects.
 

If a rule refers to an ‘attack’, it applies to an individual roll. The rules might also refer specifically  
to ranged or melee attacks (attacks typically made with a weapon or part of your mech) or tech  
attacks (attacks made with electronic warfare). 
 

                                           CONTESTED CHECK  

As a mech or pilot, you may be called on to perform a contested check. Both the attacker and  
defender make skill checks, adding bonuses and penalties. The winner of the contest is whoever  
has the highest total result - in the case of any ties, the attacker wins.
 

                                             FAILING CHECKS  

You can always choose to voluntarily fail any skill check (mech or otherwise). You can take this  
option if a friendly actor is trying to help you out, or simply if you think it would lead to a more  
interesting situation or make more sense narratively.
 