\section{Smith-Shimano Corpro}

 SMITH-SHIMANO CORPRO   

                                        “YOU ONLY NEED ONE”  

Smith-Shimano is the second-oldest Galactic-Tier corporation next to GMS. An early  
contender in the sublight, downwell, and EVA vehicle race, SSC cut its teeth making some of the  
earliest private mech cores for other corporate colonial expeditions. They specialized primarily in  
construction vehicles, long-range scout suits, and hardened EVA units. The transition to military  
came slowly, but when the ruling partners saw there was a need for mechanized, armed, and  
armored cores, they duo-laterally decided to change their business model.
 

Smith-Shimano mechs reflect their rapid, agile business model and pedigree. They’re built not to  
take hits, but avoid them entirely, to stay mobile and low, to land not the hardest hit, but the most  
accurate. Economy is the name of the game for SSC: why fire a thousand rounds when one will  
do just as good?
 

Smith-Shimano mechs are available to pilots with the proper license. They’re a good choice for  
pilots who want to be quick and hit what they’re aiming at, but not recommended for those who  
want to be on the front line. Remember, Smith-Shimano mechs are meant to avoid the hit, not  
get hit.  
 

SSC Mechs:
 

SSC SWALLOWTAIL (Scout)  
SSC MONARCH (Missile)  
SSC MOURNING CLOAK (Assassination)  
SSC DEATH’S HEAD (Marksmanship  
SSC DUSK WING (Rapid Assault)  
SSC METALMARK (Infiltration Line Mech)  
SSC BLACK WITCH (Magnetic/Battlefield control mech)  

\input{./SSC/gear.tex} 
                                                                                                         
\input{./SSC/core.tex} 
                                                                                                                         
\input{./SSC/BlackWitch.tex}

\input{./SSC/DeathsHead.tex}

\input{./SSC/DuskWing.tex}

\input{./SSC/Metalmark.tex}

\input{./SSC/Monarch.tex}

\input{./SSC/MourningCloak.tex}

\input{./SSC/Swallowtail.tex}
                                                                                                                     

                                                                                                                      


                                                                                                                  

                                                                                                                      

                                                                                                               


                                                                                                                            

                                                                                                                      


                                                                                                             


                                                                                                                        
