\section{Statuses}

  STATUSES  

During combat, characters might inflict statuses on opponents, giving temporary conditions. Most  
statuses indicate when they are inflicted and when they end in the weapon, system, or piece of  
gear that inflicts them.  

CORE BREACH  
    -   You cannot cool heat or lose heat
 
    -   Make an overheating check each time you take heat
 
CRITICAL  
    $$\bullet$$   You cannot gain HP or repair  
    $\bullet$    Make a structure check each time you take damage  
Engaged  
    -   While Engaged in melee, all your ranged attacks are made with +1 difficulty
 
    -   If you become engaged with a target the same size or larger, you immediately stop  
        moving and lose any unspent movement from that move.
 
Hidden  
    -   You cannot be targeted by hostile attacks or actions, and enemies only know your  
        approximate location. Performing any attack, taking reactions, or ending your turn out of  
        cover will lose hidden.
 
Immobilized 
 
    $\bullet$    Your maximum speed becomes 0. You cannot move or boost.  
Impaired  
    $\bullet$    +1 Difficulty on all actions, attacks, and skill checks  
Invisible  
    $\bullet$    All attacks against an invisible target have a 50% chance to miss outright (check before  
        the attack roll).
 
Jammed 
 
    $\bullet$    The only attacks a Jammed mech can make are improvised attacks, grapples, or rams
 
    $\bullet$    A Jammed mech cannot use comms to talk to other players (can only talk to GM)   
    $\bullet$    A Jammed mech cannot make or benefit from Tech actions
 
    $\bullet$    A Jammed mech cannot take reactions
 
Lock On  
    -   An attacker can consume the Lock On status on a target to gain +1 Accuracy on its next  
        attack against that target. Lock On may also activate other talents or abilities.
 
Shut Down   
    $\bullet$    Your mech is stunned, but you can still take the Boot Up action  
    $\bullet$    Your mech’s evasion becomes 5  
    $\bullet$    Your mech cools  
    $\bullet$    You cannot be affected by tech actions or system attacks or effects  
    $\bullet$    Shutting down (or being shut down) re-shackles any unshackled AI.
 
Shredded  
    $\bullet$    A shredded mech cannot benefit from armor or resistance
 

                                                                                                          


Slowed  
     $\bullet$    Your maximum speed becomes 2 (after all modifiers)  
     $\bullet$    You cannot boost
 
Stunned 
 
     $\bullet$    You cannot overcharge, take free actions, reactions, move, or take any actions with your  
         mech. A pilot in a stunned mech can still mount or dismount their mech, eject, or take  
         actions normally.  
     $\bullet$    Attackers receive +1 Accuracy to attack you
 
     $\bullet$    You automatically fail all hull or agility checks
 
Prone 
 
     $\bullet$    Attackers receive +1 Accuracy to attack prone targets  
     $\bullet$    A mech knocked prone is Slowed while prone but can still move. A prone mech can stand  
         up as its regular movement. A mech cannot stand up while immobilized.  
\subsection{Stat and Terminology Glossary}
                          STAT AND TERMINOLOGY GLOSSARY  

Armor - The amount of damage you reduce all incoming sources of damage by. For mechs,  
cannot go higher than 4  
Electronic Defense - The number that most electronic warfare attacks must beat to be  
successful  
Evasion - The number that most melee and ranged attacks must beat in order to hit with an  
attack  
Grit - 1/2 your level. Added to melee and ranged attacks, system points, and hp  
Heat Capacity - The amount of heat your mech can take before making an overheating check.  
Hit Points (HP) - The amount of damage you can take as a pilot before going down and out, and  
the amount of damage a mech can take before it takes 1 point of structure damage.  
Modifier - The number added to mech skill checks and attacks, equals your targeting, hull, agility,  
engineering, or systems  
Range - The range of your ranged attack, measured from yourself. Depends on weapon  
Repair Cap - The maximum number of repairs to your mech you can make per mission  
Resistance - Resistance to damage or a type of damage means it is reduced by half, rounded up,  
after armor is applied. You can only have resistance to damage once (it doesn’t stack multiple  
times)  
Structure - When a target with structure goes to 0 HP, it makes a structure check, then takes 1  
structure damage. When a target runs out of structure, it either goes into the CRITICAL state  
(player mechs) or is destroyed outright.  
Tech attack - Electronic Warfare attacks, modified by your systems  
Threat - The range of your melee and overwatch attacks with certain weapons, measured from  
yourself. Base threat for all weapons is 1, but it may be greater depending on the weapon.  
Sensor Range - The range in which you can make electronic warfare attacks, lock on, and use  
some systems  
Size - The area that your mech takes up, rounded up for determining space. For example, a size  
2 mech is an area 2 spaces on each side approximately 2 spaces high  
Speed - How far your mech moves when it moves (in spaces)  

                                                                                                              
\subsection{Ending Combat}

                                           ENDING COMBAT
 

Combat ends when one side has accomplished their main objective. Usually this means they  
have defeated, destroyed, or routed the other side, but not necessarily. Combat doesn’t have to  
end with total destruction of one side or another - it’s perfectly fine for a GM to call combat early  
if the outcome is not in question, and return to narrative play. NPCs often have their own goals  
and are typically concerned with self-preservation.