\section{Technology and Culture in Union Space}

Technology and Culture in Union Space  
\subsection{Cloning}
Cloning   

Under the Third Committee, cloning -- the cultivation and growth of whole or partial genetic  
facsimiles of persons and other fauna -- occupies a space of grey legality. 
 

To clone a whole person, or constituent parts of a person, legally under the Third Committee  
requires informed consent from the donor; the person who is being cloned must understand that,  
should they requisition a full body clone, they are their own person, with their own subjectivity,  
and their own personal rights. Nothing will give the donor legal claim over the facsimile of the  
donor, unless the donor has requested a facsimile to raise as if it were their own child -- in this  
case, they are granted a culture-normalized parent-offspring relationship, commensurate with the  
mores, traditions, and legal rights of their culture. 
 

Whole body clones under Union’s Third Committee government are, for all intents and purposes,  
legally, subjectively, and in reality, their own individuals distinct from their donor. They are people,  
with their own legal rights and entitlements, whose only difference from “natural” born persons is  
that their genetic data is a facsimile of their donor. Otherwise, they are indistinguishable from that  
of a “natural” born person. 
 

Partial cloning is common enough in the medical field. Tissue, major organs, viable follicles,  
limbs, and bodily fluids -- nothing capable of conscious or unconscious thought -- are all  
commonly cloned in order to provide a donor exact-match replacements, generally to satisfy  
medical requirements. Again in this case, donors must display informed consent as determined  
by their culture or state before even this type of cloning is allowed. 
 

The above is how cloning works in civilian life. In a military context, it is different. It is important  
to know how echoes and artifacts of recent history weigh modern perception on clones in the  
Third Committee’s Union. 
 

Under the Second Committee, clones were a popular option for states, corporations, and non- 
government entities in need of labor, muscle, or constituents. The anthrochauvinist government  
widely viewed clones not as individual persons, but the legal property of their donors -- a kind of  
persistent patriarchal construct that recognized donors legally as the “progenitor” of their  
offspring, giving them all legal right over beings that would not have existed without the donor’s  
intervention. 
 

Clones under the Second Committee occupied this second-class tier of person. They were  
viewed as individuals, but with truncated legal right, as they were officially the result of an  
“investment” made by their progenitor. Thus, they were allowed to be pressed into military, labor,  
or other dangerous service, with their owners only mandated to provide the bare minimum level  
of care to ensure that they did not die on account of hunger, thirst, or “easily preventable illness  
or exposure”. 
 

                                                                                                         


Clones were widely used by state and private militaries, with specific martial traits emphasized  
by geneticists; under the Second Committee, clones were rare in civilian life, though commonly  
encountered in retinues among the upper classes of more stratified societies. Among the  
Baronies in particular, clones occupied the highest echelons of society as facsimile-heirs,  
doubles, and tokens of pleasure-trading; they often formed the entirety of many barons’ labor  
force, as well. 
 

In times of crisis, or when a state or non-state entity needed a rush order filled, flash clones were  
used. 
 

Grown in artificial birthing chambers, so-called flash clones could be cultivated from zygote to  
adult in less than five years. Whole both flash and facsimile clones began with the same donor  
materiel, the accelerated growth process that flash clones undergo is often traumatic and prone  
to error. Where facsimile clones have the duration of a natural life to learn, grow, and form their  
own subjectivity, flash clones were typically task-focused -- needed to fill out the ranks of armed  
forces, or to replace a depleted mining corps -- and disposable. 
 

Because of the traumatic growth and cognition process of flash cloning, these clones were prone  
to rapid onset degenerative diseases, atypical neurogenesis, a wide range of anomalous tumors,  
catastrophic immunodeficiencies, and so on. This was not viewed as a process in need of  
correction, as success rates were greater than 50%, and the people made in this manner were  
intended to be disposable. 
 

Flash cloning was a process designed to churn out human bodies with speed, not accuracy, and  
set the people that it made to one task -- usually menial labor or fodder, with little regard for their  
rights, decency, or humanity. The Third Committee rejected flash cloning as part of its manifesto. 
 

Now the process that bears the name “Flash” cloning is typically reserved for medical  
constituant tissue cloning -- simple procedures where a limb, gross tissue, digits, minor organs,  
or major organs are needed to rectify a stable patient’s physical trauma -- say, to graft new skin  
on after a burn, or to transplant a perfect-match organ or limb where one has been severed or  
otherwise disabled. 
 

Cloning methods practiced under the Second Committee are still present and occupy a grey  
legality space. Outlawed by the Third Committee, whole body flash cloning is known to be  
practiced by Harrison Armory and a number of the larger houses in the Baronies. Progressive  
Third Committee members urge action to fulfil their mandate, and often set the DoJ/HR to  
enforce the ban on smaller targets; the Armory and the Baronies argue that their processes bear  
similarities in name only, and that their processes are safer than the old practice prior to the Third  
Committee’s rise to power. 
 

UN DoJ/HR’s Facsimile Rights Department frequently handles legal claims of facsimile persons,  
as well as oversight of cloning facilities, spot checks, and maintenance of public genetic proof  
data. UN DoJ/HR Liberator teams commonly run point on regulation and enforcement actions on  
ID’d flash cloning sites. 
 

                                                                                                          


Should one of your players wish to play as a facsimile person, they would have some knowledge  
of their donor. Should they wish to play as a flash clone, they would likely be a citizen (to some  
degree) of Harrison Armory or a subject of one of the Karrakin Trade Barons. Their natural life  
span may or may not be truncated as a result of the flash cloning process. If they wish to play as  
a flash clone of an entity other than the Armory or the Baronies, then they might face more  
complications, as well as likely being regarded as a sympathetic witness in a UN DoJ/HR  
investigation. 
 
\subsection{Androidism, Transhumanism, and Divorced Consciousness}
Androidism, Transhumanism, and Divorced Consciousness  

Whole-body or majority-body technical and biological augmentation is uncommon in Union,  
typically reserved for elective subcultures and medical necessity. Transferring consciousness --  
divorcing it from its physical form, containing it, transporting it, and implanting it in a different  
organic or inorganic, physical or digital space, form, or unit -- is currently impossible with the  
technology that Union has. Furthermore, the First Contact Accords agreed to following the  
Deimos Event prohibit substantive research into such technologies.  
 

On a given developed Core world, the average adult will have a small complement of personal,  
medical, or professional modifications, augmentations, and enhancements. Tailored panacea  
cells for warding off disease, subdermal aural netting with a linked omnicaster for communication  
via the omninet, full or hyper-spectral ocular modifications to enhance their vision, embedded  
pay chits, and so on.
 

On a given developed Core world, it is noticeable but not uncommon when a person has a  
visible, clearly inorganic body modification. Typically, if they’ve visible, the person wants them to  
be seen as a fashion or other aesthetic statement, or they are a major prosthetic. 
 
 
 
On a given developing settlement or colony world, an average adult will have a small  
complement of personal/professional modifications, similar to an adult on a Core world with  
slight but significant differences -- localization to harsh climates, a more aggressive panacea  
system, and so on. 
 

Heavily modified persons tend to be either survivors of terrible accidents or attacks that need  
modifications to live, people who have opted for extensive augmentation to better manage a  
chronic or genetic condition that would significantly impact their quality of life otherwise, or they  
work in a specialized field and have opted to (or been encouraged to) undergo extensive  
modification in order to perform their duties. 
 

Generally speaking, a subdermal or internal augmentation is small enough to not tax a body too  
much, but the closer a person gets to majority inorganic body mass, the more difficulty their  
organic system has in managing major systems without significant chemical or external support. 
 

Because of the systemic stress, danger posed to organic matter by radiation, and energy  
limitations on the human body, it is not yet possible to modify a person enough that they can live  
in perpetuity exposed to hard vacuum. It is possible to extend the time a person can survive in  
the case of spacing, but these biological modifications are usually only found in Cosmopolitans,  

                                                                                                                  


naval personnel, and other professions where there is considerable risk of hard vacuum  
exposure.  
 

Aesthetic biological body modification is common enough and varies depending on cultural and  
counter-cultural practices. Generally, light aesthetic body modification is something additive, and  
can be obtained from a wide range of locations on a given Core world, from expensive private  
clinics to streetside kiosks. Skin color tint, patterning, eye coloring, hair coloring, piercing,  
scarring, feathering, tattooing, hair/fur promotion, and so on. Heavy modifications such as  
secondary limbs, tails, changes to digits, etc, are rare -- usually only found in counter-cultural  
cliques.   
 

Various subcultures exist around extensive augmentation -- androidism -- from transhumanist  
movements and disability rights groups, to android cults and nihilist machine adherents.  
Androidism is a movement with many subcultures, and common dialogue around it is usually  
lacking outside of technical, academic, medical, and other nuanced settings. Depending on the  
world(s) your character visits, they may face some prejudice from the dominant culture. 
 

A second, related field of transhumanist concern is the identification, manipulation, and  
perpetuation of an individual’s consciousness beyond the body.   
 

True consciousness transfer, or decorporalization (often abbreviated to CT/DeCorp) is not  
currently possible, but it is a field of interest for paracausal atheorists. 
 
Both the Union Science Bureau and Harrison Armory’s Think Tank are known to test the edges of  
what the First Contact Accords allow, but both operate in a tight, closed, information-sharing  
agreement, with Union having ultimate regulatory power over the Armory. 
 

Private, non-Union study of CT/DeCorp is outlawed, but joint reports from the Union Naval  
Department and Union Science Bureau intelligence divisions have determined, with confidence,  
that there is a high degree of possibility that the Armory, HORUS, and Smith Shimano Corpro  
engage in ontological/acontextual research and development.  
 

False CT/DeCorp is possible and common enough. Professional and consumer grade  
homunculus units are available, but they only simulate personalities. Constructed through deep  
omni mining, uploaded artifacts, and archived psychological evaluations, profiles, and other  
relevant data, homunculi are prominent features in museums, memorials, theme parks, and so  
on. They are not conscious, nor are they true strong or weak AI -- they are simply tuned  
simulations of a person. 
 

For more on the particulars of how CT/DeCorp fits into the First Contact Accords, see The  
Deimos Event and First Contact Accords. 
 

If your campaign features movement towards consciousness transfer or decorporealization, we  
recommend including encounters -- positive, negative, or otherwise -- with elements of the  
Union Science Bureau, Union Intelligence Bureau, Union Naval Intelligence, Harrison Armory’s  
Think Tank, HORUS, Horizon, or SSC’s General Development Unit.  
 

                                                                                                               


Indigenous Peoples and Recontact  

A fact of the Fall and the First Expansion Period is that many worlds under Union -- but that have  
not yet been formally contacted by Union -- now have self-sustaining indigenous populations,  
often with many-thousand-year long cultural histories that track from pre-settlement voyages to  
foundation and the modern day. Only with the rise of the Third Committee has Union taken a  
second look at how it approaches these indigenous enclaves -- and how it intervenes when  
Union-recognized title-holders seek redress for their claims made under the previous  
government.  
 

Prior to the discovery of the blink and stabilization of the gate system, all interstellar space travel  
was made under causal constraints and limitations of relativity, gravity, time, and distance. Under  
the First Committee, habitable worlds were ID’d and their charters sold following probe and  
telescope surveys made to determine their viability. Then, colonial ventures launched generation  
ships -- or, as technology and research into machine minds advanced,  automated, surrogate- 
enabled seed ships -- to physically claim the so-ID’d habitable worlds. 
 

At time of launch, the populations sent to claim these worlds were not legally recognized as that  
world’s indigenous population: only the first generation to set foot on the planet and establish a  
viable colony would be recognized as the legal indigenous population. 
 

Given the temporal complications of relativistic travel, the significant difference between  
generation ships and seed ships often led to conflict: for slower generation ships -- launched in  
the early days of the First Expansion Period and before, during the Fall -- the first generation to  
set foot on a given world was not the generation that embarked on the ship; often, hundreds to  
thousands of years had passed in realtime and subjective time as the ship crossed the stars, and  
shipboard cultures had grown to account for their travel and distant, presumed homeland. These  
landfall generations, while not native to the world that they set foot on, often had a strong  
cultural tie to the world, developed over successive generations on-pilgrimage. They considered  
themselves indigenous to their promised world. 
 

Not so for seed ships. 
 

This pre-landfall cultivation of indigenous culture was a non-issue unless the world a generation  
ship arrived at had been targeted for rapid colonization by later iterations of the First Committee  
-- later the Second -- during the many thousands of years that passed realtime during their  
colonial voyage. The discrepancy between subjective near-c travel and “normal” real time meant  
that while these first waves of pre- and post-Fall generation ships were burning for ID’d stars,  
research and development into near-c “Nearlight” drives advanced, and faster and faster colony  
ships were developed. The first ships sent would, often, not be the first to arrive.  
 

                                                                                          6 
Fully automated, with an onboard organic-parallel surrogate machine mind  to manage neonatal  
and postnatal development upon arrival, these seed ships did not need to take into account for  

6 Many of these seed ships were built and launched pre-Deimos. Modern versions have abandoned their  
machine mind cores in favor of a specialized companion/concierge unit paired with a stable NHP imprint. Of  
course, regular check-ups are needed, and a small team of cycled engineers is necessary as a failsafe.  

                                                                                                                 


organic life and the systems necessary to support it during the long voyage. Combined with the  
faster drives and more advanced survey and navigation techniques, seed ships rapidly  
outstripped generation ships, bolting to ID’d worlds and establishing colonies before the earlier  
ships could reach their destinations.
 

When these landfall generations did arrive, they often encountered states established by native- 
born colonists, hundreds of years old, with systems in place to greet and naturalize the landfall  
generations. This, generally speaking, was not within the cultural narrative of the landfall  
generations, and on many occasions led to conflict and bitter political friction. The faster,  
second-sent nearlight seed ships had landed and produced generations of native-born colonists  
without the cultural history of voyage; to the landfall generations aboard slower-burn generation  
ships, this impatience by Union was tantamount to stealing their promised land from them. 
 

While novel instances of this overlap are nonexistent under the Third Committee, the newly  
formed government faces a host of legitimate grievances filed by indigenous cultures ignored by  
the Second Committee, and petitions for redress by colonial charter holders as a result of the  
Third Committee’s dissolution of the Second Committee’s government. 
 

To address this, the newly empowered Union Department of Justice and Human Rights runs a  
joint court with the Union Colonial Administration Bureau -- reconstituted from the defunct the  
Union Colonial Mission. This court handles all complaints and petitions by landfall (and post- 
landfall) generations and colonial charter holders alike, and is empowered to endow the rights of  
first peoples upon populations following the conclusion of a case. 
 

Standards for determining first peoples is a relatively new body of legal work under the Third  
Committee. Under the Second Committee, primacy was given to populations able to take and  
hold power -- typically the holders of charters and titles -- and not the landfall generations first  
promised the world by previous governments.    

If one of your players wishes to play a character with this kind of background, you/they may wish  
to write their homeworld as one in the middle of an ongoing trial. If this is the case, be aware  
that, while the UN DoJ/HR takes a long time to determine first peoples, the case will be decided;  
time dilation may allow your players to return to a world that has, at long last, be returned to  
them -- or one that has been stolen from them.   
\subsection{Life-Extension}
Life-Extension  

Non-relativistic life-extension through medicines, augmentations, and other technologies can  
carry a human life to around 150 years of age.
 

Relativistic life-extension (RLE) has no “real” limit, but one’s subjective experience of life is still  
limited by their body and the technologies that can sustain it. A person attempting RLE will still  
experience time passing normally: from their perspective aboard their ship, time outside the ship  
will pass at increasing speeds. 
 

                                                                                                              


Thus, when someone going through RLE returns to their home world or arrives at their  
destination, they will have subjectively aged only the hours, days, months, or years that their  
journey took: to everyone else in “real” time, they will legally be much older. More on this can be  
found in the entry under Interstellar Travel. 
 
\subsection{Piracy}
Piracy   

Piracy remains outlawed by Union’s Third Committee, as it was during the Second and First  
Committees. It is an act generally recognized as a predatory assault on an individual or group,  
meant to sow terror, abduct people, and/or steal goods. 
 

Piracy under the Third Committee typically exists in one of two forms: either as state or non-state  
sponsored privateering -- unlicensed mercenary work -- that targets flagged opposition or  
civilian ships, stations, and populations; and as wolfpack piracy, or a self-contained group of  
stateless actors engaging in that same pattern of assault, robbery, and abduction. 
 

Piracy and/or privateering is most common in middle distal, middle proximal, and frontier space,  
areas outside the inner rings where blink travel and core worlds are far less common. Piracy  
relies on scarcity of goods and coverage gaps in the system-local stellar power;
 
following the restructuring of the Union Navy by the Third Committee, Union leans on active  
participation by constituent states to enforce anti-piracy laws. This has led to gaps in coverage  
that both privateers and wolfpack pirates exploit. In response to this uptick in piracy, some in the  
Third Committee have called for a series of trial programs using the Union Navy to address the  
problem directly, rather than relying on the cooperation of constituent states. Debate is ongoing,  
meanwhile the problem remains. 
 

Whether privateering or engaging in wolfpack piracy, stellar piracy most commonly manifests in  
two places: in interstellar shipping and transit lanes, where pirates know nearlight ships,  
freighters, and yachts will be underway, bound to or from a local blink gate; and in low to  
medium orbit, where shuttles and corvettes will transport goods and people from a planet’s  
surface to a waiting ship or station. 
 

Piracy in interstellar shipping lanes is risky in that the location and time of a potential attack is  
known to all parties. Without the protection of low-to-medium orbit debris, asteroid fields, natural  
and artificial satellites, and high orbital traffic, interstellar piracy relies on a far more advanced  
suite of systems, sensors, tactics, and other technical packages. 
 

To interdict a nearlight ship of any class bound to or from a blink gate means meeting it at like  
speed -- so to begin, any pirate engaging in interstellar piracy will typically have a standard of  
vessel far above that of an orbital pirate. Engaging a nearlight ship of any class at-speed requires  
a significant investment in navigation suites and personnel, as well as the ability to spoof,  
misdirect, conceal, or otherwise confound a target’s near/sublight proximity and active sensors.  
Beyond the power plant and navigational capacity at least as good as their target, a pirate  
attempting to interdict a nearlight ship generally will mount weapons systems that are accurate  
and precise -- their payout is only good if the goods, vessels, or persons they’re attempting to  
steal are intact and functional, or could be made functional with minimal repairs. 
 

                                                                                                         


An engagement, if it happens, would happen fast and with little warning; milspec signals  
spoofing, misdirection, or concealment technology is strong, outpacing the sensor suites of  
civilian and merchant ships. Oftentimes the first warning one has of an impending attack is a  
ship’s impact sensor -- generally a simple, independent, dedicated system -- issuing a proximity  
or likely-trajectory proximity alert. 
 

This alert, unless the pirate’s sig/int attack fails scrutiny prior to the proximity warning, generally  
targets sensitive areas on mapped hulls: drives, life support subsystems, crew quarters, and  
weapon magazines or batteries. Pirates generally use precision weapons (as noted above)  
intended to pierce one or two bulkheads and fragment upon registering 0  -- soft target killers,  
                                                                                            2  

relying on fragmentation and combustion to eliminate organic personnel -- or lead with massive  
systemic attacks meant to cripple a ship and/or give priority administrative control over to the  
pirate’s ship.   

Once the target ship has been disabled or their speed matched -- it is difficult and dangerous to  
make sudden maneuvers while approaching c -- then pirates will assume direct control of their  
target ship, either by systemic or physical means.   

Interstellar piracy is the home of wolfpack pirates -- dangerous, dedicated non-state actors and  
their retinues -- who are Cosmopolitan professionals, many with naval backgrounds, and access  
to a wealth of experience and technology gathered together over their long years of piracy. They  
are rare, given the amount of experience and tech that goes into interstellar travel and piracy, and  
on account of their constant exposure to the effects of relativistic and gravitational time dilation,  
they  -- like the Albatross -- often attain a legendary status among their pursuers, victims, and  
fans.   

In low to medium orbit and within solar systems, piracy is decidedly more low-tech and localized,  
generally the domain of privateers who adopt the role temporarily, resistance or opposition groups  
looking to disrupt local governments, or well-funded local criminal elements seeking to diversify  
their portfolios or gain more notoriety.   

Orbital and systemic piracy is messy and low-tech where interstellar piracy is elegant, expensive,  
and storied. Orbital pirates rarely utilize subline or capital ships in their engagements, instead  
preferring the maneuverability, atmospheric capabilities, anonymous, and and cheap platforms of  
shuttles, corvettes, and light freighters. The name of the game for orbital and systemic pirates is  
to strike fast, grab what is valuable, and escape, either to a safehouse back on the planet’s  
surface, or to a nearby moon or station where they can hide.   

Often, orbital piracy begins as a ground-to-orbit engagement, with powerful mobile antennae on  
the ground -- or sited on a nearby moon or other natural satellite -- blasting the pirates’ target with  
bombard code and white-out attacks, taxing sensor, comm, and navigation suites with  
overwhelming, single-use system spikes -- systemic weapons often developed by black-hat  
coders, designed for simple, limited use -- to cover the pirates’ advance.   

Previously mothballed fighters, converted freighters, armed and armored shuttles, and other  
myriad ships follow the whiteout attack, main guns and onboard weaponry firing in classic kill- 

                                                                                                                      


cloud, mass-helix, and other common kinetic patterns. These ships are, generally speaking,  
stripped of all extraneous systems but their drives, weapons, cockpits, and some rudimentary  
armor: their goal is simply to physically disable their targets and land their payload -- subalterns,  
drones, or pirate marines. Surviving multiple engagements is not a priority, as if these pirates are  
successful they’ll simply use their haul to buy new scrapper ships, or convert their targets for use  
in the next raid (after they’ve been stripped for parts, of course).   

Orbital pirate attack wings feature a mix of reusable fighters and single-use transports (crash  
taxis, tin cans, party busses, trojans, and so on) that carry squads of synthetic and organic  
marines to physically seize control of the prize ship(s). These single use transports are often little  
more than a debris shield mounted at the front of a rack -- an armature structure that can secure  
its passengers (be they subalterns, organics, or mechanized chassis) via magnetic clamps,  
straps, or handholds. Fired from larger ships or self-propelled, single-use-transport doctrine sees  
these ships crashing into their targets and engaging their solid-state boosters, throwing the target  
ship(s) off course and further impairing their ability to disengage.   

Including pirates -- interstellar or orbital -- in your campaign can be a fruitful way to introduce your  
players to the politics of a region or a compelling villain (or anti-hero, or hero). Moreover, they  
make for an easy random encounter, persistent threat, or foil for the players and their group.    

A universal code of stellar conduct demands any ship that hears an S.O.S hail must respond if  
able, or face legal penalties.
 
\subsection{Slavery}
Slavery  

Now outlawed by Union’s Third Committee, once allowed with special exception by the Second  
Committee, who viewed flash clones and facsimile clones as property rather than people .  
 

Union’s DoJ/HR runs an active emancipation mission, a holistic liberation-to-integration program  
meant to not only liberate enslaved peoples, but resettle them and support them throughout the  
recovery process. 
 

DoJ/HR Liberator teams are tight-knit, small-to-medium size strike and support teams similar to  
USB Far Field teams. Their general doctrine is liberation-focused: force is valued over diplomacy,  
with their prime objective being to liberate the enslaved at cost of their masters. Their doctrines  
emphasize either infiltration and agitation or direct, top-down confrontation, depending on the  
specificities of the situation. 
 
\subsection{Paracasual Studies}
Paracausal Studies  

Not known as a field of study outside of high-tier USB campuses, however, certain Corpro- 
States -- Harrison Armory, HORUS -- are pushing into this field without Union’s approval. 
 

                                                                                                          


The extent of these CSs knowledge is a known-unknown, as joint USB-UN intelligence teams  
have engaged in clandestine missions to infiltrate and identify sites, programs, and campuses  
where unsanctioned paracausal studies are taking place.    
