\section{Timeline of Union's History}

Timeline of Union’s History  

-5000U: Anthropocene Epoch ends with the ecological and data collapse of Old Humanity. 
 

Intervening Period: The dark ages. Cradle’s population falls to estimated 300,000 persons from  
peak of around 15 billion. 
 

-150U: The first Vault, Massif-A, is discovered on Cradle (nee Earth), prompting worldwide  
civilizational growth and change.
 

-53U: The Little Wars begin.  
 
 
 
0U: Union founded after the conclusion of the Little Wars. The First Committee Established. 
 

1968U: Logged SOS transmissions received after Union reactivates long-range communications  
systems. Union Space Program announced shortly thereafter.
 

1970U: Union Space Program lands and reactivates lunar installations. Shipyard THESEUS  
reactivated. First  NEARLIGHT-CLASS ships built and launched. Following legacy star charts,  
Union establishes a colony on an ID’d Gaia world. Encounters the Aun shortly thereafter. Contact  
lost with Union colony.  
 
 
 
2000U: Mars-based ORACLE CHORUS installation discovered following GRADUATION DAY  
landings on the Vastitas Borealis. The Five Voices reactivated, contained, and managed by early  
elements of what would become Forecast/GALSIM.
 

2000U-2998U: First Expansion period. Multiple Old Human colonies discovered. Some derelict,  
others inhabited. Union Administrative Department created to manage expansion effort and  
reintegration programs for rediscovered exclaves.  
 

2880U: Second contact with the Aun Ecumene. Diplomatic failure turns to first interstellar  
conflict: now called the First Distal War. Union retreats, and hardline elements in the Union Space  
Program ignore no-fly cordon, launch a flight of “dumb” kinetic TBK weapons towards presumed  
location of the Ecumenical homeworld. Bitter political struggles grip Cradle, give rise to the  
Second Committee.  
 

2998U: RA manifested from Five Voices forecast iterative.     
 

3000U: The Deimos Event, RA’s ascension. Paracausality Studies born. Disparate ships, shuttles,  
and force organizations of the Union Space Program organized into the Union Navy.  
 

                                                                                                                  


3002U: First Contact Accords signed with RA. Non-Human Person identified as category.  
Shackling developed. 
 

3130U: Blinkspace identified and pierced. Blink fields created, first gates created, first blink  
station opens and stabilizes. Second Expansion Period begins. Union Administrative Bureau  
dissolved, replaced with Union Colonial Mission.  
 

4500U-4600U: Hercynian Crisis. Efficacy of hard suits and mechanized chassis shown: first  
galaxy-wide production and adoption of mechanized chassis (“mechs”) begins via Union state  
armorer, General Massive Systems. Second Committee deposed in a popular coup following  
revelations surrounding the Hercynian Crisis. Union Colonial Mission dissolved, replaced with  
reconstituted Union Administrative Bureau.  
 

5000U: Reports of Aunic crusade fleet operating in the Boundary Garden sector of expansion  
space confirmed. First reported loss of a Union blink gate due to hostile state actions. Second  
Distal War begins. 
 

5014U: Attack on Green Zone Alhambra , beginning of Operation Clarion in the Dawnline Shore
 

5016U: Narrative present of Lancer. 
 

                                          