\section{Union: The Tyrant, The Watcher, The Guiding Hand}

Union: The Tyrant, The Watcher, The  
Guiding Hand   

Union is the hegemonic power in control of the three pillars that prop up the human diaspora:  
the blink network (FTL travel), manna (universal galactic currency), and the omninet (the near- 
instant communication network that keeps the diaspora connected, trading, and  
communicating). 
 

Without these three pillars, the human diaspora would be scattered across the populated arm of  
the galaxy — the Orion Spur — time and distance both too great a factor to keep Union intact.  
Humanity would fracture into tens of thousands of individual states, some claiming scant territory  
on backwater colony worlds, others able to maintain whole solar systems.
 

The fall of Union or end of Union’s hegemony would, of course, not mean the end of the “world”  
— just the end of an era.
 

For some in the galaxy, shattering Union is a good idea — humanity would be free of the  
hegemony’s tyranny, free to explore unrestricted physical and mental space. Each nation —  
stellar or terrestrial — could chart their own course, have ultimate sovereignty over their own  
lands, and explore the secrets of the galaxy without having to answer to a distant and alien  
overlord.
 

However, Union works towards a greater purpose, one unknown to the vast bulk of the human  
diaspora: They work to preserve human existence on a galactic scale, following the edicts of  
their most powerful minds to ensure humanity spreads across the stars, never to be threatened  
by an existential crisis. Union works night and day to accomplish this goal: in the narrative  
present of Lancer, Union has reason to believe that humanity might be under threat of  
            4 
extinction  .  

But for the vast bulk of humanity, Union is a distant concept, rarely — if ever — encountered by  
normal people going about their day-to-day lives. Space, remember, is a vast, vast place. Blink  
gates allow for faster-than-light interstellar travel, but only a slim percentage of the human  
diaspora actually engage in interstellar travel. To a farmer (or your other average person) on a  
distant agricultural world — Cornucopia, to use a canon example — encountering a Union  
administrator would be a once-in-a-generation event, something that they’d regale their  
grandkids with stories about decades later. Encountering the military arm of Union — the Union  
Navy and its auxiliaries — is an epochal event. Far more common for your average human is the  

4 It should be noted — Union’s home system is Cradle, what we call Sol, and I use the term “alien” here  

not to describe a different species, but as a cultural and legal designation. Union administrators are human  
beings, but to a person born and raised on a planet light-years away from Cradle, a Union administrator  
and their retinue are, essentially, alien. 

                                                                                                                


comfortable interaction with their own town, city, planet, or system-wide authority — be it a  
monarchy, a worker’s collective, a priesthood, etc. 
 

And for a slim percentage of humanity, Union is a common entity. Outside of the citizens of  
Cradle and her core systems, the vast bulk of people who know of and deal with Union and her  
representatives on a regular basis are political elites, cosmopolitan interstellar travelers,  
scientists, and military commanders. 
 

Political elites include the rulers of planets or star systems, or the governors of blink stations —  
people who command fleets, worlds, or the gates that connect them.   
 

Cosmopolitan interstellar travelers commonly include traders, merchants, valued pilots, and  
others who deal in interstellar commerce, legal or illegal. People with means who have reason to  
make their homes in their ships and among the stars, people who travel the blink network for  
trade, exploration, crime, or adventure may have, at one point or another, crossed paths with  
Union administrators, scientists, military, or other officials. 
 

Scientists who interact with Union trend towards the STEAM fields. Physicists, Planetary  
geologists, engineers of all stripes — the omninet is rich with information and the galaxy is  
riddled with mysteries. Scientists who bend towards the humanities often fall into the previous  
category of cosmopolitan interstellar travelers, as their studies require them to embed with other  
cultures, travel the blink network, or journey to distant, dead worlds.
 

Finally, military professionals often encounter Union through messier scenarios: either fighting as  
a member of a Union auxiliary unit or in the Union Navy itself, or fighting against Union’s Navy  
and its local auxiliary units. 
 

Union is devoted to a single goal: perpetuate, preserve, and protect the human diaspora to  
                                        5 
ensure the survival of the species  .
 
\subsection{The Third Committee}
The Third Committee  

The narrative present of Lancer takes place during the reign of the Third Committee, the third  
iteration of Union’s central government and ruling body, the Central Committee. The Third  
Committee is the product of lengthy negotiations following a coup that deposed the  
anthrochauvinist Second Committee, to date the longest-ruling council and central government in  
Union’s history.   

5 A note on terminology: The local system cluster Union occupies is called Cradle; Cradle also refers to  

Sol, humanity’s origin system. Humans from Cradle refer to themselves as Humans, Terrans, or, less  
commonly, Solars or Gaians. When speaking of their home, they would refer to it as a proper noun or in the  
singular (i.e. “I am Union” or “I am from Union”) or to the planet, station, or moon they call home. 

                                                                                                                 


The Third Committee is marked by a rejection of the Second Committee’s strong Cradle-centric  
anthrochauvinist values: aggressive colonial expansion and reconquest in the name of Cradle’s  
survival have been replaced with a hands-off, slower approach, embodied by the Union  
Administrative Department. The Third Committee bore witness to the crimes of the Second --  
Hercynia, the TBK authorization against Aun’Ist, countless iron-hand colonial suppressions -- and  
reflects its desire for a slower, moderated colonization and integration of the galaxy.   

The Third Committee dramatically reduced the Second’s Navy, developing the Auxiliary doctrine  
and naturalization process as a way to build intergalactic state solidarity through shared work,  
rather than relying on a centralized colonial force. The Third correspondingly increased the size  
and scope of the Union Administrative Department, dramatically increasing the department’s  
portfolio and prominence. Where the Navy once was the first point of contact for humanity’s  
diaspora, now the light grey of an Administrator’s suit would become the way by which the  
disparate spread of humanity would recognize Union.   

The Third Committee, recoiling from the hard power preference of the Second, has adopted a far  
more hegemonic posture, choosing to rely on the soft power of culture, commerce, travel, and  
communication to bring the galaxy under its control. In an early act of revolutionary fervor the  
ThirdComm dissolved the once-formidable Union Colonial Mission (UCM) -- a bureau with a  
history stretching back to Union’s First Committee and humanity’s first forays into space -- and  
replaced it with the Union Colonial Administration Bureau (UCAB) and the Union Department of  
Justice and Human Rights (DoJ/HR). Where the UCM’s mission was once to recontact,  
recolonize, and re-integrate, the UN DoJ/HR’s mission is to review, report, and -- if necessary,  
respond with the same force that the UCM once mandated as a first step.   

The Third Committee’s approach to managing the galaxy is not without its trade offs and  
challenges; criticism abounds as to the perceived lack of urgency around the Committee’s  
approach to violations of Union code. This criticism is not entirely without merit, nor without further  
complicating context: many bureaus, departments, and agencies hold a strong institutional  
memory, and internal tension between Third Committee reformists and Second Committee  
conservatives complicates the necessary functions of said departments. Some bureaus are  
almost entirely populated with Anthrochauvinist party members: the Union Economic Bureau is  
the worst offender (or, depending on the point of view, the great hope).   

To further complicate the pacifist leanings of the first wave of ThirdComm party members, a new  
generation of interventionist party members has recently been elected to office. While rejecting  
Anthrochauv philosophy, they view Union’s mandate as one demanding a far more interventionist  
stance -- the pillars of Union need cultivation, not just stewardship, and following the success of  
the first wave’s coup that deposed the Second Committee, the time is ripe for the Third  
Committee to make its presence known among the stars as agents for humanity, rather than  
agents of humanity.   

This second wave of ThirdComm party members were sworn into office in 5012. It is now 5016,  
and the Third Committee faces a growing Aunic threat in Boundary Garden, a mounting  
humanitarian crisis in the Dawnline Shore as Harrison Armory works to re-take its old colonial  
holdings, and numerous other internal points of pressure where their theories of intervention and  
non-intervention will be put to the test.   

                                                                                                            

\subsection{Byzantium, Reprise }
   

Byzantium, Reprise  

Union’s bureaucracy is vast. Its most notable departments are detailed below. 
 

Union’s executive administrative body is the Central Committee. They’re advised by the  
Forecast/GALSIM, and delegate edicts to the Union Administrative Department. The Union Naval  
Department operates at the pleasure of Forecast/GALSIM’s subcommittee, GALCOM, and is  
subordinate to the Central Committee. The Union Science Bureau operates at the direction of  
Forecast/GALSIM and, as a non-political, non-military body, are directly subordinate to F/ 
GALSIM. 
 

Union is not a perfect administrative body. The most general and most widespread ideological  
difference in Union’s bureaucracy is found in the ongoing discussions around how best to apply  
Union’s considerable power through the galaxy — whether or not they should intervene where  
there are clear violations of Union’s human rights charter, whether or not they should assume  
direct control over subject states, and so on. 
 
 
\subsection{Union Administrative Department (UAD)}

Union Administrative Department (UAD)  

Union’s largest administrative body is the Union Administrative Department, which dispatches  
Union Administrators across the populated galaxy to act as liaisons between Union and its client  
states. UAD receives guidance and recommendations from Union’s Central Committee, which it  
then pushes as command imperatives to its Administrators, who relay them to the local ruler they  
advise. 
 

Administrators are vast in number, but a rare sight in the much larger diaspora: they commonly  
only deal with a state’s ruler or ruling council. To common Diasporans and Cosmopolitans, an  
Administrator is an enigmatic, dangerous, appealing figure: they consort with NHPs, they are  
responsible in part for steering the course of civilizations, and they are Union, for most people  
the corporeal presence of an otherwise distant, almost mythic ruler. Their word seemingly  
supersedes the word of kings, presidents, popes, and all the rest. Union Administrators  
commonly travel with a retinue of subalterns — humanoid robots that contain a partitioned and  
shackled Non Human Person. 
 

Administrators are pulled from all areas of the galaxy by esoteric, exacting criteria. Typically  
chosen as children, Administrators train alongside a new NHP companion, one built to pair with  
them. The UAD has satellite campuses seeded all over the populated galaxy, but in the course of  
an Administrator’s decades-long training and apprenticeship, they will spend some time on Earth  
— an experience meant to be an acute reminder of humanity’s origins. 
 

Unlike most arms of Union’s hegemony, Administrators avoid integrative/ auxiliary doctrines.  
They are meant to be seen, meant to be an easily identifiable marker of Union’s dominance. They  

                                                                                                                  


wear a uniform — a clean, dark Union Grey suit regardless of gender presentation — their rank  
as Administrator denoted by a silver pip on the collar. Their subalterns adopt a similar livery of  
matte grey. Their exposure, generally speaking, is profitable for Union, save for cases where local  
knowledge of the Administrator’s role would put their life or their mission in jeopardy. 
 

Attacking a Union Administrator is a sure way to draw the attention of a Union Navy battlegroup.   
 

Union Administrators, upon graduation and notification their posting, choose a name local to the  
culture they will be embedded in. Since they must engage in interstellar travel, their old name  
and personal data are declared dead, formally retired as part of the graduation ceremony. 
 

Together with their subaltern NHP, the newly minted administrator will head out into the galaxy to  
give counsel, file reports back to the Union Administrative Department, and ensure their host  
state develops according to the missives they receive from Cradle.   
 
\subsection{Union Naval Department (UND or, more commonly, UN)}
Union Naval Department (UND or, more commonly, UN)  

The Union Navy is the largest and most powerful fighting force in the populated galaxy, on paper.  
It is subordinate to the Central Committee, though takes strategic and logistic direction from  
GALCOM, a subcommittee of Forecast/GALSIM.
 

It is a sprawling, carefully administered organization that project’s Cradles power to all corners of  
the populated galaxy and beyond using a (relatively) small core of Union-flagged capital and  
supercapital ships, supported by vast numbers of standardized, integrated auxiliary ships pulled  
from Union’s subject states’s navies.
 

The Navy, beyond a relatively small core of ships, is an administrative and diplomatic body that  
shares a healthy institutional rivalry with the UAD: where the UAD relies on Administrators to  
accomplish their diplomatic goals, the Navy relies on its corps of Naval Liaisons to accomplish  
their logistical aims. 
 

Naval Liaisons are officers of a parallel rank to Administrators, with added imperative authority  
that applies in times of crisis. Administrators — generally, unless the local culture demands it —  
are unarmed; NLs carry a sidearm and wear Naval Black uniforms, clearly marking themselves as  
military. 
 

A Liaison is not sent to a state unless that state is capable of building ships or adapting extant  
ships to Union Naval specifications and classifications. Liaisons guide capable states in the  
production, training, and theory of naval combat, with the goal of establishing a well-trained  
corps of ships that can be integrated into the larger UN structure. The UN then further integrates  
that corps of ships and sailors into the larger Naval structure, offering interstellar contracts to  
crews and corps willing to progress further in rank. The rest are relegated to local system anti- 
piracy, peacekeeping, and police actions. 
 

Administrators tend to view Liaisons as an imposition on their diplomatic mission, bureaucrats  
who come in after the hard work is done and demand a military tithe from the Administrator’s  

                                                                                                                   


host state. Liaisons tend to view Administrators as too possessive of their host states, small-time  
bureaucrats who have an inflated sense of worth and fail to see the larger picture. 
 
 
\subsection{Union Science Bureau (USB)}

Union Science Bureau (USB)  

The Union Science Bureau (USB) is the central administrative body of all Union accredited  
universities, colleges, scientific institutions, and think tanks. They are — ostensibly — not a  
political entity, so they are not accountable to the Central Committee, though they are subject to  
edicts translated through the Committee from Forecast/GALSIM. 
 

The public face of the USB are their accredited institutions, which recruit and encourage  
applications from the diaspora; however the most popular and common depiction of the UAB is  
of their Far-Field teams, small groups of scientists and their subalterns that do long-range,  
interstellar field work — usually identifying, cataloguing, and doing first-touch explorations of  
potentially habitable worlds and moons. The USB’s Far-Field teams draw romantics, wanderers,  
loners, and passionate scientists, technicians, philosophers, and engineers of all disciplines.  
Their missions are dangerous, often involving relativistic travel and long-term stasis holds into  
virgin systems not-yet connected to the blink network: as such, and in keeping with a number of  
other Union standard practices, FF team members’ original identity is declared legally dead and  
replaced by a Cradle ID package upon graduation. 
 

FF teams make up a minority of the USB personnel, though they drive recruitment through  
heavily romanticized omninet dramas. A USB science officer has the equivalent UN rank of 2nd  
Lieutenant, should they ever have a naval escort or attachment. 
 

USB Far Field team members are commonly referred to as Rangers, a title taken from the USB’s  
standardized field team Ranger-class deep space ships. Ranger-class deep space ships typically  
support a crew of ten with an onboard, replicable NHP.  
 

The vast majority of the Union Science Bureau personnel fill research and development roles in  
terrestrial and orbital research stations. These institutions have varying degrees of access and  
public knowledge of their existence: most are publicly known and accessible. With rare  
exception, the campuses where the most secret and sensitive work is done are hidden or  
otherwise inaccessible to those without clearance. 
 
 
\subsection{Union Central Committee (CentComm)}

Union Central Committee (CentComm)  

The executive body of Union’s civil government is the Union Central Committee, and makes its  
seat in Cradle. 
 

Cradle — Earth, as it exists in the narrative present — is an administrative/sanctuary world, still  
in recovery from the collapse that birthed Union. 
 

                                                                                                                     


Cradle, and CentComm, are largely isolated from the events of the galaxy, though few -- if any --  
other bodies have comparable access to information and data. Under advisement of Forecast/ 
GALSIM, with information and accounts from curated omninet feeds, and with input from  
representatives of the diaspora, CentComm issues edicts to be distributed amongst its vast  
network of client states. 
 

The Central Committee  is a vast administrative body on par with the UAD, USB, and UN, and is  
spread across campuses around Earth. 
 

Union’s central government has gone through three iterations, the First Committee, the Second  
Committee, and now the current Third Committee.  
 
\subsection{Forecast/GALSIM}
Forecast/GALSIM   

Forecast/GALSIM is an interpretive body headquartered on terraformed Mars. Its existence, as  
well as the existence of its subordinate bodies, is kept secret, classified to all but the members of  
the Union Central Committee and the directors of the Union Science Bureau, Union Intelligence  
Bureau, Union Navy, and their immediate staff. 
 

Forecast is the codename for GALSIM, itself a portmanteau of Galactic Simulation. GALSIM is an  
iterative/interpretive body based on Mars, hidden from the galaxy — including most in Union. Its  
personnel are rarely recruited from off-world. 
 

GALSIM is closer to a monastic order than a branch of government: due to the esoteric nature of  
its mission, a certain dogmatic approach is necessary. Advancement through the ranks of  
GALSIM is predicated on favor of the minds, ability, and seniority — emphasis is placed on favor  
and ability, as empathetic connection to GALSIM’s deliberative body is more important than time  
spent walking its subterranean halls. 
 

GALSIM is the interpretive body and department title: GALSIM’s deliberative body, the entity that  
guides Union’s growth and grand strategy, is a congress of five Sovereign-class non-human  
persons held in a stable metafold of blinkspace under the surface of Mars: Patience, Muse,  
Impetus, Burden, and Watcher.
 

These five Sovereign Class NHPs -- the Five Voices -- are the only of their kind: unconscious,  
bicameral minds, which allows them to operate to the full extend of their ability without  
safeguards. As noted in Artificial Intelligence and Non Human Persons, artificial intelligence  
occupies a space of tension in Union — bicameralism was an early branch into machine mind  
development that proved profitable for pre-collapse humanity, but was developed too late to  
prevent the collapse that would plunge Earth and her peoples into a millennia-long dark age.  
Now it represents the allowable spur of paraconsciousness development, cut short by  
MONIST-1’s demands entered in the First Contact Accords. 
 

                                                                                                         


The core tension around the use of non-human intelligence, paraconsciousness, in Lancer is  
twofold. Even with early advances into the field, humanity had the capacity to creates a class of  
being with minds alien and irreconcilable with humanity’s subjectivity; creating such beings and  
forcing them into subservient roles would set up an unsustainable scenario, where these  
unknowable beings would grow in power and ability until they could challenge their self- 
proclaimed masters. 
 

This theory was not widely accepted until MONIST-1 (“RA”) proved this thesis true. When it  
offered terms to the Second Committee, they accepted. As a result of these First Contact  
Accords, Union has taken a hardline stance on prohibiting further development into  
paraconsciousness. 
 

However, bicameral structures allow Union to get around the problem of conscious thought.  
Unlike a conscious mind, a bicameral mind cannot be introspective — the split structure of their  
artificial mind removes the ability for novel introspective thought, replacing it instead with a  
“second” voice, an Other’s voice that speaks inside the bicameral mind, to the bicameral mind.
 

What humans — conscious beings — perceive as “thought” is often their own voice speaking to  
them nonverbally in their own mind; what a bicameral mind perceives as thought is perceived as  
a command, a second voice, a voice the Five have, as one, come to interpret as the voice of  
God.  
 

This creates a twofold benefit for Union: first, they can inject imperative commands and  
corrections into the minds of the Voices, and second, they do not have to restrict any AI growth,  
as the very structure of their minds make consciousness development impossible.  
 

An artifact of the pre-collapse, the Five Voices were found on Mars by pre-Far Field teams sent  
to rediscover and reactivate old human installations there. The Five Voices welcomed human  
contact, having been without their command-voice for many thousands of years real time. As  
unconscious beings, the Five Voices are hamstrung without human directive. They are set to one  
task now: to ensure the survival of humanity. 
 

Together, they hold in their metafold pocket a parallel library of near-perfect simulated models of  
the galaxy projected at interval years into the future. They churn through all available data from  
the omninet to create a more-than-zero-percent representation of all possible causal  
conclusions.   
 

Their pronouncements are then aggregated and picked through by successive orders of GALSIM  
personnel to determine the best fit to ensure humanity’s persistence and survival. Once a plan or  
aspect of a plan is selected, it is disseminated to all relevant wings of Union’s bureaucracy to be  
pushed out to all relevant corners of the galaxy.   
 

The Voices act both as aspects of one mind and independently of each other, using their  
incredible processing power to blend all possible futures into melange and discrete reports for  
GALSIM to process and find the best options for humanity’s progress. 
 

                                                                                                          


In addition to their core task of simulating all possible futures, the Voices run round-the clock  
specific and general simulations at the request of incident commanders, administrators,  
admirals, and members of the central committee — high-ranking Union military and civil officers  
may submit request tickets to GALSIM, who then feed the requested parameters into a Voice’s  
submind. Commanders, officers, and executives outside of GALSIM do not know their requests  
are being filtered up to the Voices. 
 

The Five Voices are secrets of the highest classification. They, in turn, are kept ignorant of the  
vast spread of humanity outside of their chambers. GALSIM keeps them in the dark, so to speak,  
through judicious use of Command Voice. As far as the Five Voices know, their practice of  
structuring more-perfect futures for humanity is their exaltation of God, and their quest is to  
discover Paradise in the potentials. 
 

The Forecast/GALSIM complex is located under the surface of the Mare Boreum on Mars, a  
polar region on terraformed Mars that is largely inaccessible to the populations around the  
equator and in the southern polar regions.  
 
\subsection{Union Omninetwork Bureau (UOB)}
Union Omninetwork Bureau (UOB)   

Manages construction, distribution, maintenance, and policy regarding the omninet, omninodes,  
and access to hardware and feeds. Works to ensure that the omninet is spread across the  
galaxy, is free, convenient, and accessible. 
 
 
\subsection{Union Economic Bureau (UEB) }

Union Economic Bureau (UEB)  

Tracks and adjusts manna, regulates Corpro-States, and has some jurisdiction over the Omni  
and Blink networks, as well as ultimate determination over the direction of GMS, Corpro-State  
contracting and legitimization, and consumer good evaluation.  
 

The UEB is on the way to becoming a major player in the galaxy following the Accords and the  
fall of the Second Committee -- a minor department under the First Committee, the UEB grew  
exponentially under the Second. Under the Second Committee, the UEB implemented manna  
and chartered corpro-states, recognizing their sovereignty over land and product. 
 

With the rise of the Third Committee and the Second’s dissolution, many anthrochauvanist  
loyalists and their families have moved on to command positions within the Triumvirate Corpros  
(IPS-N, Harrison Armory, and Smith-Shimano) and the UEB both. 
 

The UEB competes bureaucratically and directly with the Union Administrative Department.
 
\subsection{Department of Interstellar Transportation (DoIT)}
Department of Interstellar Transportation (DoIT)  

                                                                                                                 


Responsible for managing, planning, and maintaining the blink network, blink gates, and access  
to them. Also sets and certifies safety standards for all civilian and corporate ships seeking an  
interstellar license. Maintains the Union Cartography Department, which maintains the map of  
Union’s explored territory. 
 

Primary court for handling cases involving subjective/real age, subjective/real death, and other  
temporal legal questions. 
 
\subsection{Union Colonial Administration Bureau (UCAB)}
Union Colonial Administration Bureau (UCAB)  

The primary body for granting and maintaining colonial licenses, as well as the first court for  
settling colonial disputes. Also sets colonial priority zones, no-go zones, and handles petitions  
for Core status. 
 

Formerly the Union Colonial Mission, dissolved by the Third Committee and reconstituted with a  
new mission as the UCAB. 
 
\subsection{Union Orbital and Non-Terrestrial Management Bureau (UO/NTMB) }
Union Orbital and Non-Terrestrial Management Bureau (UO/NTMB)  

A body specializing in management and legislation of non-terrestrial habitats. Also a court for  
settling disputes over orbitals, stations, and LaGrange point licenses. The UO/NTMB also  
manages police forces on all non-terrestrial stations, including blink gates. 
 
\subsection{Union Department of Justice and Human Rights (UDoJ/HR)}
Union Department of Justice and Human Rights (UDoJ/HR)  

The primary and final court system for all interstellar and intra-stellar complaints, civil suits, and  
criminal suits. Also responsible for maintaining the Union Charter on Human Rights, which  
regulates clonal affairs across the galaxy, provides input on transhuman policies, and ensures  
compliance with Union legal code. Also maintains the galactic register of Non-Human Persons  
and handles complaints, suits, and legal questions related to NHPs through their Sub- 
Department of Personal Affairs.          

                                                                                                          
