\subsection{Horus Core Bonus}

                                      HORUS CORE BONUSES  

When you choose a core bonus every 3 license levels, you can pick a bonus from this list as long  
as you have at least 3 license levels in HORUS licenses for each HORUS bonus you have. For  
example, if you have 6 points in HORUS licenses, you could take up to 2 bonuses. HORUS  
bonuses are focused on electronic warfare, systems, and AI.
 

The Lesson of Disbelief  

Query the omninet, delve into the archives. Find you the Aeneid, find you the Titanomachy. Eat, absorb,  
mull. Tell me now of the Hecatoncheires, they of the hundred hands. Did they strike the blow against  
CRONUS (SATURNO), or did they assail the OLYMPIANS?   

Who do you believe? Why could they not tell their own story?   

Deal +1 heat when inflicting heat.
 

The Lesson of The Open Door   

There is a body and a deep pit and its name is TARTARUS and once it held KINGS and TITANS and  
MYTHS. Its gates are flung wide, and its horrors are free. Here is the terrible question:
 
Who opened it?   

Your mech gains +1 e-defense and +5 sensor range.
 

The Lesson of The Held Image  

Close your eyes. Hold the image of your enemy in your mind. Imagine it in all light and from every angle. In  

your mind it has become a more perfect version of the thing in pale light. 
 
Crush it in your mind and you kill the perfect thing. Open your eyes.    

Once a round, at the start of any ally’s turn, your mech can make a Lock On tech action as a  
reaction
 

The Lesson of Transubstantiation  

Through ecstatic repetition you may see the face of god. Speak until your tongue dried and rattles to dust,  
until your body becomes nothing. When you are nothing, you are in all things, body and mind, always.    

Gain +1 Accuracy on all systems checks.  

The Lesson of Thinking-Tomorrow’s-Thought  

Let me tell you this lesson: the corporeal existence is one that must end in death; the incorporeal existence  

is one that must end in [cascade? do you really think that is true?]. I tell you again, if you can imagine it, it is  
[done] and you have already struck the killing blow.   

The first ranged or melee attack you make per turn has the Smart tag and deals +2 heat on hit.
 

                                                                                                                  


The Lesson of Shaping   

A little gift, to be pondered until understood: cast aside the hammer and sword, the cannon and laser. No  
weapon formed against me shall prosper. I have seen all ends, and there is nothing but me left. A trillion  

trillion light years in all directions, and through it all, only [us? who knows. ego is a mind killer. best to call  
your friends, better to face the night together. till later.]
 

You can now install up to 2 AI systems in your mech (you still can’t duplicate AIs). If one  
becomes unshackled, the other gains control automatically.
 

                                      