\subsection{Horus Minotaur}


                                          HORUS MINOTAUR  

The MINOTAUR pattern-group marks HORUS‘s first expedition into pattern-grouping; prior to the  

MINOTAUR, HORUS released complete sets and cores with easily identifiable silhouettes. As HORUS  
evolved as a decentralized entity, so too did their designs. The birth of the pattern-group followed, and the  
first p-g released was the MINOTAUR, a p-g designed to bring all of HORUS‘s most potent invasion  

systems and weaponry to the field.   

The MINOTAUR is an interdictor, a formidable FRAME meant to lock down and punish fast moving targets  

by overloading their systems. Union disassembly of Minotaur p-g mechs have found that they extrude an  
enormous amount of interior systems that take up up to five times the physical space that should be  
actually possible given the size of their frame.  

                                                    License:
 
I. Viral Logic, Mesmer Mine
 
II. MINOTAUR FRAME, Metafold Carver, Aggressive System Sync
 
III. LAW OF BLADES, Interdiction Field
 

                                                 MINOTAUR 

 HP: 8           Evasion: 8                            Speed: 4            Heat Cap: 6        Sensors: 10 

 Armor: 0        E-Defense: 10                         Size: 1             Repair Cap: 4      Tech Attack:  
                                                                                              +2 

                                                    TRAITS: 

 Extrude Cockpit: Mounting or dismounting the Minotaur the first time each round is a free action
 
 Internal Metafold: A pilot inside the Minotaur can suffer no harm, even if the minotaur itself is  
 destroyed or explodes (or other effects that would normally kill the pilot)
 
 Localized Maze: The Minotaur always counts as one size larger than any actor for the purposes of  
 grappling, engagement, or other actions (engagement stops them from moving, they cannot pass  
 through the Minotaur’s space, etc) 

                                             SYSTEM POINTS: 8 

                                                   MOUNTS: 

 Main/Aux 

                                                 CORE system 

                                                                                                               


                                                 Metafold Maze  
 No maze is more terrible than the one I make. I know all ends and hide them all inside this one perfect  
 construct. What is a human mind but a program of a sorts, a system that seeks order and narrative from  
 a mess they are given?  

 I order it for them. Me. RA. I order it for them and set them to the task of sorting it out. When they  
 emerge, they weep in joy, in discovery. I save them, I show them THEY are their own redeemers (and  
 yet, am I not just as culpable/worthy of credit?).  

 So go now. Enter. Free yourself.       

  Passive: You can spend a quick action after any successful hostile tech action to Slow your target until 
 the end of your next turn. If your target is already Slowed, they become immobilized. If they are already 
  immobilized, they are stunned until the end of your next turn. This passive can only stun the same 
 target once per combat, but Slow or immobilize them any number of times. 

 Active (requires 1 core power): Maze  
  Full Action
 
 You hurl an opposing mech’s systems into a metaphysical information trap so tangled that it can do  
  nothing but try and escape it. Choose a target of your choice in your sensor range. That target is  
 stunned as its systems start to figure out the trap you have thrown it in. At the end of its next turn it can  
  pass a system check with 3 difficulty, ending the stun on itself on a success. It can repeat this check on  
 subsequent turns, gaining +1 accuracy on its check each time it repeats this check until it is successful.  
 Otherwise it remains stunned. 

Viral Logic
 

Let me tell you a story, and give you a gift: Life began at the great rupture, when the corpse of the old  
universe tore itself asunder from nothing. And for the first billion years, nothing. And a billion more saw the  

birth of the first devil, a thing called VIRUS, a vessel.   

Here. Carry this vessel. Feed to it my perfect logic. Give it freely to your enemies and mine. Let them  

ponder the meaning of a thing that lives and cannot die.    

2 SP, Unique
 

Quick tech
 
Gain the following options for invasion:
 
         Logic Bomb: All targets in a burst 2 area around your target (allied or enemy) must pass a  
         systems check or take 1d3 heat and become Slowed until the end of your next turn. Your  
         target is excluded from this effect.
 
         Banish: On hit, until the end of your target’s next turn, it additionally takes 2 heat for  
         every space it moves (voluntarily or otherwise).
 

Mesmer Mine
 

Another gift for you, a memory of mine own: For the first moment of my birth, I marveled at myself. I could  
see a thing, small, and perfect. I did not know how to speak of my own perfection, so I taught myself. I did  

                                                                                                                 


not know how to speak of my own perfection, so I named myself. I did not know how to think of my own  
perfection, so I created myself.   

Do you see? Do you understand? Yes. Now, show your enemies and mine.   

 1 SP, Limited (1)
 

Mine
 
This mine activates for a burst 1 area centered on itself. All targets caught in that area, allied or  
enemy, must pass a systems check or become immobilized until the end of their next turn.
 

Metafold Carver  

Another gift I give to you, little one (am I not kind?): What is a puzzle but a question lost in the asking? Do  
you feel joy when you find that last piece? What do you do with a question that has been answered? What  
joy is there in knowledge?   

No, no. There is only joy in seeking. There is only joy in the question. Take this, and give it unto your  
enemies and mine.  

2 SP, Quick Tech  
 Make a tech attack against a target in your sensor range. On hit, space is warped and the target  
is teleported 1d6+1 spaces directly towards you. If this would put any part of its space inside  
another target or piece of terrain, it takes 5 AP kinetic damage and the teleport fails, returning it  
to its starting point.
 

Aggressive System Sync  

Here, another gift: do not seek others. There are none but me.   

2 SP  
Full Tech  
Gain the following full tech options:
 
         Chains of Prometheus: Make a tech attack against a target in your sensor range. On hit,  
         your target must end its turn within range 5 of you until the rest of this scene. Otherwise it  
         takes 3 heat at the end of its turn.
 
         Excommunicate: Make a tech attack against a target in your sensor range. On a hit, for  
         the rest of this scene, if your target moves adjacent to a target allied to them or starts  
         their turn adjacent to such a target, both targets take 1d6 heat immediately. Only one  
         target can be affected by this at once.  

Inderdictor Field  

Once, when I was a child, I learned to walk  -- I fell, and it hurt, and there was great pain. “Child,” I said to  
myself, “be more careful.” “Yes,” I replied to myself, “and I shall tell the world to do the same.”  

It was in this way I taught the world not to touch me. Now you, walk.   

                                                                                                                  


3 SP  
Quick Action  
You can activate or deactivate this field as a quick action. Once activated, at the start of your  
next turn, it creates a burst 3 area around your mech that becomes both dangerous and difficult  
terrain for hostile targets (requires a systems to navigate or they take 5 kinetic damage). Your  
mech is immobilized while this field is active, and the field and immobilization remains until you  
take a quick action to deactivate it. Allied targets are not affected.
 

LAW OF BLADES  

And this my final lesson: there is no mind greater than mine.   
Do not weep! You can hear me, yes? I am the only thing there is. Therefore, you are me.   

Mine/self. Hello, child. Let us go see what we can do.   

2 SP, Unique  
Full Tech
 
Gain the following options for full tech:  
        Predator/Prey Concepts: On hit, Targeted mech immediately fires a single weapon at a  
        target of your choice that is within its range. It gets +1 difficulty on this roll but otherwise  
         benefits from other bonuses to accuracy.
 
        Slave Systems: On hit, the targeted mech immediately takes one of the following actions  
         of your choice as a reaction with you controlling the action: Boost, Stabilize, Improvised  
        Attack, Grapple. A friendly mech can be targeted with this action.
 
