\subsection{GMS General Market Deployables}
                               GMS General Market Deployables

\gearBox
[name = {GMS Pattern-A “Apple” High Explosive Grenades},
fluff = {The GMS Pattern-A HEX Grenade is a pilot’s best friend in a tight spot. Inert until activation by its neuro-coded welder, the “Apple” is guaranteed to neutralize any hard or soft target within its effective radius.},
template = {1 SP, \Limited{1}\\
\Grenade\\
\Range{5}, \Blast{1}},
rules = {Attacks all targets caught in the blast radius for 1d6 \explosive damage on hit.}]

\gearBox
[name = {GMS Pattern-A “Jericho”  Deployable Cover},
template = {2 SP\\
\Deployable, \QuickAction},
rules ={Using this system creates a Line 2 section of size 1 Heavy Cover adjacent to the user (in any orientation, as long as there is free space). Requires a full action to pick up. Reusable. The cover has 5 Evasion, 40 HP, and can be targeted and destroyed. A mech can spend 1 repair during a rest to repair it to full HP.}]

\gearBox
[name = {GMS “Pancake” Anti-Vehicular Mines},
fluff = {Used primarily for area denial, the GMS AV Mine system has begun to see more offensive employment by GMS pilots in combat theaters.},
template = {1 SP, \Limited{2}\\
\Mine},
rules = {This mine detonates when any target moves adjacent to it for a burst 1 attack, 1d6+3 \explosive damage. A target can pass an agility check to halve this damage.}]

\gearBox
[name = {GMS Pattern-A “Filter” Smoke Grenade}
fluff = {The Pattern-A/SL is a cheap, reliable, and low-system-cost method of deploying effective cover in a high-velocity kinetic scenario. Mixed with a proprietary blend of chaff, particulates, accelerants, and defilade-enhancers, Pattern-A/SL smoke is effective at obscuring most all sensor suites.},
template = {1 SP, \Limited{1}\\
\Grenade\\
\Range{5}, \Blast{3}},
rules = {The blast area grants light cover to all within, friend or foe. Lasts until the end of the user’s next turn, then disperses.}]