\subsection{GMS Standard Pattern I (“Everest”)}

\begin{mech}{GMS}{Standard Pattern I (“Everest”)}

\fluff{Most humans don’t think to ask about the history of the water they drink the earth they walk, or the air they breathe. And yet without water, earth, and air, there would be no place for Humanity to make their home.\linebreak
The Everest -- officially, the General Massive Systems Standard Pattern I -- is a plainly designed chassis. Simple lines. Functional grace. Sturdy bulk. Its use-name, “Everest”, comes from one of the names of the tallest mountain on Cradle. Of the surveyed, named mountains in known space, Mount Everest -- or
Sagarmatha, or Chomolungma, as it has been called in Old Human tongues -- is neither the most prominent peak, nor the even the tallest in Cradle’s local star system; and yet, pilots the galaxy over learned to call their GMS-SPi’s by that ancient name. Why?\linebreak
The sentimental answer is that the Everest is called the Everest because it is a reminder of what was once the limit of human endurance, of what once was the peak of human achievement. To summit Everest was to stand atop the world, the culmination of months -- maybe years -- of training, investment, and effort, defying death and injury upon your quest to summit.\linebreak
The real answer is probably much less intentional. Somewhere along the line, GMS’s plain naming convention coupled with Union’s anthropocentric emphasis lead a cadet, having graduated to a full pilot, to paint EVEREST across their GMS-SPi’s flank. Maybe it was meant to be their callsign, or maybe it was meant to represent their success following grueling training, but either way the name stuck in the insular pilot culture. Other pilots adopted the name, and over five centuries it has grown to become the official-
unofficial designation for all GMS-SPi chassis.\linebreak
Veteran pilots may never return to crew an Everest after they’ve moved on to other chassis, but they’ll always remember when they reached that first summit, when they proved they were worthy of planting their own flag on at the peak of the world.\linebreak
The Everest may not be the most specialized chassis in the galaxy, but it is the backbone of the galaxy, and humanity steps to the stars from its shoulders.}

\frameBox
[hp = 10,
evasion = 8,
speed = 4,
heat cap = 6,
sensors = 10,
armor = 0,
e-defense = 8,
size = 1,
repair cap= 4,
tech attack = 0,
traits = {\textbf{Initiative:} The very first turn the Everest takes in any combat, it can take an extra Quick Action as a free action},
sp = 6,
mount one = flex mount,
mount two = main mount,
mount three = heavy mount,
core system name = GMS Hyperspec Fuel Injector,
core system text = \empty,
core active name = Power up,
core active text = {\Protocol\par
This turn only, you can make an additional \FullAction as a free action or 2 \QuickAction as free actions.}]

\end{mech}
