\subsection{GMS GENERAL MARKET CHASSIS MODS}
                       GMS GENERAL MARKET CHASSIS MODS

\gearBox
[name = {Custom paint job},
template = {1 SP, Unique},
rules = {This paint job counts as a system that can be destroyed by structure damage}]

\gearBox
[name = {Manipulators},
fluff={Precise interaction with the built or natural environment, soft targets, and sensitive material below rated tonnage is part of the daily routine for support-class mechs. Manipulators, haptic-padded multi-digit “hands”, allow for such precise manipulation.},
template = {1 SP, \Unique},
rules = {Gain 2 extra sets of limbs. These limbs cannot be used to make attacks, but can otherwise hold and manipulate the environment and items as normal. In addition, these manipulators can interact with objects in the environment that a pilot would normally have to interact with (a pilot sized touch pad etc) with no penalty.}]

\gearBox
[name = {Personalizations},
template = {1 SP, \Unique},
rules = {When you take this mod, your mech gains +2 HP and you may establish with your GM 1 minor effect or modification you have made to your mech. This mod cannot grant any statistical or combat benefit to your mech other than the hp benefit, but could provide other useful effects. If your GM agrees that this mod would help you with a particular skill check, they can give you +1 Accuracy on the check.}]

\gearBox
[name = {Stable Structure},
template = {1 SP, \Unique},
rules = {You make rolls to resist getting knocked prone with +1 Accuracy.}]