\subsection{GMS General Market Systems List}

\gearBox
[name = {Companion/Concierge-Class Dummy Plug},
fluff = {The Companion/Concierge Class Dummy Plug conforms to galaxy wide standards for comp/con units. A Com/Con DP will pass even the most rigid Turing-Null classifications and is cleared for operations even when the pilot is not present.},
template = {2 SP, \Unique\\
\AI},
rules = {Your mech has a basic companion/concierge unit installed in it, gaining the AI tag. It can speak to you and has a personality but is not truly capable of independent thought, as a true AI would be. It is obedient to you alone. When you hand over the controls, it can take actions and move on its own prerogative when not piloted, using its stats, but has no independent initiative (it must take and follow commands from you, or else takes no action other than to defend itself).\\
Dummy Plugs are not true AIs and thus cannot be unshackled.}]

\gearBox
[name = {GMS Shield Type-I},
fluff = {The GMS Shield Type-I utilizes a projected, aggressive, anti-ballistic super-positional shield to trap and deny incoming solid and wave-based projectiles.},
template = {2 SP, \Unique\\
\Shield, \Protocol, \HeatSelf{1}},
rules = {You can choose to activate this shield protocol at the start of your turn. Nominate an enemy you can see. All that enemy's ranged or melee attacks against you are made at +2 difficulty until the start of your next turn, but your ranged or melee attacks against them also suffer the same penalty.}]