\chapter{Setup}
                                                  SETUP

This game makes use of two types of dice, the 20 sided dice (referred to from hereon as a d20)
and the 6 sided dice (referred to from hereon as the d6). Multiple dice will be referred to in the
following format - 1 six sided die = 1d6, 2 six sided dice = 2d6, etc.


Sometimes the rules will call for you to roll a 1d3. That is simply a 1d6 with the results halved and
rounded up (1-2 =1, 3-4=2, 5-6=3).


Each player should have at least one 1d20 and a number of d6s. Players will also need a
character sheet or a piece of paper to write down information, and it might be helpful to have
paper with a square or hexagonal grid on it (such as graph paper or a pre-prepared battle map)
since this game makes use of tactical combat. Miniatures are not required to play this game but
can make combat easier to visualize.


One player must play the Game Master (referred to from hereon as the GM). The Game Master
acts as a referee, storyteller, and arbitrator of rules. They help create the story and narrative for
the game and play all of the non-player characters (NPCs). For more information on the Game
Master as well as a list of rules, tips, and tools to use as a Game Master, you can refer to the GM
guide in the section at the end of this book. The rest of the players will play the role of pilots, or
characters in that story.

                                          THE GOLDEN RULE
When referring to the rules in this book, specific rules override general statements or rules.


For example, making a ranged attack typically takes into account cover. However, a weapon with
the Seeking keyword ignores cover. In this case, the weapon’s keyword supersedes the more
general rule.

                                                 ROUND UP




Always round up in LANCER (to the nearest whole number).