\section{Space and Measurements}

This game makes use of measurements in ‘spaces’ for ranges such as movement, weapon
ranges, etc. Most things in the game are measured in sizes, with size 1 being a square or hex 1
space wide on each side. By default 1 space = about 10 feet in game. \textbf{Size} indicates the physical
presence of a mech or other actor on the battlefield. It is measured as a number where size 1 = a
square or hex measuring 1 on each face. Size can be smaller than 1, such as 1/2, or larger, such
as 2 or 3. An actor or object is usually as tall vertically as its size, but that’s not always the case.
Size often does not represent the physical size of an actor, but the space they control around
them. An actor takes up a square area on the battle map equal to its size, rounded up, with a
minimum size of 1. For example, a size 1 mech takes up a 1x1 square area and a size 1/2 human
would also take up a 1x1 square area.

It’s recommended to use a map and tokens, icons, or miniatures to track actors while playing this
game for ease of play (though you can certainly play without them). You can easily play this game
on a tactical grid or hex battle map (as the designers of this game do) or simple measure ranges
using a standard ruler or measuring tape.

The scale of space can be changed if the situation needs it - for example, you might decide each
space is 50’ on each side, or a mile, or something similar. The space that an actor occupies does
not necessarily indicate its size, but the space it controls around it. Most actors take anywhere
from a 1x1 to a 3x3 space on the map, with some exceptions.

Measure all ranges indicated for weapons, effects, etc as originating from any exterior side of a
an actor. That means larger actors will have slightly longer range for their weapons or actions. To
be in range, an actor must be physically inside the range of an effect.